### 2023-08-22 paper/ms.tex
Add paper

%% Beginning of file 'sample631.tex'
%%
%% Modified 2021 March
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.31 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls and other external packages such as
%% latexsym, graphicx, amssymb, longtable, and epsf.  Note that as of 
%% Oct 2020, APS now uses revtex4.2e for its journals but remember that 
%% AASTeX v6+ still uses v4.1. All of these external packages should 
%% already be present in the modern TeX distributions but not always.
%% For example, revtex4.1 seems to be missing in the linux version of
%% TexLive 2020. One should be able to get all packages from www.ctan.org.
%% In particular, revtex v4.1 can be found at 
%% https://www.ctan.org/pkg/revtex4-1.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%% using aastex version 6.3
\documentclass[linenumbers, twocolumn]{aastex631}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

\newcommand{\Msun}{\ensuremath{M_{\odot}}}
\newcommand{\yr}{\ensuremath{\textrm{yr}}}
\newcommand{\kpc}{\ensuremath{\textrm{kpc}}}
\newcommand{\pc}{\ensuremath{\textrm{pc}}}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
% \received{March 1, 2021}
% \revised{April 1, 2021}
%\accepted{\today}

\shorttitle{Hydrodynamics of the GSE Merger}
\shortauthors{Beane et al.}

\graphicspath{{./}{fig/}}

\begin{document}

\title{Diluting the Merger Scenario for the Alpha Bimodality}

\author{Angus Beane}
\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian,  Cambridge, MA, USA}

\author{Federico Marinacci}
\affiliation{Department of Physics \& Astronomy `Augusto Righi', 
University of Bologna, Bologna, Italy}

\author{Lars Hernquist}
\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian,  Cambridge, MA, USA}

\author{others}

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.31 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
  The merger at $z\sim2$ between the proto-Milky Way and the
  Gaia-Sausage-Enceladus (GSE) satellite shaped the present day stellar halo and
  possibly led to the formation of the alpha-abundance bimodality seen in the
  disk today. Cosmological zoom simulations of GSE-like mergers have shown that
  the alpha bimodality can be explained by a dilution of the Milky Way's metal
  content by GSE. However, radial migration processes alone can also produce
  alpha bimodalities without the need for a fresh, metal-poor gas supply. We
  present simulations of a controlled GSE-like merger. Our simulations include
  gaseous disks, circumgalactic media, and a modern model for the interstellar
  medium, star formation, and stellar feedback. We argue that because GSE's
  orbit was mildly retrograde but mostly polar on second pericentric passage,
  the gas from GSE was able to penetrate the inner disk of the Milky Way. It
  therefore dilutes the inner Galaxy more strongly than the outer Galaxy. Models
  which explain the alpha bimodality from the GSE merger require the outer disk
  to be more diluted than the inner disk. It would seem that our results stand
  in direct opposition with the picture that the alpha bimodality resulted from
  the GSE merger.
\end{abstract}

%% Keywords should appear after the \end{abstract} command. 
%% The AAS Journals now uses Unified Astronomy Thesaurus concepts:
%% https://astrothesaurus.org
%% You will be asked to selected these concepts during the submission process
%% but this old "keyword" functionality is maintained in case authors want
%% to include these concepts in their preprints.
\keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of 
astronomy(1868) --- Interdisciplinary astronomy(804)}

%% From the front matter, we move on to the body of the paper.
%% Sections are demarcated by \section and \subsection, respectively.
%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.
%%
%% We recommend that authors also use the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below.

\section{Introduction} \label{sec:intro}
The present day Milky Way formed through a combination of external interactions
and internal secular evolution. Disentangling the role and importance of each is
a major goal of Galactic science today.

The last\footnote{i.e., not ongoing} significant merger was between the
proto-Milky Way disk and the {\em Gaia}-Sausage-Enceladus (GSE)
(\textcolor{red}{spell check}) satellite galaxy. The stellar debris from this
merger constitutes $\sim50\%$ \textcolor{red}{check} of the inner ($r<?\,\kpc$)
stellar halo. It may have also led to a tilted, triaxial dark matter halo
(\textcolor{red}{cite}).

The GSE merger is often invoked (\textcolor{red}{cite}) to explain the observed
bimodality in the \textcolor{red}{alpha iron} abundance plane
(\textcolor{red}{cite}). Because GSE-mass galaxies are expected to have a lower
star formation efficiency than proto-Milky Way-mass galaxies
(\textcolor{red}{cite}), the gas from GSE should be relatively metal poor. The
gas from GSE thus dilutes the gas in the proto-Milky Way, ``resetting'' the
chemical abundance of the Milky Way.

However, it has also been claimed that the \textcolor{red}{alpha iron}
bimodality can be explained through secular processes. \textcolor{red}{Sentence
explaining the basic concept.} The argument is not that the GSE merger did not
happen, but rather that it is not {\it necessary} and might not even be {\it
sufficient} to explain the bimodality. Ongoing work to detect the bimodality in
external galaxies may shed further light on the topic (\textcolor{red}{cite}).

Investigating GSE-like mergers in cosmological simulations is a rich and active
area of research. Many mergers believed to be similar to the GSE merger have
been identified in the literature (\textcolor{red}{cite}). \textcolor{red}{Blah
blah argue blah blah. And also blah blah argues blah blah.}

While much has been learned from GSE-like mergers in cosmological simulations,
they are not conducive to controlled experiments. It is possible to change the
mass of satellites through genetic modification (\textcolor{red}{Pontzen}), and
the GSE analog can be removed entirely (\textcolor{red}{Cooke cite}). However,
to our knowledge, no method has been applied to change the orbital parameters of
such a merger. It is also somehwat unclear if the circumgalactic media of
proto-Milky Way mass galaxies at $z\sim2$ are properly simulated.

In this work, we present hydrodynamic simulations of a controlled merger between
a GSE analog and the $z\sim2$ proto-Milky Way.

\section{Methods}\label{sec:methods}

\subsection{Gaseous Halos}\label{ssec:gashalo}

The nature of the circumgalactic media of local galaxies remains largely
uncertain. It is unclear whether the constraints we have on the local universe
apply to the circumgalactic media of $z\sim2$ galaxies. Nonetheless, we persist.

We assume the CGM of the Milky Way and GSE can be modelled using a $\beta$ profile,
\begin{equation}
  \rho(r) = \rho_0 \left( 1 + \left(\frac{r}{r_c}\right)^2 \right)^{-\frac{3}{2}\beta}\textrm{.}
\end{equation}
However, a $\beta$-profile has been shown to be a reasonable fit to the density
profile of galaxy clusters and of the $L_{*}$ galaxy NGC 3221. Whether or not
such a profile extends to lower mass galaxies at $z~2$ is unclear, but to our
knowledge there is no better motivation for another profile.

Our construction of the Milky Way and GSE CGM follows
\citet{2023MNRAS.tmp.2070B}. In particular, we set $\beta=2/3$ and $r_c=0.22
r_s$, where $r_s$ is the scale length of the dark matter halo. For the Milky Way
and GSE, $r_c=9$, $6.5\,\textrm{kpc}$, respectively. For the present study we
keep $\beta$ and $r_c$ fixed and instead vary the central density $\rho_0$. Our
fiducial values are $9.61\times10^{-5}$ and $7.57\times10^{-5}\,\Msun/\pc^3$ for
the Milky Way and GSE, respectively.

A useful metric for assessing the central density is by the universal baryon
fraction $f_{\textrm{B}}$ -- i.e., the ratio between the mass in baryons to the
mass in dark matter within $R_{200}$ as compared to the mean ratio of the
universe.\footnote{To be explicit,
$f_{\textrm{B}}=(M_{\textrm{b}}/M_{\textrm{c}})/(\Omega_{\textrm{b}}/\Omega_{\textrm{c}})$,
where $M_{\textrm{b}}$ and $M_{\textrm{c}}$ are the mass of baryons and cold
dark matter within $R_{200}$, and $\Omega_{\textrm{b}}$ and
$\Omega_{\textrm{c}}$ are the mean baryon and cold dark matter densities of the
universe.} For our fiducial central densities, this value is $1.07$ and $0.28$
for the Milky Way and GSE respectively using the universal values from
\cite{2014AA...571A..16P}. An early argument by

\bibliography{ref}{}
\bibliographystyle{aasjournal}

%% This command is needed to show the entire author+affiliation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges

\appendix

\section{Modelling the Milky Way and GSE at $z=2$}

Our merger simulations are built upon reasonable models of both the Milky Way
and GSE at $z\sim2$. Much is uncertain about the properties of the Milky Way and
GSE at these redshifts.  We describe the motivation for the choices made in
constructing these models.

\subsection{The Milky Way}
We adopt a \citet{1990ApJ...356..359H} profile for our dark matter halo. For its
structural parameters, we follow \citet{2021ApJ...923...92N} and set its mass
and scale length to be $5\times10^{11}\,\Msun$ and $40.4\,\kpc$, respectively.
This matches a \citet{1996ApJ...462..563N} profile with
$R_{200}=129\,\textrm{kpc}$ and concentration $c_{200}=3.8$
(\textcolor{red}{check this}).

Milky Way-progenitor galaxies have been observed up to $z=?$ with well-formed
disks, and more massive galaxies have dynamically cold disks up to $z\sim6$. We
therefore assume the thick disk is settled and in place at $z=2$. We use the
structural parameters of the thick disk from . It is presently unclear if before
the GSE merger the Milky Way disk was already thickened, or if it was thickened
by the merger. Some simulations indicate that only prograde mergers efficiently
thicken disks (\textcolor{red}{check and cite}). For this work, we assume the
disk is already thick.

For the bulge, we assume the present day classical bulge was already in place at
$z=2$. Measurements of the structural parameters of the classical bulge are
uncertain due to contamination by the boxy peanut bulge generated by the bar
(\textcolor{red}{cite}). Some even argue that the classical bulge does not exist
(\textcolor{red}{cite}). Nonetheless, we assume the bulge properties from
\textcolor{red}{Bland Hawthorn, but check}. Specifically, we assume a Hernquist
bulge with $M_{\textrm{bulge}}=?$ and $a=?$.

We assume a gas disk with an exponential surface density profile and scale
length matched to the stellar disk. The vertical profile is set by the condition
of gravito-hydrostatic equilibrium as described in (\textcolor{red}{Springel}).
Varying the gas fraction of the disk strongly influences the SFR of the galaxy.
We therefore varied the gas fraction of the disk until we reached a target
SFR.\footnote{Note that when we varied the gas fraction of the disk, we kept the
mass (and scale length) of the stellar disk constant. Therefore, the total mass
of the disk changes as we vary the gas fraction.} \textcolor{red}{People} argue
that in order for the thick disk to have formed thick, the SFR of the disk at
$z\sim2$ needed to be $\sim15\,\Msun/\yr$. It is not necessary for the disk to
be thick at $z\sim2$, so we acknowledge this is an upper limit on the SFR. We
adopt an initial gas fraction of $0.7$ which results in an average SFR of
$\sim16\,\Msun/\yr$.

Finally, we note that the present day Milk Way has a well-formed bar. It is
expected to have formed within a few Gyr of the GSE merger, so it is unclear if
the bar formed before, as a result of, or after the merger. This is not a focus
of the current work. The presence of a classical bulge and the disk being
dynamically hot is sufficient for the disk to be stable against bar
instabilities.

\end{document}

% End of file `sample631.tex'.

### 2023-08-22 anlys/movie/movies_special.sh
Add special and stitch movies

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+# MW2iso_fg0.5-lvl4-rng_-8_8_-8_8_gas_xy_novSFE1.mp4
+ffmpeg -i movies/MW2iso_fg0.5-lvl4-rng_-8_8_-8_8_gas_xy.mp4 -i movies/MW2iso_fg0.5-lvl4-nov-rng_-8_8_-8_8_gas_xy.mp4 -i movies/MW2iso_fg0.5-lvl4-SFE1-rng_-8_8_-8_8_gas_xy.mp4 -i movies/MW2iso_fg0.5-lvl4-novSFE1-rng_-8_8_-8_8_gas_xy.mp4 -filter_complex "[0:v][1:v]hstack[top];[2:v][3:v]hstack[bottom];[top][bottom]vstack[out]" -map "[out]" movies_special/MW2iso_fg0.5-lvl4-rng_-8_8_-8_8_gas_xy_novSFE1.mp4

### 2023-08-22 plots/dil/plot_dil.py
Add dil plot

@@ -1,0 +1,51 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+
+columnwidth = 242.26653 / 72.27
+textwidth = 513.11743 / 72.27
+
+mpl.use('Agg')
+mpl.rc('font', **{'family': 'serif', 'serif': ['Computer Modern'], 'size': 8})
+mpl.rc('text', usetex=True)
+mpl.rcParams['text.latex.preamble'] = r'\usepackage{amsmath}'
+
+tb_c = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f',
+        '#edc948', '#b07aa1', '#ff9da7', '#9c755f', '#bab0ac']
+
+basepath = '/n/holylfs05/LABS/hernquist_lab/Users/abeane/GSEgas/'
+
+dil_path = basepath + 'anlys/dilution/'
+
+MW3iso_corona3 = 'MW3iso_fg0.7_MHG0.25_RC9'
+MW3_GSE2_merge2 = 'MW3_MHG0.25_GSE2_MHG0.18_Rcut10'
+
+lvl = 4
+
+def run(snap=800):
+    fname = dil_path+'dil_'+MW3_GSE2_merge2+'-lvl'+str(lvl)+'.npy'
+    dil = np.load(fname, allow_pickle=True).item()
+    
+    aveR = dil['aveR'][snap]
+    dilution = dil['dilution'][snap]
+    metallicity = dil['metallicity'][snap]
+    
+    fig, ax = plt.subplots(2, 1, figsize=(columnwidth, 1.2*columnwidth), sharex=True)
+    
+    ax[0].plot(aveR, dilution, c=tb_c[0])
+    ax[0].set(ylim=(0, 0.2))
+    ax[0].set_ylabel(r'dilution fraction')
+    
+    ax[1].plot(aveR, np.log10(metallicity/0.0127), c=tb_c[0])
+    ax[1].axhline(-0.3, c='k', ls='dashed')
+    ax[1].axhline(-0.6, c='k', ls='dashed')
+    ax[1].set(xlim=(0, 15), ylim=(-0.7, -0.2))
+    ax[1].set_xlabel(r'$R\,[\,\text{kpc}\,]$')
+    ax[1].set_ylabel(r'$[Z/H]$')
+    
+    fig.tight_layout()
+    fig.savefig('dil.pdf')
+
+if __name__ == '__main__':
+    run()
+

### 2024-02-12 anlys/movie/stitch_movies.sh
Add stitch_movies.sh

@@ -3,3 +3,7 @@
 
 ffmpeg -i movies/${1}_star_xz.mp4 -i movies/${1}_gas_xz.mp4 -i movies/${1}_star_xy.mp4 -i movies/${1}_gas_xy.mp4 -filter_complex "[0:v][1:v]hstack[top];[2:v][3:v]hstack[bottom];[top][bottom]vstack[out]" -map "[out]" movies_stitch/${1}.mp4
 
+ffmpeg -i movies/GSE2iso_fg0.7-lvl4-rng_-15_15_-15_15_BoxCenter_nres1024_gas_xz.mp4 -i movies/GSE4iso_fg0.7-lvl4-rng_-15_15_-15_15_BoxCenter_nres1024_gas_xz.mp4 -i movies/GSE5iso_fg0.7-lvl4-rng_-15_15_-15_15_BoxCenter_nres1024_gas_xz.mp4  -filter_complex hstack=inputs=3 movies_stitch/GSE2_GSE4_GSE5.mp4
+
+ffmpeg -i movies/GSE2iso_fg0.7-lvl4-rng_-15_15_-15_15_BoxCenter_nres1024_gas_xz.mp4 -i movies/GSE2iso_fg0.7-lvl4-fSN-rng_-15_15_-15_15_BoxCenter_nres1024_gas_xz.mp4 -i movies/GSE4iso_fg0.7-lvl4-rng_-15_15_-15_15_BoxCenter_nres1024_gas_xz.mp4 -i movies/GSE5iso_fg0.7-lvl4-rng_-15_15_-15_15_BoxCenter_nres1024_gas_xz.mp4  -filter_complex hstack=inputs=4 movies_stitch/GSE2_fSN_GSE4_GSE5.mp4
+

### 2024-02-12 anlys/movie_VR/stitch_movies.sh

@@ -1,5 +1,7 @@
 
 #!/bin/bash
 
-ffmpeg -i movies/${1}_star_xz.mp4 -i movies/${1}_gas_xz.mp4 -i movies/${1}_star_xy.mp4 -i movies/${1}_gas_xy.mp4 -filter_complex "[0:v][1:v]hstack[top];[2:v][3:v]hstack[bottom];[top][bottom]vstack[out]" -map "[out]" movies_stitch/${1}.mp4
+#ffmpeg -i movies/${1}_star_xz.mp4 -i movies/${1}_gas_xz.mp4 -i movies/${1}_star_xy.mp4 -i movies/${1}_gas_xy.mp4 -filter_complex "[0:v][1:v]hstack[top];[2:v][3:v]hstack[bottom];[top][bottom]vstack[out]" -map "[out]" movies_stitch/${1}.mp4
+
+ffmpeg -i movies/$1 -i movies/$2  -filter_complex hstack=inputs=2 movies_stitch/$3
 

### 2024-02-12 paper/ms.tex
Update abstract for interacting CGM direction

@@
 
-\shorttitle{Hydrodynamics of the GSE Merger}
+\shorttitle{The CGM of Merging Galaxies}
 \shortauthors{Beane et al.}
@@
 
-\title{Diluting the Merger Scenario for the Alpha Bimodality}
+\title{Stimulated Accretion from Circumgalactic Media Interactions}
 
@@
 
-%% Note that the \and command from previous versions of AASTeX is now
-%% depreciated in this version as it is no longer necessary. AASTeX 
-%% automatically takes care of all commas and "and"s between authors names.
-
-%% AASTeX 6.31 has the new \collaboration and \nocollaboration commands to
-%% provide the collaboration status of a group of authors. These commands 
-%% can be used either before or after the list of corresponding authors. The
-%% argument for \collaboration is the collaboration identifier. Authors are
-%% encouraged to surround collaboration identifiers with ()s. The 
-%% \nocollaboration command takes no argument and exists to indicate that
-%% the nearby authors are not part of surrounding collaborations.
-
 %% Mark off the abstract in the ``abstract'' environment. 
 \begin{abstract}
-  The merger at $z\sim2$ between the proto-Milky Way and the
-  Gaia-Sausage-Enceladus (GSE) satellite shaped the present day stellar halo and
-  possibly led to the formation of the alpha-abundance bimodality seen in the
-  disk today. Cosmological zoom simulations of GSE-like mergers have shown that
-  the alpha bimodality can be explained by a dilution of the Milky Way's metal
-  content by GSE. However, radial migration processes alone can also produce
-  alpha bimodalities without the need for a fresh, metal-poor gas supply. We
-  present simulations of a controlled GSE-like merger. Our simulations include
-  gaseous disks, circumgalactic media, and a modern model for the interstellar
-  medium, star formation, and stellar feedback. We argue that because GSE's
-  orbit was mildly retrograde but mostly polar on second pericentric passage,
-  the gas from GSE was able to penetrate the inner disk of the Milky Way. It
-  therefore dilutes the inner Galaxy more strongly than the outer Galaxy. Models
-  which explain the alpha bimodality from the GSE merger require the outer disk
-  to be more diluted than the inner disk. It would seem that our results stand
-  in direct opposition with the picture that the alpha bimodality resulted from
-  the GSE merger.
+  It is now well-established that galaxies host extended gaseous haloes dubbed
+  the circumgalactic medium (CGM) which play a critical role in receiving and
+  providing gas from and to the disk. Typically metal-poor, the CGM is a major
+  actor in the nuclear abundance evolution of galaxies. While aspects of
+  isolated CGM, such as its rotation and multiphase nature, have been studied,
+  the interaction between the CGM of two merging galaxies is less well
+  understood. In this work, we present hydrodynamic simulations of a controlled
+  galaxy merger, roughly resembling a merger the Milky Way experienced early in
+  its history. Unsurprisingly, the CGM of the satellite galaxy is stripped early
+  in the merger -- mostly during its first pericentric passage (check). This has
+  the effect of stimulating the accretion of gas from the host's CGM onto its
+  disk. This occurs due to two effects: (1) Cold gas from the satellite's CGM
+  mixes with gas in the host's CGM and cools it to a regime where cooling is
+  more efficient, thus reducing the gas' thermal pressure support. (2) The
+  satellite deepens the potential well of the host galaxy, reducing its
+  free-fall time. These effects combine to enhance the accretion of gas onto the
+  host's disk. In our setup (for which there is significant uncertainty), the
+  bulk amount of gas accreted on the disk can increase by a factor of $\sim2$
+  (\textcolor{red}{checl}).
 \end{abstract}
@@
 astronomy(1868) --- Interdisciplinary astronomy(804)}
-
-%% From the front matter, we move on to the body of the paper.
-%% Sections are demarcated by \section and \subsection, respectively.
-%% Observe the use of the LaTeX \label
-%% command after the \subsection to give a symbolic KEY to the
-%% subsection for cross-referencing in a \ref command.
-%% You can use LaTeX's \ref and \label commands to keep track of
-%% cross-references to sections, equations, tables, and figures.
-%% That way, if you change the order of any elements, LaTeX will
-%% automatically renumber them.
-%%
-%% We recommend that authors also use the natbib \citep
-%% and \citet commands to identify citations.  The citations are
-%% tied to the reference list via symbolic KEYs. The KEY corresponds
-%% to the KEY in the \bibitem in the reference list below.
 

### 2024-02-15 paper/ms.tex
Adding dilution profile just to have in history

@@
 
+\subsection{Dilution Profile}\label{ssec:dilprof}
+
+Hi. We next examine the constitution of gas in the disk at $t=5\,\textrm{Gyr}$, i.e.
+post-merger when the disk has settled. We compute the ``dilution fraction'' --
+the fraction of gas in a given annulus in the disk ($|z|<3\,\textrm{kpc}$) that
+originated from GSE or its CGM, and show this in the upper panel of
+Figure~\ref{fig:dil}. The dilution factor varies from $\sim10\%$ in the inner
+disk to only a few percent in the outer disk. In fact, of all GSE gas with
+$R<15\,\textrm{kpc}$, $x\%$ is within $y$.
+
+In the bottom panel of Figure~\ref{fig:dil}, we attempt to illustrate how much
+the dilution of the disk impacts its metallicity. We assign the gas in the disk
+which was originally part of the Milky Way disk and CGM a metallicity of
+$[\textrm{Z}/\textrm{H}]=-0.3$ and the gas from the GSE disk and CGM a
+metallicity of $[\textrm{Z}/\textrm{H}]=-1.2$. We compute the metallicity of
+each annulus assuming these two gas components are well mixed.\footnote{Only
+about $1\%$ of cells in the disk contain tracer particles only from GSE.}
+Because there is little dilution in the outer disk, the metallicity hardly
+changes from $-0.3$. In the inner disk where dilution is stronger, the
+metallicity drops to $\sim-0.35$. We also plot horizontal dashed lines at the
+assumed metallicity of Milky Way gas ($-0.3$) and the approximate metallicity of
+the start of the low-alpha sequence ($-0.6$), i.e. the target metallicity of the
+GSE merger.
+
+% 1% number is in dilution_profile notebook
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{dil.pdf}
+  \caption{The dilution and metallicity profiles of the disk resulting from the
+  merger between the Milky Way and GSE. The upper panel shows the ``dilution
+  fraction'' -- the fraction of gas at each annulus originating from the disk or
+  CGM of GSE. The lower panel shows the metallicity profile of the disk,
+  assuming metallicities of $[\textrm{Z}/\textrm{H}]=-0.3$ and $-1.2$ for gas
+  from the Milky Way and GSE, respectively. The dashed lines at
+  $[\textrm{Z}/\textrm{H}]=-0.3$ and $-0.6$ are the approximate metallicites of
+  the end of the high-alpha and the beginning of the low-alpha sequences. The
+  disk is defined as having $|z|<3\,\textrm{kpc}$.}
+  \label{fig:dil}
+\end{figure}
+
 \bibliography{ref}{}

### 2024-02-15 paper/ms.tex
Remove dilution

--- 2024-02-12 paper/ms.tex
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{fig/cumprof.pdf}
+  \caption{The cumulative amount of the central's CGM gas accreted onto the disk
+  ($r<20\,\kpc$) as a function of time. The blue line shows the case of the
+  galaxy merger setup and the orange line shows the case of an isolated galaxy.
+  The effect of the merger is to increase the amount of mass accreted onto the
+  central. We stress that this plot does not include the mass from the satellite's
+  disk or CGM.}
+  \label{fig:cumprof}
+\end{figure}
+
 \bibliography{ref}{}

### 2024-04-13 runs/MW7_GSE4/lvl3-denscut/Config.sh
Add attempts to make quiescent phase

@@ -424,7 +424,7 @@ ENLARGE_DYNAMIC_RANGE_IN_TIME  # This extends the dynamic range of the integer t
 
 #PERFORMANCE_TEST_SPARSE_MPI_ALLTOALL
 #BITS_PER_DIMENSION=42      # Peano-Hilbert order
-#OVERRIDE_PEANOGRID_WARNING
+OVERRIDE_PEANOGRID_WARNING
 
 
 #--------------------------------------- Output/Input options

### 2024-04-13 runs/MW7_GSE4/lvl4-denscut-Ngb64-steep1/Config.sh

@@ -1,0 +1,1002 @@
+#!/bin/bash            # this line only there to enable syntax highlighting in this file
+
+##################################################
+#  Enable/Disable compile-time options as needed #
+##################################################
+
+
+#--------------------------------------- Basic operation mode of code
+NTYPES=6                       # number of particle types
+#PERIODIC
+#TWODIMS
+#AXISYMMETRY                    # This is for axisymmetry in cylindrical coordinates (requires TWODIMS and a stationary mesh)
+#ONEDIMS
+#LONG_X=10.0
+#LONG_Y=2.0
+#LONG_Z=10.0
+#REFLECTIVE_X=1 #=2            # if set to 2, the boundary is inflow/outflow
+#REFLECTIVE_Y=1 #=2
+#REFLECTIVE_Z=1 #=2
+
+COOLING
+UVB_SELF_SHIELDING            # gas is self-shielded from the cosmic background based on its density
+USE_SFR
+#QUICK_LYALPHA                # turns dense and cold gas to stars immediately
+#QUICK_LYALPHA_LATETIMEONLY   # cooling and star formation only after a certain time
+#SFR_KEEP_CELLS
+#GAMMA=1.4
+#ISOTHERM_EQS
+#USE_ENTROPY_FOR_COLD_FLOWS
+#ENTROPY_MACH_THRESHOLD=1.1
+#PREHEATING
+#NOHYDRO
+
+#----------------------------------------MPI/Threading Hybrid
+#NUM_THREADS=4                           # use OpenMP, with the given number of threads per MPI task
+#IMPOSE_PINNING
+#IMPOSE_PINNING_OVERRIDE_MODE
+#GENERIC_ASYNC                           # enables asynchronous communication scheme
+
+#--------------------------------------- Mesh Type
+#AMR
+VORONOI
+
+#----------------------------------------- SR/GR
+#SPECIAL_RELATIVITY
+#SPECIAL_RELATIVITY_HLLC
+#SR_HLLC_ZERO_COMPVEL
+#GENERAL_RELATIVITY
+#METRIC_TYPE=1
+#ATMOSPHERE_GENERAL_RELATIVITY
+#ADIABATIC_GENERAL_RELATIVITY=0
+
+#----------------------------------------- MHD
+#MHD
+#MHD_CT
+#MHD_CT_IC
[…]

### 2024-04-13 runs/MW7_GSE4/lvl4-denscut-Vvir110-Ngb64/job_lvl4-ice.sh

@@ -1,0 +1,27 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice
+#SBATCH -J MW7_GSE4_ngb64_l4
+#SBATCH -n 128
+#SBATCH -N 2
+#SBATCH --ntasks-per-node=64
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --exclusive
+#SBATCH --mail-user=slurmsara@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 7-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4/lvl5-denscut-Ngb64-softfactor02/job_lvl5-casc.sh

@@ -1,0 +1,27 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy
+#SBATCH -J MW7_GSE4_ngb64_soft02_l5
+#SBATCH -n 96
+#SBATCH -N 2
+#SBATCH --ntasks-per-node=48
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --exclusive
+#SBATCH --mail-user=slurmsara@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 7-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4/lvl5-denscut-Ngb64-softfactor04/job_lvl5-casc.sh

@@ -1,0 +1,27 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy
+#SBATCH -J MW7_GSE4_ngb64_soft04_l5
+#SBATCH -n 96
+#SBATCH -N 2
+#SBATCH --ntasks-per-node=48
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --exclusive
+#SBATCH --mail-user=slurmsara@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 7-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4/lvl5-denscut-Ngb64-steep1-instenrich/job_lvl5-casc-restart.sh

@@ -1,0 +1,27 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy
+#SBATCH -J MW7_GSE4_ngb64_steep1_inst_l5
+#SBATCH -n 96
+#SBATCH -N 2
+#SBATCH --ntasks-per-node=48
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --exclusive
+#SBATCH --mail-user=slurmsara@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 7-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+#cd arepo
+#make clean > ../output/MAKE.out 2> ../output/MAKE.err
+#make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+#cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 1
+

### 2024-04-13 runs/MW7_GSE4/lvl5-denscut-Ngb64-steep2/job_lvl5-ice.sh

@@ -1,0 +1,27 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice
+#SBATCH -J MW7_GSE4_ngb64_steep2_l5
+#SBATCH -n 64
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=64
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --exclusive
+#SBATCH --mail-user=slurmsara@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 7-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4/lvl5-denscut-Ngb64-tsfr15/job_lvl5-casc.sh

@@ -1,0 +1,27 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy
+#SBATCH -J MW7_GSE4_ngb64_l5
+#SBATCH -n 48
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=48
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --exclusive
+#SBATCH --mail-user=slurmsara@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 7-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4/lvl5-denscut-Ngb64-windE2/job_lvl5-casc.sh

@@ -1,0 +1,27 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy
+#SBATCH -J MW7_GSE4_ngb64_wE2_l5
+#SBATCH -n 48
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=48
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --exclusive
+#SBATCH --mail-user=slurmsara@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 7-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4/lvl5-denscut-Rstart150-Vvir110-Ngb64/job_lvl5-ice.sh

@@ -1,0 +1,27 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice
+#SBATCH -J MW7_GSE4_ngb64_l5
+#SBATCH -n 64
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=64
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --exclusive
+#SBATCH --mail-user=slurmsara@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 7-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4/lvl5-denscut-SMUGGLE/job_lvl5-ice.sh

@@ -1,0 +1,27 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice
+#SBATCH -J MW7_GSE4_l5
+#SBATCH -n 64
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=64
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --exclusive
+#SBATCH --mail-user=slurmsara@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 7-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4/lvl5-denscut-Vvir110-Ngb64/Config.sh

@@ -1,0 +1,1002 @@
+#!/bin/bash            # this line only there to enable syntax highlighting in this file
+
+##################################################
+#  Enable/Disable compile-time options as needed #
+##################################################
+
+
+#--------------------------------------- Basic operation mode of code
+NTYPES=6                       # number of particle types
+#PERIODIC
+#TWODIMS
+#AXISYMMETRY                    # This is for axisymmetry in cylindrical coordinates (requires TWODIMS and a stationary mesh)
+#ONEDIMS
+#LONG_X=10.0
+#LONG_Y=2.0
+#LONG_Z=10.0
+#REFLECTIVE_X=1 #=2            # if set to 2, the boundary is inflow/outflow
+#REFLECTIVE_Y=1 #=2
+#REFLECTIVE_Z=1 #=2
+
+COOLING
+UVB_SELF_SHIELDING            # gas is self-shielded from the cosmic background based on its density
+USE_SFR
+#QUICK_LYALPHA                # turns dense and cold gas to stars immediately
+#QUICK_LYALPHA_LATETIMEONLY   # cooling and star formation only after a certain time
+#SFR_KEEP_CELLS
+#GAMMA=1.4
+#ISOTHERM_EQS
+#USE_ENTROPY_FOR_COLD_FLOWS
+#ENTROPY_MACH_THRESHOLD=1.1
+#PREHEATING
+#NOHYDRO
+
+#----------------------------------------MPI/Threading Hybrid
+#NUM_THREADS=4                           # use OpenMP, with the given number of threads per MPI task
+#IMPOSE_PINNING
+#IMPOSE_PINNING_OVERRIDE_MODE
+#GENERIC_ASYNC                           # enables asynchronous communication scheme
+
+#--------------------------------------- Mesh Type
+#AMR
+VORONOI
+
+#----------------------------------------- SR/GR
+#SPECIAL_RELATIVITY
+#SPECIAL_RELATIVITY_HLLC
+#SR_HLLC_ZERO_COMPVEL
+#GENERAL_RELATIVITY
+#METRIC_TYPE=1
+#ATMOSPHERE_GENERAL_RELATIVITY
+#ADIABATIC_GENERAL_RELATIVITY=0
+
+#----------------------------------------- MHD
+#MHD
+#MHD_CT
+#MHD_CT_IC
[…]

### 2024-04-13 runs/MW7_GSE4/lvl5-fb01-Ngb64/job_lvl5-ice.sh

@@ -1,0 +1,27 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice
+#SBATCH -J MW7-fb01_GSE4_ngb64_l5
+#SBATCH -n 64
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=64
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --exclusive
+#SBATCH --mail-user=slurmsara@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 7-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/GSE4iso/lvl4-Ngb64/job_lvl4-casc.sh
Add GSE4 Ngb64 run

@@ -1,0 +1,27 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy
+#SBATCH -J GSE4_l4
+#SBATCH -n 96
+#SBATCH -N 2
+#SBATCH --ntasks-per-node=48
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --exclusive
+#SBATCH --mail-user=slurmsara@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 7-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl3/check_lastsnap.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+
+for Rstart in 116 129 142
+do
+    for Vvir in 116 129 142
+    do
+        for e in 04 05 06
+        do
+            ls -lthr lvl3-Rs${Rstart}-Vv${Vvir}-e${e}/output/snap* | tail -1
+        done
+    done
+done
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl3/loop_setup.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+
+for Rstart in 116 129 142
+do
+    for Vvir in 116 129 142
+    do
+        for e in 04 05 06
+        do
+            ./setup.sh ${Rstart} ${Vvir} ${e}
+        done
+    done
+done
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl3/lvl3-Rs116-Vv142-e05/job_lvl3-rst.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv142_e05_l3
+#SBATCH -n 112 
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=112
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl3.txt 1 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl3/lvl3-Rs116-Vv142-e05/job_lvl3.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv142_e05_l3
+#SBATCH -n 112 
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=112
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl3.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl3/lvl3-Rs142-Vv142-e04/Config-nosub.sh

@@ -1,0 +1,1003 @@
+#!/bin/bash            # this line only there to enable syntax highlighting in this file
+
+##################################################
+#  Enable/Disable compile-time options as needed #
+##################################################
+
+
+#--------------------------------------- Basic operation mode of code
+NTYPES=6                       # number of particle types
+#PERIODIC
+#TWODIMS
+#AXISYMMETRY                    # This is for axisymmetry in cylindrical coordinates (requires TWODIMS and a stationary mesh)
+#ONEDIMS
+#LONG_X=10.0
+#LONG_Y=2.0
+#LONG_Z=10.0
+#REFLECTIVE_X=1 #=2            # if set to 2, the boundary is inflow/outflow
+#REFLECTIVE_Y=1 #=2
+#REFLECTIVE_Z=1 #=2
+
+COOLING
+UVB_SELF_SHIELDING            # gas is self-shielded from the cosmic background based on its density
+USE_SFR
+#QUICK_LYALPHA                # turns dense and cold gas to stars immediately
+#QUICK_LYALPHA_LATETIMEONLY   # cooling and star formation only after a certain time
+#SFR_KEEP_CELLS
+#GAMMA=1.4
+#ISOTHERM_EQS
+#USE_ENTROPY_FOR_COLD_FLOWS
+#ENTROPY_MACH_THRESHOLD=1.1
+#PREHEATING
+#NOHYDRO
+
+#----------------------------------------MPI/Threading Hybrid
+#NUM_THREADS=4                           # use OpenMP, with the given number of threads per MPI task
+#IMPOSE_PINNING
+#IMPOSE_PINNING_OVERRIDE_MODE
+#GENERIC_ASYNC                           # enables asynchronous communication scheme
+
+#--------------------------------------- Mesh Type
+#AMR
+VORONOI
+
+#----------------------------------------- SR/GR
+#SPECIAL_RELATIVITY
+#SPECIAL_RELATIVITY_HLLC
+#SR_HLLC_ZERO_COMPVEL
+#GENERAL_RELATIVITY
+#METRIC_TYPE=1
+#ATMOSPHERE_GENERAL_RELATIVITY
+#ADIABATIC_GENERAL_RELATIVITY=0
+
+#----------------------------------------- MHD
+#MHD
+#MHD_CT
+#MHD_CT_IC
[…]

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl3/lvl3-Rs142-Vv142-e04/job_lvl3-nosub-rst.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv142_e04_l3
+#SBATCH -n 112 
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=112
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean CONFIG=Config-nosub.sh BUILD_DIR=build-nosub EXEC=Arepo-nosub > ../output/MAKE-nosub.out 2> ../output/MAKE-nosub.err
+make -j CONFIG=Config-nosub.sh BUILD_DIR=build-nosub EXEC=Arepo-nosub >> ../output/MAKE-nosub.out 2>> ../output/MAKE-nosub.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo-nosub param_lvl3-nosub.txt 1 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl3/lvl3-Rs142-Vv142-e04/job_lvl3-rst.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv142_e04_l3
+#SBATCH -n 112 
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=112
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl3.txt 1 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl3/lvl3-Rs142-Vv142-e04/job_lvl3-runsub.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p sapphire,hernquist_ice
+#SBATCH -J MW7_GSE4_subfind
+#SBATCH -n 64 
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=64
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 0-06:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl3.txt 3 $1 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl3/lvl3-Rs142-Vv142-e04/job_lvl3.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv142_e04_l3
+#SBATCH -n 112 
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=112
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl3.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl3/lvl3-template/Config.sh

@@ -1,0 +1,1002 @@
+#!/bin/bash            # this line only there to enable syntax highlighting in this file
+
+##################################################
+#  Enable/Disable compile-time options as needed #
+##################################################
+
+
+#--------------------------------------- Basic operation mode of code
+NTYPES=6                       # number of particle types
+#PERIODIC
+#TWODIMS
+#AXISYMMETRY                    # This is for axisymmetry in cylindrical coordinates (requires TWODIMS and a stationary mesh)
+#ONEDIMS
+#LONG_X=10.0
+#LONG_Y=2.0
+#LONG_Z=10.0
+#REFLECTIVE_X=1 #=2            # if set to 2, the boundary is inflow/outflow
+#REFLECTIVE_Y=1 #=2
+#REFLECTIVE_Z=1 #=2
+
+COOLING
+UVB_SELF_SHIELDING            # gas is self-shielded from the cosmic background based on its density
+USE_SFR
+#QUICK_LYALPHA                # turns dense and cold gas to stars immediately
+#QUICK_LYALPHA_LATETIMEONLY   # cooling and star formation only after a certain time
+#SFR_KEEP_CELLS
+#GAMMA=1.4
+#ISOTHERM_EQS
+#USE_ENTROPY_FOR_COLD_FLOWS
+#ENTROPY_MACH_THRESHOLD=1.1
+#PREHEATING
+#NOHYDRO
+
+#----------------------------------------MPI/Threading Hybrid
+#NUM_THREADS=4                           # use OpenMP, with the given number of threads per MPI task
+#IMPOSE_PINNING
+#IMPOSE_PINNING_OVERRIDE_MODE
+#GENERIC_ASYNC                           # enables asynchronous communication scheme
+
+#--------------------------------------- Mesh Type
+#AMR
+VORONOI
+
+#----------------------------------------- SR/GR
+#SPECIAL_RELATIVITY
+#SPECIAL_RELATIVITY_HLLC
+#SR_HLLC_ZERO_COMPVEL
+#GENERAL_RELATIVITY
+#METRIC_TYPE=1
+#ATMOSPHERE_GENERAL_RELATIVITY
+#ADIABATIC_GENERAL_RELATIVITY=0
+
+#----------------------------------------- MHD
+#MHD
+#MHD_CT
+#MHD_CT_IC
[…]

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl3/lvl3-template/job_lvl3-rst.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p sapphire
+#SBATCH -J MW7_GSE4_Rs_Vv_e_l3
+#SBATCH -n 112 
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=112
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl3.txt 1 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl3/lvl3-template/job_lvl3.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p sapphire
+#SBATCH -J MW7_GSE4_Rs_Vv_e_l3
+#SBATCH -n 112 
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=112
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl3.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl3/setup.sh

@@ -1,0 +1,33 @@
+#!/bin/bash
+
+Rs=$1
+Vv=$2
+E=$3
+
+DIR=lvl3-Rs${Rs}-Vv${Vv}-e${E}
+
+if [ -d ${DIR} ]; then
+    echo "Directory ${DIR} already exists, exiting..."
+    exit 1
+fi
+
+mkdir ${DIR}
+cd ${DIR}
+    echo "doing Rstart=${Rs}, Vvir=${Vv}, e=${E}"
+
+    rsync -ap --exclude arepo ../lvl3-template/* ./
+    git clone ../lvl3-template/arepo > git.log 2>&1
+    
+    cd arepo
+    ln -s ../Config.sh ./
+    cd ../
+    
+    sed -i "s/Rs_Vv_e/Rs${Rs}_Vv${Vv}_e${E}/g" job_lvl3.sh job_lvl3-rst.sh
+    sed -i "s/Rs-Vv-e/Rs${Rs}-Vv${Vv}-e${E}/g" param_lvl3.txt
+
+    JOBID=`sbatch --parsable job_lvl3.sh`
+    sbatch --dependency=afterok:${JOBID} job_lvl3-rst.sh
+
+    echo "done"
+cd ../
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/check_lastsnap.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+
+for Rstart in 116 129 142
+do
+    for Vvir in 116 129 142
+    do
+        for e in 04 05 06
+        do
+            ls -lthr lvl4-Rs${Rstart}-Vv${Vvir}-e${e}/output/snap* | tail -1
+        done
+    done
+done
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs116-Vv116-e04/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv116_e04_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs116-Vv116-e05/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv116_e05_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs116-Vv116-e06/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv116_e06_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs116-Vv129-e04/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv129_e04_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs116-Vv129-e05/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv129_e05_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs116-Vv129-e06/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv129_e06_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs116-Vv142-e04/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv142_e04_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs116-Vv142-e05/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv142_e05_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs116-Vv142-e06/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv142_e06_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs129-Vv116-e04/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv116_e04_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs129-Vv116-e05/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv116_e05_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs129-Vv116-e06/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv116_e06_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs129-Vv129-e04/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv129_e04_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs129-Vv129-e05/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv129_e05_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs129-Vv129-e06/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv129_e06_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs129-Vv142-e04/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv142_e04_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs129-Vv142-e05/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv142_e05_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs129-Vv142-e06/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv142_e06_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs142-Vv116-e04/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv116_e04_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs142-Vv116-e05/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv116_e05_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs142-Vv116-e06/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv116_e06_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs142-Vv129-e04/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv129_e04_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs142-Vv129-e05/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv129_e05_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs142-Vv129-e06/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv129_e06_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs142-Vv142-e04/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv142_e04_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs142-Vv142-e05/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv142_e05_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/lvl4-Rs142-Vv142-e06/job_lvl4.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv142_e06_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl4/setup.sh

@@ -1,0 +1,27 @@
+#!/bin/bash
+
+Rs=$1
+Vv=$2
+E=$3
+
+mkdir lvl4-Rs${Rs}-Vv${Vv}-e${E}
+cd lvl4-Rs${Rs}-Vv${Vv}-e${E}
+
+    echo "doing Rstart=${Rs}, Vvir=${Vv}, e=${E}"
+
+    rsync -ap --exclude arepo ../lvl4-template/* ./
+    git clone ../lvl4-template/arepo > git.log 2>&1
+    
+    cd arepo
+    ln -s ../Config.sh ./
+    cd ../
+    
+    sed -i "s/Rs_Vv_e/Rs${Rs}_Vv${Vv}_e${E}/g" job_lvl4.sh
+    sed -i "s/Rs-Vv-e/Rs${Rs}-Vv${Vv}-e${E}/g" param_lvl4.txt
+
+    sbatch job_lvl4.sh
+
+    echo "done"
+
+cd ../
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/check_lastsnap.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+
+for Rstart in 116 129 142
+do
+    for Vvir in 116 129 142
+    do
+        for e in 04 05 06
+        do
+            ls -lthr lvl5-Rs${Rstart}-Vv${Vvir}-e${e}/output/snap* | tail -1
+        done
+    done
+done
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs116-Vv116-e04/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv116_e04_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs116-Vv116-e05/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv116_e05_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs116-Vv116-e06/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv116_e06_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs116-Vv129-e04/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv129_e04_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs116-Vv129-e05/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv129_e05_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs116-Vv129-e06/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv129_e06_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs116-Vv142-e04/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv142_e04_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs116-Vv142-e05/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv142_e05_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs116-Vv142-e06/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs116_Vv142_e06_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs129-Vv116-e04/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv116_e04_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs129-Vv116-e05/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv116_e05_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs129-Vv116-e06/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv116_e06_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs129-Vv129-e04/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv129_e04_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs129-Vv129-e05/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv129_e05_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs129-Vv129-e06/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv129_e06_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs129-Vv142-e04/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv142_e04_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs129-Vv142-e05/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv142_e05_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs129-Vv142-e06/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs129_Vv142_e06_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs142-Vv116-e04/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv116_e04_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs142-Vv116-e05/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv116_e05_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs142-Vv116-e06/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv116_e06_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs142-Vv129-e04/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv129_e04_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs142-Vv129-e05/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv129_e05_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs142-Vv129-e06/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv129_e06_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs142-Vv142-e04/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv142_e04_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs142-Vv142-e05/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv142_e05_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-Rs142-Vv142-e06/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs142_Vv142_e06_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/lvl5-template/job_lvl5.sh

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p itc_cluster,hernquist,conroy,hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs_Vv_e_l5
+#SBATCH -n 32
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=32
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=3800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl5.txt 
+

### 2024-04-13 runs/MW7_GSE4-eRVgrid-lvl5/setup.sh

@@ -1,0 +1,27 @@
+#!/bin/bash
+
+Rs=$1
+Vv=$2
+E=$3
+
+mkdir lvl5-Rs${Rs}-Vv${Vv}-e${E}
+cd lvl5-Rs${Rs}-Vv${Vv}-e${E}
+
+    echo "doing Rstart=${Rs}, Vvir=${Vv}, e=${E}"
+
+    rsync -ap --exclude arepo ../lvl5-template/* ./
+    git clone ../lvl5-template/arepo > git.log 2>&1
+    
+    cd arepo
+    ln -s ../Config.sh ./
+    cd ../
+    
+    sed -i "s/Rs_Vv_e/Rs${Rs}_Vv${Vv}_e${E}/g" job_lvl5.sh
+    sed -i "s/Rs-Vv-e/Rs${Rs}-Vv${Vv}-e${E}/g" param_lvl5.txt
+
+    sbatch job_lvl5.sh
+
+    echo "done"
+
+cd ../
+

### 2024-04-13 note/galaxy.py
Update notebooks

@@ -69,6 +69,30 @@ class Galaxy(object):
             print('subID=', subID, 'doesnt exist')
             return
         
+        # don't orient, just use box frame
+        if self.sn.NumPart_Total[4] < 64:
+            COM = self.sub.SubhaloPos[subID]
+            COMV = self.sub.SubhaloVel[subID]
+            
+            for pt,Npart in enumerate(self.sn.NumPart_Total):
+                if Npart == 0:
+                    continue
+            
+                part = getattr(self.sn, 'part'+str(pt))
+                pos = part.Coordinates.value - COM
+                vel = part.Velocities.value - COMV
+    
+                pos_rot = np.copy(pos)
+                vel_rot = np.copy(vel)
+        
+                part.RotatedCoordinates = np.copy(pos_rot)
+                part.RotatedVelocities = np.copy(vel_rot)
+        
+                part.rotpos = part.RotatedCoordinates.view()
+                part.rotvel = part.RotatedVelocities.view()
+            
+            return
+        
         # get COM as subhalo pos
         COM = self.sub.SubhaloPos[subID]
         pos = self.sn.part4.pos.value - COM

### 2024-04-13 anlys/movie/compute_movie.py
Update movie comp

@@ -172,6 +172,7 @@ if __name__ == '__main__':
     MW7iso = 'MW7iso'
     GSE4iso = 'GSE4iso'
     MW7_GSE4 = 'MW7_GSE4'
+    MW7_GSE4_grid_l4 = 'MW7_GSE4-eRVgrid-lvl4'
 
     MW8iso = 'MW8iso'
 
@@ -250,6 +251,23 @@ if __name__ == '__main__':
                  
                  (MW9_GSE5, 'lvl5', rng6, 'Subhalo'), # 48
                  (MW9_GSE5, 'lvl4', rng6, 'Subhalo'), # 49
+
+                 (MW7iso, 'lvl5-Ngb64-artburst', rng5, 'Subhalo'), # 50
+                 (MW7iso, 'lvl5-Ngb64-artburst-windE2', rng5, 'Subhalo'), # 51
+                 (MW7iso, 'lvl5-Ngb64-artburst-auriga', rng5, 'Subhalo'), # 52
+                 
+                 (MW7_GSE4, 'lvl5-denscut-Ngb64', rng0, 'Subhalo'), # 53 
+                 (MW7_GSE4, 'lvl5-denscut-Ngb64', rng3, 'Subhalo'), # 54 
+                 (MW7_GSE4, 'lvl5-denscut-Ngb64', rng5, 'Subhalo'), # 55 
+                 (MW7_GSE4, 'lvl5-denscut-Ngb64-steep1', rng0, 'Subhalo'), # 56
+                 (MW7_GSE4, 'lvl5-denscut-Ngb64-steep1', rng3, 'Subhalo'), # 57 
+                 (MW7_GSE4, 'lvl5-denscut-Ngb64-steep1', rng5, 'Subhalo'), # 58 
+                 
+                 (MW7_GSE4_grid_l4, 'lvl4-Rs142-Vv142-e04', rng6, 'Subhalo'), # 59
+                 (MW7_GSE4_grid_l4, 'lvl4-Rs142-Vv142-e04', rng0, 'Subhalo'), # 60
+
+                 (MW7iso, 'lvl4-Ngb64', rng6, 'Subhalo'), # 61
+                 (MW7iso, 'lvl4-Ngb64', rng0, 'Subhalo'), # 61
                  ]
 
     i = int(sys.argv[1])

### 2024-04-13 anlys/movie/stitch_movies.sh
Add new movie stitches

@@ -7,3 +7,42 @@ ffmpeg -i movies/GSE2iso_fg0.7-lvl4-rng_-15_15_-15_15_BoxCenter_nres1024_gas_xz.
 
 ffmpeg -i movies/GSE2iso_fg0.7-lvl4-rng_-15_15_-15_15_BoxCenter_nres1024_gas_xz.mp4 -i movies/GSE2iso_fg0.7-lvl4-fSN-rng_-15_15_-15_15_BoxCenter_nres1024_gas_xz.mp4 -i movies/GSE4iso_fg0.7-lvl4-rng_-15_15_-15_15_BoxCenter_nres1024_gas_xz.mp4 -i movies/GSE5iso_fg0.7-lvl4-rng_-15_15_-15_15_BoxCenter_nres1024_gas_xz.mp4  -filter_complex hstack=inputs=4 movies_stitch/GSE2_fSN_GSE4_GSE5.mp4
 
+ffmpeg -i movies/MW5iso-lvl5-beta05-rng_-80_80_-80_80_Tot_COM_nres512_lowdens_gas_xy.mp4 \
+       -i movies/MW5iso-lvl5-beta06-rng_-80_80_-80_80_Tot_COM_nres512_lowdens_gas_xy.mp4 \
+       -i movies/MW5iso-lvl5-beta067-rng_-80_80_-80_80_Tot_COM_nres512_lowdens_gas_xy.mp4 \
+       -i movies/MW5iso-lvl5-beta07-rng_-80_80_-80_80_Tot_COM_nres512_lowdens_gas_xy.mp4 \
+       -i movies/MW5iso-lvl5-beta08-rng_-80_80_-80_80_Tot_COM_nres512_lowdens_gas_xy.mp4 \
+       -filter_complex hstack=inputs=5 movies_stitch/MW5iso-lvl5_allbeta_rng_-80_80_-80_80_Tot_COM_nres512_lowdens_gas_xy.mp4
+
+ffmpeg -i movies/MW6iso-lvl5-beta05-dens-rng_-80_80_-80_80_BoxCenter_nres512_lowdens2_gas_xy.mp4 \
+       -i movies/MW6iso-lvl5-beta06-dens-rng_-80_80_-80_80_BoxCenter_nres512_lowdens2_gas_xy.mp4 \
+       -i movies/MW6iso-lvl5-beta067-dens-rng_-80_80_-80_80_BoxCenter_nres512_lowdens2_gas_xy.mp4 \
[…]

### 2024-04-13 box/archive/util.py
Add closed box

@@ -1,0 +1,118 @@
+import numpy as np
+from numba import njit
+import sys
+
+# @njit
+
+# x has shape (N, Nbin) or (Nbin,)
+# x0 have shape (N,)
+# if x has shape (Nbin,), then x is cast to (N, Nbin)
+
+def _integrate_reshape_arrays(x, y, xmin, xmax):
+    assert xmin.shape == xmax.shape
+    if len(xmin.shape) == 1:
+        N = xmin.shape[0]
+    else:
+        raise ValueError('xmin must have shape (N,)')
+
+    if len(x.shape) == 1:
+        Nbin = x.shape[0]
+        x = x.reshape((1, Nbin))
+        x = np.repeat(x, N, axis=0)
+    elif len(x.shape) == 2:
+        Nbin = x.shape[1]
+        if x.shape[0] != N:
+            raise ValueError('x must have shape (Nbin,) or (N, Nbin)')        
+    else:
+        raise ValueError('x must have shape (Nbin,) or (N, Nbin)')
+
+    if len(y.shape) == 1:
+        assert y.shape[0] == Nbin
+        y = y.reshape((1, Nbin))
+        y = np.repeat(y, N, axis=0)
+    elif len(y.shape) == 2:
+        assert y.shape[1] == Nbin
+        if y.shape[0] != N:
+            raise ValueError('y must have shape (Nbin,) or (N, Nbin)')
+    else:
+        raise ValueError('y must have shape (Nbin,) or (N, Nbin)')
+    
+    # double check
+    assert x.shape == y.shape
+
+    return x, y, xmin, xmax, N, Nbin
+
+def get_bin_indices(x, x0):
+    N = x.shape[0]
+    Nbin = x.shape[1]
+
+    i = (x0[:,None] >= x).sum(axis=1) - 1
+    i = np.clip(i, 0, Nbin-2)
+
+    x_i = x[np.arange(N),i]
+    x_ip1 = x[np.arange(N),i+1]
+
+    s = (x0 - x_i) / (x_ip1 - x_i)
+    s = np.clip(s, 0, 1)
+
+    return i, s
+
+def trap_integrate(x, y, xmin, xmax, bin_width):
+    x, y, xmin, xmax, N, Nbin = _integrate_reshape_arrays(x, y, xmin, xmax)
+    # now x, y have shape (N, Nbin)
+    # xmin, xmax have shape (N,)
+
+    # assert bin_width constraint
+    assert np.allclose(np.diff(x), bin_width)
+    
[…]

### 2024-04-13 paper/ms.tex
Update header and ref
Update title and abstract

@@
-%% Beginning of file 'sample631.tex'
-%%
-%% Modified 2021 March
-%%
-%% This is a sample manuscript marked up using the
-%% AASTeX v6.31 LaTeX 2e macros.
-%%
-%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
-%% (Copyright 2000-2015).  See the classfile for details.
+\documentclass[linenumbers, twocolumn]{aastex631}
 
-%% AASTeX requires revtex4-1.cls and other external packages such as
-%% latexsym, graphicx, amssymb, longtable, and epsf.  Note that as of 
-%% Oct 2020, APS now uses revtex4.2e for its journals but remember that 
-%% AASTeX v6+ still uses v4.1. All of these external packages should 
-%% already be present in the modern TeX distributions but not always.
-%% For example, revtex4.1 seems to be missing in the linux version of
-%% TexLive 2020. One should be able to get all packages from www.ctan.org.
-%% In particular, revtex v4.1 can be found at 
-%% https://www.ctan.org/pkg/revtex4-1.
-
-%% The first piece of markup in an AASTeX v6.x document is the \documentclass
-%% command. LaTeX will ignore any data that comes before this command. The 
-%% documentclass can take an optional argument to modify the output style.
-%% The command below calls the preprint style which will produce a tightly 
-%% typeset, one-column, single-spaced document.  It is the default and thus
-%% does not need to be explicitly stated.
-%%
-%% using aastex version 6.3
-\documentclass[linenumbers, twocolumn]{aastex631}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{newtxtext,newtxmath}
+\usepackage{hyperref}
 
@@
 \newcommand{\Msun}{\ensuremath{M_{\odot}}}
+\newcommand{\Gyr}{\ensuremath{\textrm{Gyr}}}
+\newcommand{\Myr}{\ensuremath{\textrm{Myr}}}
 \newcommand{\yr}{\ensuremath{\textrm{yr}}}
@@
 \newcommand{\pc}{\ensuremath{\textrm{pc}}}
+\newcommand{\tocite}{\textcolor{blue}{cite}}
+\newcommand{\FeH}{\ensuremath{[\textrm{Fe}/\textrm{H}]}}
+\newcommand{\MgFe}{\ensuremath{[\textrm{Mg}/\textrm{Fe}]}}
+\newcommand{\alphaFe}{\ensuremath{[\alpha/\textrm{Fe}]}}
+
+\newcommand{\red}[1]{\textcolor{red}{#1}}
 
@@
 
-\title{Stimulated Accretion from Circumgalactic Media Interactions}
+\title{Rising from the Ashes: How the Milky Way Got Its Scars}
 
@@
 
-\author{Federico Marinacci}
-\affiliation{Department of Physics \& Astronomy `Augusto Righi', 
-University of Bologna, Bologna, Italy}
-
 \author{Lars Hernquist}
@@
 
-\author{others}
+\author{et al}
 
@@
 \begin{abstract}
-  It is now well-established that galaxies host extended gaseous haloes dubbed
-  the circumgalactic medium (CGM) which play a critical role in receiving and
-  providing gas from and to the disk. Typically metal-poor, the CGM is a major
-  actor in the nuclear abundance evolution of galaxies. While aspects of
-  isolated CGM, such as its rotation and multiphase nature, have been studied,
-  the interaction between the CGM of two merging galaxies is less well
-  understood. In this work, we present hydrodynamic simulations of a controlled
-  galaxy merger, roughly resembling a merger the Milky Way experienced early in
-  its history. Unsurprisingly, the CGM of the satellite galaxy is stripped early
-  in the merger -- mostly during its first pericentric passage (check). This has
-  the effect of stimulating the accretion of gas from the host's CGM onto its
-  disk. This occurs due to two effects: (1) Cold gas from the satellite's CGM
-  mixes with gas in the host's CGM and cools it to a regime where cooling is
-  more efficient, thus reducing the gas' thermal pressure support. (2) The
-  satellite deepens the potential well of the host galaxy, reducing its
-  free-fall time. These effects combine to enhance the accretion of gas onto the
-  host's disk. In our setup (for which there is significant uncertainty), the
-  bulk amount of gas accreted on the disk can increase by a factor of $\sim2$
-  (\textcolor{red}{checl}).
+  Stars are thought to inherit the elemental abundances of their birth cloud and, for the most part, to not change their surface abundances over time.
+Stellar surface abdundances are, therefore, a promising avenue to probe the time evolution of the abundance distribution of the Galaxy's gas phase.
+A particularly useful compression of the high-dimensional abundance plane is to consider the distribution of $\alpha$ elements for a given total metallicity, usually tracked by iron.
+It is well-known that this distribution of $\alpha$ is bimodal, for which there is a growing consensus that the low-$\alpha$ sequence diverges from the high-$\alpha$ sequence as a result of a merger.
+In this work, we propose the phoenix hypothesis: the bimodality is caused by a brief ($\sim300\,\Myr$) period of quiescent star formation, possibly preceded by a starburst.
+The bimodality is a natural consequence of stellar populations enriching the Galactic disk during a period in which no stars are forming.
+Our proposal is consistent with a merger, but it is agnostic to the exact mechanism by which the quiescent period arises.
+Our proposal predicts no overlap in age between the high- and low-$\alpha$ sequence at a given birth radius.
 \end{abstract}

### 2024-04-20 single_star/archive/GFM.py
Add single star stuff

@@ -1,0 +1,466 @@
+import numpy as np
+import h5py as h5
+from pygsl import spline
+import util
+from warnings import warn
+from tqdm import tqdm
+from scipy.optimize import bisect
+from scipy.interpolate import RectBivariateSpline
+
+class TNGParameters(object):
+    def __init__(self):
+        # "numerical" parameters
+        self.GFM_N_MASS_BINS = 200
+        self.GFM_MIN_METAL = -20.
+
+        # IMF parameters
+        self.IMF_MinMass_Msun = 0.1
+        self.IMF_MaxMass_Msun = 100.0
+        self.IMF_A = 0.852464
+        self.IMF_B = 0.237912
+        self.IMF_sigma = 0.69
+        self.IMF_mc = 0.079
+        self.IMF_Mhinge = 1.0
+        self.IMF_alpha = -2.3
+
+        # SNII parameters
+        self.SNII_MaxMass_Msun = 100.0
+        self.SNII_MinMass_Msun = 8.0
+
+        # SNIa parameters
+        self.SNIa_Rate_Norm = 1.3e-3
+        self.SNIa_Rate_TAU = 0.04
+        self.GFM_SNIA_DTD_POWERLAW_INDEX = 1.12
+
+class ChabrierIMF(object):
+    def __init__(self, param, renormalize=False):
+        self._verify_params(param)
+        self._init_imf(renormalize)
+        self._init_cumulative_imf()
+
+    def _verify_params(self, param):
+        self._required_params = ['IMF_MinMass_Msun', 'IMF_MaxMass_Msun', 'GFM_N_MASS_BINS', 'IMF_A', 'IMF_B', 'IMF_sigma', 'IMF_mc', 'IMF_Mhinge', 'IMF_alpha']
+        for p in self._required_params:
+            if not hasattr(param, p):
+                raise AttributeError("Must specify parameter " + p)
+        self.p = param
+    
+    def _init_imf(self, renormalize):
+        imf_dlog10_Msun = (np.log10(self.p.IMF_MaxMass_Msun) - np.log10(self.p.IMF_MinMass_Msun)) / (self.p.GFM_N_MASS_BINS - 1)
+        imf_mass_bin_log10 = np.log10(self.p.IMF_MinMass_Msun) + np.arange(self.p.GFM_N_MASS_BINS) * imf_dlog10_Msun
+        imf_mass_bin       = np.power(10, imf_mass_bin_log10)
+
[…]

### 2024-04-20 single_star/archive/sed.py

@@ -1,0 +1,299 @@
+import numpy as np
+import platform
+import h5py as h5
+from scipy.interpolate import RegularGridInterpolator, interp1d
+from numba import njit
+
+def auto_convert_to_ndarray(func):
+    def wrapper(*args, **kwargs):
+        # ignore first arg if we are a class method
+        arg0 = args[1] if isinstance(args[0], object) else args[0]
+        args_in = [np.array([arg]) if isinstance(arg, (float, int)) 
+                   else np.asarray(arg) if isinstance(arg, list)
+                   else arg for arg in args]
+        result = func(*args_in, **kwargs)
+        # Convert ndarray result to float if the input was a float
+        # print(args[0])
+        return float(result[0]) if isinstance(arg0, (float, int)) else result
+    return wrapper
+
+class IMFClass(object):
+    def __init__(self, mmin=0.1, mmax=100, A=0.852464, B=0.237912,
+                 mc=0.079, sigma=0.69, mhinge=1):
+        
+        self.mmin = mmin
+        self.mmax = mmax
+        self.A = A
+        self.B = B
+        self.mc = mc
+        self.sigma = sigma
+        self.mhinge = mhinge
+    
+        self._test_norm()
+
+    def _test_norm(self):
+        m = np.logspace(np.log10(self.mmin), np.log10(self.mmax), 1000)
+        imf = self(m)
+        norm = np.trapz(m*imf, m)
+        assert np.isclose(norm, 1.0)
+
+    @auto_convert_to_ndarray
+    def __call__(self, m):
+        imf = np.zeros(m.shape)
+
+        m = np.clip(m, self.mmin, self.mmax)
+
+        imf_lower = self.A * m**(-1.) * np.exp(-np.log10(m/self.mc)**2 / (2*self.sigma**2))
+        imf_upper = self.B * m**(-2.3)
+
+        imf[m < self.mhinge] = imf_lower[m < self.mhinge]
+        imf[m >= self.mhinge] = imf_upper[m >= self.mhinge]
+
+        imf[m < self.mmin] = 0.0
+        imf[m > self.mmax] = 0.0
+
+        return imf
+
+@auto_convert_to_ndarray
+def _my_interp(x, xp, yp, deriv=False):
+    # x is assumed to be an array of length (N,)
+    # xp is assumed to be an array of length (N, M)
[…]

### 2024-04-20 paper/ms.tex
Update abstract, title

@@
 \usepackage{hyperref}
+\usepackage{gensymb}
 
@@
 \newcommand{\alphaFe}{\ensuremath{[\alpha/\textrm{Fe}]}}
+\newcommand{\tform}{\ensuremath{t_{\textrm{form}}}}
+\newcommand{\dex}{\ensuremath{\textrm{dex}}}
 
@@
 
-\shorttitle{The CGM of Merging Galaxies}
+\shorttitle{The Milky Way's Phoenix Phase}
 \shortauthors{Beane et al.}
@@
 It is well-known that this distribution of $\alpha$ is bimodal, for which there is a growing consensus that the low-$\alpha$ sequence diverges from the high-$\alpha$ sequence as a result of a merger.
+The general idea is that fresh, pristine gas from the merger causes a sudden change in the abundance structure of the disk, such that the gas spends relatively little time in the valley of bimodality.
+However, we argue that it is also possible that when the Galaxy's gas phase was in the valley that it was quiescent.
+This relaxes the necessity for a rapid abundance transition.
+A preceding starburst, which may cause the quiescent phase, would also be a culprit in the abundance transition.
+
   In this work, we propose the phoenix hypothesis: the bimodality is caused by a brief ($\sim300\,\Myr$) period of quiescent star formation, possibly preceded by a starburst.

### 2024-04-20 paper/ms.tex
Some updates to introduction

@@
 \section{Introduction} \label{sec:intro}
-The present day Milky Way formed through a combination of external interactions
-and internal secular evolution. Disentangling the role and importance of each is
-a major goal of Galactic science today.
+Elements heavier than hydrogen are produced through nuclear fusion.
+After Big Bang Nucleosynthesis, this only occurs in compact objects.
+The distribution of elemental abundances in the gas-phase of a galaxy is determined by a complicated combination of physical processes - stellar evolution and supernovae, gas accretion, galaxy mergers, gas outflows from stellar and AGN feedback, metal mixing and diffusion, etc.
+
+By necessity, stars inherit the constituitive properties of the gas cloud from which they formed.
+Moreover, the surface abundance of stars do not change over time.\footnote{For the most part.} We therefore have the unique opportunity to examine the historical record of the gas-phase abundance of a galaxy by way of the distribution of the surface abundances of stars.
+Because the processes which give rise to this distribution are complex, there is almost certainly some structure in this distribution for every galaxy.
+However, it has only been definitively measured in the Milky Way.
+
+The distribution of elemental abundances is a high dimensional space (\red{e.g.
+up to 8 billion elements by XYZ}).
+However, this space is highly degenerate, and so the effective number of dimensions is much smaller - even possibly compressed to just \FeH and age \citep{2019ApJ...883..177N}.
+
+Two elements in particular have received particular interest - iron and $\alpha$-elements (elements produced through the $\alpha$-process, typically tracked with just Mg).
+Type Ia and Type II supernovae are the main contributors of elemental enrichment.
+Iron is broadly produced in both types, and so its abundance is a proxy for the total metallicity of a star.
+$\alpha$-elements, on the other hand, are mainly produced in Type II supernovae.
+The ratio of $\alpha$-elements to iron is then a measure of the relative contributions of Type Ia and II to the enrichment of a parcel of gas.
+It has therefore become common to compress the high-dimensional abundance space to the two dimensional \FeH-\alphaFe plane.
+
+In this plane, it is now well-established that a significant bimodality exists in the Milky Way \red{cite a boatload}.
+
+Elemental enrichment is accounted for in modern galaxy formation models, though the validity of the yield tables is suspect.
+It is not known if the yields (i.e., the amount of metals produced by the SN) used in such models are accurate.
+This issue is further compounded by the fact that the mixing of metals is unresolved and is sensitive to numerical choices (e.g., Eulerian codes being generally more diffusive than Lagrangian).
+To make matters even worse, the inflows and outflows of gas from galaxies is sensitive to the choices of the feedback model, which has a strong impact on a galaxy's elemental history.
 

### 2024-04-20 paper/ms.tex
Add a bunch of figures

@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{figure1.pdf}
+  \caption{\textbf{The abundance bimodality seen in the Milky Way can be reproduced in some idealized merger simulations.} In the upper panels, we show the distribution of stars in the \MgFe-\FeH plane.
+The left panel shows the observed distribution in the Milky Way from ASPCAP \red{cite}, while the right two panels show two idealized merger simulations.
+The idealized merger simulations are nearly identical, except that the bimodal simulation has a starting radius of $129\,\kpc$, while the unimodal simulation has a starting radius of $142\,\kpc$.
+We emphasize that the labels ``unimodal'' and ``bimodal'' are of the \textit{outcome} of the simulation, and do not reflect a particular choice in the setup.
+The bottom panels show the distribution of \MgFe at fixed \FeH.
+The colors indicate the fixed \FeH values, which are $-0.5$, $-0.375$, $-0.25$, and $0.25$.
+The Milky Way (left panels) exhibits a strong bimodal distribution of \MgFe at various \FeH.
+The idealized merger simulation marked as bimodal (center panels) also exhibits a bimodal distribution of \MgFe, though the structure is not as strongly defined.
+The idealized merger simulation marked as unimodal exhibits only weak structure, if any at all.}
+  \label{fig:fig1}
+\end{figure*}
+
 \section{Methods}\label{sec:methods}
@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{before_after.pdf}
+  \caption{\textbf{The high-$\alpha$ sequence forms before the merger, the low-$\alpha$ sequence forms after the merger.} This plot shows the sequence of events leading to the build-up of the low- and high-$\alpha$ sequences for our fiducial bimodal simulation.
+We have separated the high- and low-$\alpha$ sequences by a dashed line at $-0.1\FeH + 0.31$, which was chosen by eye to lie in the trough.
+The left panel shows all star particles in our solar neighborhood cut.
+The middle left panel shows the star particles that form before the merger ($\tform < 1.5\,\Gyr$), which form a weak sequence of star particles at the lowest \FeH and highest \MgFe.
+The middle right panel shows the star particles that form during the merger ($1.5\,\Gyr < \tform < 2.5\,\Gyr$).
+These star particless form the portion of the high-$\alpha$ sequence closest to the trough, and the density of star particless is higher than those that form before.
+The middle right panel shows the star particles which form after the merger ($\tform > 2.5\,\Gyr$).
+These star particles form almost entirely below the trough.}
+  \label{fig:before_after}
+\end{figure*}
+
 \begin{figure}
   \centering
-  \includegraphics[width=\columnwidth]{fig/cumprof.pdf}
-  \caption{The cumulative amount of the central's CGM gas accreted onto the disk
-  ($r<20\,\kpc$) as a function of time. The blue line shows the case of the
-  galaxy merger setup and the orange line shows the case of an isolated galaxy.
-  The effect of the merger is to increase the amount of mass accreted onto the
-  central. We stress that this plot does not include the mass from the satellite's
-  disk or CGM.}
-  \label{fig:cumprof}
+  \includegraphics[width=\columnwidth]{before_after_sfh.pdf}
+  \caption{\textbf{At fixed metallicity, the low- and high-$\alpha$ sequence are cleanly separated in time, with an intervening quiescent period.} Here we show the star formation history of the high- and low-$\alpha$ sequences.
+The blue (low-$\alpha$) and orange (high-$\alpha$) histograms correspond to the dashed line cut made in the \MgFe-\FeH plane in Figure~\ref{fig:before_after}, at a fixed metallicity of $\FeH\sim0$.
+One can see that there is a nearly perfect separation in time between the formation of the high-$\alpha$ and low-$\alpha$ sequence, except for a brief overlap which can be attributed to the inadequacy of the linear cut model of the two sequences.
+Separating the formation periods lies a quiescent period with a duration of $\sim300\,\Myr$.
+\red{make sfr per dex}.}
+  \label{fig:before_after_sfh}
 \end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{before_after_sfh_by_iron.pdf}
+  \caption{\textbf{The timing of the quiescent period which divides the high- and low-$\alpha$ sequences is metallicity dependent.} The star formation history of stars at various fixed metallicities ($\FeH\sim0$, $-0.25$, and $-0.5\,\textrm{dex}$).
+As in Figure~\ref{fig:before_after_sfh}, there is a quiescent period period which separates the formation of the low- and high-$\alpha$ sequence \red{maybe a better way to show this?}.
+However, one can see that the timing of the quiescent period is metallicity-dependent.
+It occurs earlier at lower metallicity, by $\sim300\,\Myr$ for the metallicities shown in this plot.
+\red{make sfr per dex}.}
+  \label{fig:before_after_sfh_by_iron}
+\end{figure}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{SFR_alpha.pdf}
+  \caption{\textbf{A global suppression of star formation is associcated with a decrease in \MgFe{}, which is seen in the bimodal simulation but not in the unimodal simulation.} Here, we show both the SFR of the central galaxy ($r<15\,\kpc$) and the median \MgFe{} for gas at $2\,\kpc<r<5\,\kpc$ at a fixed \FeH{} bin centered on $-0.2$ with width $0.02\,\dex$.
+The left panel shows the bimodal simulation while the right panel shows the unimodal simulation.
+The time of the merger (i.e., the second pericenter) is indicated by the vertical dashed line.
+In the bimodal simulation, the star formation is suppressed after the merger.
+This suppression of star formation is associated with a sudden drop in the median \MgFe{} of the gas.
+Neither the suppression of star formation nor the drop in \MgFe{} are seen in the unimodal simulation.}
+  \label{fig:SFR_alpha}
+\end{figure*}
 
@@
 
+\section{Cause of Suppressed Star Formation}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{SFR_Mgas_tdep.pdf}
+  \caption{\textbf{The suppression of star formation in the bimodal simulation is associated with both a reduction in gas mass as well as an increase in the depletion time.} The drop in star formation (blue line) at $\sim2.5-3\,\Gyr$ is associated with both a reduction in the total gas mass (red line) as well as an increase in the depletion time (green line).
+This shows that the SFR suppression is a result of both less gas mass and more inefficient star formation.
+\red{Should this only include the bimodal?
+Also, move to appendix?}}
+  \label{fig:SFR_Mgas_tdep}
+\end{figure*}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=242.26653pt]{MdotBH_rsep.pdf}
+  \caption{\textbf{The bimodal merger is associated with high accretion rates onto the central SMBH.} Around the time of each pericentric passage, and slightly after, the accretion rate (blue line) becomes very high.
+Here, it is shown as a fraction of the Eddington accretion rate.
+During the merger, the accretion rate reaches as high as Eddington at some times, but is always above $10\%$.
+The orbital separation between the central and satellite is shown in the orange line.}
+  \label{fig:MdotBH_rsep}
+\end{figure}
+
 \end{document}
@@
 % End of file `sample631.tex'.
+
+% Ness 2019

### 2024-04-21 paper/ms.tex
Update abstract

@@
 \begin{abstract}
-  Stars are thought to inherit the elemental abundances of their birth cloud and, for the most part, to not change their surface abundances over time.
-Stellar surface abdundances are, therefore, a promising avenue to probe the time evolution of the abundance distribution of the Galaxy's gas phase.
-A particularly useful compression of the high-dimensional abundance plane is to consider the distribution of $\alpha$ elements for a given total metallicity, usually tracked by iron.
-It is well-known that this distribution of $\alpha$ is bimodal, for which there is a growing consensus that the low-$\alpha$ sequence diverges from the high-$\alpha$ sequence as a result of a merger.
-The general idea is that fresh, pristine gas from the merger causes a sudden change in the abundance structure of the disk, such that the gas spends relatively little time in the valley of bimodality.
-However, we argue that it is also possible that when the Galaxy's gas phase was in the valley that it was quiescent.
-This relaxes the necessity for a rapid abundance transition.
-A preceding starburst, which may cause the quiescent phase, would also be a culprit in the abundance transition.
-
-  In this work, we propose the phoenix hypothesis: the bimodality is caused by a brief ($\sim300\,\Myr$) period of quiescent star formation, possibly preceded by a starburst.
-The bimodality is a natural consequence of stellar populations enriching the Galactic disk during a period in which no stars are forming.
-Our proposal is consistent with a merger, but it is agnostic to the exact mechanism by which the quiescent period arises.
-Our proposal predicts no overlap in age between the high- and low-$\alpha$ sequence at a given birth radius.
+  The nuclear abundance distribution of stars encodes the history of the gas-phase abundance in the Milky Way.
+Without a large, unbiased sample of stellar ages, the exact timing and nature of this history must be \textit{inferred} from the abundances.
+In the two-dimensional plane of \alphaFe-\FeH, it is now clear that two separate populations exist - the low-$\alpha$ and high-$\alpha$ sequences.
+A restatement of this fact is that the distribution of \alphaFe{} is bimodal at a fixed Fe.
+Structure in the nuclear abundance distribution can arise from many processes - proposals include radial migration, high-redshift clump formation, and various effects associated with galaxy mergers, among others.
+In this work, we demonstrate another possible avenue for structure formation with clear observational predictions.
+We propose that the Galaxy underwent a starburst followed by a brief (hundreds of Myr) quiescent phase.
+A natural consequence of this quiescent phase is that stars in the valley of the bimodality do not form because: (1) the absence of enrichment from high-mass stars leads to a rapid reduction in \alphaFe{}, and (2) any time the gas spends in the abundance valley is deemphasized in the present day distribution because the star formation rate is lower.
+With a set of idealized merger simulations, we demonstrate the feasibility of this proposal.
+The starburst and quiescent phase can result from a merger, but it is not a necessary component of the theory.
+This ``phoenix hypothesis'' predicts a gap in stellar ages at a fixed \FeH{} and that stars which form directly after this gap would have lower \alphaFe{} than stars which form slightly later.
 \end{abstract}

### 2024-04-21 paper/ms.tex
Write new methods, move old text to appendix

@@
 \section{Methods}\label{sec:methods}
+\subsection{Simulation Setup}\label{ssec:setup}
+Our goal in setting up the simulations in this work is not an attempt at matching any Milky Way observable in any detail.
+Our aim is to construct a setup resembling the merger between the Milky Way and GSE at $z\sim2$.
+However, there are great uncertainities associated with the state of the Milky Way and of GSE at this time.
+In Appendix~\ref{app:ics}, we discuss in more detail the choices made in tuning our setup to arrive at a system which is reasonably useful for understanding the Galaxy.
 
-\subsection{Gaseous Halos}\label{ssec:gashalo}
+Here, we provide an overview of some salient details of our setup.
+The interested reader is referred to Appendix~\ref{app:ics} for more details.
+In isolation, each galaxy is a compound halo setup, with a Hernquist dark matter halo and a gaseous halo with a $\beta$-profile.
+The dark matter halo is initialized to be in gravitational equilibrium with the total potential.
+The gaseous halo is in gravito-hydrostatic equilibrium, where the temperature is allowed to vary as a function of radius.
+The azimuthal velocity of the gaseous halo is given as a fraction of the circular velocity.
+There is no initial stellar disk or bulge, and the gaseous halo is initially metal-free.
+All star particles and metals are formed self-consistently.
+Both the central and satellite galaxies are setup in this way.
 
-The nature of the circumgalactic media of local galaxies remains largely
-uncertain. It is unclear whether the constraints we have on the local universe
-apply to the circumgalactic media of $z\sim2$ galaxies. Nonetheless, we persist.
+In order to combine the galaxies, we follow \citet{2021ApJ...923...92N}, and place the satellite galaxy on a retrograde orbit.
+In the fiducial simulation, the satellite is placed at the virial radius with the virial velocity with a circularity of $0.5$.
+In order to test minor changes to the orbit, we ran a grid of simulations with $\pm10\%$ in each the starting radius and velocity, and $\pm0.1$ in the circularity, for a total of $27$ simulations.
 
-We assume the CGM of the Milky Way and GSE can be modelled using a $\beta$ profile,
-\begin{equation}
-  \rho(r) = \rho_0 \left( 1 + \left(\frac{r}{r_c}\right)^2 \right)^{-\frac{3}{2}\beta}\textrm{.}
-\end{equation}
-However, a $\beta$-profile has been shown to be a reasonable fit to the density
-profile of galaxy clusters and of the $L_{*}$ galaxy NGC 3221. Whether or not
-such a profile extends to lower mass galaxies at $z~2$ is unclear, but to our
-knowledge there is no better motivation for another profile.
-
-Our construction of the Milky Way and GSE CGM follows
-\citet{2023MNRAS.tmp.2070B}. In particular, we set $\beta=2/3$ and $r_c=0.22
-r_s$, where $r_s$ is the scale length of the dark matter halo. For the Milky Way
-and GSE, $r_c=9$, $6.5\,\textrm{kpc}$, respectively. For the present study we
-keep $\beta$ and $r_c$ fixed and instead vary the central density $\rho_0$. Our
-fiducial values are $9.61\times10^{-5}$ and $7.57\times10^{-5}\,\Msun/\pc^3$ for
-the Milky Way and GSE, respectively.
-
-A useful metric for assessing the central density is by the universal baryon
-fraction $f_{\textrm{B}}$ -- i.e., the ratio between the mass in baryons to the
-mass in dark matter within $R_{200}$ as compared to the mean ratio of the
-universe.\footnote{To be explicit,
-$f_{\textrm{B}}=(M_{\textrm{b}}/M_{\textrm{c}})/(\Omega_{\textrm{b}}/\Omega_{\textrm{c}})$,
-where $M_{\textrm{b}}$ and $M_{\textrm{c}}$ are the mass of baryons and cold
-dark matter within $R_{200}$, and $\Omega_{\textrm{b}}$ and
-$\Omega_{\textrm{c}}$ are the mean baryon and cold dark matter densities of the
-universe.} For our fiducial central densities, this value is $1.07$ and $0.28$
-for the Milky Way and GSE respectively using the universal values from
-\cite{2014AA...571A..16P}. An early argument by
+\section{Results}\label{sec:results}
+\subsection{Abundance Distribution}
+In Figure~\ref{fig:fig1}, briefly discussed in the Introduction, we show the abundance distribution of the Milky Way as well as two of our idealized merger simulations.
+A number of our idealized simulations exhibit either a bimodal or unimodal abundance distribution, and so we have selected two which are representative examples of
 
@@
 
-\section{Modelling the Milky Way and GSE at $z=2$}
+\section{Initial Conditions}\label{app:ics}
+\subsection{Update to Initial Conditions Code}
+The routines to generate the initial conditions of the central and satellite galaxies are descended from the \texttt{MakeNewDisk} code first described in \tocite.
+This code originally allowed for a Hernquist halo, exponential gas and stellar disk, and Hernquist bulge to be constructed in equilibrium by approximating the distribution function as a Gaussian.
+This code was recently extended by \citet{2023MNRAS.tmp.2070B} to also allow for the construction of a gaseous halo with a $\beta$-profile which surrounds the disk.
+This halo is given a rotational velocity which is a fixed ratio of the circular velocity.
+The interested
 
-Our merger simulations are built upon reasonable models of both the Milky Way
-and GSE at $z\sim2$. Much is uncertain about the properties of the Milky Way and
-GSE at these redshifts.  We describe the motivation for the choices made in
-constructing these models.
+We have made a few modifications to the \citet{2023MNRAS.tmp.2070B} code.
+First, we have added the ability to vary the value of $\beta$, which was previously fixed to $2/3$.
+Second, we can now vary the fraction of the gaseous halo's rotational velocity to the circular velocity, which was fixed at $0.4$.
+The central density of the $\beta$ profile is also chosen differently.
+We now fix the total mass inside of $R_{200}$.
+The user now specifies the baryon fraction within $R_{200}$ (nominally the universal baryon fraction), from which the dark matter halo mass and central density are derived.
+For other details of the setup, we refer the interested reader to \citet{2023MNRAS.tmp.2070B}.
+
+A detailed description of our setup is described in Appendix~\ref{app:ics}.
+Briefly, for both the central and satellite galaxies we initialize a dual system of both a Hernquist halo as well as a $\beta$-profile.
+\red{fix: this is confusing}.
+The haloes are in gravito-hydrostatic equilibrium with themselved.
+We do not initialize either galaxy with a disk, rather allowing the disk to form self-consistently out of the collapsing profile.
+This is an attractive setup because it means that the disk-CGM interface as well as the abundance of star particles are formed self-consistently.
+
+For the central galaxy, meant to imitate the Milky Way, we choose a halo mass of $5\times10^{11}\,\Msun$.\footnote{When discussing halo masses in the \texttt{MakeNewDisk} lineage, it is important to remember that a Hernquist profile is chosen such that its profile within the scale radius matches an NFW halo\red{cite} of a certain mass, size, and concentration.
+This means that the actual mass contained within $R_{200}$ is less than would be contained within an NFW halo, since the Hernquist halo's density drops more quickly than NFW past the scale radius.
+This is unimportant for studies of the internal structure of galaxies, but in our work this distinction would mean that the given orbits would need to be adjusted.} This is roughly the expected halo mass of the Milky Way at $z\sim2$ from abundance matching\red{cite} in combination with the expected stellar mass-halo mass relation \red{cite}.
+We allow $\beta$ to be $0.8$ and set the central density to $\sim4.1\times10^{-4}\,\Msun/\pc^3$, such that the baryon fraction within $R_{200}$ is $8\%$.
+The core radius is set to be $9\,\kpc$, though the resultant galaxy is not very sensitive to the core radius.
+
+For the satellite galaxy, meant to imitate GSE, we choose a halo mass of $\sim2.2\times10^{11}\,\Msun$.
+We also use a $\beta$ value of $0.8$ and set the central density to $\sim3.5\times10^{-4}\,\Msun/\pc^3$, such that the baryon fraction within $R_{200}$ is $6\%$.
+The core radius is set to $6.5\,\kpc$, which similar to the central does not have a large impact.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{mass_size.pdf}
+  \caption{The mass and size evolution of the central (Milky Way, blue) and satellite (GSE, orange) galaxies.
+The mass is taken to be the stellar mass within twice the half-mass radius, and the size is taken to be the half-mass radius.
+In the upper panel, we also show as a horizontal line the mass of the Milky Way and GSE from the best-fit model of \citet{2021ApJ...923...92N}.
+This comparison is taken to be made at $3\,\Gyr$ (vertical dashed line), our proxy for $z\sim2$.
+A precise match is not attempted given the wide ranging uncertainties.}
+  \label{fig:mass_size}
+\end{figure}
+
+Our setup is not meant to be taken literally as a representation of the evolution of the Universe from $z=\inf$ to $z\sim2$.
+In particular, we have made manual adjustments to the setup parameters as well as the feedback model in order to arrive at a well-behaved disk after $\sim3\,\Gyr$ of evolution.
+We experimented with stronger feedback models, but found that higher baryon fractions were required to achieve reasonable stellar masses.
+This may come from the unrealistic aspects of our setup.
+In particular, our potential is initially deep, while in the real universe the potential will deepen gradually over time.
+Thus, a galaxy can form and become self-regulating in a less intense environment than in our setup.
+We account for this by lowering the baryon fraction to well below the universal value.
+
+\subsection{Orbital Parameters}\label{ssec:orbits}
+In this work, we explore a very narrow region of the orbital parameter space, building on the maximum likelihood model from \citet{2021ApJ...923...92N}.
+We situate the satellite galaxy at a given starting radius $R_0$.
+Given the symmetry, the satellite is placed on the $x$-axis.
+
+We then assign a velocity of magnitude $V_0$ with a circularity $\eta$ where $\eta=0$ means $V_0$ is directed radially inward and $\eta=1$ means the satellite is on a circular orbit.
+The radal velocity is set to be $\sqrt{1-\eta^2}V_0$ and the azimuthal and vertical velocities are each set to $V_0 \eta / \sqrt{2}$.
+The sign of the azimuthal velocity is chosen to be retrograde.
+
+After assigning the initial position and velocity of the satellite, we rotate the satellite in the $x$-$z$ plane such that the center of mass is inclined $15\degree$ above the plane and the halo is counterrotating with respect to the central.
+
+For the particular values of the orbital parameters, we take the fiducial model from \citet{2021ApJ...923...92N}.
+We set $R_0$ to be $R_{200}$, $V_0$ to be $V_{200}$ (the circular velocity at $R_{2002}$), and the circularity $\eta$ to be $0.5$.
+We explored a grid of values in which we varied $R_0$ and $V_0$ each by $\pm10\%$, and $\eta$ by $\pm0.1$, for a total of $27$ simulations.
+In this work, we focus on the outcome of two of these simulations in order to demonstrate that our main argument is, in principle, valid.
+A broader exploration and expansion of the orbital grid is a topic of further investigation.
+
+\subsection{Gaseous Halos}\label{ssec:gashalo}
+
+The nature of the circumgalactic media of local galaxies remains largely
+uncertain. It is unclear whether the constraints we have on the local universe
+apply to the circumgalactic media of $z\sim2$ galaxies. Nonetheless, we persist.
+
+We assume the CGM of the Milky Way and GSE can be modelled using a $\beta$ profile,
+
+However, a $\beta$-profile has been shown to be a reasonable fit to the density
+profile of galaxy clusters and of the $L_{*}$ galaxy NGC 3221. Whether or not
+such a profile extends to lower mass galaxies at $z~2$ is unclear, but to our
+knowledge there is no better motivation for another profile.
+
+Our construction of the Milky Way and GSE CGM follows
+\citet{2023MNRAS.tmp.2070B}. In particular, we set $\beta=2/3$ and $r_c=0.22
+r_s$, where $r_s$ is the scale length of the dark matter halo. For the Milky Way
+and GSE, $r_c=9$, $6.5\,\textrm{kpc}$, respectively. For the present study we
+keep $\beta$ and $r_c$ fixed and instead vary the central density $\rho_0$. Our
+fiducial values are $9.61\times10^{-5}$ and $7.57\times10^{-5}\,\Msun/\pc^3$ for
+the Milky Way and GSE, respectively.
+
+A useful metric for assessing the central density is by the universal baryon
+fraction $f_{\textrm{B}}$ -- i.e., the ratio between the mass in baryons to the
+mass in dark matter within $R_{200}$ as compared to the mean ratio of the
+universe.\footnote{To be explicit,
+$f_{\textrm{B}}=(M_{\textrm{b}}/M_{\textrm{c}})/(\Omega_{\textrm{b}}/\Omega_{\textrm{c}})$,
+where $M_{\textrm{b}}$ and $M_{\textrm{c}}$ are the mass of baryons and cold
+dark matter within $R_{200}$, and $\Omega_{\textrm{b}}$ and
+$\Omega_{\textrm{c}}$ are the mean baryon and cold dark matter densities of the
+universe.} For our fiducial central densities, this value is $1.07$ and $0.28$
+for the Milky Way and GSE respectively using the universal values from
+\cite{2014AA...571A..16P}. An early argument by
 

### 2024-04-21 paper/appendix.tex
Split doc across multiple files

--- 2024-04-21 paper/ms.tex
@@
-\documentclass[linenumbers, twocolumn]{aastex631}
-
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{newtxtext,newtxmath}
-\usepackage{hyperref}
-\usepackage{gensymb}
-
-\newcommand{\vdag}{(v)^\dagger}
-\newcommand\aastex{AAS\TeX}
-\newcommand\latex{La\TeX}
-
-\newcommand{\Msun}{\ensuremath{M_{\odot}}}
-\newcommand{\Gyr}{\ensuremath{\textrm{Gyr}}}
-\newcommand{\Myr}{\ensuremath{\textrm{Myr}}}
-\newcommand{\yr}{\ensuremath{\textrm{yr}}}
-\newcommand{\kpc}{\ensuremath{\textrm{kpc}}}
-\newcommand{\pc}{\ensuremath{\textrm{pc}}}
-\newcommand{\tocite}{\textcolor{blue}{cite}}
-\newcommand{\FeH}{\ensuremath{[\textrm{Fe}/\textrm{H}]}}
-\newcommand{\MgFe}{\ensuremath{[\textrm{Mg}/\textrm{Fe}]}}
-\newcommand{\alphaFe}{\ensuremath{[\alpha/\textrm{Fe}]}}
-\newcommand{\tform}{\ensuremath{t_{\textrm{form}}}}
-\newcommand{\dex}{\ensuremath{\textrm{dex}}}
-
-\newcommand{\red}[1]{\textcolor{red}{#1}}
-
-%% Reintroduced the \received and \accepted commands from AASTeX v5.2
-% \received{March 1, 2021}
-% \revised{April 1, 2021}
-%\accepted{\today}
-
-\shorttitle{The Milky Way's Phoenix Phase}
-\shortauthors{Beane et al.}
-
-\graphicspath{{./}{fig/}}
-
-\begin{document}
-
-\title{Rising from the Ashes: How the Milky Way Got Its Scars}
-
-\author{Angus Beane}
-\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
-
-\author{Lars Hernquist}
-\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
-
-\author{et al}
-
-%% Mark off the abstract in the ``abstract'' environment. 
-\begin{abstract}
-  The nuclear abundance distribution of stars encodes the history of the gas-phase abundance in the Milky Way.
-Without a large, unbiased sample of stellar ages, the exact timing and nature of this history must be \textit{inferred} from the abundances.
-In the two-dimensional plane of \alphaFe-\FeH, it is now clear that two separate populations exist - the low-$\alpha$ and high-$\alpha$ sequences.
-A restatement of this fact is that the distribution of \alphaFe{} is bimodal at a fixed Fe.
-Structure in the nuclear abundance distribution can arise from many processes - proposals include radial migration, high-redshift clump formation, and various effects associated with galaxy mergers, among others.
-In this work, we demonstrate another possible avenue for structure formation with clear observational predictions.
-We propose that the Galaxy underwent a starburst followed by a brief (hundreds of Myr) quiescent phase.
-A natural consequence of this quiescent phase is that stars in the valley of the bimodality do not form because: (1) the absence of enrichment from high-mass stars leads to a rapid reduction in \alphaFe{}, and (2) any time the gas spends in the abundance valley is deemphasized in the present day distribution because the star formation rate is lower.
-With a set of idealized merger simulations, we demonstrate the feasibility of this proposal.
-The starburst and quiescent phase can result from a merger, but it is not a necessary component of the theory.
-This ``phoenix hypothesis'' predicts a gap in stellar ages at a fixed \FeH{} and that stars which form directly after this gap would have lower \alphaFe{} than stars which form slightly later.
-\end{abstract}
-
-%% Keywords should appear after the \end{abstract} command. 
-%% The AAS Journals now uses Unified Astronomy Thesaurus concepts:
-%% https://astrothesaurus.org
-%% You will be asked to selected these concepts during the submission process
-%% but this old "keyword" functionality is maintained in case authors want
-%% to include these concepts in their preprints.
-\keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of 
-astronomy(1868) --- Interdisciplinary astronomy(804)}
-
-\section{Introduction} \label{sec:intro}
-Elements heavier than hydrogen are produced through nuclear fusion.
-After Big Bang Nucleosynthesis, this only occurs in compact objects.
-The distribution of elemental abundances in the gas-phase of a galaxy is determined by a complicated combination of physical processes - stellar evolution and supernovae, gas accretion, galaxy mergers, gas outflows from stellar and AGN feedback, metal mixing and diffusion, etc.
-
-By necessity, stars inherit the constituitive properties of the gas cloud from which they formed.
-Moreover, the surface abundance of stars do not change over time.\footnote{For the most part.} We therefore have the unique opportunity to examine the historical record of the gas-phase abundance of a galaxy by way of the distribution of the surface abundances of stars.
-Because the processes which give rise to this distribution are complex, there is almost certainly some structure in this distribution for every galaxy.
-However, it has only been definitively measured in the Milky Way.
-
-The distribution of elemental abundances is a high dimensional space (\red{e.g.
-up to 8 billion elements by XYZ}).
-However, this space is highly degenerate, and so the effective number of dimensions is much smaller - even possibly compressed to just \FeH and age \citep{2019ApJ...883..177N}.
-
-Two elements in particular have received particular interest - iron and $\alpha$-elements (elements produced through the $\alpha$-process, typically tracked with just Mg).
-Type Ia and Type II supernovae are the main contributors of elemental enrichment.
-Iron is broadly produced in both types, and so its abundance is a proxy for the total metallicity of a star.
-$\alpha$-elements, on the other hand, are mainly produced in Type II supernovae.
-The ratio of $\alpha$-elements to iron is then a measure of the relative contributions of Type Ia and II to the enrichment of a parcel of gas.
-It has therefore become common to compress the high-dimensional abundance space to the two dimensional \FeH-\alphaFe plane.
-
-In this plane, it is now well-established that a significant bimodality exists in the Milky Way \red{cite a boatload}.
-
-Elemental enrichment is accounted for in modern galaxy formation models, though the validity of the yield tables is suspect.
-It is not known if the yields (i.e., the amount of metals produced by the SN) used in such models are accurate.
-This issue is further compounded by the fact that the mixing of metals is unresolved and is sensitive to numerical choices (e.g., Eulerian codes being generally more diffusive than Lagrangian).
-To make matters even worse, the inflows and outflows of gas from galaxies is sensitive to the choices of the feedback model, which has a strong impact on a galaxy's elemental history.
-
-The last\footnote{i.e., not ongoing} significant merger was between the
-proto-Milky Way disk and the {\em Gaia}-Sausage-Enceladus (GSE)
-(\textcolor{red}{spell check}) satellite galaxy. The stellar debris from this
-merger constitutes $\sim50\%$ \textcolor{red}{check} of the inner ($r<?\,\kpc$)
-stellar halo. It may have also led to a tilted, triaxial dark matter halo
-(\textcolor{red}{cite}).
-
-The GSE merger is often invoked (\textcolor{red}{cite}) to explain the observed
-bimodality in the \textcolor{red}{alpha iron} abundance plane
-(\textcolor{red}{cite}). Because GSE-mass galaxies are expected to have a lower
-star formation efficiency than proto-Milky Way-mass galaxies
-(\textcolor{red}{cite}), the gas from GSE should be relatively metal poor. The
-gas from GSE thus dilutes the gas in the proto-Milky Way, ``resetting'' the
-chemical abundance of the Milky Way.
-
-However, it has also been claimed that the \textcolor{red}{alpha iron}
-bimodality can be explained through secular processes. \textcolor{red}{Sentence
-explaining the basic concept.} The argument is not that the GSE merger did not
-happen, but rather that it is not {\it necessary} and might not even be {\it
-sufficient} to explain the bimodality. Ongoing work to detect the bimodality in
-external galaxies may shed further light on the topic (\textcolor{red}{cite}).
-
-Investigating GSE-like mergers in cosmological simulations is a rich and active
-area of research. Many mergers believed to be similar to the GSE merger have
-been identified in the literature (\textcolor{red}{cite}). \textcolor{red}{Blah
-blah argue blah blah. And also blah blah argues blah blah.}
-
-While much has been learned from GSE-like mergers in cosmological simulations,
-they are not conducive to controlled experiments. It is possible to change the
-mass of satellites through genetic modification (\textcolor{red}{Pontzen}), and
-the GSE analog can be removed entirely (\textcolor{red}{Cooke cite}). However,
-to our knowledge, no method has been applied to change the orbital parameters of
-such a merger. It is also somehwat unclear if the circumgalactic media of
-proto-Milky Way mass galaxies at $z\sim2$ are properly simulated.
-
-In this work, we present hydrodynamic simulations of a controlled merger between
-a GSE analog and the $z\sim2$ proto-Milky Way.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{figure1.pdf}
-  \caption{\textbf{The abundance bimodality seen in the Milky Way can be reproduced in some idealized merger simulations.} In the upper panels, we show the distribution of stars in the \MgFe-\FeH plane.
-The left panel shows the observed distribution in the Milky Way from ASPCAP \red{cite}, while the right two panels show two idealized merger simulations.
-The idealized merger simulations are nearly identical, except that the bimodal simulation has a starting radius of $129\,\kpc$, while the unimodal simulation has a starting radius of $142\,\kpc$.
-We emphasize that the labels ``unimodal'' and ``bimodal'' are of the \textit{outcome} of the simulation, and do not reflect a particular choice in the setup.
-The bottom panels show the distribution of \MgFe at fixed \FeH.
-The colors indicate the fixed \FeH values, which are $-0.5$, $-0.375$, $-0.25$, and $0.25$.
-The Milky Way (left panels) exhibits a strong bimodal distribution of \MgFe at various \FeH.
-The idealized merger simulation marked as bimodal (center panels) also exhibits a bimodal distribution of \MgFe, though the structure is not as strongly defined.
-The idealized merger simulation marked as unimodal exhibits only weak structure, if any at all.}
-  \label{fig:fig1}
-\end{figure*}
-
-\section{Methods}\label{sec:methods}
-\subsection{Simulation Setup}\label{ssec:setup}
-Our goal in setting up the simulations in this work is not an attempt at matching any Milky Way observable in any detail.
-Our aim is to construct a setup resembling the merger between the Milky Way and GSE at $z\sim2$.
-However, there are great uncertainities associated with the state of the Milky Way and of GSE at this time.
-In Appendix~\ref{app:ics}, we discuss in more detail the choices made in tuning our setup to arrive at a system which is reasonably useful for understanding the Galaxy.
-
-Here, we provide an overview of some salient details of our setup.
-The interested reader is referred to Appendix~\ref{app:ics} for more details.
-In isolation, each galaxy is a compound halo setup, with a Hernquist dark matter halo and a gaseous halo with a $\beta$-profile.
-The dark matter halo is initialized to be in gravitational equilibrium with the total potential.
-The gaseous halo is in gravito-hydrostatic equilibrium, where the temperature is allowed to vary as a function of radius.
-The azimuthal velocity of the gaseous halo is given as a fraction of the circular velocity.
-There is no initial stellar disk or bulge, and the gaseous halo is initially metal-free.
-All star particles and metals are formed self-consistently.
-Both the central and satellite galaxies are setup in this way.
-
-In order to combine the galaxies, we follow \citet{2021ApJ...923...92N}, and place the satellite galaxy on a retrograde orbit.
-In the fiducial simulation, the satellite is placed at the virial radius with the virial velocity with a circularity of $0.5$.
-In order to test minor changes to the orbit, we ran a grid of simulations with $\pm10\%$ in each the starting radius and velocity, and $\pm0.1$ in the circularity, for a total of $27$ simulations.
-
-\section{Results}\label{sec:results}
-\subsection{Abundance Distribution}
-In Figure~\ref{fig:fig1}, briefly discussed in the Introduction, we show the abundance distribution of the Milky Way as well as two of our idealized merger simulations.
-A number of our idealized simulations exhibit either a bimodal or unimodal abundance distribution, and so we have selected two which are representative examples of
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{before_after.pdf}
-  \caption{\textbf{The high-$\alpha$ sequence forms before the merger, the low-$\alpha$ sequence forms after the merger.} This plot shows the sequence of events leading to the build-up of the low- and high-$\alpha$ sequences for our fiducial bimodal simulation.
-We have separated the high- and low-$\alpha$ sequences by a dashed line at $-0.1\FeH + 0.31$, which was chosen by eye to lie in the trough.
-The left panel shows all star particles in our solar neighborhood cut.
-The middle left panel shows the star particles that form before the merger ($\tform < 1.5\,\Gyr$), which form a weak sequence of star particles at the lowest \FeH and highest \MgFe.
-The middle right panel shows the star particles that form during the merger ($1.5\,\Gyr < \tform < 2.5\,\Gyr$).
-These star particless form the portion of the high-$\alpha$ sequence closest to the trough, and the density of star particless is higher than those that form before.
-The middle right panel shows the star particles which form after the merger ($\tform > 2.5\,\Gyr$).
-These star particles form almost entirely below the trough.}
-  \label{fig:before_after}
-\end{figure*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{before_after_sfh.pdf}
-  \caption{\textbf{At fixed metallicity, the low- and high-$\alpha$ sequence are cleanly separated in time, with an intervening quiescent period.} Here we show the star formation history of the high- and low-$\alpha$ sequences.
-The blue (low-$\alpha$) and orange (high-$\alpha$) histograms correspond to the dashed line cut made in the \MgFe-\FeH plane in Figure~\ref{fig:before_after}, at a fixed metallicity of $\FeH\sim0$.
-One can see that there is a nearly perfect separation in time between the formation of the high-$\alpha$ and low-$\alpha$ sequence, except for a brief overlap which can be attributed to the inadequacy of the linear cut model of the two sequences.
-Separating the formation periods lies a quiescent period with a duration of $\sim300\,\Myr$.
-\red{make sfr per dex}.}
-  \label{fig:before_after_sfh}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{before_after_sfh_by_iron.pdf}
-  \caption{\textbf{The timing of the quiescent period which divides the high- and low-$\alpha$ sequences is metallicity dependent.} The star formation history of stars at various fixed metallicities ($\FeH\sim0$, $-0.25$, and $-0.5\,\textrm{dex}$).
-As in Figure~\ref{fig:before_after_sfh}, there is a quiescent period period which separates the formation of the low- and high-$\alpha$ sequence \red{maybe a better way to show this?}.
-However, one can see that the timing of the quiescent period is metallicity-dependent.
-It occurs earlier at lower metallicity, by $\sim300\,\Myr$ for the metallicities shown in this plot.
-\red{make sfr per dex}.}
-  \label{fig:before_after_sfh_by_iron}
-\end{figure}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{SFR_alpha.pdf}
-  \caption{\textbf{A global suppression of star formation is associcated with a decrease in \MgFe{}, which is seen in the bimodal simulation but not in the unimodal simulation.} Here, we show both the SFR of the central galaxy ($r<15\,\kpc$) and the median \MgFe{} for gas at $2\,\kpc<r<5\,\kpc$ at a fixed \FeH{} bin centered on $-0.2$ with width $0.02\,\dex$.
-The left panel shows the bimodal simulation while the right panel shows the unimodal simulation.
-The time of the merger (i.e., the second pericenter) is indicated by the vertical dashed line.
-In the bimodal simulation, the star formation is suppressed after the merger.
-This suppression of star formation is associated with a sudden drop in the median \MgFe{} of the gas.
-Neither the suppression of star formation nor the drop in \MgFe{} are seen in the unimodal simulation.}
-  \label{fig:SFR_alpha}
-\end{figure*}
-
-\bibliography{ref}{}
-\bibliographystyle{aasjournal}
-
-%% This command is needed to show the entire author+affiliation list when
-%% the collaboration and author truncation commands are used.  It has to
-%% go at the end of the manuscript.
-%\allauthors
-
-%% Include this line if you are using the \added, \replaced, \deleted
-%% commands to see a summary list of all changes at the end of the article.
-%\listofchanges
-
 \appendix
@@
 \end{figure}
-
-\end{document}
-
-% End of file `sample631.tex'.
-
-% Ness 2019

### 2024-04-21 paper/introduction.tex
Split doc across multiple files

--- 2024-04-21 paper/ms.tex
@@
-\documentclass[linenumbers, twocolumn]{aastex631}
-
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{newtxtext,newtxmath}
-\usepackage{hyperref}
-\usepackage{gensymb}
-
-\newcommand{\vdag}{(v)^\dagger}
-\newcommand\aastex{AAS\TeX}
-\newcommand\latex{La\TeX}
-
-\newcommand{\Msun}{\ensuremath{M_{\odot}}}
-\newcommand{\Gyr}{\ensuremath{\textrm{Gyr}}}
-\newcommand{\Myr}{\ensuremath{\textrm{Myr}}}
-\newcommand{\yr}{\ensuremath{\textrm{yr}}}
-\newcommand{\kpc}{\ensuremath{\textrm{kpc}}}
-\newcommand{\pc}{\ensuremath{\textrm{pc}}}
-\newcommand{\tocite}{\textcolor{blue}{cite}}
-\newcommand{\FeH}{\ensuremath{[\textrm{Fe}/\textrm{H}]}}
-\newcommand{\MgFe}{\ensuremath{[\textrm{Mg}/\textrm{Fe}]}}
-\newcommand{\alphaFe}{\ensuremath{[\alpha/\textrm{Fe}]}}
-\newcommand{\tform}{\ensuremath{t_{\textrm{form}}}}
-\newcommand{\dex}{\ensuremath{\textrm{dex}}}
-
-\newcommand{\red}[1]{\textcolor{red}{#1}}
-
-%% Reintroduced the \received and \accepted commands from AASTeX v5.2
-% \received{March 1, 2021}
-% \revised{April 1, 2021}
-%\accepted{\today}
-
-\shorttitle{The Milky Way's Phoenix Phase}
-\shortauthors{Beane et al.}
-
-\graphicspath{{./}{fig/}}
-
-\begin{document}
-
-\title{Rising from the Ashes: How the Milky Way Got Its Scars}
-
-\author{Angus Beane}
-\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
-
-\author{Lars Hernquist}
-\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
-
-\author{et al}
-
-%% Mark off the abstract in the ``abstract'' environment. 
-\begin{abstract}
-  The nuclear abundance distribution of stars encodes the history of the gas-phase abundance in the Milky Way.
-Without a large, unbiased sample of stellar ages, the exact timing and nature of this history must be \textit{inferred} from the abundances.
-In the two-dimensional plane of \alphaFe-\FeH, it is now clear that two separate populations exist - the low-$\alpha$ and high-$\alpha$ sequences.
-A restatement of this fact is that the distribution of \alphaFe{} is bimodal at a fixed Fe.
-Structure in the nuclear abundance distribution can arise from many processes - proposals include radial migration, high-redshift clump formation, and various effects associated with galaxy mergers, among others.
-In this work, we demonstrate another possible avenue for structure formation with clear observational predictions.
-We propose that the Galaxy underwent a starburst followed by a brief (hundreds of Myr) quiescent phase.
-A natural consequence of this quiescent phase is that stars in the valley of the bimodality do not form because: (1) the absence of enrichment from high-mass stars leads to a rapid reduction in \alphaFe{}, and (2) any time the gas spends in the abundance valley is deemphasized in the present day distribution because the star formation rate is lower.
-With a set of idealized merger simulations, we demonstrate the feasibility of this proposal.
-The starburst and quiescent phase can result from a merger, but it is not a necessary component of the theory.
-This ``phoenix hypothesis'' predicts a gap in stellar ages at a fixed \FeH{} and that stars which form directly after this gap would have lower \alphaFe{} than stars which form slightly later.
-\end{abstract}
-
-%% Keywords should appear after the \end{abstract} command. 
-%% The AAS Journals now uses Unified Astronomy Thesaurus concepts:
-%% https://astrothesaurus.org
-%% You will be asked to selected these concepts during the submission process
-%% but this old "keyword" functionality is maintained in case authors want
-%% to include these concepts in their preprints.
-\keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of 
-astronomy(1868) --- Interdisciplinary astronomy(804)}
-
 \section{Introduction} \label{sec:intro}
@@
 \end{figure*}
-
-\section{Methods}\label{sec:methods}
-
-\subsection{Gaseous Halos}\label{ssec:gashalo}
-
-The nature of the circumgalactic media of local galaxies remains largely
-uncertain. It is unclear whether the constraints we have on the local universe
-apply to the circumgalactic media of $z\sim2$ galaxies. Nonetheless, we persist.
-
-We assume the CGM of the Milky Way and GSE can be modelled using a $\beta$ profile,
-\begin{equation}
-  \rho(r) = \rho_0 \left( 1 + \left(\frac{r}{r_c}\right)^2 \right)^{-\frac{3}{2}\beta}\textrm{.}
-\end{equation}
-However, a $\beta$-profile has been shown to be a reasonable fit to the density
-profile of galaxy clusters and of the $L_{*}$ galaxy NGC 3221. Whether or not
-such a profile extends to lower mass galaxies at $z~2$ is unclear, but to our
-knowledge there is no better motivation for another profile.
-
-Our construction of the Milky Way and GSE CGM follows
-\citet{2023MNRAS.tmp.2070B}. In particular, we set $\beta=2/3$ and $r_c=0.22
-r_s$, where $r_s$ is the scale length of the dark matter halo. For the Milky Way
-and GSE, $r_c=9$, $6.5\,\textrm{kpc}$, respectively. For the present study we
-keep $\beta$ and $r_c$ fixed and instead vary the central density $\rho_0$. Our
-fiducial values are $9.61\times10^{-5}$ and $7.57\times10^{-5}\,\Msun/\pc^3$ for
-the Milky Way and GSE, respectively.
-
-A useful metric for assessing the central density is by the universal baryon
-fraction $f_{\textrm{B}}$ -- i.e., the ratio between the mass in baryons to the
-mass in dark matter within $R_{200}$ as compared to the mean ratio of the
-universe.\footnote{To be explicit,
-$f_{\textrm{B}}=(M_{\textrm{b}}/M_{\textrm{c}})/(\Omega_{\textrm{b}}/\Omega_{\textrm{c}})$,
-where $M_{\textrm{b}}$ and $M_{\textrm{c}}$ are the mass of baryons and cold
-dark matter within $R_{200}$, and $\Omega_{\textrm{b}}$ and
-$\Omega_{\textrm{c}}$ are the mean baryon and cold dark matter densities of the
-universe.} For our fiducial central densities, this value is $1.07$ and $0.28$
-for the Milky Way and GSE respectively using the universal values from
-\cite{2014AA...571A..16P}. An early argument by
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{before_after.pdf}
-  \caption{\textbf{The high-$\alpha$ sequence forms before the merger, the low-$\alpha$ sequence forms after the merger.} This plot shows the sequence of events leading to the build-up of the low- and high-$\alpha$ sequences for our fiducial bimodal simulation.
-We have separated the high- and low-$\alpha$ sequences by a dashed line at $-0.1\FeH + 0.31$, which was chosen by eye to lie in the trough.
-The left panel shows all star particles in our solar neighborhood cut.
-The middle left panel shows the star particles that form before the merger ($\tform < 1.5\,\Gyr$), which form a weak sequence of star particles at the lowest \FeH and highest \MgFe.
-The middle right panel shows the star particles that form during the merger ($1.5\,\Gyr < \tform < 2.5\,\Gyr$).
-These star particless form the portion of the high-$\alpha$ sequence closest to the trough, and the density of star particless is higher than those that form before.
-The middle right panel shows the star particles which form after the merger ($\tform > 2.5\,\Gyr$).
-These star particles form almost entirely below the trough.}
-  \label{fig:before_after}
-\end{figure*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{before_after_sfh.pdf}
-  \caption{\textbf{At fixed metallicity, the low- and high-$\alpha$ sequence are cleanly separated in time, with an intervening quiescent period.} Here we show the star formation history of the high- and low-$\alpha$ sequences.
-The blue (low-$\alpha$) and orange (high-$\alpha$) histograms correspond to the dashed line cut made in the \MgFe-\FeH plane in Figure~\ref{fig:before_after}, at a fixed metallicity of $\FeH\sim0$.
-One can see that there is a nearly perfect separation in time between the formation of the high-$\alpha$ and low-$\alpha$ sequence, except for a brief overlap which can be attributed to the inadequacy of the linear cut model of the two sequences.
-Separating the formation periods lies a quiescent period with a duration of $\sim300\,\Myr$.
-\red{make sfr per dex}.}
-  \label{fig:before_after_sfh}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{before_after_sfh_by_iron.pdf}
-  \caption{\textbf{The timing of the quiescent period which divides the high- and low-$\alpha$ sequences is metallicity dependent.} The star formation history of stars at various fixed metallicities ($\FeH\sim0$, $-0.25$, and $-0.5\,\textrm{dex}$).
-As in Figure~\ref{fig:before_after_sfh}, there is a quiescent period period which separates the formation of the low- and high-$\alpha$ sequence \red{maybe a better way to show this?}.
-However, one can see that the timing of the quiescent period is metallicity-dependent.
-It occurs earlier at lower metallicity, by $\sim300\,\Myr$ for the metallicities shown in this plot.
-\red{make sfr per dex}.}
-  \label{fig:before_after_sfh_by_iron}
-\end{figure}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{SFR_alpha.pdf}
-  \caption{\textbf{A global suppression of star formation is associcated with a decrease in \MgFe{}, which is seen in the bimodal simulation but not in the unimodal simulation.} Here, we show both the SFR of the central galaxy ($r<15\,\kpc$) and the median \MgFe{} for gas at $2\,\kpc<r<5\,\kpc$ at a fixed \FeH{} bin centered on $-0.2$ with width $0.02\,\dex$.
-The left panel shows the bimodal simulation while the right panel shows the unimodal simulation.
-The time of the merger (i.e., the second pericenter) is indicated by the vertical dashed line.
-In the bimodal simulation, the star formation is suppressed after the merger.
-This suppression of star formation is associated with a sudden drop in the median \MgFe{} of the gas.
-Neither the suppression of star formation nor the drop in \MgFe{} are seen in the unimodal simulation.}
-  \label{fig:SFR_alpha}
-\end{figure*}
-
-\bibliography{ref}{}
-\bibliographystyle{aasjournal}
-
-%% This command is needed to show the entire author+affiliation list when
-%% the collaboration and author truncation commands are used.  It has to
-%% go at the end of the manuscript.
-%\allauthors
-
-%% Include this line if you are using the \added, \replaced, \deleted
-%% commands to see a summary list of all changes at the end of the article.
-%\listofchanges
-
-\appendix
-
-\section{Modelling the Milky Way and GSE at $z=2$}
-
-Our merger simulations are built upon reasonable models of both the Milky Way
-and GSE at $z\sim2$. Much is uncertain about the properties of the Milky Way and
-GSE at these redshifts.  We describe the motivation for the choices made in
-constructing these models.
-
-\subsection{The Milky Way}
-We adopt a \citet{1990ApJ...356..359H} profile for our dark matter halo. For its
-structural parameters, we follow \citet{2021ApJ...923...92N} and set its mass
-and scale length to be $5\times10^{11}\,\Msun$ and $40.4\,\kpc$, respectively.
-This matches a \citet{1996ApJ...462..563N} profile with
-$R_{200}=129\,\textrm{kpc}$ and concentration $c_{200}=3.8$
-(\textcolor{red}{check this}).
-
-Milky Way-progenitor galaxies have been observed up to $z=?$ with well-formed
-disks, and more massive galaxies have dynamically cold disks up to $z\sim6$. We
-therefore assume the thick disk is settled and in place at $z=2$. We use the
-structural parameters of the thick disk from . It is presently unclear if before
-the GSE merger the Milky Way disk was already thickened, or if it was thickened
-by the merger. Some simulations indicate that only prograde mergers efficiently
-thicken disks (\textcolor{red}{check and cite}). For this work, we assume the
-disk is already thick.
-
-For the bulge, we assume the present day classical bulge was already in place at
-$z=2$. Measurements of the structural parameters of the classical bulge are
-uncertain due to contamination by the boxy peanut bulge generated by the bar
-(\textcolor{red}{cite}). Some even argue that the classical bulge does not exist
-(\textcolor{red}{cite}). Nonetheless, we assume the bulge properties from
-\textcolor{red}{Bland Hawthorn, but check}. Specifically, we assume a Hernquist
-bulge with $M_{\textrm{bulge}}=?$ and $a=?$.
-
-We assume a gas disk with an exponential surface density profile and scale
-length matched to the stellar disk. The vertical profile is set by the condition
-of gravito-hydrostatic equilibrium as described in (\textcolor{red}{Springel}).
-Varying the gas fraction of the disk strongly influences the SFR of the galaxy.
-We therefore varied the gas fraction of the disk until we reached a target
-SFR.\footnote{Note that when we varied the gas fraction of the disk, we kept the
-mass (and scale length) of the stellar disk constant. Therefore, the total mass
-of the disk changes as we vary the gas fraction.} \textcolor{red}{People} argue
-that in order for the thick disk to have formed thick, the SFR of the disk at
-$z\sim2$ needed to be $\sim15\,\Msun/\yr$. It is not necessary for the disk to
-be thick at $z\sim2$, so we acknowledge this is an upper limit on the SFR. We
-adopt an initial gas fraction of $0.7$ which results in an average SFR of
-$\sim16\,\Msun/\yr$.
-
-Finally, we note that the present day Milk Way has a well-formed bar. It is
-expected to have formed within a few Gyr of the GSE merger, so it is unclear if
-the bar formed before, as a result of, or after the merger. This is not a focus
-of the current work. The presence of a classical bulge and the disk being
-dynamically hot is sufficient for the disk to be stable against bar
-instabilities.
-
-\section{Cause of Suppressed Star Formation}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{SFR_Mgas_tdep.pdf}
-  \caption{\textbf{The suppression of star formation in the bimodal simulation is associated with both a reduction in gas mass as well as an increase in the depletion time.} The drop in star formation (blue line) at $\sim2.5-3\,\Gyr$ is associated with both a reduction in the total gas mass (red line) as well as an increase in the depletion time (green line).
-This shows that the SFR suppression is a result of both less gas mass and more inefficient star formation.
-\red{Should this only include the bimodal?
-Also, move to appendix?}}
-  \label{fig:SFR_Mgas_tdep}
-\end{figure*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=242.26653pt]{MdotBH_rsep.pdf}
-  \caption{\textbf{The bimodal merger is associated with high accretion rates onto the central SMBH.} Around the time of each pericentric passage, and slightly after, the accretion rate (blue line) becomes very high.
-Here, it is shown as a fraction of the Eddington accretion rate.
-During the merger, the accretion rate reaches as high as Eddington at some times, but is always above $10\%$.
-The orbital separation between the central and satellite is shown in the orange line.}
-  \label{fig:MdotBH_rsep}
-\end{figure}
-
-\end{document}
-
-% End of file `sample631.tex'.
-
-% Ness 2019

### 2024-04-21 paper/methods.tex
Split doc across multiple files

--- 2024-04-21 paper/ms.tex
@@
-\documentclass[linenumbers, twocolumn]{aastex631}
+\section{Methods}\label{sec:methods}
+\subsection{Simulation Setup}\label{ssec:setup}
+Our goal in setting up the simulations in this work is not an attempt at matching any Milky Way observable in any detail.
+Our aim is to construct a setup resembling the merger between the Milky Way and GSE at $z\sim2$.
+However, there are great uncertainities associated with the state of the Milky Way and of GSE at this time.
+In Appendix~\ref{app:ics}, we discuss in more detail the choices made in tuning our setup to arrive at a system which is reasonably useful for understanding the Galaxy.
 
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{newtxtext,newtxmath}
-\usepackage{hyperref}
-\usepackage{gensymb}
+Here, we provide an overview of some salient details of our setup.
+The interested reader is referred to Appendix~\ref{app:ics} for more details.
+In isolation, each galaxy is a compound halo setup, with a Hernquist dark matter halo and a gaseous halo with a $\beta$-profile.
+The dark matter halo is initialized to be in gravitational equilibrium with the total potential.
+The gaseous halo is in gravito-hydrostatic equilibrium, where the temperature is allowed to vary as a function of radius.
+The azimuthal velocity of the gaseous halo is given as a fraction of the circular velocity.
+There is no initial stellar disk or bulge, and the gaseous halo is initially metal-free.
+All star particles and metals are formed self-consistently.
+Both the central and satellite galaxies are setup in this way.
 
-\newcommand{\vdag}{(v)^\dagger}
-\newcommand\aastex{AAS\TeX}
-\newcommand\latex{La\TeX}
-
-\newcommand{\Msun}{\ensuremath{M_{\odot}}}
-\newcommand{\Gyr}{\ensuremath{\textrm{Gyr}}}
-\newcommand{\Myr}{\ensuremath{\textrm{Myr}}}
-\newcommand{\yr}{\ensuremath{\textrm{yr}}}
-\newcommand{\kpc}{\ensuremath{\textrm{kpc}}}
-\newcommand{\pc}{\ensuremath{\textrm{pc}}}
-\newcommand{\tocite}{\textcolor{blue}{cite}}
-\newcommand{\FeH}{\ensuremath{[\textrm{Fe}/\textrm{H}]}}
-\newcommand{\MgFe}{\ensuremath{[\textrm{Mg}/\textrm{Fe}]}}
-\newcommand{\alphaFe}{\ensuremath{[\alpha/\textrm{Fe}]}}
-\newcommand{\tform}{\ensuremath{t_{\textrm{form}}}}
-\newcommand{\dex}{\ensuremath{\textrm{dex}}}
-
-\newcommand{\red}[1]{\textcolor{red}{#1}}
-
-%% Reintroduced the \received and \accepted commands from AASTeX v5.2
-% \received{March 1, 2021}
-% \revised{April 1, 2021}
-%\accepted{\today}
-
-\shorttitle{The Milky Way's Phoenix Phase}
-\shortauthors{Beane et al.}
-
-\graphicspath{{./}{fig/}}
-
-\begin{document}
-
-\title{Rising from the Ashes: How the Milky Way Got Its Scars}
-
-\author{Angus Beane}
-\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
-
-\author{Lars Hernquist}
-\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
-
-\author{et al}
-
-%% Mark off the abstract in the ``abstract'' environment. 
-\begin{abstract}
-  The nuclear abundance distribution of stars encodes the history of the gas-phase abundance in the Milky Way.
-Without a large, unbiased sample of stellar ages, the exact timing and nature of this history must be \textit{inferred} from the abundances.
-In the two-dimensional plane of \alphaFe-\FeH, it is now clear that two separate populations exist - the low-$\alpha$ and high-$\alpha$ sequences.
-A restatement of this fact is that the distribution of \alphaFe{} is bimodal at a fixed Fe.
-Structure in the nuclear abundance distribution can arise from many processes - proposals include radial migration, high-redshift clump formation, and various effects associated with galaxy mergers, among others.
-In this work, we demonstrate another possible avenue for structure formation with clear observational predictions.
-We propose that the Galaxy underwent a starburst followed by a brief (hundreds of Myr) quiescent phase.
-A natural consequence of this quiescent phase is that stars in the valley of the bimodality do not form because: (1) the absence of enrichment from high-mass stars leads to a rapid reduction in \alphaFe{}, and (2) any time the gas spends in the abundance valley is deemphasized in the present day distribution because the star formation rate is lower.
-With a set of idealized merger simulations, we demonstrate the feasibility of this proposal.
-The starburst and quiescent phase can result from a merger, but it is not a necessary component of the theory.
-This ``phoenix hypothesis'' predicts a gap in stellar ages at a fixed \FeH{} and that stars which form directly after this gap would have lower \alphaFe{} than stars which form slightly later.
-\end{abstract}
-
-%% Keywords should appear after the \end{abstract} command. 
-%% The AAS Journals now uses Unified Astronomy Thesaurus concepts:
-%% https://astrothesaurus.org
-%% You will be asked to selected these concepts during the submission process
-%% but this old "keyword" functionality is maintained in case authors want
-%% to include these concepts in their preprints.
-\keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of 
-astronomy(1868) --- Interdisciplinary astronomy(804)}
-
-\section{Introduction} \label{sec:intro}
-Elements heavier than hydrogen are produced through nuclear fusion.
-After Big Bang Nucleosynthesis, this only occurs in compact objects.
-The distribution of elemental abundances in the gas-phase of a galaxy is determined by a complicated combination of physical processes - stellar evolution and supernovae, gas accretion, galaxy mergers, gas outflows from stellar and AGN feedback, metal mixing and diffusion, etc.
-
-By necessity, stars inherit the constituitive properties of the gas cloud from which they formed.
-Moreover, the surface abundance of stars do not change over time.\footnote{For the most part.} We therefore have the unique opportunity to examine the historical record of the gas-phase abundance of a galaxy by way of the distribution of the surface abundances of stars.
-Because the processes which give rise to this distribution are complex, there is almost certainly some structure in this distribution for every galaxy.
-However, it has only been definitively measured in the Milky Way.
-
-The distribution of elemental abundances is a high dimensional space (\red{e.g.
-up to 8 billion elements by XYZ}).
-However, this space is highly degenerate, and so the effective number of dimensions is much smaller - even possibly compressed to just \FeH and age \citep{2019ApJ...883..177N}.
-
-Two elements in particular have received particular interest - iron and $\alpha$-elements (elements produced through the $\alpha$-process, typically tracked with just Mg).
-Type Ia and Type II supernovae are the main contributors of elemental enrichment.
-Iron is broadly produced in both types, and so its abundance is a proxy for the total metallicity of a star.
-$\alpha$-elements, on the other hand, are mainly produced in Type II supernovae.
-The ratio of $\alpha$-elements to iron is then a measure of the relative contributions of Type Ia and II to the enrichment of a parcel of gas.
-It has therefore become common to compress the high-dimensional abundance space to the two dimensional \FeH-\alphaFe plane.
-
-In this plane, it is now well-established that a significant bimodality exists in the Milky Way \red{cite a boatload}.
-
-Elemental enrichment is accounted for in modern galaxy formation models, though the validity of the yield tables is suspect.
-It is not known if the yields (i.e., the amount of metals produced by the SN) used in such models are accurate.
-This issue is further compounded by the fact that the mixing of metals is unresolved and is sensitive to numerical choices (e.g., Eulerian codes being generally more diffusive than Lagrangian).
-To make matters even worse, the inflows and outflows of gas from galaxies is sensitive to the choices of the feedback model, which has a strong impact on a galaxy's elemental history.
-
-The last\footnote{i.e., not ongoing} significant merger was between the
-proto-Milky Way disk and the {\em Gaia}-Sausage-Enceladus (GSE)
-(\textcolor{red}{spell check}) satellite galaxy. The stellar debris from this
-merger constitutes $\sim50\%$ \textcolor{red}{check} of the inner ($r<?\,\kpc$)
-stellar halo. It may have also led to a tilted, triaxial dark matter halo
-(\textcolor{red}{cite}).
-
-The GSE merger is often invoked (\textcolor{red}{cite}) to explain the observed
-bimodality in the \textcolor{red}{alpha iron} abundance plane
-(\textcolor{red}{cite}). Because GSE-mass galaxies are expected to have a lower
-star formation efficiency than proto-Milky Way-mass galaxies
-(\textcolor{red}{cite}), the gas from GSE should be relatively metal poor. The
-gas from GSE thus dilutes the gas in the proto-Milky Way, ``resetting'' the
-chemical abundance of the Milky Way.
-
-However, it has also been claimed that the \textcolor{red}{alpha iron}
-bimodality can be explained through secular processes. \textcolor{red}{Sentence
-explaining the basic concept.} The argument is not that the GSE merger did not
-happen, but rather that it is not {\it necessary} and might not even be {\it
-sufficient} to explain the bimodality. Ongoing work to detect the bimodality in
-external galaxies may shed further light on the topic (\textcolor{red}{cite}).
-
-Investigating GSE-like mergers in cosmological simulations is a rich and active
-area of research. Many mergers believed to be similar to the GSE merger have
-been identified in the literature (\textcolor{red}{cite}). \textcolor{red}{Blah
-blah argue blah blah. And also blah blah argues blah blah.}
-
-While much has been learned from GSE-like mergers in cosmological simulations,
-they are not conducive to controlled experiments. It is possible to change the
-mass of satellites through genetic modification (\textcolor{red}{Pontzen}), and
-the GSE analog can be removed entirely (\textcolor{red}{Cooke cite}). However,
-to our knowledge, no method has been applied to change the orbital parameters of
-such a merger. It is also somehwat unclear if the circumgalactic media of
-proto-Milky Way mass galaxies at $z\sim2$ are properly simulated.
-
-In this work, we present hydrodynamic simulations of a controlled merger between
-a GSE analog and the $z\sim2$ proto-Milky Way.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{figure1.pdf}
-  \caption{\textbf{The abundance bimodality seen in the Milky Way can be reproduced in some idealized merger simulations.} In the upper panels, we show the distribution of stars in the \MgFe-\FeH plane.
-The left panel shows the observed distribution in the Milky Way from ASPCAP \red{cite}, while the right two panels show two idealized merger simulations.
-The idealized merger simulations are nearly identical, except that the bimodal simulation has a starting radius of $129\,\kpc$, while the unimodal simulation has a starting radius of $142\,\kpc$.
-We emphasize that the labels ``unimodal'' and ``bimodal'' are of the \textit{outcome} of the simulation, and do not reflect a particular choice in the setup.
-The bottom panels show the distribution of \MgFe at fixed \FeH.
-The colors indicate the fixed \FeH values, which are $-0.5$, $-0.375$, $-0.25$, and $0.25$.
-The Milky Way (left panels) exhibits a strong bimodal distribution of \MgFe at various \FeH.
-The idealized merger simulation marked as bimodal (center panels) also exhibits a bimodal distribution of \MgFe, though the structure is not as strongly defined.
-The idealized merger simulation marked as unimodal exhibits only weak structure, if any at all.}
-  \label{fig:fig1}
-\end{figure*}
-
-\section{Methods}\label{sec:methods}
-
-\subsection{Gaseous Halos}\label{ssec:gashalo}
-
-The nature of the circumgalactic media of local galaxies remains largely
-uncertain. It is unclear whether the constraints we have on the local universe
-apply to the circumgalactic media of $z\sim2$ galaxies. Nonetheless, we persist.
-
-We assume the CGM of the Milky Way and GSE can be modelled using a $\beta$ profile,
-\begin{equation}
-  \rho(r) = \rho_0 \left( 1 + \left(\frac{r}{r_c}\right)^2 \right)^{-\frac{3}{2}\beta}\textrm{.}
-\end{equation}
-However, a $\beta$-profile has been shown to be a reasonable fit to the density
-profile of galaxy clusters and of the $L_{*}$ galaxy NGC 3221. Whether or not
-such a profile extends to lower mass galaxies at $z~2$ is unclear, but to our
-knowledge there is no better motivation for another profile.
-
-Our construction of the Milky Way and GSE CGM follows
-\citet{2023MNRAS.tmp.2070B}. In particular, we set $\beta=2/3$ and $r_c=0.22
-r_s$, where $r_s$ is the scale length of the dark matter halo. For the Milky Way
-and GSE, $r_c=9$, $6.5\,\textrm{kpc}$, respectively. For the present study we
-keep $\beta$ and $r_c$ fixed and instead vary the central density $\rho_0$. Our
-fiducial values are $9.61\times10^{-5}$ and $7.57\times10^{-5}\,\Msun/\pc^3$ for
-the Milky Way and GSE, respectively.
-
-A useful metric for assessing the central density is by the universal baryon
-fraction $f_{\textrm{B}}$ -- i.e., the ratio between the mass in baryons to the
-mass in dark matter within $R_{200}$ as compared to the mean ratio of the
-universe.\footnote{To be explicit,
-$f_{\textrm{B}}=(M_{\textrm{b}}/M_{\textrm{c}})/(\Omega_{\textrm{b}}/\Omega_{\textrm{c}})$,
-where $M_{\textrm{b}}$ and $M_{\textrm{c}}$ are the mass of baryons and cold
-dark matter within $R_{200}$, and $\Omega_{\textrm{b}}$ and
-$\Omega_{\textrm{c}}$ are the mean baryon and cold dark matter densities of the
-universe.} For our fiducial central densities, this value is $1.07$ and $0.28$
-for the Milky Way and GSE respectively using the universal values from
-\cite{2014AA...571A..16P}. An early argument by
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{before_after.pdf}
-  \caption{\textbf{The high-$\alpha$ sequence forms before the merger, the low-$\alpha$ sequence forms after the merger.} This plot shows the sequence of events leading to the build-up of the low- and high-$\alpha$ sequences for our fiducial bimodal simulation.
-We have separated the high- and low-$\alpha$ sequences by a dashed line at $-0.1\FeH + 0.31$, which was chosen by eye to lie in the trough.
-The left panel shows all star particles in our solar neighborhood cut.
-The middle left panel shows the star particles that form before the merger ($\tform < 1.5\,\Gyr$), which form a weak sequence of star particles at the lowest \FeH and highest \MgFe.
-The middle right panel shows the star particles that form during the merger ($1.5\,\Gyr < \tform < 2.5\,\Gyr$).
-These star particless form the portion of the high-$\alpha$ sequence closest to the trough, and the density of star particless is higher than those that form before.
-The middle right panel shows the star particles which form after the merger ($\tform > 2.5\,\Gyr$).
-These star particles form almost entirely below the trough.}
-  \label{fig:before_after}
-\end{figure*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{before_after_sfh.pdf}
-  \caption{\textbf{At fixed metallicity, the low- and high-$\alpha$ sequence are cleanly separated in time, with an intervening quiescent period.} Here we show the star formation history of the high- and low-$\alpha$ sequences.
-The blue (low-$\alpha$) and orange (high-$\alpha$) histograms correspond to the dashed line cut made in the \MgFe-\FeH plane in Figure~\ref{fig:before_after}, at a fixed metallicity of $\FeH\sim0$.
-One can see that there is a nearly perfect separation in time between the formation of the high-$\alpha$ and low-$\alpha$ sequence, except for a brief overlap which can be attributed to the inadequacy of the linear cut model of the two sequences.
-Separating the formation periods lies a quiescent period with a duration of $\sim300\,\Myr$.
-\red{make sfr per dex}.}
-  \label{fig:before_after_sfh}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{before_after_sfh_by_iron.pdf}
-  \caption{\textbf{The timing of the quiescent period which divides the high- and low-$\alpha$ sequences is metallicity dependent.} The star formation history of stars at various fixed metallicities ($\FeH\sim0$, $-0.25$, and $-0.5\,\textrm{dex}$).
-As in Figure~\ref{fig:before_after_sfh}, there is a quiescent period period which separates the formation of the low- and high-$\alpha$ sequence \red{maybe a better way to show this?}.
-However, one can see that the timing of the quiescent period is metallicity-dependent.
-It occurs earlier at lower metallicity, by $\sim300\,\Myr$ for the metallicities shown in this plot.
-\red{make sfr per dex}.}
-  \label{fig:before_after_sfh_by_iron}
-\end{figure}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{SFR_alpha.pdf}
-  \caption{\textbf{A global suppression of star formation is associcated with a decrease in \MgFe{}, which is seen in the bimodal simulation but not in the unimodal simulation.} Here, we show both the SFR of the central galaxy ($r<15\,\kpc$) and the median \MgFe{} for gas at $2\,\kpc<r<5\,\kpc$ at a fixed \FeH{} bin centered on $-0.2$ with width $0.02\,\dex$.
-The left panel shows the bimodal simulation while the right panel shows the unimodal simulation.
-The time of the merger (i.e., the second pericenter) is indicated by the vertical dashed line.
-In the bimodal simulation, the star formation is suppressed after the merger.
-This suppression of star formation is associated with a sudden drop in the median \MgFe{} of the gas.
-Neither the suppression of star formation nor the drop in \MgFe{} are seen in the unimodal simulation.}
-  \label{fig:SFR_alpha}
-\end{figure*}
-
-\bibliography{ref}{}
-\bibliographystyle{aasjournal}
-
-%% This command is needed to show the entire author+affiliation list when
-%% the collaboration and author truncation commands are used.  It has to
-%% go at the end of the manuscript.
-%\allauthors
-
-%% Include this line if you are using the \added, \replaced, \deleted
-%% commands to see a summary list of all changes at the end of the article.
-%\listofchanges
-
-\appendix
-
-\section{Modelling the Milky Way and GSE at $z=2$}
-
-Our merger simulations are built upon reasonable models of both the Milky Way
-and GSE at $z\sim2$. Much is uncertain about the properties of the Milky Way and
-GSE at these redshifts.  We describe the motivation for the choices made in
-constructing these models.
-
-\subsection{The Milky Way}
-We adopt a \citet{1990ApJ...356..359H} profile for our dark matter halo. For its
-structural parameters, we follow \citet{2021ApJ...923...92N} and set its mass
-and scale length to be $5\times10^{11}\,\Msun$ and $40.4\,\kpc$, respectively.
-This matches a \citet{1996ApJ...462..563N} profile with
-$R_{200}=129\,\textrm{kpc}$ and concentration $c_{200}=3.8$
-(\textcolor{red}{check this}).
-
-Milky Way-progenitor galaxies have been observed up to $z=?$ with well-formed
-disks, and more massive galaxies have dynamically cold disks up to $z\sim6$. We
-therefore assume the thick disk is settled and in place at $z=2$. We use the
-structural parameters of the thick disk from . It is presently unclear if before
-the GSE merger the Milky Way disk was already thickened, or if it was thickened
-by the merger. Some simulations indicate that only prograde mergers efficiently
-thicken disks (\textcolor{red}{check and cite}). For this work, we assume the
-disk is already thick.
-
-For the bulge, we assume the present day classical bulge was already in place at
-$z=2$. Measurements of the structural parameters of the classical bulge are
-uncertain due to contamination by the boxy peanut bulge generated by the bar
-(\textcolor{red}{cite}). Some even argue that the classical bulge does not exist
-(\textcolor{red}{cite}). Nonetheless, we assume the bulge properties from
-\textcolor{red}{Bland Hawthorn, but check}. Specifically, we assume a Hernquist
-bulge with $M_{\textrm{bulge}}=?$ and $a=?$.
-
-We assume a gas disk with an exponential surface density profile and scale
-length matched to the stellar disk. The vertical profile is set by the condition
-of gravito-hydrostatic equilibrium as described in (\textcolor{red}{Springel}).
-Varying the gas fraction of the disk strongly influences the SFR of the galaxy.
-We therefore varied the gas fraction of the disk until we reached a target
-SFR.\footnote{Note that when we varied the gas fraction of the disk, we kept the
-mass (and scale length) of the stellar disk constant. Therefore, the total mass
-of the disk changes as we vary the gas fraction.} \textcolor{red}{People} argue
-that in order for the thick disk to have formed thick, the SFR of the disk at
-$z\sim2$ needed to be $\sim15\,\Msun/\yr$. It is not necessary for the disk to
-be thick at $z\sim2$, so we acknowledge this is an upper limit on the SFR. We
-adopt an initial gas fraction of $0.7$ which results in an average SFR of
-$\sim16\,\Msun/\yr$.
-
-Finally, we note that the present day Milk Way has a well-formed bar. It is
-expected to have formed within a few Gyr of the GSE merger, so it is unclear if
-the bar formed before, as a result of, or after the merger. This is not a focus
-of the current work. The presence of a classical bulge and the disk being
-dynamically hot is sufficient for the disk to be stable against bar
-instabilities.
-
-\section{Cause of Suppressed Star Formation}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{SFR_Mgas_tdep.pdf}
-  \caption{\textbf{The suppression of star formation in the bimodal simulation is associated with both a reduction in gas mass as well as an increase in the depletion time.} The drop in star formation (blue line) at $\sim2.5-3\,\Gyr$ is associated with both a reduction in the total gas mass (red line) as well as an increase in the depletion time (green line).
-This shows that the SFR suppression is a result of both less gas mass and more inefficient star formation.
-\red{Should this only include the bimodal?
-Also, move to appendix?}}
-  \label{fig:SFR_Mgas_tdep}
-\end{figure*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=242.26653pt]{MdotBH_rsep.pdf}
-  \caption{\textbf{The bimodal merger is associated with high accretion rates onto the central SMBH.} Around the time of each pericentric passage, and slightly after, the accretion rate (blue line) becomes very high.
-Here, it is shown as a fraction of the Eddington accretion rate.
-During the merger, the accretion rate reaches as high as Eddington at some times, but is always above $10\%$.
-The orbital separation between the central and satellite is shown in the orange line.}
-  \label{fig:MdotBH_rsep}
-\end{figure}
-
-\end{document}
-
-% End of file `sample631.tex'.
-
-% Ness 2019
+In order to combine the galaxies, we follow \citet{2021ApJ...923...92N}, and place the satellite galaxy on a retrograde orbit.
+In the fiducial simulation, the satellite is placed at the virial radius with the virial velocity with a circularity of $0.5$.
+In order to test minor changes to the orbit, we ran a grid of simulations with $\pm10\%$ in each the starting radius and velocity, and $\pm0.1$ in the circularity, for a total of $27$ simulations.

### 2024-04-21 paper/ms.tex
Split doc across multiple files

--- 2024-04-21 paper/ms.tex
@@
 
-%% Reintroduced the \received and \accepted commands from AASTeX v5.2
 % \received{March 1, 2021}
@@
 
-%% Mark off the abstract in the ``abstract'' environment. 
 \begin{abstract}
@@
 
-%% Keywords should appear after the \end{abstract} command. 
-%% The AAS Journals now uses Unified Astronomy Thesaurus concepts:
-%% https://astrothesaurus.org
-%% You will be asked to selected these concepts during the submission process
-%% but this old "keyword" functionality is maintained in case authors want
-%% to include these concepts in their preprints.
 \keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of 
@@
 
-\section{Introduction} \label{sec:intro}
-Elements heavier than hydrogen are produced through nuclear fusion.
-After Big Bang Nucleosynthesis, this only occurs in compact objects.
-The distribution of elemental abundances in the gas-phase of a galaxy is determined by a complicated combination of physical processes - stellar evolution and supernovae, gas accretion, galaxy mergers, gas outflows from stellar and AGN feedback, metal mixing and diffusion, etc.
+\input{introduction.tex}
 
-By necessity, stars inherit the constituitive properties of the gas cloud from which they formed.
-Moreover, the surface abundance of stars do not change over time.\footnote{For the most part.} We therefore have the unique opportunity to examine the historical record of the gas-phase abundance of a galaxy by way of the distribution of the surface abundances of stars.
-Because the processes which give rise to this distribution are complex, there is almost certainly some structure in this distribution for every galaxy.
-However, it has only been definitively measured in the Milky Way.
+\input{methods.tex}
 
-The distribution of elemental abundances is a high dimensional space (\red{e.g.
-up to 8 billion elements by XYZ}).
-However, this space is highly degenerate, and so the effective number of dimensions is much smaller - even possibly compressed to just \FeH and age \citep{2019ApJ...883..177N}.
+\input{results.tex}
 
-Two elements in particular have received particular interest - iron and $\alpha$-elements (elements produced through the $\alpha$-process, typically tracked with just Mg).
-Type Ia and Type II supernovae are the main contributors of elemental enrichment.
-Iron is broadly produced in both types, and so its abundance is a proxy for the total metallicity of a star.
-$\alpha$-elements, on the other hand, are mainly produced in Type II supernovae.
-The ratio of $\alpha$-elements to iron is then a measure of the relative contributions of Type Ia and II to the enrichment of a parcel of gas.
-It has therefore become common to compress the high-dimensional abundance space to the two dimensional \FeH-\alphaFe plane.
+\input{discussion.tex}
 
-In this plane, it is now well-established that a significant bimodality exists in the Milky Way \red{cite a boatload}.
-
-Elemental enrichment is accounted for in modern galaxy formation models, though the validity of the yield tables is suspect.
-It is not known if the yields (i.e., the amount of metals produced by the SN) used in such models are accurate.
-This issue is further compounded by the fact that the mixing of metals is unresolved and is sensitive to numerical choices (e.g., Eulerian codes being generally more diffusive than Lagrangian).
-To make matters even worse, the inflows and outflows of gas from galaxies is sensitive to the choices of the feedback model, which has a strong impact on a galaxy's elemental history.
-
-The last\footnote{i.e., not ongoing} significant merger was between the
-proto-Milky Way disk and the {\em Gaia}-Sausage-Enceladus (GSE)
-(\textcolor{red}{spell check}) satellite galaxy. The stellar debris from this
-merger constitutes $\sim50\%$ \textcolor{red}{check} of the inner ($r<?\,\kpc$)
-stellar halo. It may have also led to a tilted, triaxial dark matter halo
-(\textcolor{red}{cite}).
-
-The GSE merger is often invoked (\textcolor{red}{cite}) to explain the observed
-bimodality in the \textcolor{red}{alpha iron} abundance plane
-(\textcolor{red}{cite}). Because GSE-mass galaxies are expected to have a lower
-star formation efficiency than proto-Milky Way-mass galaxies
-(\textcolor{red}{cite}), the gas from GSE should be relatively metal poor. The
-gas from GSE thus dilutes the gas in the proto-Milky Way, ``resetting'' the
-chemical abundance of the Milky Way.
-
-However, it has also been claimed that the \textcolor{red}{alpha iron}
-bimodality can be explained through secular processes. \textcolor{red}{Sentence
-explaining the basic concept.} The argument is not that the GSE merger did not
-happen, but rather that it is not {\it necessary} and might not even be {\it
-sufficient} to explain the bimodality. Ongoing work to detect the bimodality in
-external galaxies may shed further light on the topic (\textcolor{red}{cite}).
-
-Investigating GSE-like mergers in cosmological simulations is a rich and active
-area of research. Many mergers believed to be similar to the GSE merger have
-been identified in the literature (\textcolor{red}{cite}). \textcolor{red}{Blah
-blah argue blah blah. And also blah blah argues blah blah.}
-
-While much has been learned from GSE-like mergers in cosmological simulations,
-they are not conducive to controlled experiments. It is possible to change the
-mass of satellites through genetic modification (\textcolor{red}{Pontzen}), and
-the GSE analog can be removed entirely (\textcolor{red}{Cooke cite}). However,
-to our knowledge, no method has been applied to change the orbital parameters of
-such a merger. It is also somehwat unclear if the circumgalactic media of
-proto-Milky Way mass galaxies at $z\sim2$ are properly simulated.
-
-In this work, we present hydrodynamic simulations of a controlled merger between
-a GSE analog and the $z\sim2$ proto-Milky Way.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{figure1.pdf}
-  \caption{\textbf{The abundance bimodality seen in the Milky Way can be reproduced in some idealized merger simulations.} In the upper panels, we show the distribution of stars in the \MgFe-\FeH plane.
-The left panel shows the observed distribution in the Milky Way from ASPCAP \red{cite}, while the right two panels show two idealized merger simulations.
-The idealized merger simulations are nearly identical, except that the bimodal simulation has a starting radius of $129\,\kpc$, while the unimodal simulation has a starting radius of $142\,\kpc$.
-We emphasize that the labels ``unimodal'' and ``bimodal'' are of the \textit{outcome} of the simulation, and do not reflect a particular choice in the setup.
-The bottom panels show the distribution of \MgFe at fixed \FeH.
-The colors indicate the fixed \FeH values, which are $-0.5$, $-0.375$, $-0.25$, and $0.25$.
-The Milky Way (left panels) exhibits a strong bimodal distribution of \MgFe at various \FeH.
-The idealized merger simulation marked as bimodal (center panels) also exhibits a bimodal distribution of \MgFe, though the structure is not as strongly defined.
-The idealized merger simulation marked as unimodal exhibits only weak structure, if any at all.}
-  \label{fig:fig1}
-\end{figure*}
-
-\section{Methods}\label{sec:methods}
-
-\subsection{Gaseous Halos}\label{ssec:gashalo}
-
-The nature of the circumgalactic media of local galaxies remains largely
-uncertain. It is unclear whether the constraints we have on the local universe
-apply to the circumgalactic media of $z\sim2$ galaxies. Nonetheless, we persist.
-
-We assume the CGM of the Milky Way and GSE can be modelled using a $\beta$ profile,
-\begin{equation}
-  \rho(r) = \rho_0 \left( 1 + \left(\frac{r}{r_c}\right)^2 \right)^{-\frac{3}{2}\beta}\textrm{.}
-\end{equation}
-However, a $\beta$-profile has been shown to be a reasonable fit to the density
-profile of galaxy clusters and of the $L_{*}$ galaxy NGC 3221. Whether or not
-such a profile extends to lower mass galaxies at $z~2$ is unclear, but to our
-knowledge there is no better motivation for another profile.
-
-Our construction of the Milky Way and GSE CGM follows
-\citet{2023MNRAS.tmp.2070B}. In particular, we set $\beta=2/3$ and $r_c=0.22
-r_s$, where $r_s$ is the scale length of the dark matter halo. For the Milky Way
-and GSE, $r_c=9$, $6.5\,\textrm{kpc}$, respectively. For the present study we
-keep $\beta$ and $r_c$ fixed and instead vary the central density $\rho_0$. Our
-fiducial values are $9.61\times10^{-5}$ and $7.57\times10^{-5}\,\Msun/\pc^3$ for
-the Milky Way and GSE, respectively.
-
-A useful metric for assessing the central density is by the universal baryon
-fraction $f_{\textrm{B}}$ -- i.e., the ratio between the mass in baryons to the
-mass in dark matter within $R_{200}$ as compared to the mean ratio of the
-universe.\footnote{To be explicit,
-$f_{\textrm{B}}=(M_{\textrm{b}}/M_{\textrm{c}})/(\Omega_{\textrm{b}}/\Omega_{\textrm{c}})$,
-where $M_{\textrm{b}}$ and $M_{\textrm{c}}$ are the mass of baryons and cold
-dark matter within $R_{200}$, and $\Omega_{\textrm{b}}$ and
-$\Omega_{\textrm{c}}$ are the mean baryon and cold dark matter densities of the
-universe.} For our fiducial central densities, this value is $1.07$ and $0.28$
-for the Milky Way and GSE respectively using the universal values from
-\cite{2014AA...571A..16P}. An early argument by
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{before_after.pdf}
-  \caption{\textbf{The high-$\alpha$ sequence forms before the merger, the low-$\alpha$ sequence forms after the merger.} This plot shows the sequence of events leading to the build-up of the low- and high-$\alpha$ sequences for our fiducial bimodal simulation.
-We have separated the high- and low-$\alpha$ sequences by a dashed line at $-0.1\FeH + 0.31$, which was chosen by eye to lie in the trough.
-The left panel shows all star particles in our solar neighborhood cut.
-The middle left panel shows the star particles that form before the merger ($\tform < 1.5\,\Gyr$), which form a weak sequence of star particles at the lowest \FeH and highest \MgFe.
-The middle right panel shows the star particles that form during the merger ($1.5\,\Gyr < \tform < 2.5\,\Gyr$).
-These star particless form the portion of the high-$\alpha$ sequence closest to the trough, and the density of star particless is higher than those that form before.
-The middle right panel shows the star particles which form after the merger ($\tform > 2.5\,\Gyr$).
-These star particles form almost entirely below the trough.}
-  \label{fig:before_after}
-\end{figure*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{before_after_sfh.pdf}
-  \caption{\textbf{At fixed metallicity, the low- and high-$\alpha$ sequence are cleanly separated in time, with an intervening quiescent period.} Here we show the star formation history of the high- and low-$\alpha$ sequences.
-The blue (low-$\alpha$) and orange (high-$\alpha$) histograms correspond to the dashed line cut made in the \MgFe-\FeH plane in Figure~\ref{fig:before_after}, at a fixed metallicity of $\FeH\sim0$.
-One can see that there is a nearly perfect separation in time between the formation of the high-$\alpha$ and low-$\alpha$ sequence, except for a brief overlap which can be attributed to the inadequacy of the linear cut model of the two sequences.
-Separating the formation periods lies a quiescent period with a duration of $\sim300\,\Myr$.
-\red{make sfr per dex}.}
-  \label{fig:before_after_sfh}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{before_after_sfh_by_iron.pdf}
-  \caption{\textbf{The timing of the quiescent period which divides the high- and low-$\alpha$ sequences is metallicity dependent.} The star formation history of stars at various fixed metallicities ($\FeH\sim0$, $-0.25$, and $-0.5\,\textrm{dex}$).
-As in Figure~\ref{fig:before_after_sfh}, there is a quiescent period period which separates the formation of the low- and high-$\alpha$ sequence \red{maybe a better way to show this?}.
-However, one can see that the timing of the quiescent period is metallicity-dependent.
-It occurs earlier at lower metallicity, by $\sim300\,\Myr$ for the metallicities shown in this plot.
-\red{make sfr per dex}.}
-  \label{fig:before_after_sfh_by_iron}
-\end{figure}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{SFR_alpha.pdf}
-  \caption{\textbf{A global suppression of star formation is associcated with a decrease in \MgFe{}, which is seen in the bimodal simulation but not in the unimodal simulation.} Here, we show both the SFR of the central galaxy ($r<15\,\kpc$) and the median \MgFe{} for gas at $2\,\kpc<r<5\,\kpc$ at a fixed \FeH{} bin centered on $-0.2$ with width $0.02\,\dex$.
-The left panel shows the bimodal simulation while the right panel shows the unimodal simulation.
-The time of the merger (i.e., the second pericenter) is indicated by the vertical dashed line.
-In the bimodal simulation, the star formation is suppressed after the merger.
-This suppression of star formation is associated with a sudden drop in the median \MgFe{} of the gas.
-Neither the suppression of star formation nor the drop in \MgFe{} are seen in the unimodal simulation.}
-  \label{fig:SFR_alpha}
-\end{figure*}
+\input{conclusions.tex}
 
@@
 
-%% This command is needed to show the entire author+affiliation list when
-%% the collaboration and author truncation commands are used.  It has to
-%% go at the end of the manuscript.
-%\allauthors
-
-%% Include this line if you are using the \added, \replaced, \deleted
-%% commands to see a summary list of all changes at the end of the article.
-%\listofchanges
-
-\appendix
-
-\section{Modelling the Milky Way and GSE at $z=2$}
-
-Our merger simulations are built upon reasonable models of both the Milky Way
-and GSE at $z\sim2$. Much is uncertain about the properties of the Milky Way and
-GSE at these redshifts.  We describe the motivation for the choices made in
-constructing these models.
-
-\subsection{The Milky Way}
-We adopt a \citet{1990ApJ...356..359H} profile for our dark matter halo. For its
-structural parameters, we follow \citet{2021ApJ...923...92N} and set its mass
-and scale length to be $5\times10^{11}\,\Msun$ and $40.4\,\kpc$, respectively.
-This matches a \citet{1996ApJ...462..563N} profile with
-$R_{200}=129\,\textrm{kpc}$ and concentration $c_{200}=3.8$
-(\textcolor{red}{check this}).
-
-Milky Way-progenitor galaxies have been observed up to $z=?$ with well-formed
-disks, and more massive galaxies have dynamically cold disks up to $z\sim6$. We
-therefore assume the thick disk is settled and in place at $z=2$. We use the
-structural parameters of the thick disk from . It is presently unclear if before
-the GSE merger the Milky Way disk was already thickened, or if it was thickened
-by the merger. Some simulations indicate that only prograde mergers efficiently
-thicken disks (\textcolor{red}{check and cite}). For this work, we assume the
-disk is already thick.
-
-For the bulge, we assume the present day classical bulge was already in place at
-$z=2$. Measurements of the structural parameters of the classical bulge are
-uncertain due to contamination by the boxy peanut bulge generated by the bar
-(\textcolor{red}{cite}). Some even argue that the classical bulge does not exist
-(\textcolor{red}{cite}). Nonetheless, we assume the bulge properties from
-\textcolor{red}{Bland Hawthorn, but check}. Specifically, we assume a Hernquist
-bulge with $M_{\textrm{bulge}}=?$ and $a=?$.
-
-We assume a gas disk with an exponential surface density profile and scale
-length matched to the stellar disk. The vertical profile is set by the condition
-of gravito-hydrostatic equilibrium as described in (\textcolor{red}{Springel}).
-Varying the gas fraction of the disk strongly influences the SFR of the galaxy.
-We therefore varied the gas fraction of the disk until we reached a target
-SFR.\footnote{Note that when we varied the gas fraction of the disk, we kept the
-mass (and scale length) of the stellar disk constant. Therefore, the total mass
-of the disk changes as we vary the gas fraction.} \textcolor{red}{People} argue
-that in order for the thick disk to have formed thick, the SFR of the disk at
-$z\sim2$ needed to be $\sim15\,\Msun/\yr$. It is not necessary for the disk to
-be thick at $z\sim2$, so we acknowledge this is an upper limit on the SFR. We
-adopt an initial gas fraction of $0.7$ which results in an average SFR of
-$\sim16\,\Msun/\yr$.
-
-Finally, we note that the present day Milk Way has a well-formed bar. It is
-expected to have formed within a few Gyr of the GSE merger, so it is unclear if
-the bar formed before, as a result of, or after the merger. This is not a focus
-of the current work. The presence of a classical bulge and the disk being
-dynamically hot is sufficient for the disk to be stable against bar
-instabilities.
-
-\section{Cause of Suppressed Star Formation}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{SFR_Mgas_tdep.pdf}
-  \caption{\textbf{The suppression of star formation in the bimodal simulation is associated with both a reduction in gas mass as well as an increase in the depletion time.} The drop in star formation (blue line) at $\sim2.5-3\,\Gyr$ is associated with both a reduction in the total gas mass (red line) as well as an increase in the depletion time (green line).
-This shows that the SFR suppression is a result of both less gas mass and more inefficient star formation.
-\red{Should this only include the bimodal?
-Also, move to appendix?}}
-  \label{fig:SFR_Mgas_tdep}
-\end{figure*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=242.26653pt]{MdotBH_rsep.pdf}
-  \caption{\textbf{The bimodal merger is associated with high accretion rates onto the central SMBH.} Around the time of each pericentric passage, and slightly after, the accretion rate (blue line) becomes very high.
-Here, it is shown as a fraction of the Eddington accretion rate.
-During the merger, the accretion rate reaches as high as Eddington at some times, but is always above $10\%$.
-The orbital separation between the central and satellite is shown in the orange line.}
-  \label{fig:MdotBH_rsep}
-\end{figure}
+% \input{appendix.tex}
 
 \end{document}
-
-% End of file `sample631.tex'.
-
-% Ness 2019

### 2024-04-21 paper/results.tex
Split doc across multiple files

\section{Results}\label{sec:results}
\subsection{Abundance Distribution}
In Figure~\ref{fig:fig1}, briefly discussed in the Introduction, we show the abundance distribution of the Milky Way as well as two of our idealized merger simulations. A number of our idealized simulations exhibit either a bimodal or unimodal abundance distribution, and so we have selected two which are representative examples of

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{before_after.pdf}
  \caption{\textbf{The high-$\alpha$ sequence forms before the merger, the low-$\alpha$ sequence forms after the merger.} This plot shows the sequence of events leading to the build-up of the low- and high-$\alpha$ sequences for our fiducial bimodal simulation. We have separated the high- and low-$\alpha$ sequences by a dashed line at $-0.1\FeH + 0.31$, which was chosen by eye to lie in the trough. The left panel shows all star particles in our solar neighborhood cut. The middle left panel shows the star particles that form before the merger ($\tform < 1.5\,\Gyr$), which form a weak sequence of star particles at the lowest \FeH and highest \MgFe. The middle right panel shows the star particles that form during the merger ($1.5\,\Gyr < \tform < 2.5\,\Gyr$). These star particless form the portion of the high-$\alpha$ sequence closest to the trough, and the density of star particless is higher than those that form before. The middle right panel shows the star particles which form after the merger ($\tform > 2.5\,\Gyr$). These star particles form almost entirely below the trough.}
  \label{fig:before_after}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{before_after_sfh.pdf}
  \caption{\textbf{At fixed metallicity, the low- and high-$\alpha$ sequence are cleanly separated in time, with an intervening quiescent period.} Here we show the star formation history of the high- and low-$\alpha$ sequences. The blue (low-$\alpha$) and orange (high-$\alpha$) histograms correspond to the dashed line cut made in the \MgFe-\FeH plane in Figure~\ref{fig:before_after}, at a fixed metallicity of $\FeH\sim0$. One can see that there is a nearly perfect separation in time between the formation of the high-$\alpha$ and low-$\alpha$ sequence, except for a brief overlap which can be attributed to the inadequacy of the linear cut model of the two sequences. Separating the formation periods lies a quiescent period with a duration of $\sim300\,\Myr$. \red{make sfr per dex}.}
  \label{fig:before_after_sfh}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{before_after_sfh_by_iron.pdf}
  \caption{\textbf{The timing of the quiescent period which divides the high- and low-$\alpha$ sequences is metallicity dependent.} The star formation history of stars at various fixed metallicities ($\FeH\sim0$, $-0.25$, and $-0.5\,\textrm{dex}$). As in Figure~\ref{fig:before_after_sfh}, there is a quiescent period period which separates the formation of the low- and high-$\alpha$ sequence \red{maybe a better way to show this?}. However, one can see that the timing of the quiescent period is metallicity-dependent. It occurs earlier at lower metallicity, by $\sim300\,\Myr$ for the metallicities shown in this plot. \red{make sfr per dex}.}
  \label{fig:before_after_sfh_by_iron}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{SFR_alpha.pdf}
  \caption{\textbf{A global suppression of star formation is associcated with a decrease in \MgFe{}, which is seen in the bimodal simulation but not in the unimodal simulation.} Here, we show both the SFR of the central galaxy ($r<15\,\kpc$) and the median \MgFe{} for gas at $2\,\kpc<r<5\,\kpc$ at a fixed \FeH{} bin centered on $-0.2$ with width $0.02\,\dex$. The left panel shows the bimodal simulation while the right panel shows the unimodal simulation. The time of the merger (i.e., the second pericenter) is indicated by the vertical dashed line. In the bimodal simulation, the star formation is suppressed after the merger. This suppression of star formation is associated with a sudden drop in the median \MgFe{} of the gas. Neither the suppression of star formation nor the drop in \MgFe{} are seen in the unimodal simulation.}
  \label{fig:SFR_alpha}
\end{figure*}

### 2024-04-23 paper/ms.tex
Just, a ton of changes

@@
 \usepackage{gensymb}
+\usepackage{enumitem}
 
@@
 \newcommand{\pc}{\ensuremath{\textrm{pc}}}
+\newcommand{\kms}{\ensuremath{\textrm{km}/\textrm{s}}}
 \newcommand{\tocite}{\textcolor{blue}{cite}}
@@
 
-\input{introduction.tex}
+\input{sec/int.tex}
 
-\input{methods.tex}
+\input{sec/met.tex}
 
-\input{results.tex}
+\input{sec/res.tex}
 
-\input{discussion.tex}
+\input{sec/dis.tex}
 
-\input{conclusions.tex}
+\input{sec/con.tex}
+
+\begin{acknowledgements}
+This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}).
+Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
+\end{acknowledgements}
 
@@
 
-% \input{appendix.tex}
+% \input{app.tex}
 

### 2024-04-23 paper/sec/met.tex
Just, a ton of changes

\section{Methods}\label{sec:methods}
\subsection{Simulation Setup}\label{ssec:setup}
Our goal in setting up the simulations in this work is not an attempt at matching any Milky Way observable in any detail. Our aim is to construct a setup resembling the merger between the Milky Way and GSE at $z\sim2$. However, there are great uncertainities associated with the state of the Milky Way and of GSE at this time. In Appendix~\ref{app:ics}, we discuss in more detail the choices made in tuning our setup to arrive at a system which is reasonably useful for understanding the Galaxy.

Here, we provide an overview of some salient details of our setup. The interested reader is referred to Appendix~\ref{app:ics} for more details. In isolation, each galaxy is a compound halo setup, with a Hernquist dark matter halo and a gaseous halo with a $\beta$-profile. The dark matter halo is initialized to be in gravitational equilibrium with the total potential. The gaseous halo is in gravito-hydrostatic equilibrium, where the temperature is allowed to vary as a function of radius. The azimuthal velocity of the gaseous halo is given as a fraction of the circular velocity. There is no initial stellar disk or bulge, and the gaseous halo is initially metal-free. All star particles and metals are formed self-consistently. Both the central and satellite galaxies are setup in this way.

In order to combine the galaxies, we follow \citet{2021ApJ...923...92N}, and place the satellite galaxy on a retrograde orbit. In the fiducial simulation, the satellite is placed at the virial radius ($129\,\kpc$), with the virial velocity ($129\,\kms$), and with a circularity of $0.5$. To test minor changes to the orbit, we ran a grid of simulations with $\pm10\%$ in each the starting radius and velocity, and $\pm0.1$ in the circularity, for a total of $27$ simulations.

Some of the simulations in this orbital grid resulted in bimodal abundance distributions, while some had little to no structure in the abundance distribution plane. We show the abundance plane for all $27$ simulations in Appendix~\ref{app:allsims}, but for the main body of this work we consider two representative simulations in detail. For the bimodal simulation, we chose the simulation with $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$. For the unimodal simulation, the parameters are the same except that $R_0=129\,\kpc$.

\subsection{Observed Abundances}\label{ssec:obs_abund}
Our aim in this work is to demonstrate the feasibility of a mechanism for structure formation in the abundance plane. We are only making a qualitative comparison to data. Therefore, we use the ASPCAP DR17 catalog of stellar abundances (\citet{2016AJ....151..144G}; J.A.~Holtzman et al., in preparation), which is publicly available, well-established, and widely used.

We first make some quality cuts, as well as restricting our sample to dwarfs. We require:
\begin{itemize}[noitemsep]
    \item $\textrm{SNR} > 200$,
    \item $\textrm{VSCATTER} < 1\,\kms$,
    \item STARFLAG not set,
    \item $\varpi/\sigma_{\varpi} > 1$,
    \item $\log{g} < 3.5$,
    \item $\sigma_{\log{g}} < 0.2$,
\end{itemize}
where $\varpi$ is the parallax. We use the parallax, proper motion, and radial velocity from Gaia EDR3 \citep{2016AA...595A...1G, 2021AA...649A...1G, 2021AA...649A...2L, 2021AA...653A.160S}.

We next make a selection on the angular momentum of stars in order to make a ``solar neighborhood'' selection.\footnote{The definition of the solar neighborhood is always changing.} We assume the solar radius and azimuthal velocity are $R_0=8\,\kpc$ and $V_0=220\,\kms$ \red{cite}, and select stars which have $L_z$ within $10\%$ of the solar angular momentum. We further require that $\left|z\right| < 3\,\kpc$.

As is typically done, we use \FeH{} as an indicator of the total metallicity of a star. We use Mg alone as a representative of the $\alpha$-elements, though some authors choose to sum several $\alpha$-elements.

\subsection{Simulation Solar Neighborhood}\label{ssec:solarneigh}
When comparing galaxy simulations to the observed solar neighborhood, some ambiguity arises in how to make a ``solar neighborhood-like'' selection of star particles. Naturally, this selection is dependent on the posed question. In this work, this is the formation of the abundance bimodality. The Sun is known to sit near the end of the thick disk, where the thick and thin disk have comparable surface densities (the ratio of thick-to-thin is $\sim12\%$ \red{cite}). As a result, the abundance bimodality appears most strongly near the Sun -- further inwards the high-$\alpha$ sequence is more dominant and further outwards the high-$\alpha$ sequence vanishes \red{cite}.

We mimic our selection of the solar neighborhood by also making a cut in angular momentum. However, in the simulation, the high-$\alpha$ disk is more compact than in the Galaxy. Therefore, in order to strike a balance between the low-$\alpha$ and high-$\alpha$ disks, we used an angular momentum cut which is $20\%$ that of our assumed solar angular momentum. In particular, we select all star particles with angular momenta within $30\%$ of $0.2\times8\,\kpc\times220\,\kms$ -- as well as requiring $\left| z \right| < 3\,\kpc$.

This choice of angular momentum may seem unrealistic. However, it corresponds to roughly selecting star particles with radii between $2$ and $5\,\kpc$. The half-mass radius of the isolated central galaxy is $\sim2\,\kpc$ after $3\,\Gyr$ of evolution (the formation epoch of the high-$\alpha$ disk). For comparison, the scale-length of the thick disk is $\sim2\,\kpc$, which corresponds to a half-mass radius of $\sim3.36\,\kpc$ for an exponential disk. Our simulated galaxy does form more compactly, which is a justification for our ``solar neighborhood'' to lie at a lower angular momentum.

### 2024-04-29 paper/sec/app.tex
Just, a ton of changes
Paper updates

--- 2024-04-21 paper/appendix.tex
@@
 The core radius is set to $6.5\,\kpc$, which similar to the central does not have a large impact.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{mass_size.pdf}
-  \caption{The mass and size evolution of the central (Milky Way, blue) and satellite (GSE, orange) galaxies.
-The mass is taken to be the stellar mass within twice the half-mass radius, and the size is taken to be the half-mass radius.
-In the upper panel, we also show as a horizontal line the mass of the Milky Way and GSE from the best-fit model of \citet{2021ApJ...923...92N}.
-This comparison is taken to be made at $3\,\Gyr$ (vertical dashed line), our proxy for $z\sim2$.
-A precise match is not attempted given the wide ranging uncertainties.}
-  \label{fig:mass_size}
-\end{figure}
 
@@
 
-\section{Cause of Suppressed Star Formation}
+\section{Cause of Suppressed Star Formation}\label{app:cause_qui}
 

### 2024-04-29 paper/src/dis.tex
Rename sec to src

\section{Discussion}\label{sec:discussion}
In this work, we demonstrate that a bimodal structure in the nuclear abundance plane is associated with a brief quiescent phase. We now construct a possible framework for understanding the formation of the bimodality in our simulation, discuss its relation to prior work, and then discuss predictions and connections to observations.

\subsection{Quiescence Leads to Bimodality}\label{ssec:formqui}
We executed a series of idealized merger simulations in which we modified the starting radius and velocity by $\pm10\%$ and the circularity by $\pm0.1$, for a total of $27$ simulations. The central and satellite galaxies, which are meant to resemble the Milky Way and GSE at $z\sim2$, are otherwise identical across the simulations. Some of these simulations induce a bimodality, while others do not. We have examined a representative of each scenario in detail.

We described a series of results in Section~\ref{sec:results} which give a natural explanation for the separation between the high- and low-$\alpha$ sequences in our simulations. First, a merger induces a starburst in the simulation. If this starburst does not induce a quiescent period, then the median \MgFe{} of the gas briefly increases before continuing along the typical evolutionary path (right panel of Figure~\ref{fig:SFR_alpha}). However, if there is a quiescent period, the median \MgFe{} drops for the duration of the quiescent period before recovering to the typical path (left panel of Figure~\ref{fig:SFR_alpha}).

This drop can be understood in terms of the mechanics of the galaxy formation model as described in Section~\ref{ssec:gfm}. When a star particle forms, it only takes $\sim40\,\Myr$ before the last Type II SN has gone off and iron enrichment is dominated by Type Ia SNe. As a result, during the quiescent phase there is relatively little $\alpha$-element production. On the other hand, star particles are still able to generate iron through Type Ia SNe which have a much longer period of influence. In the TNG model, the number of Type Ia SNe decays with time as $(t/\tau_8)^{-s}$, where $\tau_8=40\,\Myr$ is the lifetime of an $8\,\Msun$ star and $s=1.12$. Therefore, the burst of star formation at $t\sim2.25\,\Gyr$ is able to generously produce iron starting at $2.5\,\Gyr$, when the drop is the most steep.

\subsection{Dilution Interpretation}\label{ssec:dilute}
In some previous work, it was reported that the bimodality is a consequence of a sudden deposition of metal-poor, $\alpha$-poor gas by a satellite or cosmological filament -- i.e., a ``dilution'' \citep{2020MNRAS.491.5435B,}. The separation of the sequences follows from the rapidity of the dilution.

We have shown that minor changes to the orbit of our idealized merger can result in outcomes that are either bimodal or unimodal. The content of gas that is delivered to the system is similar between the two regimes, and so our simulations do not support the dilution interpretation. However, this may be because the inflowing gas is too enriched, arising from an unrealistic feedback and enrichment routine, or from the unrealistic aspects of our setup. Our work does argue against the necessity of the dilution interpretation, but we also cannot completely rule it out.

\subsection{Direct Search for Quiescence}\label{ssec:obsqui}
Figure~\ref{fig:before_after_sfh_by_iron} indicates a very direct observational test of the mechanism proposed in this work: for disk stars at a given \FeH{}, there should be a gap of $\sim300\,\Myr$ in ages at $\sim8\,\Gyr$. With a survey of properly chosen stars, this could potentially be achieved with a modest (few hundred) sample of stars with age uncertainties of $\sim1\%$. The present observational landscape for age dating of old stars is far from this goal. To our knowledge, the best method at these ages is differential analysis of solar twins, which can provide an age uncertainty of $\sim5\%$ \citep[e.g.][]{2014ApJ...795...23B,2018MNRAS.474.2580S}. However, this only works for stars with solar metallicity, where there is not a clear separation between the high- and low-$\alpha$ sequences (though a gap in ages may still be present).

And so, this test may only be possible to a reader in the distant future. However, the situation might not be completely hopeless. The necessary sample size is small, and so copious time and instruments can be dedicated. Moreover, only \textit{relative} ages need to be determined, so a sort of differential approach may yield interesting results. In addition to the presence of the gap, our work also predicts that the timing of the gap is \FeH{} dependent.

\subsection{Observational Evidence of Quiescence}\label{ssec:obshiz}
Our main argument in this paper is that the Milky Way underwent a brief quiescent phase induced by a starburst at $z\sim2$. In observations, a Milky Way-analogue would be identified as a post-starburst galaxy (PSB). With abundance matching, we expect the Milky Way's total stellar mass to be $\sim2\times10^{10}\,\Msun$. A number of authors have explored PSBs and quiescent galaxies of this mass at $z\sim2$, with large advances in the post-JWST era.

First, PSBs are not uncommon. \citet{2023ApJ...953..119P} found that in massive galaxies ($M_* > 10^{10.6}\,\Msun$) the fraction of PSBs increases from $\sim2.7\%$ ($99/3655$) at $1.0 < z < 1.44$ to $\sim8\%$ ($89/1118$) at $2.16 < z < 2.5$, confirming previous work that PSBs are more common towards $z\sim2$ \citep[e.g.,][]{2016MNRAS.463..832W}. If these galaxies can be quickly rejuvenated as the system studied in this work would suggest, then the true fraction of galaxies that go through a starburst-quenching phase may be higher.

\citet{2023arXiv231215012C} found that lower mass quiescent galaxies (towards $10^{10.3}\,\Msun$) tend to be younger and more disky, pointing to a merger driven scenario. \citet{2023arXiv231212207A} found that at even lower masses ($<10^{9.5}\,\Msun$) Furthermore, the AGN quenching mechanism, which we believe to be responsible for the quenching in our system (Appendix~\ref{app:cause_qui}), is thought to operate at these redshifts \citep[e.g.][and references therein]{2023arXiv230805795B}.

\subsection{Connection to Cosmological Simulations}\label{ssec:cosmo}
As discussed in Section~\ref{sec:intro}, several authors have examined the formation of abundance plane structure in cosmological simulations. Of most interest to us is the zoom Au~23 in \citet{2018MNRAS.474.3629G}. This galaxy, one of six considered in their work, exhibits a bimodality that extends beyond the inner disk. The interpretation given by the authors is of a ``shrinking'' gaseous disk. This is equivalent to saying that the outer disk becomes depleted of gas. This shrinking of the disk, which occurs at $t_{\textrm{lookback}}\sim6\,\Gyr$, is associated with a dip in the SFR at that radius and a decrement in the median \alphaFe{} of $\sim0.05\,\dex$ (their Figure~2), which shortly after recovers. This sequence of events is more extended than in our work, but it strongly resembles the scenario in Figure~\ref{fig:before_after_sfh}.

\citet{2018MNRAS.477.5072M} found that Milky Way-like bimodalities are rare in EAGLE, occuring in $\sim5\%$ of galaxies. \citet{2021MNRAS.501..236D,2022MNRAS.515.1430D} showed that merger-induced quenching in zooms can occur in the EAGLE model \citep[see also][]{2017MNRAS.465..547P}. However, the situation may be different in the lower resolution large box.

\citet{2023arXiv231016085K} explored the impact of quenching in the Magneticum Pathfinder suite. They found that galaxies which quench undergo a starburst followed by an AGN-driven quenching phase. In the post-starburst regime, they claim galaxies are $\alpha$-enhanced. From their Figure~8 it is difficult to quantify the difference between the quenched and non-quenched galaxies as the two populations almost completely overlap. We do find that the bulk stellar \MgFe{} is enhanced after the merger in our fiducial simulation, but only at the $\sim0.01\,\dex$ level.

\subsection{Future Work}
A natural next step would be to extend the idealized simulations in this work to a wider range of orbits, galaxy properties, and feedback models. However, the unrealism of our setup, which aids interpretation, limits its applicability to the real universe. And so something along the lines of the genetic modification technique to explore various mergers as done in this work may be useful \citep{2016MNRAS.455..974R,2017MNRAS.465..547P}.

There is, of course, still great uncertainties in the stellar evolution models commonly adopted by different groups. Initial work on systematically exploring the stellar evolution parameters has been done by \citet{2017A&A...605A..59R,2021MNRAS.508.3365B}. Exploring these variations in the simulations presented in this work would be interesting, though exploring their interactions with brief quiescent periods in simpler chemical evolution models may be a better first step.

There is also the perennial problem of diffusion within the hydrodynamics solver. In purely Lagrangian solvers, there is no diffusion between resolution elements, while in Eulerian codes the diffusion can be quite high. AREPO limits the numerical diffusion by allowing the mesh to move in a quasi-Lagrangian manner, and using a second-order solver \red{cite}. In FIRE-2 \citep{2018MNRAS.480..800H}, which uses the Lagrangian code GIZMO \citep{2015MNRAS.450...53H}, a subgrid turbulent metal diffusion model was used. It would be interesting to see how models with different diffusivity properties would relax or strengthen the necessity of a quiescent period to produce a bimodality.

% JWST quiescent galaxies https://arxiv.org/abs/2404.12432

### 2024-04-29 paper/src/int.tex
Rename sec to src

--- 2024-04-21 paper/introduction.tex
@@
 \section{Introduction} \label{sec:intro}
+% What leads to distribution of heavy elements in a galaxy
 Elements heavier than hydrogen are produced through nuclear fusion.
@@
 
+% How present-day stellar surface abundances are linked to history of gas-phase abundances
 By necessity, stars inherit the constituitive properties of the gas cloud from which they formed.
@@
 
+% Why alpha-elements are important
 The distribution of elemental abundances is a high dimensional space (\red{e.g.
@@
 
-Two elements in particular have received particular interest - iron and $\alpha$-elements (elements produced through the $\alpha$-process, typically tracked with just Mg).
+Two elements in particular have received particular interest - iron and $\alpha$-elements (elements produced through the $\alpha$-process, often tracked with just Mg).
 Type Ia and Type II supernovae are the main contributors of elemental enrichment.
@@
 
-In this plane, it is now well-established that a significant bimodality exists in the Milky Way \red{cite a boatload}.
+% Observed chemical bimodality in the Milky Way
+It is now well-established that, in the Milky Way, a bimodality exists in the \alphaFe{}-\FeH{} plane \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R,2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}.
+This bimodality is typically separated into the high-$\alpha$ and low-$\alpha$ sequences.
+The high-$\alpha$ sequence is more centrally compact and vertically extended than the low-$\alpha$ sequence.
+
+% Different explanations of bimodality
+Naturally, many different processes that could lead to structure in the abundance plane have been discussed in the literature.
+They can be separated into two broad classes: (1) structure arising from internal processes, and (2) structure arising from external processes.
+We will summarize these classes of explanations in turn.
+
+An early explanation of the bimodality is the two-phase gas infall model \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}.
+In this model, the thick disk first forms rapidly from an initial infall of gas.
+Because the typical SFR is high, these stars are $\alpha$-enhanced.
+In some variants, star formation halts completely before a second supply of pristine gas falls into the Galaxy.
+This dilutes the gas supply from which the thin disk forms more gradually.
+The thin disk is then more $\alpha$-poor because its associated SFR is lower.
+
+Another mechanism to generate structure in the abundance plane was pointed out by \citet{2009MNRAS.396..203S}, further developed by \citet{2021MNRAS.507.5882S,2023MNRAS.523.3791C}, and explored by \citet{2011ApJ...737....8L,2021MNRAS.508.4484J}.
+This model claims that, since stars are thought to migrate from their birth radius, there will be stars throughout the entire disk that formed in the inner disk.
+These $\alpha$-enhanced stars will then form the high-$\alpha$ sequence.
+This model and its variants also match some chemodynamic properties of the disk.
+One salient feature of these models is that the bimodality can result from a smooth star formation history.
+
+Yet another explanation invoking an internal process is that the formation of clumps at high redshift are responsible for both the chemistry and dynamics of the high-$\alpha$ sequence \citep{2019MNRAS.484.3476C,2020MNRAS.492.4716B,2021MNRAS.502..260B,2023ApJ...953..128G}.
+Instabilities are thought to form clumps in gas-rich disks, and such clumps are seen at intermediate redshifts \citep[$z\sim2$;][]{2005ApJ...627..632E,2007ApJ...658..763E}.
+These clumps then self-enrich, forming $\alpha$-enhanced stars.
+The high-$\alpha$ sequence stops forming once the gas fraction is low enough for the instabilities to no longer arise.
+This model predicts that the high-$\alpha$ and low-$\alpha$ sequences form simultaneously.
+
+Next, we turn to models which argue the bimodality results from some external influence.
+Early arguments were made that both the $\alpha$-enhancement of the disk and the thickening of the disk can result from gas-rich mergers \citep{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R}.\footnote{See also \citet{2009MNRAS.400.1347C} for an argument invoking semi-analytic models.} These mergers lead to an enhanced SFR which leads to the $\alpha$-enhancement of the thick disk.
+
+In cosmological simulations, which naturally include early gas-rich mergers, the situation is not as clear.
+Early work by \citet{2012MNRAS.426..690B} found a general separation between the thin and thick disk, though other authors found a smooth evolution \citep{2013A&A...558A...9M}.
+\citet{2018MNRAS.474.3629G} found what they referred to as a chemical dichotomy, and argued that it can come from either gas-rich mergers as described before or a ``compaction'' of the disk (we will return to this point later).
+Other authors highlight the metal content of the infalling gas, stating that the pristine gas associated with satellites can suddenly dilute or reset the disk's metallicity \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}
+
+The inability of a particular conceptual framework to match every minute detail of the Galaxy does not invalidate its usefulness.
+It is, in our view, simplistic to claim any one factor to be the cause of structure in the abundance plane -- especially given the context that much deeper, unobserved structure almost certainly exists.
+The goal of this work is to argue for a closer examination of a process that has been
+
+In this work, we revisit the idea first touched upon by \citet{1997ApJ...477..765C} that a quiescent period may have contributed to the separation of the $\alpha$-sequences.
+We use fully self-consistent simulations of a galaxy merger which vaguely resembles the merger between the Milky Way and GSE.
+Under minor changes to the orbital parameters, we show that some mergers result in bimodal abundance planes while some result in unimodal planes (i.e., abundance plane bimodalities are not generically caused by gas-rich mergers).
+
+We are not confident that stellar dynamics is properly modeled in our simulations, and so we leave this aspect of the system to future work.
+
+% GSE merger explanation
+
+% In this work, ...
 

### 2024-04-29 paper/src/met.tex
Rename sec to src

\section{Methods}\label{sec:methods}
\subsection{Isolated Setup}\label{ssec:iso_setup}
In isolation, each of the central and satellite galaxies are a compound halo setup, with a Hernquist dark matter halo and a gaseous halo with a $\beta$-profile:
\begin{equation*}
\rho = \rho_0 \left[1 + \left(\frac{r}{r_c}\right)^2\right]^{-\frac{3\beta}{2}}
\end{equation*}
The total mass within the virial radius is kept fixed, and the mass of the dark matter halo and central density of the gaseous halo are chosen to satisfy a given baryon fraction $f_b$. The dark matter halo is initialized to be in gravitational equilibrium with the total potential. The gaseous halo is in gravito-hydrostatic equilibrium, where the temperature is allowed to vary as a function of radius. The azimuthal velocity of the gaseous halo is given as a fraction of the circular velocity. There is no initial stellar disk or bulge, and the gas is initially metal-free. Thus, all star particles and metals are formed self-consistently.

We manually varied the different model parameters until we arrived at a setup that resulted in reaosnable galaxies (as determined by their stellar mass). For the central (Milky Way) galaxy, we set $M_{200}=5\times10^{11}\,\Msun$, $c_{200}=4.1$, $\beta=0.8$, $r_c=9\,\kpc$, $f_b=0.08$, and $v_{\phi}/v_{\textrm{c}}=0.2$, where $c_{200}$ is the concentration and $v_{\phi}/v_{\textrm{c}}$ is the azimuthal velocity of the gaseous halo (as a fraction of the circular velocity). For the satellite (GSE) galaxy, we set $M_{200}=2.2\times10^{11}\,\Msun$, $c_{200}=4.33$, $\beta=0.8$, $r_c=6.5\,\kpc$, $f_b=0.06$, and $v_{\phi}/v_{\textrm{c}}=0.4$.

The stellar mass build-up of our Milky Way-like and GSE-like galaxies is given in Figure~\ref{fig:mass_size}. The upper panel shows the stellar mass history. We attempt to match the expected mass of the present-day thick disk \citep[$\sim6\times10^9\,\Msun$, horizontal blue dashed line][]{2016ARA&A..54..529B} at an evolution time of $\sim3\,\Gyr$ (corresponding to $z\sim2$, vertical dashed gray line).\footnote{Of course, this neglects the significant mass contribution of the bulge, which presumably formed earlier. However, our setup does not form a strong spheroidal component. Using the trick in e.g. \citet{2022MNRAS.515.1524Z}, we take the bulge mass to be twice the counterrotating stellar mass. At $3\,\Gyr$ in the isolated Milky Way-like galaxy, the bulge mass is $\sim7\times10^{8}\,\Msun$, or $\sim13\%$ of the total mass. The Milky Way's bulge is  $\sim1.5\times10^{10}\,\Msun$, although there is strong debate about just how much of the bulge is a classical bulge which formed before the disk \citep{2016ARA&A..54..529B}. In any case, we did not attempt to match any particular property of the bulge, though one could promote bulge formation by reducing the rotation of the gas in the inner region.} We get reasonably close at $\sim5\times10^9\,\Msun$ (blue line). For GSE, we use the best-fit mass from the $N$-body simulations of \citet{2021ApJ...923...92N} -- $5\times10^8\,\Msun$ (horizontal dashed orange line). For this, we slightly overestimate (orange line).

As for the galaxy sizes, there is significant spread amongst the real galaxy population, and the sizes are thought to be influenced by the merger history not present in our setup \citep[e.g.][]{2014ApJ...788...28V}. We note that the sizes of each simulated galaxy (lower panel) are within the range of observed galaxy sizes. For the Milky Way, we know the thick disk has scale length of $\sim2\,\kpc$, which converts to a half-mass radius of $\sim3.36\,\kpc$. At $\sim3\,\Gyr$, our Milky Way-like galaxy has a half-mass radius of $\sim2\,\kpc$. Curiously, after $3\,\Gyr$, the size of the Milky Way-like galaxy continues to grow while the GSE galaxy's size remains constant for the duration of the simulation.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{mass_size.pdf}
    \caption{The mass and size evolution of the central (Milky Way, blue) and satellite (GSE, orange) galaxies. The mass is taken to be the stellar mass within twice the half-mass radius, and the size is taken to be the half-mass radius. In the upper panel, we also show as a horizontal line the mass of the Milky Way's disk and GSE from the best-fit model of \citet{2021ApJ...923...92N}. This comparison is taken to be made at $3\,\Gyr$ (vertical dashed line), our proxy for $z\sim2$. A precise match is not attempted given the wide ranging uncertainties.}
    \label{fig:mass_size}
  \end{figure}

\subsection{Orbital Configuration}\label{ssec:orbit_setup}
In order to combine the galaxies, we follow \citet{2021ApJ...923...92N}, and place the satellite galaxy on a retrograde orbit. In the fiducial simulation of \citet{2021ApJ...923...92N}, the satellite is placed at the virial radius ($129\,\kpc$), with the virial velocity ($129\,\kms$), and with a circularity of $0.5$. To test minor changes to the orbit, we ran a grid of simulations with $\pm10\%$ in each the starting radius and velocity, and $\pm0.1$ in the circularity, for a total of $27$ simulations. We performed each simulation for a duration of $8\,\Gyr$.\footnote{Here, and throughout, we refer to the standard native time unit $\kpc/\left(\kms\right)$ as $\Gyr$ for convenience. There is only a $\sim3\%$ difference between the two.}

Some of the simulations in this orbital grid resulted in bimodal abundance distributions, while some had little to no structure in the abundance distribution plane. We show the abundance plane for all $27$ simulations in Appendix~\ref{app:allsims}, but for the main body of this work we consider two representative simulations in detail. For the bimodal simulation, we chose the simulation with $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$. For the unimodal simulation, the parameters are the same except that $R_0=129\,\kpc$.

\subsection{Feedback and Enrichment Model}\label{ssec:gfm}
Our feedback model is most closely related to that used in the Illustris TNG simulation suite \citep{2013MNRAS.436.3031V,2017MNRAS.465.3291W,2018MNRAS.473.4077P}. In this model, gravity and magnetohydrodynamics are solved using a \citet{1986Natur.324..446B} tree coupled to a second order finite volume fluid solver in AREPO \citep{2010MNRAS.401..791S,2016MNRAS.455.1134P}. Stellar feedback is included through a subgrid wind particle model \citep{2003MNRAS.339..289S}. AGN feedback follows a dual kinetic and thermal mode for low- and high-accretion rates \citep{2017MNRAS.465.3291W}.

In this work, we made some simplifications to this model in order to aid interpretation. First, we ignore magnetic fields. This was motivated by an initial desire to understand the CGM accretion rates in terms of idealized cooling flow solutions, but we did not revisit turning them back on. In any case, it is not clear if the magnetic fields would be realistically generated given our initial setup. Second, we use a gentler wind feedback model as described in \citet{2019MNRAS.489.4233M}. Because our setup includes both an initially steep central potential and no steady-state disk, a stronger feedback model would require a higher central gas density to achieve a reasonable SFH which introduced its own set of instabilities.

In this model, star particles synthesize elements through three different channels for which we cite the relevant yield tables: SNe Ia \citep{1997NuPhA.621..467N}, SNe II \citep{1998A&A...334..505P,2006ApJ...653.1145K}, and AGB stars \citep{2010MNRAS.403.1413K,2014MNRAS.437..195D,2014ApJ...797...44F}. Recall that star particles are simple stellar populations (i.e., a collection of stars with the same age and chemical composition). Each star particle continuously injects metals into its surroundings in the following sequence\footnote{The kinetic/thermal feedback component is handled through the wind generation, which is completely separate in this model.}:
\begin{enumerate}
    \item $t\lesssim10\,\Myr$: no metal injection as the first supernova ($M\sim100\,\Msun$) has not gone off
    \item $10\,\Myr \lesssim t \lesssim 40\,\Myr$: metal injection as $8\,\Msun<M<100\,\Msun$ stars die as Type II SNe
    \item $t\gtrsim40\,\Myr$: metal injection from Type Ia SNe and AGB stars
\end{enumerate}
There are a few things to note: (1) The exact timings are metallicity-dependent. (2) The \MgFe{} of ejected gas from Type II SNe are mass/time-dependent, with more massive stars contributing more Mg than less massive stars. (3) Type II SNe contribute the vast majority of Mg ($\sim10\times$ AGB and $\sim100\times$ Type Ia SNe). Type Ia and Type II SNe contribute approximately equal amounts of Fe ($\sim3\times$ AGB). See Figure~1 from \citet{2018MNRAS.473.4077P}. (4) The number of Type Ia SNe is greater for a younger stellar population, with a power law relationship $\propto t^{-1.12}$.

\subsection{Observed Abundances}\label{ssec:obs_abund}
Our aim in this work is to demonstrate the feasibility of a mechanism for structure formation in the abundance plane. We are only making a qualitative comparison to data. Therefore, we use the ASPCAP DR17 catalog of stellar abundances (\citet{2016AJ....151..144G}; J.A.~Holtzman et al., in preparation), which is publicly available, well-established, and widely used.

We first make some quality cuts, as well as restricting our sample to dwarfs \red{check}. We require:
\begin{itemize}[noitemsep]
    \item $\textrm{SNR} > 200$,
    \item $\textrm{VSCATTER} < 1\,\kms$,
    \item STARFLAG not set,
    \item $\varpi/\sigma_{\varpi} > 1$,
    \item $\log{g} < 3.5$,
    \item $\sigma_{\log{g}} < 0.2$,
\end{itemize}
where $\varpi$ is the parallax. We use the parallax, proper motion, and radial velocity from Gaia EDR3 \citep{2016AA...595A...1G, 2021AA...649A...1G, 2021AA...649A...2L, 2021AA...653A.160S}.

We next make a selection on the angular momentum of stars in order to make a solar neighborhood selection. We assume the solar radius and azimuthal velocity are $R_0=8\,\kpc$ and $V_0=220\,\kms$ \red{cite}, and select stars which have $L_z$ within $10\%$ of the solar angular momentum. We further require that $\left|z\right| < 3\,\kpc$.

As is typically done, we use \FeH{} as an indicator of the total metallicity of a star. We use Mg alone as a representative of the $\alpha$-elements.

\subsection{Solar Neighborhood in Simulations}\label{ssec:solarneigh}
When comparing galaxy simulations to the observed solar neighborhood, some ambiguity arises in how to make a ``solar neighborhood-like'' selection of star particles. Naturally, this selection is dependent on the posed question. In this work, this is the formation of the abundance bimodality. The Sun is known to sit near the end of the thick disk, where the thick and thin disk have comparable surface densities (the ratio of thick-to-thin is $\sim12\%$ \red{cite}). As a result, the abundance bimodality appears most strongly near the Sun -- further inwards the high-$\alpha$ sequence is more dominant and further outwards the high-$\alpha$ sequence vanishes \red{cite}.

We mimic our selection of the solar neighborhood by also making a cut in angular momentum. However, in the simulation, the high-$\alpha$ disk is more compact than in the Galaxy. Therefore, in order to strike a balance between the low-$\alpha$ and high-$\alpha$ disks, we used an angular momentum cut which is $20\%$ that of our assumed solar angular momentum. In particular, we select all star particles with angular momenta within $30\%$ of $0.2\times8\,\kpc\times220\,\kms$ -- as well as requiring $\left| z \right| < 3\,\kpc$.

This choice of angular momentum may seem unrealistic. However, it corresponds to roughly selecting star particles with radii between $2$ and $5\,\kpc$. As discussed in Section~\ref{ssec:iso_setup}, our Milky Way-like galaxy is more compact than the Milky Way's thick disk.

### 2024-04-29 paper/src/res.tex
Rename sec to src

\section{Results}\label{sec:results}
\subsection{Orbital Summary}\label{ssec:orbit}

\subsection{Abundance Distribution}\label{ssec:abundplane}
In Figure~\ref{fig:fig1}, briefly discussed in Section~\ref{sec:intro}, we show the abundance distribution of the Milky Way as well as two of our idealized merger simulations in the upper panels. A number of our idealized simulations exhibit either a bimodal or unimodal abundance distribution, and so we have selected two representative examples. In detail, the simulation labeled bimodal had orbital parameters of $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$. The unimodal simulation is identical, except that $R_0=129s\,\kpc$.

There are, of course, differences between the bimodal simulation and the Milky Way. First, the scaling in \MgFe{} is different -- in the simulation, the low-$\alpha$ sequence lies at $\sim0.2$, while in the Milky Way it is at about $\MgFe\sim0$. Second, in the Milky Way the high-$\alpha$ sequence neatly joins the low-$\alpha$ sequence at $\FeH\sim0$, while in the simulation the two actually diverge more at higher \FeH{}. Finally, at high \FeH{} the distribution bends upwards while in the simulation it bends downwards. The explanations for these differences are numerous, and are not the focus of the current work.

Finally, in the lower panels of Figure~\ref{fig:fig1}, we show the distributions of \MgFe{} at different fixed \FeH{}. The (blue, orange, red, green) lines show the \MgFe{} distribution at a \FeH{} of ($-0.5$, $-0.375$, $-0.25$, $0.25$), in bins of width $0.05\,\dex$. The distributions of \MgFe{} are offset so that they do not overlap. Here, the bimodality seen in the Milky Way is quite striking at lower metallicities. The peaks are well-separated, by $\sim0.2\,\dex$. In the bimodal simulation, the distribution is still clearly bimodal, but the peaks are less well-separated, by $\sim0.1\,\dex$. In the unimodal simulation, the distributions are clearly unimodal, with the hint of some structure in the $\FeH=0.25\,\dex$ bin.

\subsection{Build up of the Abundance Plane}\label{ssec:abundplane_build}
Next, we examine the build up of the abundance plane. First, in Figure~\ref{fig:before_after}, we show the abundance plane at various points along the merger. We have divided the history of the merger into ``before'' ($t < 1.5\,\Gyr$), ``during'' ($1.5\,\Gyr < t < 2.5\,\Gyr$), and ``after'' ($t > 2.5\,\Gyr$). These times have been chosen somewhat by the orbital history and somewhat by visually inspecting the movie of the simulation, and so these deliniations are, to an extent, arbitrary. Nonetheless, it is clear that the high-$\alpha$ sequence forms before and during the merger (middle panels), and that the low-$\alpha$ sequence forms after the merger (right panel). We show a dashed line given by $-0.1\FeH + 0.31$, which is a crude way of separating the high- and low-$\alpha$ sequence.

It is informative to examine the star formation history (SFH) split into the high- and low-$\alpha$ sequences, shown in Figure~\ref{fig:before_after_sfh}. The high- and low-$\alpha$ sequences (blue and orange) are defined as the star particles lying above and below the dashed line in Figure~\ref{fig:before_after}, respectively. We show this only in a narrow bin of width $0.1\,\dex$ at $\FeH\sim0$. One can see a very clear separation in time between the high- and low-$\alpha$ sequences, with the high-$\alpha$ sequence forming before the low-$\alpha$ sequence.\footnote{There is a small amount of low-$\alpha$ formation at the very end of the high-$\alpha$ sequence, but this can be understood as simply an inadequacy in our simple way of separating the two sequences.} Furthermore, there is a brief period of $\sim300\,\Myr$ between the two sequences where no stars have formed.

It can also be shown that the exact timing of this quiescent period is metallicity-dependent. We show the same SFH, but at varying bins in \FeH{} of $-0.5$, $-0.25$, and $0$ (blue, orange, and red, respectively). For clarity, we do not separate the SFHs by the high- and low-$\alpha$ sequences, but have verified that the same demarcation arises as in Figure~\ref{fig:before_after_sfh}. Here, we can see that at $\FeH=-0.5$ the quiescent period begins $\sim250\,\Myr$ earlier than at $\FeH=0$.

\subsection{\alphaFe{} Behavior Associated with Quiescence}
Given the sequence of events presented in Section~\ref{ssec:abundplane_build}, it is natural to suspect that the quiescent phase in Figure~\ref{fig:before_after_sfh} is responsible for the bimodal structure in Figure~\ref{fig:before_after}. We now examine this possibility more closely.

In Figure~\ref{fig:SFR_alpha}, we show the SFR (blue lines) of each of the bimodal and unimodal galaxies (left and right panels, respectively) as well as the median \MgFe{} of the gas (orange lines) in a bin centered on $\FeH{}=-0.1$ with width $0.02\,\dex$. The SFR is shown for the entire galaxy ($r<15\,\kpc$) while the median \MgFe{} is shown for $2\,\kpc<r<5\,\kpc$.\footnote{The solar neighborhood-like selection of stars mostly selects stars at $2\,\kpc<r<5\,\kpc$. We choose to plot the median \MgFe{} of the gas at these radii, since it is that gas which is forming stars that ends up in our sample. On the other hand, we choose to show the SFR for the entire galaxy, as the enrichment from that star formation affects the entire galaxy.}

As expected, we see a period of suppressed star formation in the bimodal simulation, which is also preceded by a period of enhanced star formation. The dip in SFR is not as pronounced as it was when we plotted the SFH at a particular iron (Figure~\ref{fig:before_after_sfh}). The period of a suppressed SFR is associated with a sudden drop in \MgFe{}. In $\sim250\,\Myr$, \MgFe{} drops from $\sim0.35$ to $\sim0.2\,\dex$. Once the SFR recovers $\sim500\,\Myr$ later, \MgFe{} again rises, but only to $\sim0.28\,\dex$. Roughly speaking, when star formation ceases, \MgFe{} has a value of $\sim0.35\,\dex$. When it recovers, \MgFe{} has a value of $\sim0.28\,\dex$.

This behavior is present in the unimodal simulation (right panel) -- it does not display a period of suppressed star formation, and there is no associated drop in \MgFe{}. It does still have a period of enhanced star formation, but this is actually coincident with an enhancement in \MgFe{}.

\subsection{Cause of Quiescence}\label{ssec:cause_qui}
The exact cause of quiescence in our simulation is not the main focus of our work. However, it appears to arise as a result of AGN activity triggered by the merger. We present some evidence of this in Appendix~\ref{app:cause_qui}.

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{before_after.pdf}
  \caption{\textbf{The high-$\alpha$ sequence forms before the merger, the low-$\alpha$ sequence forms after the merger.} This plot shows the sequence of events leading to the build-up of the low- and high-$\alpha$ sequences for our fiducial bimodal simulation. We have separated the high- and low-$\alpha$ sequences by a dashed line at $-0.1\FeH + 0.31$, which was chosen by eye to lie in the trough. The left panel shows all star particles in our solar neighborhood cut. The middle left panel shows the star particles that form before the merger ($\tform < 1.5\,\Gyr$), which form a weak sequence of star particles at the lowest \FeH and highest \MgFe. The middle right panel shows the star particles that form during the merger ($1.5\,\Gyr < \tform < 2.5\,\Gyr$). These star particless form the portion of the high-$\alpha$ sequence closest to the trough, and the density of star particless is higher than those that form before. The middle right panel shows the star particles which form after the merger ($\tform > 2.5\,\Gyr$). These star particles form almost entirely below the trough.}
  \label{fig:before_after}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{before_after_sfh.pdf}
  \caption{\textbf{At fixed metallicity, the low- and high-$\alpha$ sequence are cleanly separated in time, with an intervening quiescent period.} Here we show the star formation history of the high- and low-$\alpha$ sequences. The blue (low-$\alpha$) and orange (high-$\alpha$) histograms correspond to the dashed line cut made in the \MgFe-\FeH plane in Figure~\ref{fig:before_after}, at a fixed metallicity of $\FeH\sim0$. One can see that there is a nearly perfect separation in time between the formation of the high-$\alpha$ and low-$\alpha$ sequence, except for a brief overlap which can be attributed to the inadequacy of the linear cut model of the two sequences. Separating the formation periods lies a quiescent period with a duration of $\sim300\,\Myr$. \red{make sfr per dex}.}
  \label{fig:before_after_sfh}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{before_after_sfh_by_iron.pdf}
  \caption{\textbf{The timing of the quiescent period which divides the high- and low-$\alpha$ sequences is metallicity dependent.} The star formation history of stars at various fixed metallicities ($\FeH\sim0$, $-0.25$, and $-0.5\,\textrm{dex}$). As in Figure~\ref{fig:before_after_sfh}, there is a quiescent period period which separates the formation of the low- and high-$\alpha$ sequence \red{maybe a better way to show this?}. However, one can see that the timing of the quiescent period is metallicity-dependent. It occurs earlier at lower metallicity, by $\sim300\,\Myr$ for the metallicities shown in this plot. \red{make sfr per dex}.}
  \label{fig:before_after_sfh_by_iron}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{SFR_alpha.pdf}
  \caption{\textbf{A global suppression of star formation is associcated with a decrease in \MgFe{}, which is seen in the bimodal simulation but not in the unimodal simulation.} Here, we show both the SFR of the central galaxy ($r<15\,\kpc$) and the median \MgFe{} for gas at $2\,\kpc<r<5\,\kpc$ at a fixed \FeH{} bin centered on $-0.2$ with width $0.02\,\dex$. The left panel shows the bimodal simulation while the right panel shows the unimodal simulation. The time of the merger (i.e., the second pericenter) is indicated by the vertical dashed line. In the bimodal simulation, the star formation is suppressed after the merger. This suppression of star formation is associated with a sudden drop in the median \MgFe{} of the gas. Neither the suppression of star formation nor the drop in \MgFe{} are seen in the unimodal simulation.}
  \label{fig:SFR_alpha}
\end{figure*}

### 2024-04-29 paper/ms.tex
Paper updates
Rename sec to src
Move and update abstract

@@
 
-\begin{abstract}
-  The nuclear abundance distribution of stars encodes the history of the gas-phase abundance in the Milky Way.
-Without a large, unbiased sample of stellar ages, the exact timing and nature of this history must be \textit{inferred} from the abundances.
-In the two-dimensional plane of \alphaFe-\FeH, it is now clear that two separate populations exist - the low-$\alpha$ and high-$\alpha$ sequences.
-A restatement of this fact is that the distribution of \alphaFe{} is bimodal at a fixed Fe.
-Structure in the nuclear abundance distribution can arise from many processes - proposals include radial migration, high-redshift clump formation, and various effects associated with galaxy mergers, among others.
-In this work, we demonstrate another possible avenue for structure formation with clear observational predictions.
-We propose that the Galaxy underwent a starburst followed by a brief (hundreds of Myr) quiescent phase.
-A natural consequence of this quiescent phase is that stars in the valley of the bimodality do not form because: (1) the absence of enrichment from high-mass stars leads to a rapid reduction in \alphaFe{}, and (2) any time the gas spends in the abundance valley is deemphasized in the present day distribution because the star formation rate is lower.
-With a set of idealized merger simulations, we demonstrate the feasibility of this proposal.
-The starburst and quiescent phase can result from a merger, but it is not a necessary component of the theory.
-This ``phoenix hypothesis'' predicts a gap in stellar ages at a fixed \FeH{} and that stars which form directly after this gap would have lower \alphaFe{} than stars which form slightly later.
-\end{abstract}
+\input{src/abs.tex}
 
-\keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of 
-astronomy(1868) --- Interdisciplinary astronomy(804)}
+\input{src/int.tex}
 
-\input{sec/int.tex}
+\input{src/met.tex}
 
-\input{sec/met.tex}
+\input{src/res.tex}
 
-\input{sec/res.tex}
+\input{src/dis.tex}
 
-\input{sec/dis.tex}
-
-\input{sec/con.tex}
+\input{src/con.tex}
 
@@
 
-\bibliography{ref}{}
+\bibliography{src/ref}{}
 \bibliographystyle{aasjournal}
 
-% \input{app.tex}
+\input{src/app.tex}
 

### 2024-04-29 paper/src/abs.tex
Move and update abstract

\begin{abstract}
    The nuclear abundance distribution of stars encodes the history of the gas-phase abundance in the Milky Way. Without a large, unbiased sample of stellar ages, the exact timing and nature of this history must be \textit{inferred} from the abundances. In the two-dimensional plane of \alphaFe-\FeH, it is now clear that two separate populations exist - the low-$\alpha$ and high-$\alpha$ sequences. Structure in the nuclear abundance distribution can arise from many processes -- proposals include specific gas infall scenarios, radial migration, high-redshift clump formation, and various effects associated with galaxy mergers, among others. In this work, we demonstrate another possible avenue for structure formation with clear observational predictions. We propose that the Galaxy underwent a starburst followed by a brief (hundreds of Myr) quiescent phase -- i.e., the Galaxy underwent a post-starburst rejuvenation sequence at $z\sim2$. A natural consequence of the quiescent phase is that stars in the valley of the bimodality do not form because: (1) the absence of enrichment from high-mass stars leads to a rapid reduction in \alphaFe{}, and (2) any time the gas spends in the abundance valley is deemphasized in the present day distribution because the star formation rate is lower. With a set of idealized merger simulations, we demonstrate the feasibility of this proposal. This ``phoenix hypothesis'' predicts a $\sim300\,\Myr$ gap in stellar ages at a fixed \FeH{} and that stars which form directly after this gap would have lower \alphaFe{} than stars which form slightly ($\sim1\,\Gyr$) later.
  \end{abstract}

\keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of astronomy(1868) --- Interdisciplinary astronomy(804)}

### 2024-04-29 paper/src/con.tex
Update intro
Also moves some stuff to other places

--- 2024-04-21 paper/introduction.tex
@@
-\section{Introduction} \label{sec:intro}
-Elements heavier than hydrogen are produced through nuclear fusion.
-After Big Bang Nucleosynthesis, this only occurs in compact objects.
-The distribution of elemental abundances in the gas-phase of a galaxy is determined by a complicated combination of physical processes - stellar evolution and supernovae, gas accretion, galaxy mergers, gas outflows from stellar and AGN feedback, metal mixing and diffusion, etc.
-
-By necessity, stars inherit the constituitive properties of the gas cloud from which they formed.
-Moreover, the surface abundance of stars do not change over time.\footnote{For the most part.} We therefore have the unique opportunity to examine the historical record of the gas-phase abundance of a galaxy by way of the distribution of the surface abundances of stars.
-Because the processes which give rise to this distribution are complex, there is almost certainly some structure in this distribution for every galaxy.
-However, it has only been definitively measured in the Milky Way.
-
-The distribution of elemental abundances is a high dimensional space (\red{e.g.
-up to 8 billion elements by XYZ}).
-However, this space is highly degenerate, and so the effective number of dimensions is much smaller - even possibly compressed to just \FeH and age \citep{2019ApJ...883..177N}.
-
-Two elements in particular have received particular interest - iron and $\alpha$-elements (elements produced through the $\alpha$-process, typically tracked with just Mg).
-Type Ia and Type II supernovae are the main contributors of elemental enrichment.
-Iron is broadly produced in both types, and so its abundance is a proxy for the total metallicity of a star.
-$\alpha$-elements, on the other hand, are mainly produced in Type II supernovae.
-The ratio of $\alpha$-elements to iron is then a measure of the relative contributions of Type Ia and II to the enrichment of a parcel of gas.
-It has therefore become common to compress the high-dimensional abundance space to the two dimensional \FeH-\alphaFe plane.
-
-In this plane, it is now well-established that a significant bimodality exists in the Milky Way \red{cite a boatload}.
-
-Elemental enrichment is accounted for in modern galaxy formation models, though the validity of the yield tables is suspect.
-It is not known if the yields (i.e., the amount of metals produced by the SN) used in such models are accurate.
-This issue is further compounded by the fact that the mixing of metals is unresolved and is sensitive to numerical choices (e.g., Eulerian codes being generally more diffusive than Lagrangian).
-To make matters even worse, the inflows and outflows of gas from galaxies is sensitive to the choices of the feedback model, which has a strong impact on a galaxy's elemental history.
-
-The last\footnote{i.e., not ongoing} significant merger was between the
-proto-Milky Way disk and the {\em Gaia}-Sausage-Enceladus (GSE)
-(\textcolor{red}{spell check}) satellite galaxy. The stellar debris from this
-merger constitutes $\sim50\%$ \textcolor{red}{check} of the inner ($r<?\,\kpc$)
-stellar halo. It may have also led to a tilted, triaxial dark matter halo
-(\textcolor{red}{cite}).
-
-The GSE merger is often invoked (\textcolor{red}{cite}) to explain the observed
-bimodality in the \textcolor{red}{alpha iron} abundance plane
-(\textcolor{red}{cite}). Because GSE-mass galaxies are expected to have a lower
-star formation efficiency than proto-Milky Way-mass galaxies
-(\textcolor{red}{cite}), the gas from GSE should be relatively metal poor. The
-gas from GSE thus dilutes the gas in the proto-Milky Way, ``resetting'' the
-chemical abundance of the Milky Way.
-
-However, it has also been claimed that the \textcolor{red}{alpha iron}
-bimodality can be explained through secular processes. \textcolor{red}{Sentence
-explaining the basic concept.} The argument is not that the GSE merger did not
-happen, but rather that it is not {\it necessary} and might not even be {\it
-sufficient} to explain the bimodality. Ongoing work to detect the bimodality in
-external galaxies may shed further light on the topic (\textcolor{red}{cite}).
-
-Investigating GSE-like mergers in cosmological simulations is a rich and active
-area of research. Many mergers believed to be similar to the GSE merger have
-been identified in the literature (\textcolor{red}{cite}). \textcolor{red}{Blah
-blah argue blah blah. And also blah blah argues blah blah.}
-
-While much has been learned from GSE-like mergers in cosmological simulations,
-they are not conducive to controlled experiments. It is possible to change the
-mass of satellites through genetic modification (\textcolor{red}{Pontzen}), and
-the GSE analog can be removed entirely (\textcolor{red}{Cooke cite}). However,
-to our knowledge, no method has been applied to change the orbital parameters of
-such a merger. It is also somehwat unclear if the circumgalactic media of
-proto-Milky Way mass galaxies at $z\sim2$ are properly simulated.
-
-In this work, we present hydrodynamic simulations of a controlled merger between
-a GSE analog and the $z\sim2$ proto-Milky Way.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{figure1.pdf}
-  \caption{\textbf{The abundance bimodality seen in the Milky Way can be reproduced in some idealized merger simulations.} In the upper panels, we show the distribution of stars in the \MgFe-\FeH plane.
-The left panel shows the observed distribution in the Milky Way from ASPCAP \red{cite}, while the right two panels show two idealized merger simulations.
-The idealized merger simulations are nearly identical, except that the bimodal simulation has a starting radius of $129\,\kpc$, while the unimodal simulation has a starting radius of $142\,\kpc$.
-We emphasize that the labels ``unimodal'' and ``bimodal'' are of the \textit{outcome} of the simulation, and do not reflect a particular choice in the setup.
-The bottom panels show the distribution of \MgFe at fixed \FeH.
-The colors indicate the fixed \FeH values, which are $-0.5$, $-0.375$, $-0.25$, and $0.25$.
-The Milky Way (left panels) exhibits a strong bimodal distribution of \MgFe at various \FeH.
-The idealized merger simulation marked as bimodal (center panels) also exhibits a bimodal distribution of \MgFe, though the structure is not as strongly defined.
-The idealized merger simulation marked as unimodal exhibits only weak structure, if any at all.}
-  \label{fig:fig1}
-\end{figure*}
+\section{Conclusion}\label{sec:conclusion}
+The inability of a particular conceptual framework to match every minute detail of the Galaxy does not invalidate its usefulness.
+It is, in our view, simplistic to claim any one factor to be the cause of structure in the abundance plane -- especially given the context that much deeper, unobserved structure almost certainly exists.
+The goal of this work is to argue for a closer examination of a process that has been

### 2024-04-29 paper/src/int.tex
Update intro
Also moves some stuff to other places

@@
 Elements heavier than hydrogen are produced through nuclear fusion.
-After Big Bang Nucleosynthesis, this only occurs in compact objects.
-The distribution of elemental abundances in the gas-phase of a galaxy is determined by a complicated combination of physical processes - stellar evolution and supernovae, gas accretion, galaxy mergers, gas outflows from stellar and AGN feedback, metal mixing and diffusion, etc.
+After Big Bang Nucleosynthesis, this only occurs in compact objects such as supernovae, dying low mass stars, and neutron star-neutron star mergers \citep[e.g.][]{2023A&ARv..31....1A}.
+By necessity, stars inherit the constituitive properties of the gas from which they formed.
+Moreover, the surface abundance of most elements for most stars do not change over most of their lifetime.
+We therefore have the unique opportunity to examine the historical record of the gas-phase abundance of a galaxy by way of the distribution of the surface abundances of stars.
+
+The enrichment of the gas-phase of a galaxy is determined by a complicated combination of physical processes - stellar evolution and supernovae, gas accretion, mergers, gas outflows from stellar and AGN feedback, metal mixing and diffusion, etc.
+Because the processes which give rise to this distribution are complex, there is almost certainly some structure in the stellar abundance distribution for every galaxy.
+However, it has only been definitively measured in the Milky Way (there is a claim of no measured structure in M31 by \citet{2024IAUS..377..115N}).
 
 % How present-day stellar surface abundances are linked to history of gas-phase abundances
-By necessity, stars inherit the constituitive properties of the gas cloud from which they formed.
-Moreover, the surface abundance of stars do not change over time.\footnote{For the most part.} We therefore have the unique opportunity to examine the historical record of the gas-phase abundance of a galaxy by way of the distribution of the surface abundances of stars.
-Because the processes which give rise to this distribution are complex, there is almost certainly some structure in this distribution for every galaxy.
-However, it has only been definitively measured in the Milky Way.
 
 % Why alpha-elements are important
-The distribution of elemental abundances is a high dimensional space (\red{e.g.
-up to 8 billion elements by XYZ}).
-However, this space is highly degenerate, and so the effective number of dimensions is much smaller - even possibly compressed to just \FeH and age \citep{2019ApJ...883..177N}.
-
-Two elements in particular have received particular interest - iron and $\alpha$-elements (elements produced through the $\alpha$-process, often tracked with just Mg).
-Type Ia and Type II supernovae are the main contributors of elemental enrichment.
-Iron is broadly produced in both types, and so its abundance is a proxy for the total metallicity of a star.
-$\alpha$-elements, on the other hand, are mainly produced in Type II supernovae.
-The ratio of $\alpha$-elements to iron is then a measure of the relative contributions of Type Ia and II to the enrichment of a parcel of gas.
-It has therefore become common to compress the high-dimensional abundance space to the two dimensional \FeH-\alphaFe plane.
+The distribution of elemental abundances is a high dimensional space \citep[e.g., up to 26 elements for Arcturus;][]{2024A&A...684A..85V}.
+However, this space is highly degenerate, and so the effective number of dimensions is much smaller -- even possibly compressed to just \FeH{} and age \citep{2019ApJ...883..177N}.
+Two elements in particular have received particular interest - Fe and $\alpha$-elements.
+Type Ia and Type II supernovae are the main contributors of Fe and $\alpha$ enrichment.
+Fe is broadly produced in both types, and so its abundance is a proxy for the total metallicity of a star.
+On the other hand, $\alpha$-elements are mainly produced in Type II supernovae.
+The ratio of $\alpha$-elements to Fe (\alphaFe{}) is then a measure of the relative contributions of Type Ia and II SNe to the enrichment of a parcel of gas.
+It has therefore become common to compress the high-dimensional abundance space to the two dimensional \alphaFe{}-\FeH{} plane.
 
@@
 Early work by \citet{2012MNRAS.426..690B} found a general separation between the thin and thick disk, though other authors found a smooth evolution \citep{2013A&A...558A...9M}.
-\citet{2018MNRAS.474.3629G} found what they referred to as a chemical dichotomy, and argued that it can come from either gas-rich mergers as described before or a ``compaction'' of the disk (we will return to this point later).
-Other authors highlight the metal content of the infalling gas, stating that the pristine gas associated with satellites can suddenly dilute or reset the disk's metallicity \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}
+\citet{2018MNRAS.474.3629G} found what they referred to as a chemical dichotomy, and argued that it can come from either gas-rich mergers as described before or a ``compaction'' of the disk (we will return to this point in Section~\ref{ssec:cosmo}).
+Other authors highlight the metal content of the infalling gas, stating that the metal-poor gas associated with satellites can suddenly dilute or reset the disk's metallicity \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}
 
-The inability of a particular conceptual framework to match every minute detail of the Galaxy does not invalidate its usefulness.
-It is, in our view, simplistic to claim any one factor to be the cause of structure in the abundance plane -- especially given the context that much deeper, unobserved structure almost certainly exists.
-The goal of this work is to argue for a closer examination of a process that has been
+The merger explanation of the bimodality is highly synergistic with our picture of the hierarchical assembly of the stellar halo \citep{2005ApJ...635..931B}.
+Indeed, there is strong evidence that the Milky Way underwent a significant merger with the so-called Gaia-Sausage-Enceladus satellite \citep[GSE;][]{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N}.
+This merger is thought to have occurred $\sim8-10\,\Gyr$ ago \citep[see also][]{2020ApJ...897L..18B}.
 
-In this work, we revisit the idea first touched upon by \citet{1997ApJ...477..765C} that a quiescent period may have contributed to the separation of the $\alpha$-sequences.
-We use fully self-consistent simulations of a galaxy merger which vaguely resembles the merger between the Milky Way and GSE.
-Under minor changes to the orbital parameters, we show that some mergers result in bimodal abundance planes while some result in unimodal planes (i.e., abundance plane bimodalities are not generically caused by gas-rich mergers).
+Claims in the literature on the stellar mass of GSE vary widely.
+Early estimates argued from $6\times10^8$ up to even $10^{10}\,\Msun$ \citep{2018MNRAS.478..611B,2018Natur.563...85H,2019MNRAS.484.4471F,2019MNRAS.487L..47V,2019MNRAS.488.1235M,2020MNRAS.493.5195D,2020MNRAS.497..109F}.
+Later estimates have been more conservatives with estimates from a mass of $3\times10^8\,\Msun$ to $10^9\,\Msun$ \citep{2019MNRAS.482.3426M,2020MNRAS.492.3631M,2021ApJ...923...92N,2022AJ....164..249H}, and even as low as $1.5\times10^8\,\Msun$ \citep{2023MNRAS.526.1209L}.
 
-We are not confident that stellar dynamics is properly modeled in our simulations, and so we leave this aspect of the system to future work.
+In this work, we explored an idealized merger simulation which resembles the merger between the Milky Way and GSE.
+We found that in certain configurations, which have only minor differences in their orbit, a bimodal distribution of stellar abundances in the \alphaFe{}-\FeH{} plane is produced.
+This is shown in Figure~\ref{fig:fig1}.
+The configurations which produce a bimodality are associated with a starburst followed by a quiescent phase followed by rejuvenation $\sim300\,\Myr$ later.
 
-% GSE merger explanation
-
-% In this work, ...
-
-Elemental enrichment is accounted for in modern galaxy formation models, though the validity of the yield tables is suspect.
-It is not known if the yields (i.e., the amount of metals produced by the SN) used in such models are accurate.
-This issue is further compounded by the fact that the mixing of metals is unresolved and is sensitive to numerical choices (e.g., Eulerian codes being generally more diffusive than Lagrangian).
-To make matters even worse, the inflows and outflows of gas from galaxies is sensitive to the choices of the feedback model, which has a strong impact on a galaxy's elemental history.
-
-The last\footnote{i.e., not ongoing} significant merger was between the
-proto-Milky Way disk and the {\em Gaia}-Sausage-Enceladus (GSE)
-(\textcolor{red}{spell check}) satellite galaxy. The stellar debris from this
-merger constitutes $\sim50\%$ \textcolor{red}{check} of the inner ($r<?\,\kpc$)
-stellar halo. It may have also led to a tilted, triaxial dark matter halo
-(\textcolor{red}{cite}).
-
-The GSE merger is often invoked (\textcolor{red}{cite}) to explain the observed
-bimodality in the \textcolor{red}{alpha iron} abundance plane
-(\textcolor{red}{cite}). Because GSE-mass galaxies are expected to have a lower
-star formation efficiency than proto-Milky Way-mass galaxies
-(\textcolor{red}{cite}), the gas from GSE should be relatively metal poor. The
-gas from GSE thus dilutes the gas in the proto-Milky Way, ``resetting'' the
-chemical abundance of the Milky Way.
-
-However, it has also been claimed that the \textcolor{red}{alpha iron}
-bimodality can be explained through secular processes. \textcolor{red}{Sentence
-explaining the basic concept.} The argument is not that the GSE merger did not
-happen, but rather that it is not {\it necessary} and might not even be {\it
-sufficient} to explain the bimodality. Ongoing work to detect the bimodality in
-external galaxies may shed further light on the topic (\textcolor{red}{cite}).
-
-Investigating GSE-like mergers in cosmological simulations is a rich and active
-area of research. Many mergers believed to be similar to the GSE merger have
-been identified in the literature (\textcolor{red}{cite}). \textcolor{red}{Blah
-blah argue blah blah. And also blah blah argues blah blah.}
-
-While much has been learned from GSE-like mergers in cosmological simulations,
-they are not conducive to controlled experiments. It is possible to change the
-mass of satellites through genetic modification (\textcolor{red}{Pontzen}), and
-the GSE analog can be removed entirely (\textcolor{red}{Cooke cite}). However,
-to our knowledge, no method has been applied to change the orbital parameters of
-such a merger. It is also somehwat unclear if the circumgalactic media of
-proto-Milky Way mass galaxies at $z\sim2$ are properly simulated.
-
-In this work, we present hydrodynamic simulations of a controlled merger between
-a GSE analog and the $z\sim2$ proto-Milky Way.
+In Section~\ref{sec:methods}, we describe our setup.
+In Section~\ref{sec:results}, we present the main results of our simulations.
+In Section~\ref{sec:discussion}, we discuss and interpret our results, as well as connections to previous and future work, before concluding in Section~\ref{sec:conclusion}.
+Throughout this work we refer to the standard native time unit $\kpc/\left(\kms\right)$ as \Gyr{} for convenience.
 

### 2024-04-29 paper/src/dis.tex
Update intro
Also moves some stuff to other places
More changes

@@
 \section{Discussion}\label{sec:discussion}
-In this work, we demonstrate that a bimodal structure in the nuclear abundance plane is associated with a brief quiescent phase.
-We now construct a possible framework for understanding the formation of the bimodality in our simulation, discuss its relation to prior work, and then discuss predictions and connections to observations.
+We have demonstrated that a bimodal structure in the nuclear abundance plane is associated with a brief quiescent phase in our idealized merger simulations.
+We now construct a possible framework for understanding the formation of the bimodality, discuss its relation to prior work, and then discuss predictions and connections to observations.
 
@@
 This drop can be understood in terms of the mechanics of the galaxy formation model as described in Section~\ref{ssec:gfm}.
-When a star particle forms, it only takes $\sim40\,\Myr$ before the last Type II SN has gone off and iron enrichment is dominated by Type Ia SNe.
+When a star particle forms, it only takes $\sim40\,\Myr$ before the last Type II SN has gone off and Fe enrichment is dominated by Type Ia SNe.
 As a result, during the quiescent phase there is relatively little $\alpha$-element production.
-On the other hand, star particles are still able to generate iron through Type Ia SNe which have a much longer period of influence.
+On the other hand, star particles are still able to generate Fe through Type Ia SNe which have a much longer period of influence.
 In the TNG model, the number of Type Ia SNe decays with time as $(t/\tau_8)^{-s}$, where $\tau_8=40\,\Myr$ is the lifetime of an $8\,\Msun$ star and $s=1.12$.
-Therefore, the burst of star formation at $t\sim2.25\,\Gyr$ is able to generously produce iron starting at $2.5\,\Gyr$, when the drop is the most steep.
-
-\subsection{Dilution Interpretation}\label{ssec:dilute}
-In some previous work, it was reported that the bimodality is a consequence of a sudden deposition of metal-poor, $\alpha$-poor gas by a satellite or cosmological filament -- i.e., a ``dilution'' \citep{2020MNRAS.491.5435B,}.
-The separation of the sequences follows from the rapidity of the dilution.
-
-We have shown that minor changes to the orbit of our idealized merger can result in outcomes that are either bimodal or unimodal.
-The content of gas that is delivered to the system is similar between the two regimes, and so our simulations do not support the dilution interpretation.
-However, this may be because the inflowing gas is too enriched, arising from an unrealistic feedback and enrichment routine, or from the unrealistic aspects of our setup.
-Our work does argue against the necessity of the dilution interpretation, but we also cannot completely rule it out.
-
-\subsection{Direct Search for Quiescence}\label{ssec:obsqui}
-Figure~\ref{fig:before_after_sfh_by_iron} indicates a very direct observational test of the mechanism proposed in this work: for disk stars at a given \FeH{}, there should be a gap of $\sim300\,\Myr$ in ages at $\sim8\,\Gyr$.
-With a survey of properly chosen stars, this could potentially be achieved with a modest (few hundred) sample of stars with age uncertainties of $\sim1\%$.
-The present observational landscape for age dating of old stars is far from this goal.
-To our knowledge, the best method at these ages is differential analysis of solar twins, which can provide an age uncertainty of $\sim5\%$ \citep[e.g.][]{2014ApJ...795...23B,2018MNRAS.474.2580S}.
-However, this only works for stars with solar metallicity, where there is not a clear separation between the high- and low-$\alpha$ sequences (though a gap in ages may still be present).
-
-And so, this test may only be possible to a reader in the distant future.
-However, the situation might not be completely hopeless.
-The necessary sample size is small, and so copious time and instruments can be dedicated.
-Moreover, only \textit{relative} ages need to be determined, so a sort of differential approach may yield interesting results.
-In addition to the presence of the gap, our work also predicts that the timing of the gap is \FeH{} dependent.
-
-\subsection{Observational Evidence of Quiescence}\label{ssec:obshiz}
-Our main argument in this paper is that the Milky Way underwent a brief quiescent phase induced by a starburst at $z\sim2$.
-In observations, a Milky Way-analogue would be identified as a post-starburst galaxy (PSB).
-With abundance matching, we expect the Milky Way's total stellar mass to be $\sim2\times10^{10}\,\Msun$.
-A number of authors have explored PSBs and quiescent galaxies of this mass at $z\sim2$, with large advances in the post-JWST era.
-
-First, PSBs are not uncommon.
-\citet{2023ApJ...953..119P} found that in massive galaxies ($M_* > 10^{10.6}\,\Msun$) the fraction of PSBs increases from $\sim2.7\%$ ($99/3655$) at $1.0 < z < 1.44$ to $\sim8\%$ ($89/1118$) at $2.16 < z < 2.5$, confirming previous work that PSBs are more common towards $z\sim2$ \citep[e.g.,][]{2016MNRAS.463..832W}.
-If these galaxies can be quickly rejuvenated as the system studied in this work would suggest, then the true fraction of galaxies that go through a starburst-quenching phase may be higher.
-
-\citet{2023arXiv231215012C} found that lower mass quiescent galaxies (towards $10^{10.3}\,\Msun$) tend to be younger and more disky, pointing to a merger driven scenario.
-\citet{2023arXiv231212207A} found that at even lower masses ($<10^{9.5}\,\Msun$) Furthermore, the AGN quenching mechanism, which we believe to be responsible for the quenching in our system (Appendix~\ref{app:cause_qui}), is thought to operate at these redshifts \citep[e.g.][and references therein]{2023arXiv230805795B}.
+Therefore, the burst of star formation at $t\sim2.25\,\Gyr$ is able to generously produce Fe starting at $2.5\,\Gyr$, when the drop in \MgFe{} is the most steep.
 
@@
 However, the situation may be different in the lower resolution large box.
+Furthermore, if the proposed starburst-quenching phase is driven by AGN feedback, then the outcome of any particular cosmological simulation with regards to the bimodality is intimately tied to its AGN model.
+Unfortunately, such models are highly uncertain \red{cite}.
 
@@
 We do find that the bulk stellar \MgFe{} is enhanced after the merger in our fiducial simulation, but only at the $\sim0.01\,\dex$ level.
+
+\subsection{Dilution Interpretation}\label{ssec:dilute}
+In some previous work, it was reported that the bimodality is a consequence of a sudden deposition of metal-poor, $\alpha$-poor gas by a satellite or cosmological filament -- i.e., a ``dilution'' \citep{2020MNRAS.491.5435B,2021MNRAS.503.5846R}.
+The separation of the sequences follows from the rapidity of the dilution.
+This was elaborated upon by \citet{2021MNRAS.503.5868R} who described a setup where the low-$\alpha$ disk forms inclined relative to the high-$\alpha$ disk.
+
+We have shown that minor changes to the orbit of our idealized merger can result in outcomes that are either bimodal or unimodal.
+The content of gas that is delivered to the system is similar between the two regimes, and so our simulations do not support the dilution interpretation.
+However, this may be because the inflowing gas is too enriched, arising from an unrealistic feedback and enrichment routine, or from the unrealistic aspects of our setup.
+Our work does argue against the necessity of the dilution interpretation, but we also cannot completely rule it out.
+
+\subsection{Observational Evidence of Quiescence}\label{ssec:obshiz}
+Our main argument in this paper is that the Milky Way underwent a brief quiescent phase induced by a starburst at $z\sim2$.
+In observations, a Milky Way-analogue would then be identified as a post-starburst galaxy (PSB).
+With abundance matching, we expect the Milky Way's total stellar mass to be $\sim2\times10^{10}\,\Msun$ at $z\sim2$ \citep{2013ApJ...771L..35V}.
+A number of authors have explored PSBs and quiescent galaxies at slightly higher masses at $z\sim2$, with large advances in the post-JWST era.
+
+First, PSBs are not uncommon.
+\citet{2023ApJ...953..119P} found that in massive galaxies ($M_* > 10^{10.6}\,\Msun$) the fraction of PSBs increases from $\sim2.7\%$ ($99/3655$) at $1.0 < z < 1.44$ to $\sim8\%$ ($89/1118$) at $2.16 < z < 2.5$, confirming previous work that PSBs are more common towards $z\sim2$ \citep[e.g.,][]{2016MNRAS.463..832W}.
+If these galaxies can be quickly rejuvenated, as the system studied in this work would suggest, then the total fraction of galaxies that go through a starburst-quenching phase may be higher.
+
+\citet{2023arXiv231215012C} found that lower mass quiescent galaxies (towards $10^{10.3}\,\Msun$) tend to be younger and more disky, pointing to a merger driven scenario.
+\citet{2023arXiv231212207A} found that at even lower masses ($<10^{9.5}\,\Msun$) Furthermore, the AGN quenching mechanism, which we believe to be responsible for the quenching in our system (Appendix~\ref{app:cause_qui}), is thought to operate at these redshifts \citep[e.g.][and references therein]{2023arXiv230805795B}.
+
+\subsection{Direct Search for Quiescence}\label{ssec:obsqui}
+Figure~\ref{fig:before_after_sfh_by_iron} indicates a very direct observational test of the mechanism proposed in this work: for disk stars at a given \FeH{}, there should be a gap of $\sim300\,\Myr$ in ages at $\sim8\,\Gyr$.
+With a survey of properly chosen stars, this could potentially be achieved with a modestly sized (few hundred) sample of old stars with age uncertainties of $\sim1\%$.
+The present observational landscape for age dating of old stars is far from this goal.
+To our knowledge, the best method at these ages is differential analysis of solar twins, which can provide an age uncertainty of $\sim5\%$ \citep[e.g.][]{2014ApJ...795...23B,2018MNRAS.474.2580S}.
+However, this only works for stars with solar metallicity, where there is not a clear separation between the high- and low-$\alpha$ sequences (though a gap in ages may still be present).
+
+And so, this test may only be possible to a reader in the distant future.
+However, the situation might not be completely hopeless.
+The necessary sample size is small, and so copious time and instruments can be dedicated.
+Moreover, only \textit{relative} ages need to be determined, so a sort of differential approach may yield interesting results.
+In addition to the presence of the gap, our work also predicts that the timing of the gap is \FeH{} dependent.
 
@@
 In purely Lagrangian solvers, there is no diffusion between resolution elements, while in Eulerian codes the diffusion can be quite high.
-AREPO limits the numerical diffusion by allowing the mesh to move in a quasi-Lagrangian manner, and using a second-order solver \red{cite}.
+AREPO limits the numerical diffusion by allowing the mesh to move in a quasi-Lagrangian manner, and using a second-order solver \citep{2010MNRAS.401..791S}.
 In FIRE-2 \citep{2018MNRAS.480..800H}, which uses the Lagrangian code GIZMO \citep{2015MNRAS.450...53H}, a subgrid turbulent metal diffusion model was used.

### 2024-04-29 paper/src/int.tex
More changes

@@
 % Why alpha-elements are important
-The distribution of elemental abundances is a high dimensional space \citep[e.g., up to 26 elements for Arcturus;][]{2024A&A...684A..85V}.
+The distribution of elemental abundances is a high dimensional space \citep[e.g., 32 elements in][]{2024ApJ...961L..41J}.
 However, this space is highly degenerate, and so the effective number of dimensions is much smaller -- even possibly compressed to just \FeH{} and age \citep{2019ApJ...883..177N}.
@@
   \caption{\textbf{The abundance bimodality seen in the Milky Way can be reproduced in some idealized merger simulations.} In the upper panels, we show the distribution of stars in the \MgFe-\FeH plane.
-The left panel shows the observed distribution in the Milky Way from ASPCAP \red{cite}, while the right two panels show two idealized merger simulations.
+The left panel shows the observed distribution in the Milky Way from ASPCAP DR17 \citep[][J.A.~Holtzman et al., in preparation]{2016AJ....151..144G}, while the right two panels show two idealized merger simulations.
 The idealized merger simulations are nearly identical, except that the bimodal simulation has a starting radius of $129\,\kpc$, while the unimodal simulation has a starting radius of $142\,\kpc$.

### 2024-04-29 paper/src/met.tex
Update intro
Also moves some stuff to other places
More changes

@@
 \subsection{Isolated Setup}\label{ssec:iso_setup}
-In isolation, each of the central and satellite galaxies are a compound halo setup, with a Hernquist dark matter halo and a gaseous halo with a $\beta$-profile:
+We use a modified version of the \texttt{MakeNewDisk} variant described in \citet{2023MNRAS.tmp.2070B}.
+In isolation, each of the central and satellite galaxies are a compound halo setup, with a \citet{1990ApJ...356..359H} dark matter halo and a gaseous halo with a $\beta$-profile:
 \begin{equation*}
@@
 
-We manually varied the different model parameters until we arrived at a setup that resulted in reaosnable galaxies (as determined by their stellar mass).
-For the central (Milky Way) galaxy, we set $M_{200}=5\times10^{11}\,\Msun$, $c_{200}=4.1$, $\beta=0.8$, $r_c=9\,\kpc$, $f_b=0.08$, and $v_{\phi}/v_{\textrm{c}}=0.2$, where $c_{200}$ is the concentration and $v_{\phi}/v_{\textrm{c}}$ is the azimuthal velocity of the gaseous halo (as a fraction of the circular velocity).
+We used the fiducial halos in \citet{2021ApJ...923...92N} as a starting point for each galaxy.
+We then manually varied the different model parameters until we arrived at a setup that resulted in reasonable galaxies as determined by their stellar mass.
+For the central (Milky Way) galaxy, we set $M_{200}=5\times10^{11}\,\Msun$, $c_{200}=4.1$, $\beta=0.8$, $r_c=9\,\kpc$, $f_b=0.08$, and $v_{\phi}/v_{\textrm{c}}=0.2$, where $c_{200}$ is the concentration and $v_{\phi}/v_{\textrm{c}}$ is the azimuthal velocity of the gaseous halo as a fraction of the local circular velocity.
 For the satellite (GSE) galaxy, we set $M_{200}=2.2\times10^{11}\,\Msun$, $c_{200}=4.33$, $\beta=0.8$, $r_c=6.5\,\kpc$, $f_b=0.06$, and $v_{\phi}/v_{\textrm{c}}=0.4$.
@@
 For GSE, we use the best-fit mass from the $N$-body simulations of \citet{2021ApJ...923...92N} -- $5\times10^8\,\Msun$ (horizontal dashed orange line).
-For this, we slightly overestimate (orange line).
+For this, we slightly overestimate at $\sim6\times10^8\,\Msun$ (orange line).
 
@@
 \subsection{Orbital Configuration}\label{ssec:orbit_setup}
-In order to combine the galaxies, we follow \citet{2021ApJ...923...92N}, and place the satellite galaxy on a retrograde orbit.
+In order to combine the galaxies, we follow \citet{2021ApJ...923...92N}, and place the satellite on a retrograde orbit.
 In the fiducial simulation of \citet{2021ApJ...923...92N}, the satellite is placed at the virial radius ($129\,\kpc$), with the virial velocity ($129\,\kms$), and with a circularity of $0.5$.
 To test minor changes to the orbit, we ran a grid of simulations with $\pm10\%$ in each the starting radius and velocity, and $\pm0.1$ in the circularity, for a total of $27$ simulations.
-We performed each simulation for a duration of $8\,\Gyr$.\footnote{Here, and throughout, we refer to the standard native time unit $\kpc/\left(\kms\right)$ as $\Gyr$ for convenience.
-There is only a $\sim3\%$ difference between the two.}
+We performed each simulation for a duration of $8\,\Gyr$, and used \texttt{FOF} and \texttt{SUBFIND} in order to identify substructure \citep{2005Natur.435..629S,2009MNRAS.399..497D}.
 
@@
 
+We show the bimodal and unimodal orbits in Figure~\ref{fig:orbit}.
+The centers of  The upper and middle panels show the orbits in the $x$-$y$ and $x$-$z$ planes, respectively.
+The lower panel shows the separation distance as a function of time.
+The orbits are initially retrograde, but quickly radialize after the first pericentric passage.
+Coalescence occurs rapidly after the second pericentric passage at $\sim2\,\Gyr$.
+Soon after, \texttt{SUBFIND} does not recognize the satellite as a separate subhalo as the two galaxies coalesce.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{orbit.pdf}
+    \caption{The orbits of the bimodal (blue) and unimodal (orange) simulations.
+The upper and middle panels show the orbit in the $x$-$y$ and $x$-$z$ planes, respectively.
+The bottom panel shows the separation distance as a function of time.
+The orbit begins retrograde but then radializes after the first pericentric passage.
+The satellite then coalesces quickly after the second pericentric passage, after about $\sim2\,\Gyr$ of evolution.}
+    \label{fig:orbit}
+\end{figure}
+
 \subsection{Feedback and Enrichment Model}\label{ssec:gfm}
@@
 Stellar feedback is included through a subgrid wind particle model \citep{2003MNRAS.339..289S}.
-AGN feedback follows a dual kinetic and thermal mode for low- and high-accretion rates \citep{2017MNRAS.465.3291W}.
+AGN feedback follows a dual kinetic and thermal mode for low- and high-accretion rates \citep{2017MNRAS.465.3291W}, though in our setup the AGN is only ever in the high-accretion mode.
+The central galaxy is seeded with a black hole with the typical seed mass ($8\times10^5\,\Msun$).
 
@@
 Second, we use a gentler wind feedback model as described in \citet{2019MNRAS.489.4233M}.
-Because our setup includes both an initially steep central potential and no steady-state disk, a stronger feedback model would require a higher central gas density to achieve a reasonable SFH which introduced its own set of instabilities.
+Because our setup includes both an initially steep central potential and no steady-state disk, a stronger feedback model would require a higher central gas density to achieve a reasonable SFH which introduced its own set of pathological instabilities.
 
@@
 There are a few things to note: (1) The exact timings are metallicity-dependent.
-(2) The \MgFe{} of ejected gas from Type II SNe are mass/time-dependent, with more massive stars contributing more Mg than less massive stars.
-(3) Type II SNe contribute the vast majority of Mg ($\sim10\times$ AGB and $\sim100\times$ Type Ia SNe).
-Type Ia and Type II SNe contribute approximately equal amounts of Fe ($\sim3\times$ AGB).
+(2) The \MgFe{} of ejected gas from Type II SNe is mass/time-dependent, with more massive stars contributing more Mg than less massive stars.
+(3) In a Hubble time, type II SNe contribute the vast majority of Mg ($\sim10\times$ AGB and $\sim100\times$ Type Ia SNe).
+Type Ia and Type II SNe contribute approximately equal amounts of Fe (each $\sim3\times$ AGB).
 See Figure~1 from \citet{2018MNRAS.473.4077P}.
-(4) The number of Type Ia SNe is greater for a younger stellar population, with a power law relationship $\propto t^{-1.12}$.
+(4) The number of Type Ia SNe is greater for a younger stellar population, with a power law relationship $\propto \left(t/\tau_8\right)^{-1.12}$, where $\tau_8=40\,\Myr$ is the lifetime of an $8\,\Msun$ star.
 
@@
 We are only making a qualitative comparison to data.
-Therefore, we use the ASPCAP DR17 catalog of stellar abundances (\citet{2016AJ....151..144G}; J.A.~Holtzman et al., in preparation), which is publicly available, well-established, and widely used.
+Therefore, we use the ASPCAP DR17 catalog of stellar abundances \citep[][J.A.~Holtzman et al., in preparation]{2016AJ....151..144G}, which is publicly available, well-established, and widely used.
 
-We first make some quality cuts, as well as restricting our sample to dwarfs \red{check}. We require:
+We first make some quality cuts, as well as restricting our sample to giants. We require:
 \begin{itemize}[noitemsep]
@@
 \end{itemize}
-where $\varpi$ is the parallax. We use the parallax, proper motion, and radial velocity from Gaia EDR3 \citep{2016AA...595A...1G, 2021AA...649A...1G, 2021AA...649A...2L, 2021AA...653A.160S}.
+where $\varpi$ is the parallax. We use the parallax, proper motion, and radial velocity from Gaia EDR3 \citep{2016AA...595A...1G,2021AA...649A...1G,2021AA...649A...2L,2021AA...653A.160S}.
 
 We next make a selection on the angular momentum of stars in order to make a solar neighborhood selection.
-We assume the solar radius and azimuthal velocity are $R_0=8\,\kpc$ and $V_0=220\,\kms$ \red{cite}, and select stars which have $L_z$ within $10\%$ of the solar angular momentum.
+We assume the solar radius and azimuthal velocity are $R_0=8\,\kpc$ and $V_0=220\,\kms$ \citep{2016ARA&A..54..529B}, and select stars which have $L_z$ within $10\%$ of the solar angular momentum.
 We further require that $\left|z\right| < 3\,\kpc$.
@@
 In this work, this is the formation of the abundance bimodality.
-The Sun is known to sit near the end of the thick disk, where the thick and thin disk have comparable surface densities (the ratio of thick-to-thin is $\sim12\%$ \red{cite}).
-As a result, the abundance bimodality appears most strongly near the Sun -- further inwards the high-$\alpha$ sequence is more dominant and further outwards the high-$\alpha$ sequence vanishes \red{cite}.
+The Sun is known to sit near the end of the thick disk, where the thick and thin disk have comparable surface densities \citep[the ratio of thick-to-thin is $\sim12\%$][]{2016ARA&A..54..529B}.
+As a result, the abundance bimodality appears most strongly near the Sun -- further inwards the high-$\alpha$ sequence is more dominant and further outwards the high-$\alpha$ sequence vanishes \citep[e.g.,][]{2015ApJ...808..132H}.
 
@@
 However, it corresponds to roughly selecting star particles with radii between $2$ and $5\,\kpc$.
-As discussed in Section~\ref{ssec:iso_setup}, our Milky Way-like galaxy is more compact than the Milky Way's thick disk.
+As discussed in Section~\ref{ssec:iso_setup}, our Milky Way-like galaxy at $3\,\Gyr$ is more compact than the Milky Way's thick disk.

### 2024-04-29 paper/src/res.tex
More changes

@@
 \section{Results}\label{sec:results}
-\subsection{Orbital Summary}\label{ssec:orbit}
-
 \subsection{Abundance Distribution}\label{ssec:abundplane}
@@
 In detail, the simulation labeled bimodal had orbital parameters of $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$.
-The unimodal simulation is identical, except that $R_0=129s\,\kpc$.
+The unimodal simulation is identical, except that $R_0=129\,\kpc$.
 
@@
 Finally, at high \FeH{} the distribution bends upwards while in the simulation it bends downwards.
-The explanations for these differences are numerous, and are not the focus of the current work.
 
@@
 The (blue, orange, red, green) lines show the \MgFe{} distribution at a \FeH{} of ($-0.5$, $-0.375$, $-0.25$, $0.25$), in bins of width $0.05\,\dex$.
-The distributions of \MgFe{} are offset so that they do not overlap.
+The distributions of \MgFe{} are offset (but not rescaled) so that they do not overlap.
 Here, the bimodality seen in the Milky Way is quite striking at lower metallicities.
@@
 We have divided the history of the merger into ``before'' ($t < 1.5\,\Gyr$), ``during'' ($1.5\,\Gyr < t < 2.5\,\Gyr$), and ``after'' ($t > 2.5\,\Gyr$).
-These times have been chosen somewhat by the orbital history and somewhat by visually inspecting the movie of the simulation, and so these deliniations are, to an extent, arbitrary.
+These times have been chosen somewhat by the orbital history and somewhat by visually inspecting the simulation, and so these deliniations are, to an extent, arbitrary.
 Nonetheless, it is clear that the high-$\alpha$ sequence forms before and during the merger (middle panels), and that the low-$\alpha$ sequence forms after the merger (right panel).
@@
 
-As expected, we see a period of suppressed star formation in the bimodal simulation, which is also preceded by a period of enhanced star formation.
+The merger appears to induce a starburst, where the SFR rises from $\sim3.5\,\Msunyr$ at $\sim1\Gyr$ to a peak of $\sim12\,\Msunyr$ at $\sim2\,\Gyr$.
+This starburst is then followed by a quiescent period, with a depth of $\sim1\,\Msunyr$ and a duration of $\sim500\,\Myr$.
 The dip in SFR is not as pronounced as it was when we plotted the SFH at a particular iron (Figure~\ref{fig:before_after_sfh}).
-The period of a suppressed SFR is associated with a sudden drop in \MgFe{}.
+This quiescent period is associated with a sudden drop in \MgFe{}.
 In $\sim250\,\Myr$, \MgFe{} drops from $\sim0.35$ to $\sim0.2\,\dex$.
 Once the SFR recovers $\sim500\,\Myr$ later, \MgFe{} again rises, but only to $\sim0.28\,\dex$.
-Roughly speaking, when star formation ceases, \MgFe{} has a value of $\sim0.35\,\dex$.
-When it recovers, \MgFe{} has a value of $\sim0.28\,\dex$.
 
@@
 It does still have a period of enhanced star formation, but this is actually coincident with an enhancement in \MgFe{}.
+This sequence of events is further emphasized in Figure~\ref{fig:alpha_vs_tform}, which shows a transparent scatter plot of \MgFe{} as a function of formation time.
+In the bimodal simulation, there is a clear gap in \MgFe{} during the period of quiescence followed by the brief formation of $\alpha$-deficient stars.
+In the unimodal simulation, on the other hand, there is no gap and the brief formation of $\alpha$-enhanced stars.
 
@@
 \end{figure*}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{alpha_vs_tform.pdf}
+  \caption{The formation times and \MgFe{} values of star particles in the bimodal (blue) and unimodal (orange) simulations.
+In the bimodal simulation, a gap in stellar ages is briefly followed by the formation of $\alpha$-deficient star particles.
+In the unimodal simulation, no gap is present and there is briefly the formation of $\alpha$-enhanced star particles at the same time.
+The \MgFe{} values of the unimodal simulation have been offset by $-0.3$ for clarity.}
+  \label{fig:alpha_vs_tform}
+\end{figure}

### 2024-04-30 paper/src/res.tex
Add surfdens movie plot

@@
 \section{Results}\label{sec:results}
+\subsection{Surface Density Projections}\label{ssec:projections}
+Before dissecting the simulated galaxies in detail, we first take a look at the surface density projections of the gas and stars in the central region, situated on the central galaxy.
+This is shown in Figure~\ref{fig:projections}.
+In each grouping of four, the bottom and top rows show the face-on and edge-on views, respectively.
+The left and right columns show the gas and stellar surface density.
+Each panel is oriented with respect to the stellar angular momentum of the final snapshot ($t=8\,\Gyr$).
+The angular momentum is computed using all star particles within the half-mass radius.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{surfdens.pdf}
+  \caption{The surface density projections of the gas and stars over time of the idealized merger simulation with $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$ (i.e., the ``bimodal'' simulation).
+Every panel is oriented with respect to the final ($t=8\,\Gyr$) snapshot.
+In each grouping of four, the lower and upper rows show the face-on and edge-on projections, respectively.
+The left and right columns show the gas and stellar surface densities, respectively.
+The side-length of each panel is $30\,\kpc$, and the image is a projection through a box with the same side-length.
+\red{Need to fix spacing between panels and add scale bar.}}
+  \label{fig:projections}
+\end{figure*}
+
 \subsection{Abundance Distribution}\label{ssec:abundplane}
@@
 A number of our idealized simulations exhibit either a bimodal or unimodal abundance distribution, and so we have selected two representative examples.
-In detail, the simulation labeled bimodal had orbital parameters of $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$.
+The simulation labeled bimodal had orbital parameters of $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$.
 The unimodal simulation is identical, except that $R_0=129\,\kpc$.

### 2024-04-30 paper/src/app.tex
Update appendix, small changes throughout

\appendix
\section{Abundance Plane of All Simulations}\label{app:allmerge}
We show summary plots of the abundance planes of all simulations in our orbital grid in Figures~\ref{fig:allmerge0} to \ref{fig:allmerge8}.

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{allmerge/allmerge0.pdf}
  \caption{A summary of the abundance plane and star formation history of all simulations within the orbital grid. Each figure shows the outcome of a simulation at a fixed $R_0$ and $V_0$, varying $\eta$. The title of each column shows the $R_0$, $V_0$, and $\eta$ of that simulation, in order. The upper and middle rows replicate Figure~\ref{fig:fig1}, which show the distribution of stars in the abundance plane of \MgFe{}-\FeH{} as well as 1D histograms at a fixed \FeH{} of $-0.5$, $-0.25$, $0$, and $0.25$. The lower rows replicate Figure~\ref{fig:before_after_sfh_by_iron}, showing the star formation history at each \FeH{}.}
  \label{fig:allmerge0}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{allmerge/allmerge1.pdf}
  \caption{A continuation of Figure~\ref{fig:allmerge0}.}
  \label{fig:allmerge1}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{allmerge/allmerge2.pdf}
  \caption{A continuation of Figure~\ref{fig:allmerge0}.}
  \label{fig:allmerge2}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{allmerge/allmerge3.pdf}
  \caption{A continuation of Figure~\ref{fig:allmerge0}.}
  \label{fig:allmerge3}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{allmerge/allmerge4.pdf}
  \caption{A continuation of Figure~\ref{fig:allmerge0}.}
  \label{fig:allmerge4}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{allmerge/allmerge5.pdf}
  \caption{A continuation of Figure~\ref{fig:allmerge0}.}
  \label{fig:allmerge5}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{allmerge/allmerge6.pdf}
  \caption{A continuation of Figure~\ref{fig:allmerge0}.}
  \label{fig:allmerge6}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{allmerge/allmerge7.pdf}
  \caption{A continuation of Figure~\ref{fig:allmerge0}.}
  \label{fig:allmerge7}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{allmerge/allmerge8.pdf}
  \caption{A continuation of Figure~\ref{fig:allmerge0}.}
  \label{fig:allmerge8}
\end{figure*}

\section{Cause of Suppressed Star Formation}\label{app:cause_qui}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{SFR_Mgas_tdep.pdf}
  \caption{\textbf{The suppression of star formation in the bimodal simulation is associated with both a reduction in gas mass as well as an increase in the depletion time.} The drop in star formation (blue line) at $\sim2.5-3\,\Gyr$ is associated with both a reduction in the total gas mass (red line) as well as an increase in the depletion time (green line). This shows that the SFR suppression is a result of both less gas mass and more inefficient star formation.}
  \label{fig:SFR_Mgas_tdep}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=242.26653pt]{MdotBH_rsep.pdf}
  \caption{\textbf{The bimodal merger is associated with high accretion rates onto the central SMBH.} Around the time of each pericentric passage, and slightly after, the accretion rate (blue line) becomes very high. Here, it is shown as a fraction of the Eddington accretion rate. During the merger, the accretion rate reaches as high as Eddington at some times, but is always above $10\%$. The orbital separation between the central and satellite is shown in the orange line.}
  \label{fig:MdotBH_rsep}
\end{figure}

### 2024-04-30 paper/src/con.tex
Update appendix, small changes throughout

@@
 \section{Conclusion}\label{sec:conclusion}
-The inability of a particular conceptual framework to match every minute detail of the Galaxy does not invalidate its usefulness.
-It is, in our view, simplistic to claim any one factor to be the cause of structure in the abundance plane -- especially given the context that much deeper, unobserved structure almost certainly exists.
-The goal of this work is to argue for a closer examination of a process that has been
+The \alphaFe{}-\FeH{} plane of stellar abundances is a record of the gas-phase abundances of the Galaxy.
+In this plane, a significant bimodality has now been definitively measured.
+Proposals for its formation include radial migration, particular gas infall scenarios, and galaxy mergers.
+
+In this work, using idealized merger simulations, we have shown that (1) a starburst, followed by (2) a brief ($\sim300\,\Myr$) quiescent period, followed by (3) rejuvenation can lead to a bimodal abundance structure.
+We found that the starburst-to-quiescent period allowed for prodigious Fe-enrichment without any corresponding $\alpha$-enrichment.
+This ``phoenix hypothesis'' would predict that, for stars at a given \FeH{}, there would be a $\sim300\,\Myr$ gap in stellar ages at $\sim8\,\Gyr$.
+Furthermore, stars which form directly after this gap would have lower \alphaFe{} than stars which form slightly later ($\sim1\,\Gyr$).
+
+The bimodality in the \alphaFe{}-\FeH{} plane of stellar abundances points to deeper, unobserved structure.
+That structure is a record of the complicated processes that gave rise to the Galaxy.
+In the absence of highly precise stellar ages, that history must be largely inferred.

### 2024-04-30 paper/src/int.tex
Update appendix, small changes throughout

@@
 The thin disk is then more $\alpha$-poor because its associated SFR is lower.
+
+A later argument by \citet{2021MNRAS.501.5176K} bears a passing resemblance to the two-infall model.
+Here, they argue that the two sequences follow from two phases of gas infall, except driven by stellar feedback instead of cosmological inflow.
+An initial bursty phase follows from the direct collapse of the gaseous halo.
+The disk has a high SFR leads to the formation of the high-$\alpha$ sequence.
+Feedback then halts the inflow, and a slower accretion of high-angular momentum and metal-rich gas commences, forming the low-$\alpha$ sequence.
 

### 2024-04-30 paper/src/res.tex
Update appendix, small changes throughout

@@
 The left and right columns show the gas and stellar surface densities, respectively.
-The side-length of each panel is $30\,\kpc$, and the image is a projection through a box with the same side-length.
-\red{Need to fix spacing between panels and add scale bar.}}
+The side-length of each panel is $30\,\kpc$, and the image is a projection through a box with the same side-length.}
   \label{fig:projections}
@@
 One can see that there is a nearly perfect separation in time between the formation of the high-$\alpha$ and low-$\alpha$ sequence, except for a brief overlap which can be attributed to the inadequacy of the linear cut model of the two sequences.
-Separating the formation periods lies a quiescent period with a duration of $\sim300\,\Myr$.
-\red{make sfr per dex}.}
+Separating the formation periods lies a quiescent period with a duration of $\sim300\,\Myr$.}
   \label{fig:before_after_sfh}
@@
   \caption{\textbf{The timing of the quiescent period which divides the high- and low-$\alpha$ sequences is metallicity dependent.} The star formation history of stars at various fixed metallicities ($\FeH\sim0$, $-0.25$, and $-0.5\,\textrm{dex}$).
-As in Figure~\ref{fig:before_after_sfh}, there is a quiescent period period which separates the formation of the low- and high-$\alpha$ sequence \red{maybe a better way to show this?}.
+As in Figure~\ref{fig:before_after_sfh}, there is a quiescent period period which separates the formation of the low- and high-$\alpha$ sequence.
 However, one can see that the timing of the quiescent period is metallicity-dependent.
-It occurs earlier at lower metallicity, by $\sim300\,\Myr$ for the metallicities shown in this plot.
-\red{make sfr per dex}.}
+It occurs earlier at lower metallicity, by $\sim300\,\Myr$ for the metallicities shown in this plot.}
   \label{fig:before_after_sfh_by_iron}

### 2024-05-02 paper/src/met.tex
Add res levels to methods

@@
 For the satellite (GSE) galaxy, we set $M_{200}=2.2\times10^{11}\,\Msun$, $c_{200}=4.33$, $\beta=0.8$, $r_c=6.5\,\kpc$, $f_b=0.06$, and $v_{\phi}/v_{\textrm{c}}=0.4$.
+
+We used a mass resolution of $6\times10^4\,\Msun$ for the gas and $3\times10^5\,\Msun$ for the dark matter.
+This is closest to a resolution of level 4 in the AURIGA simulations \citep{2017MNRAS.467..179G}, and is about $0.7\times$ the mass resolution of TNG50-1 \citep{2019MNRAS.490.3234N,2019MNRAS.490.3196P}.
+All collisionless particles have a fixed softening length of $40\,\pc$.
+The gas has a softening length $2.5\times$ the cell size, with a minimum size of $10\,\pc$.
+Snapshots were saved at intervals of $0.025\,\Gyr$.
 

### 2024-05-02 paper/src/dis.tex
Add MJ's new paper

@@
 
-\subsection{Observational Evidence of Quiescence}\label{ssec:obshiz}
+\subsection{Observational Connections: High Redshift Quenching}\label{ssec:obshiz}
 Our main argument in this paper is that the Milky Way underwent a brief quiescent phase induced by a starburst at $z\sim2$.
 In observations, a Milky Way-analogue would then be identified as a post-starburst galaxy (PSB).
-With abundance matching, we expect the Milky Way's total stellar mass to be $\sim2\times10^{10}\,\Msun$ at $z\sim2$ \citep{2013ApJ...771L..35V}.
+With abundance matching, we expect the Milky Way's total stellar mass to be $\sim10^{10.3}\,\Msun$ at $z\sim2$ \citep{2013ApJ...771L..35V}.
 A number of authors have explored PSBs and quiescent galaxies at slightly higher masses at $z\sim2$, with large advances in the post-JWST era.
@@
 First, PSBs are not uncommon.
-\citet{2023ApJ...953..119P} found that in massive galaxies ($M_* > 10^{10.6}\,\Msun$) the fraction of PSBs increases from $\sim2.7\%$ ($99/3655$) at $1.0 < z < 1.44$ to $\sim8\%$ ($89/1118$) at $2.16 < z < 2.5$, confirming previous work that PSBs are more common towards $z\sim2$ \citep[e.g.,][]{2016MNRAS.463..832W}.
+\citet{2023ApJ...953..119P} found that in massive galaxies ($M_* > 10^{10.6}\,\Msun$) the fraction of PSBs increases from $\sim2.7\%$ ($99/3655$) at $1.0 < z < 1.44$ to $\sim8\%$ ($89/1118$) at $2.16 < z < 2.5$.
+Later, \citet{2024arXiv240417945P} found that $\sim10\%$ of galaxies at $\sim10^{10.3}\,\Msun$ are quenched \citep[consistent with][]{2013ApJ...777...18M}, and $\sim30\%$ of their total sample is a PSB at $z\sim2$.
 If these galaxies can be quickly rejuvenated, as the system studied in this work would suggest, then the total fraction of galaxies that go through a starburst-quenching phase may be higher.
 
-\citet{2023arXiv231215012C} found that lower mass quiescent galaxies (towards $10^{10.3}\,\Msun$) tend to be younger and more disky, pointing to a merger driven scenario.
-\citet{2023arXiv231212207A} found that at even lower masses ($<10^{9.5}\,\Msun$) Furthermore, the AGN quenching mechanism, which we believe to be responsible for the quenching in our system (Appendix~\ref{app:cause_qui}), is thought to operate at these redshifts \citep[e.g.][and references therein]{2023arXiv230805795B}.
+Furthermore, \citet{2023arXiv231215012C} found that lower mass quiescent galaxies (towards $10^{10.3}\,\Msun$) tend to be younger and more disky, pointing to a merger driven scenario.
+\citet{2023arXiv231212207A} found that at even lower masses ($<10^{9.5}\,\Msun$) Furthermore, the AGN quenching mechanism, which we believe to be responsible for the quenching in our system (Appendix~\ref{app:cause_qui}), is thought to operate at these redshifts \citep[e.g.][and references therein]{2023arXiv230805795B,2024arXiv240417945P}.
 

### 2024-05-22 paper/src/res.tex
Some Sarah changes

@@
 The left and right columns show the gas and stellar surface densities, respectively.
-The side-length of each panel is $30\,\kpc$, and the image is a projection through a box with the same side-length.}
+The side-length of each panel is $30\,\kpc$, and the image is a projection through a box with the same side-length.
+The colormap for the gas ranges from $10^3$ to $10^7\,\Msun/\pc^2$, while for the stars ranges from $10^2$ to $3\times10^5\,\Msun/\pc^2$.
+(A movie of this figure is given in \red{TBD}.)}
   \label{fig:projections}
@@
 Finally, in the lower panels of Figure~\ref{fig:fig1}, we show the distributions of \MgFe{} at different fixed \FeH{}.
-The (blue, orange, red, green) lines show the \MgFe{} distribution at a \FeH{} of ($-0.5$, $-0.375$, $-0.25$, $0.25$), in bins of width $0.05\,\dex$.
+The (blue, orange, red, green) lines show the \MgFe{} distribution at a \FeH{} of ($-0.5$, $-0.25$, $0$, $0.25$), in bins of width $0.05\,\dex$.
 The distributions of \MgFe{} are offset (but not rescaled) so that they do not overlap.
@@
 In the bimodal simulation, the distribution is still clearly bimodal, but the peaks are less well-separated, by $\sim0.1\,\dex$.
-In the unimodal simulation, the distributions are clearly unimodal, with the hint of some structure in the $\FeH=0.25\,\dex$ bin.
+In the unimodal simulation, the distributions are clearly unimodal, with the hint of some structure in the $\FeH=0.25\,\dex$ bin and at higher metallicities.
 
@@
   \caption{\textbf{At fixed metallicity, the low- and high-$\alpha$ sequence are cleanly separated in time, with an intervening quiescent period.} Here we show the star formation history of the high- and low-$\alpha$ sequences.
-The blue (low-$\alpha$) and orange (high-$\alpha$) histograms correspond to the dashed line cut made in the \MgFe-\FeH plane in Figure~\ref{fig:before_after}, at a fixed metallicity of $\FeH\sim0$.
+The blue (low-$\alpha$) and orange (high-$\alpha$) histograms correspond to the dashed line cut made in the \MgFe{}-\FeH{} plane in Figure~\ref{fig:before_after}, at a fixed metallicity of $\FeH=0$ with width $0.05\,\dex$.
 One can see that there is a nearly perfect separation in time between the formation of the high-$\alpha$ and low-$\alpha$ sequence, except for a brief overlap which can be attributed to the inadequacy of the linear cut model of the two sequences.
@@
   \includegraphics[width=\columnwidth]{before_after_sfh_by_iron.pdf}
-  \caption{\textbf{The timing of the quiescent period which divides the high- and low-$\alpha$ sequences is metallicity dependent.} The star formation history of stars at various fixed metallicities ($\FeH\sim0$, $-0.25$, and $-0.5\,\textrm{dex}$).
+  \caption{\textbf{The timing of the quiescent period which divides the high- and low-$\alpha$ sequences is metallicity dependent.} The star formation history of stars at various fixed metallicities ($\FeH=0$, $-0.25$, and $-0.5\,\textrm{dex}$) in bins of width $0.05\,\dex$.
 As in Figure~\ref{fig:before_after_sfh}, there is a quiescent period period which separates the formation of the low- and high-$\alpha$ sequence.
@@
   \includegraphics[width=\textwidth]{SFR_alpha.pdf}
-  \caption{\textbf{A global suppression of star formation is associcated with a decrease in \MgFe{}, which is seen in the bimodal simulation but not in the unimodal simulation.} Here, we show both the SFR of the central galaxy ($r<15\,\kpc$) and the median \MgFe{} for gas at $2\,\kpc<r<5\,\kpc$ at a fixed \FeH{} bin centered on $-0.2$ with width $0.02\,\dex$.
+  \caption{\textbf{A global suppression of star formation is associcated with a decrease in \MgFe{}, which is seen in the bimodal simulation but not in the unimodal simulation.} Here, we show both the SFR of the central galaxy ($r<15\,\kpc$) and the median \MgFe{} for gas at $2\,\kpc<r<5\,\kpc$ at a fixed \FeH{} bin centered on $0$ with width $0.05\,\dex$.
 The left panel shows the bimodal simulation while the right panel shows the unimodal simulation.
-The time of the merger (i.e., the second pericenter) is indicated by the vertical dashed line.
-In the bimodal simulation, the star formation is suppressed after the merger.
+A vertical dashed line at $2\,\Gyr$ in each plot indicates the approximate time of the merger, but before complete coalescence.
+In the left panel, a shaded region from $2.5\,\Gyr$ to $2.75\,\Gyr$ indicates the approximate period of quiescence shown in Figure~\ref{fig:before_after_sfh}.
 This suppression of star formation is associated with a sudden drop in the median \MgFe{} of the gas.

### 2024-05-30 paper/src/dis.tex
Add ref to new dwarf AGN paper

@@
 Furthermore, \citet{2023arXiv231215012C} found that lower mass quiescent galaxies (towards $10^{10.3}\,\Msun$) tend to be younger and more disky, pointing to a merger driven scenario.
-\citet{2023arXiv231212207A} found that at even lower masses ($<10^{9.5}\,\Msun$) Furthermore, the AGN quenching mechanism, which we believe to be responsible for the quenching in our system (Appendix~\ref{app:cause_qui}), is thought to operate at these redshifts \citep[e.g.][and references therein]{2023arXiv230805795B,2024arXiv240417945P}.
+\citet{2023arXiv231212207A} found that at even lower masses ($<10^{9.5}\,\Msun$) Furthermore, the AGN quenching mechanism, which we believe to be responsible for the quenching in our system (Appendix~\ref{app:cause_qui}), is thought to operate at these redshifts \citep[e.g.][and references therein]{2023arXiv230805795B,2024arXiv240417945P,2024arXiv240518685M}.
 

### 2024-05-31 paper/src/res.tex
Update movie figure in text

@@
   \centering
-  \includegraphics[width=\textwidth]{surfdens.pdf}
-  \caption{The surface density projections of the gas and stars over time of the idealized merger simulation with $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$ (i.e., the ``bimodal'' simulation).
+
+    \gridline{\fig{all_L30/all_L30_frame60.pdf}{0.3\textwidth}{}
+              \fig{all_L30/all_L30_frame70.pdf}{0.3\textwidth}{}
+              \fig{all_L30/all_L30_frame80.pdf}{0.3\textwidth}{}
+              }
+    \gridline{\fig{all_L30/all_L30_frame90.pdf}{0.3\textwidth}{}
+              \fig{all_L30/all_L30_frame100.pdf}{0.3\textwidth}{}
+              \fig{all_L30/all_L30_frame110.pdf}{0.3\textwidth}{}
+              }
+    \gridline{\fig{all_L30/all_L30_frame120.pdf}{0.3\textwidth}{}
+              \fig{all_L30/all_L30_frame200.pdf}{0.3\textwidth}{}
+              \fig{all_L30/all_L30_frame320.pdf}{0.3\textwidth}{}
+              }
+  % \includegraphics[width=\textwidth]{surfdens.pdf}
+  \caption{The surface density projections of the gas and stars over time of the idealized merger simulation with $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$ (the ``bimodal'' simulation).
 Every panel is oriented with respect to the final ($t=8\,\Gyr$) snapshot.
@@
 The side-length of each panel is $30\,\kpc$, and the image is a projection through a box with the same side-length.
-The colormap for the gas ranges from $10^3$ to $10^7\,\Msun/\pc^2$, while for the stars ranges from $10^2$ to $3\times10^5\,\Msun/\pc^2$.
+The colormap for the gas ranges from $1$ to $10^2\,\Msun/\pc^2$, while for the stars ranges from $1$ to $10^4\,\Msun/\pc^2$.
 (A movie of this figure is given in \red{TBD}.)}

### 2024-05-31 paper/src/dis.tex
Update infall interpretations

@@
 
-\subsection{Dilution Interpretation}\label{ssec:dilute}
+\subsection{Infall Interpretations}\label{ssec:dilute}
 In some previous work, it was reported that the bimodality is a consequence of a sudden deposition of metal-poor, $\alpha$-poor gas by a satellite or cosmological filament -- i.e., a ``dilution'' \citep{2020MNRAS.491.5435B,2021MNRAS.503.5846R}.
@@
 We have shown that minor changes to the orbit of our idealized merger can result in outcomes that are either bimodal or unimodal.
-The content of gas that is delivered to the system is similar between the two regimes, and so our simulations do not support the dilution interpretation.
-However, this may be because the inflowing gas is too enriched, arising from an unrealistic feedback and enrichment routine, or from the unrealistic aspects of our setup.
-Our work does argue against the necessity of the dilution interpretation, but we also cannot completely rule it out.
+The content of gas that is delivered to the system is nearly identical regardless of the orbit, and so the dilution interpretation is not applicable to our simulations.
+
+The longer-standing two-infall class of models argue that the two sequences diverge due to two episodic accretion episodes, with some possible enrichment of the second episode arising from an associated satellite \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}.
+As mentioned in the previous paragraph, our simulations do not support a strict gas dilution interpretation, but it was recently elaborated by \citet{2024arXiv240511025S} that these models also argue for a star formation gap between the two accretion episodes \citep[see also][]{1996ASPC...92..307G,1998A&A...338..161F,2000A&A...358..671G}.
+This gap is starvation-driven and can last several \Gyr{}.
+The present work argues for a starburst-driven quiescence followed by a rapid rejuvenation, with the entire process taking less than $1\,\Gyr$ and the gap only lasting a few hundred \Myr{}.
+The physical origin and some details are different, but one can appreciate that the bimodality arises from the same physical process.\footnote{Compare Section~\ref{ssec:formqui} to the first key result in the Conclusions of \citet{2024arXiv240511025S}.}
 

### 2024-05-31 paper/src/dis.tex
Add more gap citations

@@
 The longer-standing two-infall class of models argue that the two sequences diverge due to two episodic accretion episodes, with some possible enrichment of the second episode arising from an associated satellite \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}.
-As mentioned in the previous paragraph, our simulations do not support a strict gas dilution interpretation, but it was recently elaborated by \citet{2024arXiv240511025S} that these models also argue for a star formation gap between the two accretion episodes \citep[see also][]{1996ASPC...92..307G,1998A&A...338..161F,2000A&A...358..671G}.
+As mentioned in the previous paragraph, our simulations do not support a strict gas dilution interpretation, but it was recently elaborated by \citet{2024arXiv240511025S} that these models also argue for a star formation gap between the two accretion episodes \citep[see also][]{1996ASPC...92..307G,1998A&A...338..161F,2000A&A...358..671G,2015A&A...578A..87S,2020A&A...640A..81N}.
 This gap is starvation-driven and can last several \Gyr{}.

### 2024-07-01 TNG/note/lowda.py
Misc note

@@ -134,18 +134,20 @@ def load_zoom_group(outputDir, snapnum, nproc=16, types=[0, 4, 5], fields=None):
 class EmptyClass:
     pass
 
-def load_galaxy(snapnum, subID_99, rhalf_fac=2, phys=True, load_DM=False,
+def load_galaxy(snapnum, subID, subIDat99=True, rhalf_fac=2, phys=True, load_DM=False,
                 TNGbase='/n/holylfs05/LABS/hernquist_lab/IllustrisTNG/Runs/L35n2160TNG/output/'):
     # create output object
     galaxy = EmptyClass()
     
-    # subID_99 is the subhalo ID at snapshot 99
     header = arepo.Snapshot(TNGbase, snapnum, onlyHeader=True)
     h = header.HubbleParam
     a = header.Time
     galaxy.header = header
     
-    treeMPB = il.sublink.loadTree(TNGbase, 99, subID_99, onlyMPB=True)
+    if subIDat99:
+        treeMPB = il.sublink.loadTree(TNGbase, 99, subID, onlyMPB=True)
+    else:
+        treeMPB = il.sublink.loadTree(TNGbase, snapnum, subID, onlyMPB=True)
     galaxy.treeMPB = treeMPB
     
     # retrieve subID and subhalo at given snapnum

### 2024-07-01 paper/src/abs.tex
First draft edits

@@
     The nuclear abundance distribution of stars encodes the history of the gas-phase abundance in the Milky Way.
-Without a large, unbiased sample of stellar ages, the exact timing and nature of this history must be \textit{inferred} from the abundances.
-In the two-dimensional plane of \alphaFe-\FeH, it is now clear that two separate populations exist - the low-$\alpha$ and high-$\alpha$ sequences.
+Without a large, unbiased sample of highly precise stellar ages, the exact timing and nature of this history must be \textit{inferred} from the abundances.
+In the two-dimensional plane of \alphaFe-\FeH, it is now clear that two separate populations exist -- the low-$\alpha$ and high-$\alpha$ sequences.
 Structure in the nuclear abundance distribution can arise from many processes -- proposals include specific gas infall scenarios, radial migration, high-redshift clump formation, and various effects associated with galaxy mergers, among others.

### 2024-07-01 paper/src/con.tex
First draft edits

@@
 In this work, using idealized merger simulations, we have shown that (1) a starburst, followed by (2) a brief ($\sim300\,\Myr$) quiescent period, followed by (3) rejuvenation can lead to a bimodal abundance structure.
-We found that the starburst-to-quiescent period allowed for prodigious Fe-enrichment without any corresponding $\alpha$-enrichment.
-This ``phoenix hypothesis'' would predict that, for stars at a given \FeH{}, there would be a $\sim300\,\Myr$ gap in stellar ages at $\sim8\,\Gyr$.
+We found that the starburst-to-quiescent period allowed for prodigious Fe-enrichment without any contemperaneous $\alpha$-enrichment.
+This sequence of events, somewhat resembling the life cycle of a phoenix, would predict that for stars at a given \FeH{}, there would be a $\sim300\,\Myr$ gap in stellar ages at $\sim8\,\Gyr$.
 Furthermore, stars which form directly after this gap would have lower \alphaFe{} than stars which form slightly later ($\sim1\,\Gyr$).
@@
 In the absence of highly precise stellar ages, that history must be largely inferred.
+There are many ways in which a galaxy could end up with the coarse-grained structure we can observe in the present day.
+We have argued in this work that a brief, starburst-driven quiescent phase is one of them.

### 2024-07-01 paper/src/dis.tex
First draft edits

--- 2024-05-31 paper/src/dis.tex
@@
 This drop can be understood in terms of the mechanics of the galaxy formation model as described in Section~\ref{ssec:gfm}.
-When a star particle forms, it only takes $\sim40\,\Myr$ before the last Type II SN has gone off and Fe enrichment is dominated by Type Ia SNe.
-As a result, during the quiescent phase there is relatively little $\alpha$-element production.
-On the other hand, star particles are still able to generate Fe through Type Ia SNe which have a much longer period of influence.
+When a star particle forms, it only takes $\sim40\,\Myr$ before the last Type II SN has gone off and its material enrichment is dominated by Fe from Type Ia SNe.
+As a result, during the quiescent phase which lasts a few hundred Myr, there is relatively little $\alpha$-element production.
+On the other hand, star particles are still able to generate Fe through Type Ia SNe which have a longer period of influence.
+The fact that the quiescent period is preceded by a starburst is important.
+Even though star particles produce Fe through the Type Ia channel for Gyr, younger star particles still produce much more Fe than older star particles.
 In the TNG model, the number of Type Ia SNe decays with time as $(t/\tau_8)^{-s}$, where $\tau_8=40\,\Myr$ is the lifetime of an $8\,\Msun$ star and $s=1.12$.
-Therefore, the burst of star formation at $t\sim2.25\,\Gyr$ is able to generously produce Fe starting at $2.5\,\Gyr$, when the drop in \MgFe{} is the most steep.
+Therefore, the burst of star formation at $t\sim2.25\,\Gyr$ is able to generously produce Fe starting at $2.5\,\Gyr$, when is indeed when the drop in \MgFe{} is the most steep.
 
@@
 Furthermore, if the proposed starburst-quenching phase is driven by AGN feedback, then the outcome of any particular cosmological simulation with regards to the bimodality is intimately tied to its AGN model.
-Unfortunately, such models are highly uncertain \red{cite}.
+Unfortunately, such models are highly uncertain \citep[e.g.][]{2022MNRAS.511.3751H}.
 
@@
 In the post-starburst regime, they claim galaxies are $\alpha$-enhanced.
-From their Figure~8 it is difficult to quantify the difference between the quenched and non-quenched galaxies as the two populations almost completely overlap.
-We do find that the bulk stellar \MgFe{} is enhanced after the merger in our fiducial simulation, but only at the $\sim0.01\,\dex$ level.
+We do find that the bulk stellar \MgFe{} is enhanced after the merger in our bimodal simulation compared to the isolated simulation, but only at the $\sim0.01\,\dex$ level.
 
@@
 The separation of the sequences follows from the rapidity of the dilution.
-This was elaborated upon by \citet{2021MNRAS.503.5868R} who described a setup where the low-$\alpha$ disk forms inclined relative to the high-$\alpha$ disk.
+This was elaborated upon by \citet{2021MNRAS.503.5868R} who described a zoom where the low-$\alpha$ disk forms out of a relatively pristine cosmological filament.
+This disk is inclined relative to the high-$\alpha$ disk, with the two disks later tidally realigning.
+The longer-standing two-infall class of models argue that the two sequences diverge due to two episodic accretion episodes, with some possible enrichment of the second episode arising from an associated satellite \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}.
 
@@
 
-The longer-standing two-infall class of models argue that the two sequences diverge due to two episodic accretion episodes, with some possible enrichment of the second episode arising from an associated satellite \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}.
-As mentioned in the previous paragraph, our simulations do not support a strict gas dilution interpretation, but it was recently elaborated by \citet{2024arXiv240511025S} that these models also argue for a star formation gap between the two accretion episodes \citep[see also][]{1996ASPC...92..307G,1998A&A...338..161F,2000A&A...358..671G}.
+It was recently elaborated by \citet{2024arXiv240511025S} that these models also argue for a star formation gap between the two accretion episodes \citep[see also][]{1996ASPC...92..307G,1998A&A...338..161F,2000A&A...358..671G,2015A&A...578A..87S,2020A&A...640A..81N}.
 This gap is starvation-driven and can last several \Gyr{}.
@@
 \subsection{Observational Connections: High Redshift Quenching}\label{ssec:obshiz}
-Our main argument in this paper is that the Milky Way underwent a brief quiescent phase induced by a starburst at $z\sim2$.
-In observations, a Milky Way-analogue would then be identified as a post-starburst galaxy (PSB).
+If the Milky Way underwent a starburst to quiescent to rejuvenation sequence, as we argue in this paper, then an an analogue at $z\sim2$ would be identified as a post-starburst galaxy (PSB).
 With abundance matching, we expect the Milky Way's total stellar mass to be $\sim10^{10.3}\,\Msun$ at $z\sim2$ \citep{2013ApJ...771L..35V}.
@@
 First, PSBs are not uncommon.
-\citet{2023ApJ...953..119P} found that in massive galaxies ($M_* > 10^{10.6}\,\Msun$) the fraction of PSBs increases from $\sim2.7\%$ ($99/3655$) at $1.0 < z < 1.44$ to $\sim8\%$ ($89/1118$) at $2.16 < z < 2.5$.
-Later, \citet{2024arXiv240417945P} found that $\sim10\%$ of galaxies at $\sim10^{10.3}\,\Msun$ are quenched \citep[consistent with][]{2013ApJ...777...18M}, and $\sim30\%$ of their total sample is a PSB at $z\sim2$.
+\citet{2023ApJ...953..119P} found that in massive galaxies ($M_* > 10^{10.6}\,\Msun$) the fraction of PSBs (inferred ages $< 800\,\Myr$) increases from $\sim2.7\%$ ($99/3655$) at $1.0 < z < 1.44$ to $\sim8\%$ ($89/1118$) at $2.16 < z < 2.5$ \citep[see also][]{2012ApJ...745..179W,2019ApJ...874...17B}.
+Later, \citet{2024arXiv240417945P} found that $\sim10\%$ of galaxies at $\sim10^{10.3}\,\Msun$ are quenched \citep[consistent with][]{2013ApJ...777...18M}, and $\sim30\%$ of their quiescent sample is a PSB at $z\sim2$.
 If these galaxies can be quickly rejuvenated, as the system studied in this work would suggest, then the total fraction of galaxies that go through a starburst-quenching phase may be higher.
@@
 Furthermore, \citet{2023arXiv231215012C} found that lower mass quiescent galaxies (towards $10^{10.3}\,\Msun$) tend to be younger and more disky, pointing to a merger driven scenario.
-\citet{2023arXiv231212207A} found that at even lower masses ($<10^{9.5}\,\Msun$) Furthermore, the AGN quenching mechanism, which we believe to be responsible for the quenching in our system (Appendix~\ref{app:cause_qui}), is thought to operate at these redshifts \citep[e.g.][and references therein]{2023arXiv230805795B,2024arXiv240417945P,2024arXiv240518685M}.
+\citet{2023arXiv231212207A} found that at even lower masses ($<10^{9.5}\,\Msun$) There is also evidence that the AGN quenching mechanism, which we believe to be responsible for the quenching in our system (Appendix~\ref{app:cause_qui}), is operating at these redshifts \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024arXiv240518685M,2024Natur.630...54B}.
+
+Overall, the starburst-driven quenching mechanism proposed in this work is allowed by high-redshift observations.
 
@@
 However, the situation might not be completely hopeless.
-The necessary sample size is small, and so copious time and instruments can be dedicated.
-Moreover, only \textit{relative} ages need to be determined, so a sort of differential approach may yield interesting results.
-In addition to the presence of the gap, our work also predicts that the timing of the gap is \FeH{} dependent.
+The necessary sample size is small, and so copious time and instruments can be dedicated to each source.
+Moreover, only \textit{relative} ages need to be determined, so a sort of differential approach may be prudent.
+
+In addition to the presence of the gap, our work also predicts that: (1) the timing of the gap is \FeH{} dependent, and that (2) stars which form immediately after the gap are $\alpha$-poor compared to stars which form slightly later (see Figure~\ref{fig:alpha_vs_tform}).
+However, both of these tests rely on the precise age estimates.
 
@@
 There is also the perennial problem of diffusion within the hydrodynamics solver.
-In purely Lagrangian solvers, there is no diffusion between resolution elements, while in Eulerian codes the diffusion can be quite high.
-AREPO limits the numerical diffusion by allowing the mesh to move in a quasi-Lagrangian manner, and using a second-order solver \citep{2010MNRAS.401..791S}.
+In purely Lagrangian solvers, there is no diffusion between resolution elements, while in Eulerian codes the diffusion can be quite high.\footnote{No galaxy formation simulation is fully Lagrangian since there must be, at a minimum, mass exchange between star particles and gas.
+Here we just mean that there is no mass exchange between gas elements.} AREPO limits the numerical diffusion by allowing the mesh to move in a quasi-Lagrangian manner, and using a second-order solver \citep{2010MNRAS.401..791S}.
 In FIRE-2 \citep{2018MNRAS.480..800H}, which uses the Lagrangian code GIZMO \citep{2015MNRAS.450...53H}, a subgrid turbulent metal diffusion model was used.

### 2024-07-01 paper/src/int.tex
Some Sarah changes
First draft edits

--- 2024-04-29 paper/src/int.tex
@@
 However, this space is highly degenerate, and so the effective number of dimensions is much smaller -- even possibly compressed to just \FeH{} and age \citep{2019ApJ...883..177N}.
-Two elements in particular have received particular interest - Fe and $\alpha$-elements.
+Two elements have received particular interest - Fe and elements produced by the $\alpha$-process.
 Type Ia and Type II supernovae are the main contributors of Fe and $\alpha$ enrichment.
@@
 This bimodality is typically separated into the high-$\alpha$ and low-$\alpha$ sequences.
-The high-$\alpha$ sequence is more centrally compact and vertically extended than the low-$\alpha$ sequence.
+These sequences are also associated with differences in their physical extent -- the high-$\alpha$ sequence is more centrally compact and vertically extended than the low-$\alpha$ sequence.
 
@@
 Naturally, many different processes that could lead to structure in the abundance plane have been discussed in the literature.
-They can be separated into two broad classes: (1) structure arising from internal processes, and (2) structure arising from external processes.
-We will summarize these classes of explanations in turn.
-
 An early explanation of the bimodality is the two-phase gas infall model \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}.
@@
 Because the typical SFR is high, these stars are $\alpha$-enhanced.
-In some variants, star formation halts completely before a second supply of pristine gas falls into the Galaxy.
+In some variants, star formation halts completely before a second supply of pristine gas falls into the Galaxy \citep[][and references therein]{2024arXiv240511025S}.
 This dilutes the gas supply from which the thin disk forms more gradually.
 The thin disk is then more $\alpha$-poor because its associated SFR is lower.
+
+A later argument by \citet{2021MNRAS.501.5176K} asserts that the two sequences follow from two phases of gas infall, except driven by stellar feedback instead of cosmological inflow.
+An initial bursty phase follows from the direct collapse of the gaseous halo.
+The disk has a high SFR leading to the formation of the high-$\alpha$ sequence.
+Feedback then halts the inflow, and a slower accretion of high-angular momentum and metal-rich gas commences, forming the low-$\alpha$ sequence.
 
@@
 
-Yet another explanation invoking an internal process is that the formation of clumps at high redshift are responsible for both the chemistry and dynamics of the high-$\alpha$ sequence \citep{2019MNRAS.484.3476C,2020MNRAS.492.4716B,2021MNRAS.502..260B,2023ApJ...953..128G}.
+Yet another explanation, which also invokes an internal process, is that the formation of clumps at high redshift are responsible for both the chemistry and dynamics of the high-$\alpha$ sequence \citep{2019MNRAS.484.3476C,2020MNRAS.492.4716B,2021MNRAS.502..260B,2023ApJ...953..128G}.
 Instabilities are thought to form clumps in gas-rich disks, and such clumps are seen at intermediate redshifts \citep[$z\sim2$;][]{2005ApJ...627..632E,2007ApJ...658..763E}.
@@
 
-In this work, we explored an idealized merger simulation which resembles the merger between the Milky Way and GSE.
+In this work, we explored an idealized simulation which resembles the merger between the Milky Way and GSE.
 We found that in certain configurations, which have only minor differences in their orbit, a bimodal distribution of stellar abundances in the \alphaFe{}-\FeH{} plane is produced.
@@
   \includegraphics[width=\textwidth]{figure1.pdf}
-  \caption{\textbf{The abundance bimodality seen in the Milky Way can be reproduced in some idealized merger simulations.} In the upper panels, we show the distribution of stars in the \MgFe-\FeH plane.
-The left panel shows the observed distribution in the Milky Way from ASPCAP DR17 \citep[][J.A.~Holtzman et al., in preparation]{2016AJ....151..144G}, while the right two panels show two idealized merger simulations.
-The idealized merger simulations are nearly identical, except that the bimodal simulation has a starting radius of $129\,\kpc$, while the unimodal simulation has a starting radius of $142\,\kpc$.
-We emphasize that the labels ``unimodal'' and ``bimodal'' are of the \textit{outcome} of the simulation, and do not reflect a particular choice in the setup.
-The bottom panels show the distribution of \MgFe at fixed \FeH.
-The colors indicate the fixed \FeH values, which are $-0.5$, $-0.375$, $-0.25$, and $0.25$.
-The Milky Way (left panels) exhibits a strong bimodal distribution of \MgFe at various \FeH.
-The idealized merger simulation marked as bimodal (center panels) also exhibits a bimodal distribution of \MgFe, though the structure is not as strongly defined.
-The idealized merger simulation marked as unimodal exhibits only weak structure, if any at all.}
+  \caption{\textbf{The abundance bimodality seen in the Milky Way can be reproduced in some idealized merger simulations.} In the upper panels, we show the distribution of stars in the \MgFe{}-\FeH{} plane.
+The lower panels show the distribution of \MgFe{} at a fixed \FeH{} bin of width $0.05\,\dex$.
+The colors indicate the fixed \FeH values, which are $-0.5$, $-0.25$, $0$, and $0.25$.
+The left column shows the observed distribution in the Milky Way from ASPCAP DR17 \citep[][J.A.~Holtzman et al., in preparation]{2016AJ....151..144G}, while the right two columns show two idealized merger simulations.
+The idealized merger simulations are nearly identical, except that in the bimodal simulation the satellite has a starting radius of $129\,\kpc$, while in the unimodal simulation it has a starting radius of $142\,\kpc$.
+The labels ``unimodal'' and ``bimodal'' are of the \textit{outcome} of the simulation, and do not reflect a particular choice in the setup.
+The Milky Way (left column) exhibits a strong bimodal distribution of \MgFe{} at various \FeH{}.
+The idealized merger simulation marked as bimodal (center column) also exhibits a bimodal distribution of \MgFe{}, though the structure is not as strongly defined.
+The idealized merger simulation marked as unimodal (right column) exhibits only weak structure, if any at all.}
   \label{fig:fig1}

### 2024-07-01 paper/src/met.tex
First draft edits

@@
 The gas has a softening length $2.5\times$ the cell size, with a minimum size of $10\,\pc$.
-Snapshots were saved at intervals of $0.025\,\Gyr$.
+Snapshots were saved at intervals of $25\,\Myr$.
 
@@
 Some of the simulations in this orbital grid resulted in bimodal abundance distributions, while some had little to no structure in the abundance distribution plane.
-We show the abundance plane for all $27$ simulations in Appendix~\ref{app:allsims}, but for the main body of this work we consider two representative simulations in detail.
+We show the abundance plane for all $27$ simulations in Appendix~\ref{app:allmerge}, but for the main body of this work we consider two representative simulations in detail which were chosen based on their structure in the abundance plane as shown in Figure~\ref{fig:fig1}.
 For the bimodal simulation, we chose the simulation with $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$.
@@
 
-We show the bimodal and unimodal orbits in Figure~\ref{fig:orbit}.
-The centers of  The upper and middle panels show the orbits in the $x$-$y$ and $x$-$z$ planes, respectively.
+We show the bimodal and unimodal simulations' orbits in Figure~\ref{fig:orbit}.
+For the center of the central and satellite, we use the position of the particle with minimum potential in each substructure identified by \texttt{SUBFIND}.
+The upper and middle panels show the orbits in the $x$-$y$ and $x$-$z$ planes, respectively.
 The lower panel shows the separation distance as a function of time.
-The orbits are initially retrograde, but quickly radialize after the first pericentric passage.
-Coalescence occurs rapidly after the second pericentric passage at $\sim2\,\Gyr$.
-Soon after, \texttt{SUBFIND} does not recognize the satellite as a separate subhalo as the two galaxies coalesce.
+The orbit is initially retrograde, but quickly radializes after the first pericentric passage.
+Coalescence occurs rapidly after the second pericentric passage at $\sim2\,\Gyr$, and \texttt{SUBFIND} ceases to recognize the satellite as a separate subhalo.
 
@@
 The orbit begins retrograde but then radializes after the first pericentric passage.
-The satellite then coalesces quickly after the second pericentric passage, after about $\sim2\,\Gyr$ of evolution.}
+The satellite then coalesces quickly after the second pericentric passage, after $\sim2\,\Gyr$ of evolution.}
     \label{fig:orbit}
@@
 \end{enumerate}
-There are a few things to note: (1) The exact timings are metallicity-dependent.
+There are a few things to note about this model: (1) The exact timings are metallicity-dependent.
 (2) The \MgFe{} of ejected gas from Type II SNe is mass/time-dependent, with more massive stars contributing more Mg than less massive stars.
@@
 When comparing galaxy simulations to the observed solar neighborhood, some ambiguity arises in how to make a ``solar neighborhood-like'' selection of star particles.
-Naturally, this selection is dependent on the posed question.
-In this work, this is the formation of the abundance bimodality.
+Naturally, this selection is dependent on the posed question, which in this work is the formation of the abundance bimodality.
 The Sun is known to sit near the end of the thick disk, where the thick and thin disk have comparable surface densities \citep[the ratio of thick-to-thin is $\sim12\%$][]{2016ARA&A..54..529B}.
@@
 In particular, we select all star particles with angular momenta within $30\%$ of $0.2\times8\,\kpc\times220\,\kms$ -- as well as requiring $\left| z \right| < 3\,\kpc$.
-
-This choice of angular momentum may seem unrealistic.
-However, it corresponds to roughly selecting star particles with radii between $2$ and $5\,\kpc$.
-As discussed in Section~\ref{ssec:iso_setup}, our Milky Way-like galaxy at $3\,\Gyr$ is more compact than the Milky Way's thick disk.
+This corresponds to roughly selecting star particles with radii between $2$ and $5\,\kpc$.

### 2024-07-01 paper/src/res.tex
First draft edits

@@
 \subsection{Surface Density Projections}\label{ssec:projections}
-Before dissecting the simulated galaxies in detail, we first take a look at the surface density projections of the gas and stars in the central region, situated on the central galaxy.
+Before dissecting the simulated galaxies in detail, we first take a look at the surface density projections of the gas and stars in the central region, situated on the central galaxy in the bimodal simulation.
 This is shown in Figure~\ref{fig:projections}.
 In each grouping of four, the bottom and top rows show the face-on and edge-on views, respectively.
-The left and right columns show the gas and stellar surface density.
+The left and right columns show the gas (blue) and stellar (orange) surface density, respectively.
 Each panel is oriented with respect to the stellar angular momentum of the final snapshot ($t=8\,\Gyr$).
 The angular momentum is computed using all star particles within the half-mass radius.
+
+We can see that the galaxy grows in size after the merger.
+Additionally, the galaxy's orientation continues to change even within the last $3\,\Gyr$.
+The final galaxy is oriented $\sim126\degree$ with respect to the initial orientation of the central galaxy's gas halo.
+The dynamical and kinematic consequences of such a gas-rich merger is beyond the scope of our current work.
 
@@
   % \includegraphics[width=\textwidth]{surfdens.pdf}
-  \caption{The surface density projections of the gas and stars over time of the idealized merger simulation with $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$ (the ``bimodal'' simulation).
+  \caption{Frames from a movie showing a surface density projection of the bimodal simulation over time.
+In each frame, the left/right (blue/orange) column shows the gas/star surface density.
+The upper/lower panels show the edge-on and face-on view.
 Every panel is oriented with respect to the final ($t=8\,\Gyr$) snapshot.
-In each grouping of four, the lower and upper rows show the face-on and edge-on projections, respectively.
-The left and right columns show the gas and stellar surface densities, respectively.
 The side-length of each panel is $30\,\kpc$, and the image is a projection through a box with the same side-length.
 The colormap for the gas ranges from $1$ to $10^2\,\Msun/\pc^2$, while for the stars ranges from $1$ to $10^4\,\Msun/\pc^2$.
-(A movie of this figure is given in \red{TBD}.)}
+(A full movie, also for the unimodal and isolated simulations, is here \red{TBD}.)}
   \label{fig:projections}
@@
 The unimodal simulation is identical, except that $R_0=129\,\kpc$.
+The bimodal and unimodal labels are of the outcome of the simulation, and do not reflect any particular choice made in their setup.
 
@@
 
-Finally, in the lower panels of Figure~\ref{fig:fig1}, we show the distributions of \MgFe{} at different fixed \FeH{}.
+In the lower panels of Figure~\ref{fig:fig1}, we show the distributions of \MgFe{} at different fixed \FeH{}.
 The (blue, orange, red, green) lines show the \MgFe{} distribution at a \FeH{} of ($-0.5$, $-0.25$, $0$, $0.25$), in bins of width $0.05\,\dex$.
@@
 In the bimodal simulation, the distribution is still clearly bimodal, but the peaks are less well-separated, by $\sim0.1\,\dex$.
-In the unimodal simulation, the distributions are clearly unimodal, with the hint of some structure in the $\FeH=0.25\,\dex$ bin and at higher metallicities.
+In the unimodal simulation, there is a hint of some structure at $\FeH \gtrsim 0.25$, but there is not a strong multimodal structure.
 
@@
 Nonetheless, it is clear that the high-$\alpha$ sequence forms before and during the merger (middle panels), and that the low-$\alpha$ sequence forms after the merger (right panel).
-We show a dashed line given by $-0.1\FeH + 0.31$, which is a crude way of separating the high- and low-$\alpha$ sequence.
+We show a dashed line given by $-0.1\times\FeH + 0.31$, which is a crude way of separating the high- and low-$\alpha$ sequence.
 
-It is informative to examine the star formation history (SFH) split into the high- and low-$\alpha$ sequences, shown in Figure~\ref{fig:before_after_sfh}.
+It is informative to examine the star formation history (SFH) split into the high- and low-$\alpha$ sequences at a fixed \FeH{}, shown in Figure~\ref{fig:before_after_sfh}.
 The high- and low-$\alpha$ sequences (blue and orange) are defined as the star particles lying above and below the dashed line in Figure~\ref{fig:before_after}, respectively.
 We show this only in a narrow bin of width $0.1\,\dex$ at $\FeH\sim0$.
-One can see a very clear separation in time between the high- and low-$\alpha$ sequences, with the high-$\alpha$ sequence forming before the low-$\alpha$ sequence.\footnote{There is a small amount of low-$\alpha$ formation at the very end of the high-$\alpha$ sequence, but this can be understood as simply an inadequacy in our simple way of separating the two sequences.} Furthermore, there is a brief period of $\sim300\,\Myr$ between the two sequences where no stars have formed.
+We chose this value of \FeH{} because here the valley of the bimodality is deepest (see Figure~\ref{fig:fig1}).
+One can see a very clear separation in time between the high- and low-$\alpha$ sequences, with the high-$\alpha$ sequence forming before the low-$\alpha$ sequence.\footnote{There is a small amount of low-$\alpha$ formation at the very end of the high-$\alpha$ sequence, but this can be understood as simply an inadequacy in our simple way of separating the two sequences.
+Alternatively, one could assert that the separation in time is the real delineation between the two sequences, and that the boundary in the abundance plane has only mild contamination.} Furthermore, there is a brief period of $\sim300\,\Myr$ between the two sequences where no stars have formed.
 
 It can also be shown that the exact timing of this quiescent period is metallicity-dependent.
-We show the same SFH, but at varying bins in \FeH{} of $-0.5$, $-0.25$, and $0$ (blue, orange, and red, respectively).
+We show the same SFH in Figure~\ref{fig:before_after_sfh_by_iron}, but at varying bins in \FeH{} of $-0.5$, $-0.25$, and $0$ (blue, orange, and red, respectively).
 For clarity, we do not separate the SFHs by the high- and low-$\alpha$ sequences, but have verified that the same demarcation arises as in Figure~\ref{fig:before_after_sfh}.
@@
 \subsection{\alphaFe{} Behavior Associated with Quiescence}
-Given the sequence of events presented in Section~\ref{ssec:abundplane_build}, it is natural to suspect that the quiescent phase in Figure~\ref{fig:before_after_sfh} is responsible for the bimodal structure in Figure~\ref{fig:before_after}.
-We now examine this possibility more closely.
-
-In Figure~\ref{fig:SFR_alpha}, we show the SFR (blue lines) of each of the bimodal and unimodal galaxies (left and right panels, respectively) as well as the median \MgFe{} of the gas (orange lines) in a bin centered on $\FeH{}=-0.1$ with width $0.02\,\dex$.
-The SFR is shown for the entire galaxy ($r<15\,\kpc$) while the median \MgFe{} is shown for $2\,\kpc<r<5\,\kpc$.\footnote{The solar neighborhood-like selection of stars mostly selects stars at $2\,\kpc<r<5\,\kpc$.
-We choose to plot the median \MgFe{} of the gas at these radii, since it is that gas which is forming stars that ends up in our sample.
-On the other hand, we choose to show the SFR for the entire galaxy, as the enrichment from that star formation affects the entire galaxy.}
+We now examine more closely the natural suspicion that the quiescent phase in Figure~\ref{fig:before_after_sfh} is responsible for the bimodal structure in Figure~\ref{fig:before_after}.
+In Figure~\ref{fig:SFR_alpha}, we show the SFR (blue lines) of each of the bimodal and unimodal galaxies (left and right panels, respectively) as well as the median \MgFe{} of the gas (orange lines) in a bin centered on $\FeH{}=-0.1$ with width $0.05\,\dex$.
+The SFR is shown for the entire galaxy ($r<15\,\kpc$) while the median \MgFe{} is shown for $2\,\kpc<r<5\,\kpc$.\footnote{The solar neighborhood-like selection of stars (discussed in Section~\ref{ssec:solarneigh}) mostly selects stars at $2\,\kpc<r<5\,\kpc$.
+We choose to plot the median \MgFe{} of the gas at these radii, since it is roughly that gas which is forming stars that ends up in our sample.
+On the other hand, we choose to show the SFR for the entire galaxy, as the enrichment from that star formation affects the entire galaxy at this epoch.}
 
 The merger appears to induce a starburst, where the SFR rises from $\sim3.5\,\Msunyr$ at $\sim1\Gyr$ to a peak of $\sim12\,\Msunyr$ at $\sim2\,\Gyr$.
-This starburst is then followed by a quiescent period, with a depth of $\sim1\,\Msunyr$ and a duration of $\sim500\,\Myr$.
+This starburst is then followed by a quiescent period, with a minimum SFR of $\sim1\,\Msunyr$ and a duration of $\sim500\,\Myr$.
 The dip in SFR is not as pronounced as it was when we plotted the SFH at a particular iron (Figure~\ref{fig:before_after_sfh}).
-This quiescent period is associated with a sudden drop in \MgFe{}.
-In $\sim250\,\Myr$, \MgFe{} drops from $\sim0.35$ to $\sim0.2\,\dex$.
+This quiescent period is associated with a drop in \MgFe{} from $\sim0.35$ to $\sim0.2\,\dex$ in only $\sim250\,\Myr$.
 Once the SFR recovers $\sim500\,\Myr$ later, \MgFe{} again rises, but only to $\sim0.28\,\dex$.
 
-This behavior is present in the unimodal simulation (right panel) -- it does not display a period of suppressed star formation, and there is no associated drop in \MgFe{}.
+This behavior is absent in the unimodal simulation (right panel) -- while there is a starburst, it does not display a period of suppressed star formation, and there is no associated drop in \MgFe{}.
 It does still have a period of enhanced star formation, but this is actually coincident with an enhancement in \MgFe{}.
@@
 In the bimodal simulation, there is a clear gap in \MgFe{} during the period of quiescence followed by the brief formation of $\alpha$-deficient stars.
-In the unimodal simulation, on the other hand, there is no gap and the brief formation of $\alpha$-enhanced stars.
+In the unimodal simulation, on the other hand, there is no gap and instead a brief formation of $\alpha$-enhanced stars.
 
 \subsection{Cause of Quiescence}\label{ssec:cause_qui}
-The exact cause of quiescence in our simulation is not the main focus of our work.
-However, it appears to arise as a result of AGN activity triggered by the merger.
-We present some evidence of this in Appendix~\ref{app:cause_qui}.
+Why there is a quiescent period in the bimodal simulation but not the unimodal simulation probably has to do with some transient, stochastic property of the gas in and around the galaxy.
+In some states, the AGN is better able to quench the galaxy than in others.
+Verifying this further is beyond the scope of this work, but we show some evidence of the association in Appendix~\ref{app:cause_qui}.
 
@@
 The middle left panel shows the star particles that form before the merger ($\tform < 1.5\,\Gyr$), which form a weak sequence of star particles at the lowest \FeH and highest \MgFe.
-The middle right panel shows the star particles that form during the merger ($1.5\,\Gyr < \tform < 2.5\,\Gyr$).
-These star particless form the portion of the high-$\alpha$ sequence closest to the trough, and the density of star particless is higher than those that form before.
-The middle right panel shows the star particles which form after the merger ($\tform > 2.5\,\Gyr$).
+The middle right panel shows the star particles that form during the starburst ($1.5\,\Gyr < \tform < 2.5\,\Gyr$).
+These star particles form the portion of the high-$\alpha$ sequence closest to the trough, and the density of star particless is higher than those that form before.
+The right panel shows the star particles which form after the merger ($\tform > 2.5\,\Gyr$).
 These star particles form almost entirely below the trough.}
@@
   \includegraphics[width=\columnwidth]{before_after_sfh.pdf}
-  \caption{\textbf{At fixed metallicity, the low- and high-$\alpha$ sequence are cleanly separated in time, with an intervening quiescent period.} Here we show the star formation history of the high- and low-$\alpha$ sequences.
+  \caption{\textbf{At fixed metallicity, the low- and high-$\alpha$ sequence are cleanly separated in time by an intervening quiescent period.} Here we show the star formation history of the high- and low-$\alpha$ sequences.
 The blue (low-$\alpha$) and orange (high-$\alpha$) histograms correspond to the dashed line cut made in the \MgFe{}-\FeH{} plane in Figure~\ref{fig:before_after}, at a fixed metallicity of $\FeH=0$ with width $0.05\,\dex$.
-One can see that there is a nearly perfect separation in time between the formation of the high-$\alpha$ and low-$\alpha$ sequence, except for a brief overlap which can be attributed to the inadequacy of the linear cut model of the two sequences.
-Separating the formation periods lies a quiescent period with a duration of $\sim300\,\Myr$.}
+One can see that there is a nearly perfect separation in time between the formation of the high-$\alpha$ and low-$\alpha$ sequences by a quiescent period lasting $\sim300\,\Myr$.
+There is a small amount of contamination at the end of the high-$\alpha$ sequence which can be attributed to the inadequacy of the linear cut model of the two sequences.}
   \label{fig:before_after_sfh}
@@
 As in Figure~\ref{fig:before_after_sfh}, there is a quiescent period period which separates the formation of the low- and high-$\alpha$ sequence.
-However, one can see that the timing of the quiescent period is metallicity-dependent.
-It occurs earlier at lower metallicity, by $\sim300\,\Myr$ for the metallicities shown in this plot.}
+However, the timing of the quiescent period is metallicity-dependent.
+It occurs earlier at lower metallicities, by $\sim250\,\Myr$ for the metallicities shown in this plot.}
   \label{fig:before_after_sfh_by_iron}
@@
   \includegraphics[width=\columnwidth]{alpha_vs_tform.pdf}
-  \caption{The formation times and \MgFe{} values of star particles in the bimodal (blue) and unimodal (orange) simulations.
-In the bimodal simulation, a gap in stellar ages is briefly followed by the formation of $\alpha$-deficient star particles.
+  \caption{\textbf{In the bimodal simulation, a gap in stellar ages is briefly followed by the formation of $\alpha$-deficient star particles.} The formation times and \MgFe{} values of star particles in the bimodal (blue) and unimodal (orange) simulations.
 In the unimodal simulation, no gap is present and there is briefly the formation of $\alpha$-enhanced star particles at the same time.

### 2024-07-09 paper/src/abs.tex
Changes in response to comments

@@
 \begin{abstract}
-    The nuclear abundance distribution of stars encodes the history of the gas-phase abundance in the Milky Way.
+    The elemental abundance distribution of stars encodes the history of the gas-phase abundance in the Milky Way.
 Without a large, unbiased sample of highly precise stellar ages, the exact timing and nature of this history must be \textit{inferred} from the abundances.
 In the two-dimensional plane of \alphaFe-\FeH, it is now clear that two separate populations exist -- the low-$\alpha$ and high-$\alpha$ sequences.
-Structure in the nuclear abundance distribution can arise from many processes -- proposals include specific gas infall scenarios, radial migration, high-redshift clump formation, and various effects associated with galaxy mergers, among others.
+Structure in the elemental abundance distribution can arise from many processes -- proposals include specific gas infall scenarios, radial migration, high-redshift clump formation, and various effects associated with galaxy mergers, among others.
 In this work, we demonstrate another possible avenue for structure formation with clear observational predictions.
-We propose that the Galaxy underwent a starburst followed by a brief (hundreds of Myr) quiescent phase -- i.e., the Galaxy underwent a post-starburst rejuvenation sequence at $z\sim2$.
+In this scenario, the Galaxy underwent a starburst followed by a brief (hundreds of Myr) quiescent phase -- i.e., the Galaxy underwent a post-starburst rejuvenation sequence at $z\sim2$.
 A natural consequence of the quiescent phase is that stars in the valley of the bimodality do not form because: (1) the absence of enrichment from high-mass stars leads to a rapid reduction in \alphaFe{}, and (2) any time the gas spends in the abundance valley is deemphasized in the present day distribution because the star formation rate is lower.

### 2024-07-09 paper/src/dis.tex
Changes in response to comments

@@
 \section{Discussion}\label{sec:discussion}
-We have demonstrated that a bimodal structure in the nuclear abundance plane is associated with a brief quiescent phase in our idealized merger simulations.
+We have demonstrated that a bimodal structure in the elemental abundance plane is associated with a brief quiescent phase in our idealized merger simulations.
 We now construct a possible framework for understanding the formation of the bimodality, discuss its relation to prior work, and then discuss predictions and connections to observations.
@@
 The content of gas that is delivered to the system is nearly identical regardless of the orbit, and so the dilution interpretation is not applicable to our simulations.
+That being said, a removal of gas from the system either through star formation or through ejection could make dilution from infalling gas more efficient, so the two scenarios are not mutually exclusive.
 
@@
 \subsection{Direct Search for Quiescence}\label{ssec:obsqui}
-Figure~\ref{fig:before_after_sfh_by_iron} indicates a very direct observational test of the mechanism proposed in this work: for disk stars at a given \FeH{}, there should be a gap of $\sim300\,\Myr$ in ages at $\sim8\,\Gyr$.
-With a survey of properly chosen stars, this could potentially be achieved with a modestly sized (few hundred) sample of old stars with age uncertainties of $\sim1\%$.
-The present observational landscape for age dating of old stars is far from this goal.
+Figure~\ref{fig:before_after_sfh_by_iron} indicates a very direct observational test of the mechanism proposed in this work: for disk stars at a given \FeH{}, there should be a gap of $\sim300\,\Myr$ in ages at $\sim8\,\Gyr$, though in the Milky Way the gap could be larger.
+With a survey of properly chosen stars, this gap could be directly measured with a modestly sized (few hundred) sample of old stars with age uncertainties of $\sim1\%$.
 To our knowledge, the best method at these ages is differential analysis of solar twins, which can provide an age uncertainty of $\sim5\%$ \citep[e.g.][]{2014ApJ...795...23B,2018MNRAS.474.2580S}.
-However, this only works for stars with solar metallicity, where there is not a clear separation between the high- and low-$\alpha$ sequences (though a gap in ages may still be present).
+However, this has only been applied to stars with solar metallicity, where there is not a clear separation between the high- and low-$\alpha$ sequences (though a gap in ages may still be present).
+A sort of differential approach could be applied also at lower metallicities, which would just lack the absolute age calibration that the Sun provides.
 
-And so, this test may only be possible to a reader in the distant future.
-However, the situation might not be completely hopeless.
-The necessary sample size is small, and so copious time and instruments can be dedicated to each source.
-Moreover, only \textit{relative} ages need to be determined, so a sort of differential approach may be prudent.
+The gap could also be indirectly probed by a larger sample of slightly less precise ages.
+Astroseismology appears to be the most promising avenue.
+Currently the largest sample is APOKASC2 \citep{2018ApJS..239...32P}, which has $\sim3400$ stars with ages measured to $<20\%$ precision.\footnote{Errors here taken to be the maximum of the upper and lower age estimates in the public APOKASC2 catalog.} The upcoming PLATO mission is looking to measure $\sim20\textrm{k}$ stars with ages measured to $<10\%$ precision \citep{2024arXiv240605447R}.
+Further work is needed to determine how well these surveys could constrain the gap.
 

### 2024-07-09 paper/src/int.tex
Changes in response to comments

@@
 % What leads to distribution of heavy elements in a galaxy
-Elements heavier than hydrogen are produced through nuclear fusion.
-After Big Bang Nucleosynthesis, this only occurs in compact objects such as supernovae, dying low mass stars, and neutron star-neutron star mergers \citep[e.g.][]{2023A&ARv..31....1A}.
+Many elements heavier than hydrogen are produced through nuclear fusion in compact objects such as supernovae, dying low mass stars, and neutron star-neutron star mergers \citep[e.g.][]{2023A&ARv..31....1A}.
 By necessity, stars inherit the constituitive properties of the gas from which they formed.
 Moreover, the surface abundance of most elements for most stars do not change over most of their lifetime.
-We therefore have the unique opportunity to examine the historical record of the gas-phase abundance of a galaxy by way of the distribution of the surface abundances of stars.
+We therefore have the opportunity to examine the historical record of the gas-phase abundance of a galaxy by way of the distribution of the surface abundances of stars.
 
@@
 \citet{2018MNRAS.474.3629G} found what they referred to as a chemical dichotomy, and argued that it can come from either gas-rich mergers as described before or a ``compaction'' of the disk (we will return to this point in Section~\ref{ssec:cosmo}).
-Other authors highlight the metal content of the infalling gas, stating that the metal-poor gas associated with satellites can suddenly dilute or reset the disk's metallicity \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}
+Other authors highlight the metal content of the infalling gas, stating that the metal-poor gas associated with satellites can suddenly dilute or reset the disk's metallicity \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}.
+This interpretation can also be understood in the framework of the two-infall models.
 

### 2024-07-09 paper/src/res.tex
Changes in response to comments

@@
 
+This outcome suggests that a merger alone is not sufficient in order to generate a bimodality.
+Rather, the merger must induce a quenching phase.
+Whether this occurs depends both on the properties of the merger but also on the state of the central galaxy itself and whether it can launch AGN-driven winds that result in significant gas removal.
+Our work would argue for some stochasticity in whether a particular merger leads to such quenching.
+
 \begin{figure*}

### 2024-07-09 paper/ms.tex
More changes
First draft edits
Move figures around, add ack

@@
 \newcommand{\dex}{\ensuremath{\textrm{dex}}}
+\newcommand{\Msunyr}{\ensuremath{\Msun/\textrm{yr}}}
 
@@
 \shorttitle{The Milky Way's Phoenix Phase}
-\shortauthors{Beane et al.}
+\shortauthors{Beane}
 
@@
 
-\author{Lars Hernquist}
-\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
+% \author{Lars Hernquist}
+% \affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
 
-\author{et al}
+% \author{et al}
 
@@
 \begin{acknowledgements}
+We would like to thank Megan Bedell, Christopher Carr, Vedant Chandra, Charlie Conroy, Drummond B.
+Fielding, Lars Hernquist, Federico Marinacci, Rohan P.
+Naidu, Melissa K.
+Ness, Minjung Park, Vadim A.
+Semenov, and Turner Woody for helpful discussions.
+We would like to thank Filippo Barbani for kindly providing his version of \texttt{MakeNewDisk}.
+A.B.
+would like to thank Todd Phillips for helpful discussions.
+
 This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}).
 Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
+
+Funding for the Sloan Digital Sky 
+Survey IV has been provided by the 
+Alfred P. Sloan Foundation, the U.S. 
+Department of Energy Office of 
+Science, and the Participating 
+Institutions.
+
+SDSS-IV acknowledges support and 
+resources from the Center for High 
+Performance Computing  at the 
+University of Utah. The SDSS 
+website is www.sdss4.org.
+
+SDSS-IV is managed by the 
+Astrophysical Research Consortium 
+for the Participating Institutions 
+of the SDSS Collaboration including 
+the Brazilian Participation Group, 
+the Carnegie Institution for Science, 
+Carnegie Mellon University, Center for 
+Astrophysics | Harvard \& 
+Smithsonian, the Chilean Participation 
+Group, the French Participation Group, 
+Instituto de Astrof\'isica de 
+Canarias, The Johns Hopkins 
+University, Kavli Institute for the 
+Physics and Mathematics of the 
+Universe (IPMU) / University of 
+Tokyo, the Korean Participation Group, 
+Lawrence Berkeley National Laboratory, 
+Leibniz Institut f\"ur Astrophysik 
+Potsdam (AIP),  Max-Planck-Institut 
+f\"ur Astronomie (MPIA Heidelberg), 
+Max-Planck-Institut f\"ur 
+Astrophysik (MPA Garching), 
+Max-Planck-Institut f\"ur 
+Extraterrestrische Physik (MPE), 
+National Astronomical Observatories of 
+China, New Mexico State University, 
+New York University, University of 
+Notre Dame, Observat\'ario 
+Nacional / MCTI, The Ohio State 
+University, Pennsylvania State 
+University, Shanghai 
+Astronomical Observatory, United 
+Kingdom Participation Group, 
+Universidad Nacional Aut\'onoma 
+de M\'exico, University of Arizona, 
+University of Colorado Boulder, 
+University of Oxford, University of 
+Portsmouth, University of Utah, 
+University of Virginia, University 
+of Washington, University of 
+Wisconsin, Vanderbilt University, 
+and Yale University.
+
 \end{acknowledgements}

### 2024-07-09 paper/src/met.tex
Changes in response to comments
Move figures around, add ack

@@
 \subsection{Isolated Setup}\label{ssec:iso_setup}
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{mass_size.pdf}
+    \caption{The mass and size evolution of the central (Milky Way, blue) and satellite (GSE, orange) galaxies simulated in isolation.
+The mass is taken to be the stellar mass within twice the half-mass radius, and the size is taken to be the half-mass radius.
+In the upper panel, we also show as a horizontal line the mass of the Milky Way's disk and GSE from the best-fit model of \citet{2021ApJ...923...92N}.
+This comparison is taken to be made at $3\,\Gyr$ (vertical dashed line), our proxy for $z\sim2$.
+A precise match is not attempted given the wide ranging uncertainties.}
+    \label{fig:mass_size}
+\end{figure}
+
 We use a modified version of the \texttt{MakeNewDisk} variant described in \citet{2023MNRAS.tmp.2070B}.
@@
 Thus, all star particles and metals are formed self-consistently.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{orbit.pdf}
+    \caption{The orbits of the bimodal (blue) and unimodal (orange) simulations.
+The upper and middle panels show the orbit in the $x$-$y$ and $x$-$z$ planes, respectively.
+The bottom panel shows the separation distance as a function of time.
+The orbit begins retrograde but then radializes after the first pericentric passage.
+The satellite then coalesces quickly after the second pericentric passage, after $\sim2\,\Gyr$ of evolution.}
+    \label{fig:orbit}
+\end{figure}
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{mass_size.pdf}
-    \caption{The mass and size evolution of the central (Milky Way, blue) and satellite (GSE, orange) galaxies.
-The mass is taken to be the stellar mass within twice the half-mass radius, and the size is taken to be the half-mass radius.
-In the upper panel, we also show as a horizontal line the mass of the Milky Way's disk and GSE from the best-fit model of \citet{2021ApJ...923...92N}.
-This comparison is taken to be made at $3\,\Gyr$ (vertical dashed line), our proxy for $z\sim2$.
-A precise match is not attempted given the wide ranging uncertainties.}
-    \label{fig:mass_size}
-  \end{figure}
-
 \subsection{Orbital Configuration}\label{ssec:orbit_setup}
@@
 Coalescence occurs rapidly after the second pericentric passage at $\sim2\,\Gyr$, and \texttt{SUBFIND} ceases to recognize the satellite as a separate subhalo.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{orbit.pdf}
-    \caption{The orbits of the bimodal (blue) and unimodal (orange) simulations.
-The upper and middle panels show the orbit in the $x$-$y$ and $x$-$z$ planes, respectively.
-The bottom panel shows the separation distance as a function of time.
-The orbit begins retrograde but then radializes after the first pericentric passage.
-The satellite then coalesces quickly after the second pericentric passage, after $\sim2\,\Gyr$ of evolution.}
-    \label{fig:orbit}
-\end{figure}
 

### 2024-07-09 paper/ms.tex
Move everything into one file again

@@
 
-\input{src/abs.tex}
+\begin{abstract}
+    The elemental abundance distribution of stars encodes the history of the gas-phase abundance in the Milky Way.
+Without a large, unbiased sample of highly precise stellar ages, the exact timing and nature of this history must be \textit{inferred} from the abundances.
+In the two-dimensional plane of \alphaFe-\FeH, it is now clear that two separate populations exist -- the low-$\alpha$ and high-$\alpha$ sequences.
+Structure in the elemental abundance distribution can arise from many processes -- proposals include specific gas infall scenarios, radial migration, high-redshift clump formation, and various effects associated with galaxy mergers, among others.
+In this work, we demonstrate another possible avenue for structure formation with clear observational predictions.
+In this scenario, the Galaxy underwent a starburst followed by a brief (hundreds of Myr) quiescent phase -- i.e., the Galaxy underwent a post-starburst rejuvenation sequence at $z\sim2$.
+A natural consequence of the quiescent phase is that stars in the valley of the bimodality do not form because: (1) the absence of enrichment from high-mass stars leads to a rapid reduction in \alphaFe{}, and (2) any time the gas spends in the abundance valley is deemphasized in the present day distribution because the star formation rate is lower.
+With a set of idealized merger simulations, we demonstrate the feasibility of this proposal.
+This ``phoenix hypothesis'' predicts a $\sim300\,\Myr$ gap in stellar ages at a fixed \FeH{} and that stars which form directly after this gap would have lower \alphaFe{} than stars which form slightly ($\sim1\,\Gyr$) later.
+  \end{abstract}
 
-\input{src/int.tex}
+\keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of astronomy(1868) --- Interdisciplinary astronomy(804)}
 
-\input{src/met.tex}
+\section{Introduction} \label{sec:intro}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{figure1.pdf}
+  \caption{\textbf{The abundance bimodality seen in the Milky Way can be reproduced in some idealized merger simulations.} In the upper panels, we show the distribution of stars in the \MgFe{}-\FeH{} plane.
+The lower panels show the distribution of \MgFe{} at a fixed \FeH{} bin of width $0.05\,\dex$.
+The colors indicate the fixed \FeH values, which are $-0.5$, $-0.25$, $0$, and $0.25$.
+The left column shows the observed distribution in the Milky Way from ASPCAP DR17 \citep[][J.A.~Holtzman et al., in preparation]{2016AJ....151..144G}, while the right two columns show two idealized merger simulations.
+The idealized merger simulations are nearly identical, except that in the bimodal simulation the satellite has a starting radius of $129\,\kpc$, while in the unimodal simulation it has a starting radius of $142\,\kpc$.
+The labels ``unimodal'' and ``bimodal'' are of the \textit{outcome} of the simulation, and do not reflect a particular choice in the setup.
+The Milky Way (left column) exhibits a strong bimodal distribution of \MgFe{} at various \FeH{}.
+The idealized merger simulation marked as bimodal (center column) also exhibits a bimodal distribution of \MgFe{}, though the structure is not as strongly defined.
+The idealized merger simulation marked as unimodal (right column) exhibits only weak structure, if any at all.}
+  \label{fig:fig1}
+\end{figure*}
 
-\input{src/res.tex}
+% What leads to distribution of heavy elements in a galaxy
+Many elements heavier than hydrogen are produced through nuclear fusion in compact objects such as supernovae, dying low mass stars, and neutron star-neutron star mergers \citep[e.g.][]{2023A&ARv..31....1A}.
+By necessity, stars inherit the constituitive properties of the gas from which they formed.
+Moreover, the surface abundance of most elements for most stars do not change over most of their lifetime.
+We therefore have the opportunity to examine the historical record of the gas-phase abundance of a galaxy by way of the distribution of the surface abundances of stars.
 
-\input{src/dis.tex}
+The enrichment of the gas-phase of a galaxy is determined by a complicated combination of physical processes - stellar evolution and supernovae, gas accretion, mergers, gas outflows from stellar and AGN feedback, metal mixing and diffusion, etc.
+Because the processes which give rise to this distribution are complex, there is almost certainly some structure in the stellar abundance distribution for every galaxy.
+However, it has only been definitively measured in the Milky Way (there is a claim of no measured structure in M31 by \citet{2024IAUS..377..115N}).
 
-\input{src/con.tex}
+% How present-day stellar surface abundances are linked to history of gas-phase abundances
+
+% Why alpha-elements are important
+The distribution of elemental abundances is a high dimensional space \citep[e.g., 32 elements in][]{2024ApJ...961L..41J}.
+However, this space is highly degenerate, and so the effective number of dimensions is much smaller -- even possibly compressed to just \FeH{} and age \citep{2019ApJ...883..177N}.
+Two elements have received particular interest - Fe and elements produced by the $\alpha$-process.
+Type Ia and Type II supernovae are the main contributors of Fe and $\alpha$ enrichment.
+Fe is broadly produced in both types, and so its abundance is a proxy for the total metallicity of a star.
+On the other hand, $\alpha$-elements are mainly produced in Type II supernovae.
+The ratio of $\alpha$-elements to Fe (\alphaFe{}) is then a measure of the relative contributions of Type Ia and II SNe to the enrichment of a parcel of gas.
+It has therefore become common to compress the high-dimensional abundance space to the two dimensional \alphaFe{}-\FeH{} plane.
+
+% Observed chemical bimodality in the Milky Way
+It is now well-established that, in the Milky Way, a bimodality exists in the \alphaFe{}-\FeH{} plane \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R,2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}.
+This bimodality is typically separated into the high-$\alpha$ and low-$\alpha$ sequences.
+These sequences are also associated with differences in their physical extent -- the high-$\alpha$ sequence is more centrally compact and vertically extended than the low-$\alpha$ sequence.
+
+% Different explanations of bimodality
+Naturally, many different processes that could lead to structure in the abundance plane have been discussed in the literature.
+An early explanation of the bimodality is the two-phase gas infall model \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}.
+In this model, the thick disk first forms rapidly from an initial infall of gas.
+Because the typical SFR is high, these stars are $\alpha$-enhanced.
+In some variants, star formation halts completely before a second supply of pristine gas falls into the Galaxy \citep[][and references therein]{2024arXiv240511025S}.
+This dilutes the gas supply from which the thin disk forms more gradually.
+The thin disk is then more $\alpha$-poor because its associated SFR is lower.
+
+A later argument by \citet{2021MNRAS.501.5176K} asserts that the two sequences follow from two phases of gas infall, except driven by stellar feedback instead of cosmological inflow.
+An initial bursty phase follows from the direct collapse of the gaseous halo.
+The disk has a high SFR leading to the formation of the high-$\alpha$ sequence.
+Feedback then halts the inflow, and a slower accretion of high-angular momentum and metal-rich gas commences, forming the low-$\alpha$ sequence.
+
+Another mechanism to generate structure in the abundance plane was pointed out by \citet{2009MNRAS.396..203S}, further developed by \citet{2021MNRAS.507.5882S,2023MNRAS.523.3791C}, and explored by \citet{2011ApJ...737....8L,2021MNRAS.508.4484J}.
+This model claims that, since stars are thought to migrate from their birth radius, there will be stars throughout the entire disk that formed in the inner disk.
+These $\alpha$-enhanced stars will then form the high-$\alpha$ sequence.
+This model and its variants also match some chemodynamic properties of the disk.
+One salient feature of these models is that the bimodality can result from a smooth star formation history.
+
+Yet another explanation, which also invokes an internal process, is that the formation of clumps at high redshift are responsible for both the chemistry and dynamics of the high-$\alpha$ sequence \citep{2019MNRAS.484.3476C,2020MNRAS.492.4716B,2021MNRAS.502..260B,2023ApJ...953..128G}.
+Instabilities are thought to form clumps in gas-rich disks, and such clumps are seen at intermediate redshifts \citep[$z\sim2$;][]{2005ApJ...627..632E,2007ApJ...658..763E}.
+These clumps then self-enrich, forming $\alpha$-enhanced stars.
+The high-$\alpha$ sequence stops forming once the gas fraction is low enough for the instabilities to no longer arise.
+This model predicts that the high-$\alpha$ and low-$\alpha$ sequences form simultaneously.
+
+Next, we turn to models which argue the bimodality results from some external influence.
+Early arguments were made that both the $\alpha$-enhancement of the disk and the thickening of the disk can result from gas-rich mergers \citep{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R}.\footnote{See also \citet{2009MNRAS.400.1347C} for an argument invoking semi-analytic models.} These mergers lead to an enhanced SFR which leads to the $\alpha$-enhancement of the thick disk.
+
+In cosmological simulations, which naturally include early gas-rich mergers, the situation is not as clear.
+Early work by \citet{2012MNRAS.426..690B} found a general separation between the thin and thick disk, though other authors found a smooth evolution \citep{2013A&A...558A...9M}.
+\citet{2018MNRAS.474.3629G} found what they referred to as a chemical dichotomy, and argued that it can come from either gas-rich mergers as described before or a ``compaction'' of the disk (we will return to this point in Section~\ref{ssec:cosmo}).
+Other authors highlight the metal content of the infalling gas, stating that the metal-poor gas associated with satellites can suddenly dilute or reset the disk's metallicity \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}.
+This interpretation can also be understood in the framework of the two-infall models.
+
+The merger explanation of the bimodality is highly synergistic with our picture of the hierarchical assembly of the stellar halo \citep{2005ApJ...635..931B}.
+Indeed, there is strong evidence that the Milky Way underwent a significant merger with the so-called Gaia-Sausage-Enceladus satellite \citep[GSE;][]{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N}.
+This merger is thought to have occurred $\sim8-10\,\Gyr$ ago \citep[see also][]{2020ApJ...897L..18B}.
+
+Claims in the literature on the stellar mass of GSE vary widely.
+Early estimates argued from $6\times10^8$ up to even $10^{10}\,\Msun$ \citep{2018MNRAS.478..611B,2018Natur.563...85H,2019MNRAS.484.4471F,2019MNRAS.487L..47V,2019MNRAS.488.1235M,2020MNRAS.493.5195D,2020MNRAS.497..109F}.
+Later estimates have been more conservatives with estimates from a mass of $3\times10^8\,\Msun$ to $10^9\,\Msun$ \citep{2019MNRAS.482.3426M,2020MNRAS.492.3631M,2021ApJ...923...92N,2022AJ....164..249H}, and even as low as $1.5\times10^8\,\Msun$ \citep{2023MNRAS.526.1209L}.
+
+In this work, we explored an idealized simulation which resembles the merger between the Milky Way and GSE.
+We found that in certain configurations, which have only minor differences in their orbit, a bimodal distribution of stellar abundances in the \alphaFe{}-\FeH{} plane is produced.
+This is shown in Figure~\ref{fig:fig1}.
+The configurations which produce a bimodality are associated with a starburst followed by a quiescent phase followed by rejuvenation $\sim300\,\Myr$ later.
+
+In Section~\ref{sec:methods}, we describe our setup.
+In Section~\ref{sec:results}, we present the main results of our simulations.
+In Section~\ref{sec:discussion}, we discuss and interpret our results, as well as connections to previous and future work, before concluding in Section~\ref{sec:conclusion}.
+Throughout this work we refer to the standard native time unit $\kpc/\left(\kms\right)$ as \Gyr{} for convenience.
+
+\section{Methods}\label{sec:methods}
+\subsection{Isolated Setup}\label{ssec:iso_setup}
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{mass_size.pdf}
+    \caption{The mass and size evolution of the central (Milky Way, blue) and satellite (GSE, orange) galaxies simulated in isolation.
+The mass is taken to be the stellar mass within twice the half-mass radius, and the size is taken to be the half-mass radius.
+In the upper panel, we also show as a horizontal line the mass of the Milky Way's disk and GSE from the best-fit model of \citet{2021ApJ...923...92N}.
+This comparison is taken to be made at $3\,\Gyr$ (vertical dashed line), our proxy for $z\sim2$.
+A precise match is not attempted given the wide ranging uncertainties.}
+    \label{fig:mass_size}
+\end{figure}
+
+We use a modified version of the \texttt{MakeNewDisk} variant described in \citet{2023MNRAS.tmp.2070B}.
+In isolation, each of the central and satellite galaxies are a compound halo setup, with a \citet{1990ApJ...356..359H} dark matter halo and a gaseous halo with a $\beta$-profile:
+\begin{equation*}
+\rho = \rho_0 \left[1 + \left(\frac{r}{r_c}\right)^2\right]^{-\frac{3\beta}{2}}
+\end{equation*}
+The total mass within the virial radius is kept fixed, and the mass of the dark matter halo and central density of the gaseous halo are chosen to satisfy a given baryon fraction $f_b$.
+The dark matter halo is initialized to be in gravitational equilibrium with the total potential.
+The gaseous halo is in gravito-hydrostatic equilibrium, where the temperature is allowed to vary as a function of radius.
+The azimuthal velocity of the gaseous halo is given as a fraction of the circular velocity.
+There is no initial stellar disk or bulge, and the gas is initially metal-free.
+Thus, all star particles and metals are formed self-consistently.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{orbit.pdf}
+    \caption{The orbits of the bimodal (blue) and unimodal (orange) simulations.
+The upper and middle panels show the orbit in the $x$-$y$ and $x$-$z$ planes, respectively.
+The bottom panel shows the separation distance as a function of time.
+The orbit begins retrograde but then radializes after the first pericentric passage.
+The satellite then coalesces quickly after the second pericentric passage, after $\sim2\,\Gyr$ of evolution.}
+    \label{fig:orbit}
+\end{figure}
+
+We used the fiducial halos in \citet{2021ApJ...923...92N} as a starting point for each galaxy.
+We then manually varied the different model parameters until we arrived at a setup that resulted in reasonable galaxies as determined by their stellar mass.
+For the central (Milky Way) galaxy, we set $M_{200}=5\times10^{11}\,\Msun$, $c_{200}=4.1$, $\beta=0.8$, $r_c=9\,\kpc$, $f_b=0.08$, and $v_{\phi}/v_{\textrm{c}}=0.2$, where $c_{200}$ is the concentration and $v_{\phi}/v_{\textrm{c}}$ is the azimuthal velocity of the gaseous halo as a fraction of the local circular velocity.
+For the satellite (GSE) galaxy, we set $M_{200}=2.2\times10^{11}\,\Msun$, $c_{200}=4.33$, $\beta=0.8$, $r_c=6.5\,\kpc$, $f_b=0.06$, and $v_{\phi}/v_{\textrm{c}}=0.4$.
+
+We used a mass resolution of $6\times10^4\,\Msun$ for the gas and $3\times10^5\,\Msun$ for the dark matter.
+This is closest to a resolution of level 4 in the AURIGA simulations \citep{2017MNRAS.467..179G}, and is about $0.7\times$ the mass resolution of TNG50-1 \citep{2019MNRAS.490.3234N,2019MNRAS.490.3196P}.
+All collisionless particles have a fixed softening length of $40\,\pc$.
+The gas has a softening length $2.5\times$ the cell size, with a minimum size of $10\,\pc$.
+Snapshots were saved at intervals of $25\,\Myr$.
+
+The stellar mass build-up of our Milky Way-like and GSE-like galaxies is given in Figure~\ref{fig:mass_size}.
+The upper panel shows the stellar mass history.
+We attempt to match the expected mass of the present-day thick disk \citep[$\sim6\times10^9\,\Msun$, horizontal blue dashed line][]{2016ARA&A..54..529B} at an evolution time of $\sim3\,\Gyr$ (corresponding to $z\sim2$, vertical dashed gray line).\footnote{Of course, this neglects the significant mass contribution of the bulge, which presumably formed earlier.
+However, our setup does not form a strong spheroidal component.
+Using the trick in e.g.
+\citet{2022MNRAS.515.1524Z}, we take the bulge mass to be twice the counterrotating stellar mass.
+At $3\,\Gyr$ in the isolated Milky Way-like galaxy, the bulge mass is $\sim7\times10^{8}\,\Msun$, or $\sim13\%$ of the total mass.
+The Milky Way's bulge is  $\sim1.5\times10^{10}\,\Msun$, although there is strong debate about just how much of the bulge is a classical bulge which formed before the disk \citep{2016ARA&A..54..529B}.
+In any case, we did not attempt to match any particular property of the bulge, though one could promote bulge formation by reducing the rotation of the gas in the inner region.} We get reasonably close at $\sim5\times10^9\,\Msun$ (blue line).
+For GSE, we use the best-fit mass from the $N$-body simulations of \citet{2021ApJ...923...92N} -- $5\times10^8\,\Msun$ (horizontal dashed orange line).
+For this, we slightly overestimate at $\sim6\times10^8\,\Msun$ (orange line).
+
+As for the galaxy sizes, there is significant spread amongst the real galaxy population, and the sizes are thought to be influenced by the merger history not present in our setup \citep[e.g.][]{2014ApJ...788...28V}.
+We note that the sizes of each simulated galaxy (lower panel) are within the range of observed galaxy sizes.
+For the Milky Way, we know the thick disk has scale length of $\sim2\,\kpc$, which converts to a half-mass radius of $\sim3.36\,\kpc$.
+At $\sim3\,\Gyr$, our Milky Way-like galaxy has a half-mass radius of $\sim2\,\kpc$.
+Curiously, after $3\,\Gyr$, the size of the Milky Way-like galaxy continues to grow while the GSE galaxy's size remains constant for the duration of the simulation.
+
+\subsection{Orbital Configuration}\label{ssec:orbit_setup}
+In order to combine the galaxies, we follow \citet{2021ApJ...923...92N}, and place the satellite on a retrograde orbit.
+In the fiducial simulation of \citet{2021ApJ...923...92N}, the satellite is placed at the virial radius ($129\,\kpc$), with the virial velocity ($129\,\kms$), and with a circularity of $0.5$.
+To test minor changes to the orbit, we ran a grid of simulations with $\pm10\%$ in each the starting radius and velocity, and $\pm0.1$ in the circularity, for a total of $27$ simulations.
+We performed each simulation for a duration of $8\,\Gyr$, and used \texttt{FOF} and \texttt{SUBFIND} in order to identify substructure \citep{2005Natur.435..629S,2009MNRAS.399..497D}.
+
+Some of the simulations in this orbital grid resulted in bimodal abundance distributions, while some had little to no structure in the abundance distribution plane.
+We show the abundance plane for all $27$ simulations in Appendix~\ref{app:allmerge}, but for the main body of this work we consider two representative simulations in detail which were chosen based on their structure in the abundance plane as shown in Figure~\ref{fig:fig1}.
+For the bimodal simulation, we chose the simulation with $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$.
+For the unimodal simulation, the parameters are the same except that $R_0=129\,\kpc$.
+
+We show the bimodal and unimodal simulations' orbits in Figure~\ref{fig:orbit}.
+For the center of the central and satellite, we use the position of the particle with minimum potential in each substructure identified by \texttt{SUBFIND}.
+The upper and middle panels show the orbits in the $x$-$y$ and $x$-$z$ planes, respectively.
+The lower panel shows the separation distance as a function of time.
+The orbit is initially retrograde, but quickly radializes after the first pericentric passage.
+Coalescence occurs rapidly after the second pericentric passage at $\sim2\,\Gyr$, and \texttt{SUBFIND} ceases to recognize the satellite as a separate subhalo.
+
+\subsection{Feedback and Enrichment Model}\label{ssec:gfm}
+Our feedback model is most closely related to that used in the Illustris TNG simulation suite \citep{2013MNRAS.436.3031V,2017MNRAS.465.3291W,2018MNRAS.473.4077P}.
+In this model, gravity and magnetohydrodynamics are solved using a \citet{1986Natur.324..446B} tree coupled to a second order finite volume fluid solver in AREPO \citep{2010MNRAS.401..791S,2016MNRAS.455.1134P}.
+Stellar feedback is included through a subgrid wind particle model \citep{2003MNRAS.339..289S}.
+AGN feedback follows a dual kinetic and thermal mode for low- and high-accretion rates \citep{2017MNRAS.465.3291W}, though in our setup the AGN is only ever in the high-accretion mode.
+The central galaxy is seeded with a black hole with the typical seed mass ($8\times10^5\,\Msun$).
+
+In this work, we made some simplifications to this model in order to aid interpretation.
+First, we ignore magnetic fields.
+This was motivated by an initial desire to understand the CGM accretion rates in terms of idealized cooling flow solutions, but we did not revisit turning them back on.
+In any case, it is not clear if the magnetic fields would be realistically generated given our initial setup.
+Second, we use a gentler wind feedback model as described in \citet{2019MNRAS.489.4233M}.
+Because our setup includes both an initially steep central potential and no steady-state disk, a stronger feedback model would require a higher central gas density to achieve a reasonable SFH which introduced its own set of pathological instabilities.
+
+In this model, star particles synthesize elements through three different channels for which we cite the relevant yield tables: SNe Ia \citep{1997NuPhA.621..467N}, SNe II \citep{1998A&A...334..505P,2006ApJ...653.1145K}, and AGB stars \citep{2010MNRAS.403.1413K,2014MNRAS.437..195D,2014ApJ...797...44F}.
+Recall that star particles are simple stellar populations (i.e., a collection of stars with the same age and chemical composition).
+Each star particle continuously injects metals into its surroundings in the following sequence\footnote{The kinetic/thermal feedback component is handled through the wind generation, which is completely separate in this model.}:
+\begin{enumerate}
+    \item $t\lesssim10\,\Myr$: no metal injection as the first supernova ($M\sim100\,\Msun$) has not gone off
+    \item $10\,\Myr \lesssim t \lesssim 40\,\Myr$: metal injection as $8\,\Msun<M<100\,\Msun$ stars die as Type II SNe
+    \item $t\gtrsim40\,\Myr$: metal injection from Type Ia SNe and AGB stars
+\end{enumerate}
+There are a few things to note about this model: (1) The exact timings are metallicity-dependent.
+(2) The \MgFe{} of ejected gas from Type II SNe is mass/time-dependent, with more massive stars contributing more Mg than less massive stars.
+(3) In a Hubble time, type II SNe contribute the vast majority of Mg ($\sim10\times$ AGB and $\sim100\times$ Type Ia SNe).
+Type Ia and Type II SNe contribute approximately equal amounts of Fe (each $\sim3\times$ AGB).
+See Figure~1 from \citet{2018MNRAS.473.4077P}.
+(4) The number of Type Ia SNe is greater for a younger stellar population, with a power law relationship $\propto \left(t/\tau_8\right)^{-1.12}$, where $\tau_8=40\,\Myr$ is the lifetime of an $8\,\Msun$ star.
+
+\subsection{Observed Abundances}\label{ssec:obs_abund}
+Our aim in this work is to demonstrate the feasibility of a mechanism for structure formation in the abundance plane.
+We are only making a qualitative comparison to data.
+Therefore, we use the ASPCAP DR17 catalog of stellar abundances \citep[][J.A.~Holtzman et al., in preparation]{2016AJ....151..144G}, which is publicly available, well-established, and widely used.
+
+We first make some quality cuts, as well as restricting our sample to giants. We require:
+\begin{itemize}[noitemsep]
+    \item $\textrm{SNR} > 200$,
+    \item $\textrm{VSCATTER} < 1\,\kms$,
+    \item STARFLAG not set,
+    \item $\varpi/\sigma_{\varpi} > 1$,
+    \item $\log{g} < 3.5$,
+    \item $\sigma_{\log{g}} < 0.2$,
+\end{itemize}
+where $\varpi$ is the parallax. We use the parallax, proper motion, and radial velocity from Gaia EDR3 \citep{2016AA...595A...1G,2021AA...649A...1G,2021AA...649A...2L,2021AA...653A.160S}.
+
+We next make a selection on the angular momentum of stars in order to make a solar neighborhood selection.
+We assume the solar radius and azimuthal velocity are $R_0=8\,\kpc$ and $V_0=220\,\kms$ \citep{2016ARA&A..54..529B}, and select stars which have $L_z$ within $10\%$ of the solar angular momentum.
+We further require that $\left|z\right| < 3\,\kpc$.
+
+As is typically done, we use \FeH{} as an indicator of the total metallicity of a star. We use Mg alone as a representative of the $\alpha$-elements.
+
+\subsection{Solar Neighborhood in Simulations}\label{ssec:solarneigh}
+When comparing galaxy simulations to the observed solar neighborhood, some ambiguity arises in how to make a ``solar neighborhood-like'' selection of star particles.
+Naturally, this selection is dependent on the posed question, which in this work is the formation of the abundance bimodality.
+The Sun is known to sit near the end of the thick disk, where the thick and thin disk have comparable surface densities \citep[the ratio of thick-to-thin is $\sim12\%$][]{2016ARA&A..54..529B}.
+As a result, the abundance bimodality appears most strongly near the Sun -- further inwards the high-$\alpha$ sequence is more dominant and further outwards the high-$\alpha$ sequence vanishes \citep[e.g.,][]{2015ApJ...808..132H}.
+
+We mimic our selection of the solar neighborhood by also making a cut in angular momentum.
+However, in the simulation, the high-$\alpha$ disk is more compact than in the Galaxy.
+Therefore, in order to strike a balance between the low-$\alpha$ and high-$\alpha$ disks, we used an angular momentum cut which is $20\%$ that of our assumed solar angular momentum.
+In particular, we select all star particles with angular momenta within $30\%$ of $0.2\times8\,\kpc\times220\,\kms$ -- as well as requiring $\left| z \right| < 3\,\kpc$.
+This corresponds to roughly selecting star particles with radii between $2$ and $5\,\kpc$.
+
+\section{Results}\label{sec:results}
+\subsection{Surface Density Projections}\label{ssec:projections}
+Before dissecting the simulated galaxies in detail, we first take a look at the surface density projections of the gas and stars in the central region, situated on the central galaxy in the bimodal simulation.
+This is shown in Figure~\ref{fig:projections}.
+In each grouping of four, the bottom and top rows show the face-on and edge-on views, respectively.
+The left and right columns show the gas (blue) and stellar (orange) surface density, respectively.
+Each panel is oriented with respect to the stellar angular momentum of the final snapshot ($t=8\,\Gyr$).
+The angular momentum is computed using all star particles within the half-mass radius.
+
+We can see that the galaxy grows in size after the merger.
+Additionally, the galaxy's orientation continues to change even within the last $3\,\Gyr$.
+The final galaxy is oriented $\sim126\degree$ with respect to the initial orientation of the central galaxy's gas halo.
+The dynamical and kinematic consequences of such a gas-rich merger is beyond the scope of our current work.
+
+\begin{figure*}
+  \centering
+
+    \gridline{\fig{all_L30/all_L30_frame60.pdf}{0.3\textwidth}{}
+              \fig{all_L30/all_L30_frame70.pdf}{0.3\textwidth}{}
+              \fig{all_L30/all_L30_frame80.pdf}{0.3\textwidth}{}
+              }
+    \gridline{\fig{all_L30/all_L30_frame90.pdf}{0.3\textwidth}{}
+              \fig{all_L30/all_L30_frame100.pdf}{0.3\textwidth}{}
+              \fig{all_L30/all_L30_frame110.pdf}{0.3\textwidth}{}
+              }
+    \gridline{\fig{all_L30/all_L30_frame120.pdf}{0.3\textwidth}{}
+              \fig{all_L30/all_L30_frame200.pdf}{0.3\textwidth}{}
+              \fig{all_L30/all_L30_frame320.pdf}{0.3\textwidth}{}
+              }
+  % \includegraphics[width=\textwidth]{surfdens.pdf}
+  \caption{Frames from a movie showing a surface density projection of the bimodal simulation over time.
+In each frame, the left/right (blue/orange) column shows the gas/star surface density.
+The upper/lower panels show the edge-on and face-on view.
+Every panel is oriented with respect to the final ($t=8\,\Gyr$) snapshot.
+The side-length of each panel is $30\,\kpc$, and the image is a projection through a box with the same side-length.
+The colormap for the gas ranges from $1$ to $10^2\,\Msun/\pc^2$, while for the stars ranges from $1$ to $10^4\,\Msun/\pc^2$.
+(A full movie is \href{https://drive.google.com/file/d/1RKpFpnFIpl7XYAX5lvF7CyaPVO5dS3EO/view?usp=drive_link}{here}.)}
+  \label{fig:projections}
+\end{figure*}
+
+\subsection{Abundance Distribution}\label{ssec:abundplane}
+In Figure~\ref{fig:fig1}, briefly discussed in Section~\ref{sec:intro}, we show the abundance distribution of the Milky Way as well as two of our idealized merger simulations in the upper panels.
+A number of our idealized simulations exhibit either a bimodal or unimodal abundance distribution, and so we have selected two representative examples.
+The simulation labeled bimodal had orbital parameters of $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$.
+The unimodal simulation is identical, except that $R_0=129\,\kpc$.
+The bimodal and unimodal labels are of the outcome of the simulation, and do not reflect any particular choice made in their setup.
+
+There are, of course, differences between the bimodal simulation and the Milky Way.
+First, the scaling in \MgFe{} is different -- in the simulation, the low-$\alpha$ sequence lies at $\sim0.2$, while in the Milky Way it is at about $\MgFe\sim0$.
+Second, in the Milky Way the high-$\alpha$ sequence neatly joins the low-$\alpha$ sequence at $\FeH\sim0$, while in the simulation the two actually diverge more at higher \FeH{}.
+Finally, at high \FeH{} the distribution bends upwards while in the simulation it bends downwards.
+
+In the lower panels of Figure~\ref{fig:fig1}, we show the distributions of \MgFe{} at different fixed \FeH{}.
+The (blue, orange, red, green) lines show the \MgFe{} distribution at a \FeH{} of ($-0.5$, $-0.25$, $0$, $0.25$), in bins of width $0.05\,\dex$.
+The distributions of \MgFe{} are offset (but not rescaled) so that they do not overlap.
+Here, the bimodality seen in the Milky Way is quite striking at lower metallicities.
+The peaks are well-separated, by $\sim0.2\,\dex$.
+In the bimodal simulation, the distribution is still clearly bimodal, but the peaks are less well-separated, by $\sim0.1\,\dex$.
+In the unimodal simulation, there is a hint of some structure at $\FeH \gtrsim 0.25$, but there is not a strong multimodal structure.
+
+\subsection{Build up of the Abundance Plane}\label{ssec:abundplane_build}
+Next, we examine the build up of the abundance plane.
+First, in Figure~\ref{fig:before_after}, we show the abundance plane at various points along the merger.
+We have divided the history of the merger into ``before'' ($t < 1.5\,\Gyr$), ``during'' ($1.5\,\Gyr < t < 2.5\,\Gyr$), and ``after'' ($t > 2.5\,\Gyr$).
+These times have been chosen somewhat by the orbital history and somewhat by visually inspecting the simulation, and so these deliniations are, to an extent, arbitrary.
+Nonetheless, it is clear that the high-$\alpha$ sequence forms before and during the merger (middle panels), and that the low-$\alpha$ sequence forms after the merger (right panel).
+We show a dashed line given by $-0.1\times\FeH + 0.31$, which is a crude way of separating the high- and low-$\alpha$ sequence.
+
+It is informative to examine the star formation history (SFH) split into the high- and low-$\alpha$ sequences at a fixed \FeH{}, shown in Figure~\ref{fig:before_after_sfh}.
+The high- and low-$\alpha$ sequences (blue and orange) are defined as the star particles lying above and below the dashed line in Figure~\ref{fig:before_after}, respectively.
+We show this only in a narrow bin of width $0.1\,\dex$ at $\FeH\sim0$.
+We chose this value of \FeH{} because here the valley of the bimodality is deepest (see Figure~\ref{fig:fig1}).
+One can see a very clear separation in time between the high- and low-$\alpha$ sequences, with the high-$\alpha$ sequence forming before the low-$\alpha$ sequence.\footnote{There is a small amount of low-$\alpha$ formation at the very end of the high-$\alpha$ sequence, but this can be understood as simply an inadequacy in our simple way of separating the two sequences.
+Alternatively, one could assert that the separation in time is the real delineation between the two sequences, and that the boundary in the abundance plane has only mild contamination.} Furthermore, there is a brief period of $\sim300\,\Myr$ between the two sequences where no stars have formed.
+
+It can also be shown that the exact timing of this quiescent period is metallicity-dependent.
+We show the same SFH in Figure~\ref{fig:before_after_sfh_by_iron}, but at varying bins in \FeH{} of $-0.5$, $-0.25$, and $0$ (blue, orange, and red, respectively).
+For clarity, we do not separate the SFHs by the high- and low-$\alpha$ sequences, but have verified that the same demarcation arises as in Figure~\ref{fig:before_after_sfh}.
+Here, we can see that at $\FeH=-0.5$ the quiescent period begins $\sim250\,\Myr$ earlier than at $\FeH=0$.
+
+\subsection{\alphaFe{} Behavior Associated with Quiescence}
+We now examine more closely the natural suspicion that the quiescent phase in Figure~\ref{fig:before_after_sfh} is responsible for the bimodal structure in Figure~\ref{fig:before_after}.
+In Figure~\ref{fig:SFR_alpha}, we show the SFR (blue lines) of each of the bimodal and unimodal galaxies (left and right panels, respectively) as well as the median \MgFe{} of the gas (orange lines) in a bin centered on $\FeH{}=-0.1$ with width $0.05\,\dex$.
+The SFR is shown for the entire galaxy ($r<15\,\kpc$) while the median \MgFe{} is shown for $2\,\kpc<r<5\,\kpc$.\footnote{The solar neighborhood-like selection of stars (discussed in Section~\ref{ssec:solarneigh}) mostly selects stars at $2\,\kpc<r<5\,\kpc$.
+We choose to plot the median \MgFe{} of the gas at these radii, since it is roughly that gas which is forming stars that ends up in our sample.
+On the other hand, we choose to show the SFR for the entire galaxy, as the enrichment from that star formation affects the entire galaxy at this epoch.}
+
+The merger appears to induce a starburst, where the SFR rises from $\sim3.5\,\Msunyr$ at $\sim1\Gyr$ to a peak of $\sim12\,\Msunyr$ at $\sim2\,\Gyr$.
+This starburst is then followed by a quiescent period, with a minimum SFR of $\sim1\,\Msunyr$ and a duration of $\sim500\,\Myr$.
+The dip in SFR is not as pronounced as it was when we plotted the SFH at a particular iron (Figure~\ref{fig:before_after_sfh}).
+This quiescent period is associated with a drop in \MgFe{} from $\sim0.35$ to $\sim0.2\,\dex$ in only $\sim250\,\Myr$.
+Once the SFR recovers $\sim500\,\Myr$ later, \MgFe{} again rises, but only to $\sim0.28\,\dex$.
+
+This behavior is absent in the unimodal simulation (right panel) -- while there is a starburst, it does not display a period of suppressed star formation, and there is no associated drop in \MgFe{}.
+It does still have a period of enhanced star formation, but this is actually coincident with an enhancement in \MgFe{}.
+This sequence of events is further emphasized in Figure~\ref{fig:alpha_vs_tform}, which shows a transparent scatter plot of \MgFe{} as a function of formation time.
+In the bimodal simulation, there is a clear gap in \MgFe{} during the period of quiescence followed by the brief formation of $\alpha$-deficient stars.
+In the unimodal simulation, on the other hand, there is no gap and instead a brief formation of $\alpha$-enhanced stars.
+
+\subsection{Cause of Quiescence}\label{ssec:cause_qui}
+Why there is a quiescent period in the bimodal simulation but not the unimodal simulation probably has to do with some transient, stochastic property of the gas in and around the galaxy.
+In some states, the AGN is better able to quench the galaxy than in others.
+Verifying this further is beyond the scope of this work, but we show some evidence of the association in Appendix~\ref{app:cause_qui}.
+
+This outcome suggests that a merger alone is not sufficient in order to generate a bimodality.
+Rather, the merger must induce a quenching phase.
+Whether this occurs depends both on the properties of the merger but also on the state of the central galaxy itself and whether it can launch AGN-driven winds that result in significant gas removal.
+Our work would argue for some stochasticity in whether a particular merger leads to such quenching.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{before_after.pdf}
+  \caption{\textbf{The high-$\alpha$ sequence forms before the merger, the low-$\alpha$ sequence forms after the merger.} This plot shows the sequence of events leading to the build-up of the low- and high-$\alpha$ sequences for our fiducial bimodal simulation.
+We have separated the high- and low-$\alpha$ sequences by a dashed line at $-0.1\FeH + 0.31$, which was chosen by eye to lie in the trough.
+The left panel shows all star particles in our solar neighborhood cut.
+The middle left panel shows the star particles that form before the merger ($\tform < 1.5\,\Gyr$), which form a weak sequence of star particles at the lowest \FeH and highest \MgFe.
+The middle right panel shows the star particles that form during the starburst ($1.5\,\Gyr < \tform < 2.5\,\Gyr$).
+These star particles form the portion of the high-$\alpha$ sequence closest to the trough, and the density of star particless is higher than those that form before.
+The right panel shows the star particles which form after the merger ($\tform > 2.5\,\Gyr$).
+These star particles form almost entirely below the trough.}
+  \label{fig:before_after}
+\end{figure*}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{before_after_sfh.pdf}
+  \caption{\textbf{At fixed metallicity, the low- and high-$\alpha$ sequence are cleanly separated in time by an intervening quiescent period.} Here we show the star formation history of the high- and low-$\alpha$ sequences.
+The blue (low-$\alpha$) and orange (high-$\alpha$) histograms correspond to the dashed line cut made in the \MgFe{}-\FeH{} plane in Figure~\ref{fig:before_after}, at a fixed metallicity of $\FeH=0$ with width $0.05\,\dex$.
+One can see that there is a nearly perfect separation in time between the formation of the high-$\alpha$ and low-$\alpha$ sequences by a quiescent period lasting $\sim300\,\Myr$.
+There is a small amount of contamination at the end of the high-$\alpha$ sequence which can be attributed to the inadequacy of the linear cut model of the two sequences.}
+  \label{fig:before_after_sfh}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{before_after_sfh_by_iron.pdf}
+  \caption{\textbf{The timing of the quiescent period which divides the high- and low-$\alpha$ sequences is metallicity dependent.} The star formation history of stars at various fixed metallicities ($\FeH=0$, $-0.25$, and $-0.5\,\textrm{dex}$) in bins of width $0.05\,\dex$.
+As in Figure~\ref{fig:before_after_sfh}, there is a quiescent period period which separates the formation of the low- and high-$\alpha$ sequence.
+However, the timing of the quiescent period is metallicity-dependent.
+It occurs earlier at lower metallicities, by $\sim250\,\Myr$ for the metallicities shown in this plot.}
+  \label{fig:before_after_sfh_by_iron}
+\end{figure}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{SFR_alpha.pdf}
+  \caption{\textbf{A global suppression of star formation is associcated with a decrease in \MgFe{}, which is seen in the bimodal simulation but not in the unimodal simulation.} Here, we show both the SFR of the central galaxy ($r<15\,\kpc$) and the median \MgFe{} for gas at $2\,\kpc<r<5\,\kpc$ at a fixed \FeH{} bin centered on $0$ with width $0.05\,\dex$.
+The left panel shows the bimodal simulation while the right panel shows the unimodal simulation.
+A vertical dashed line at $2\,\Gyr$ in each plot indicates the approximate time of the merger, but before complete coalescence.
+In the left panel, a shaded region from $2.5\,\Gyr$ to $2.75\,\Gyr$ indicates the approximate period of quiescence shown in Figure~\ref{fig:before_after_sfh}.
+This suppression of star formation is associated with a sudden drop in the median \MgFe{} of the gas.
+Neither the suppression of star formation nor the drop in \MgFe{} are seen in the unimodal simulation.}
+  \label{fig:SFR_alpha}
+\end{figure*}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{alpha_vs_tform.pdf}
+  \caption{\textbf{In the bimodal simulation, a gap in stellar ages is briefly followed by the formation of $\alpha$-deficient star particles.} The formation times and \MgFe{} values of star particles in the bimodal (blue) and unimodal (orange) simulations.
+In the unimodal simulation, no gap is present and there is briefly the formation of $\alpha$-enhanced star particles at the same time.
+The \MgFe{} values of the unimodal simulation have been offset by $-0.3$ for clarity.}
+  \label{fig:alpha_vs_tform}
+\end{figure}
+
+\section{Discussion}\label{sec:discussion}
+We have demonstrated that a bimodal structure in the elemental abundance plane is associated with a brief quiescent phase in our idealized merger simulations.
+We now construct a possible framework for understanding the formation of the bimodality, discuss its relation to prior work, and then discuss predictions and connections to observations.
+
+\subsection{Quiescence Leads to Bimodality}\label{ssec:formqui}
+We executed a series of idealized merger simulations in which we modified the starting radius and velocity by $\pm10\%$ and the circularity by $\pm0.1$, for a total of $27$ simulations.
+The central and satellite galaxies, which are meant to resemble the Milky Way and GSE at $z\sim2$, are otherwise identical across the simulations.
+Some of these simulations induce a bimodality, while others do not.
+We have examined a representative of each scenario in detail.
+
+We described a series of results in Section~\ref{sec:results} which give a natural explanation for the separation between the high- and low-$\alpha$ sequences in our simulations.
+First, a merger induces a starburst in the simulation.
+If this starburst does not induce a quiescent period, then the median \MgFe{} of the gas briefly increases before continuing along the typical evolutionary path (right panel of Figure~\ref{fig:SFR_alpha}).
+However, if there is a quiescent period, the median \MgFe{} drops for the duration of the quiescent period before recovering to the typical path (left panel of Figure~\ref{fig:SFR_alpha}).
+
+This drop can be understood in terms of the mechanics of the galaxy formation model as described in Section~\ref{ssec:gfm}.
+When a star particle forms, it only takes $\sim40\,\Myr$ before the last Type II SN has gone off and its material enrichment is dominated by Fe from Type Ia SNe.
+As a result, during the quiescent phase which lasts a few hundred Myr, there is relatively little $\alpha$-element production.
+On the other hand, star particles are still able to generate Fe through Type Ia SNe which have a longer period of influence.
+The fact that the quiescent period is preceded by a starburst is important.
+Even though star particles produce Fe through the Type Ia channel for Gyr, younger star particles still produce much more Fe than older star particles.
+In the TNG model, the number of Type Ia SNe decays with time as $(t/\tau_8)^{-s}$, where $\tau_8=40\,\Myr$ is the lifetime of an $8\,\Msun$ star and $s=1.12$.
+Therefore, the burst of star formation at $t\sim2.25\,\Gyr$ is able to generously produce Fe starting at $2.5\,\Gyr$, when is indeed when the drop in \MgFe{} is the most steep.
+
+\subsection{Connection to Cosmological Simulations}\label{ssec:cosmo}
+As discussed in Section~\ref{sec:intro}, several authors have examined the formation of abundance plane structure in cosmological simulations.
+Of most interest to us is the zoom Au~23 in \citet{2018MNRAS.474.3629G}.
+This galaxy, one of six considered in their work, exhibits a bimodality that extends beyond the inner disk.
+The interpretation given by the authors is of a ``shrinking'' gaseous disk.
+This is equivalent to saying that the outer disk becomes depleted of gas.
+This shrinking of the disk, which occurs at $t_{\textrm{lookback}}\sim6\,\Gyr$, is associated with a dip in the SFR at that radius and a decrement in the median \alphaFe{} of $\sim0.05\,\dex$ (their Figure~2), which shortly after recovers.
+This sequence of events is more extended than in our work, but it strongly resembles the scenario in Figure~\ref{fig:before_after_sfh}.
+
+\citet{2018MNRAS.477.5072M} found that Milky Way-like bimodalities are rare in EAGLE, occuring in $\sim5\%$ of galaxies.
+\citet{2021MNRAS.501..236D,2022MNRAS.515.1430D} showed that merger-induced quenching in zooms can occur in the EAGLE model \citep[see also][]{2017MNRAS.465..547P}.
+However, the situation may be different in the lower resolution large box.
+Furthermore, if the proposed starburst-quenching phase is driven by AGN feedback, then the outcome of any particular cosmological simulation with regards to the bimodality is intimately tied to its AGN model.
+Unfortunately, such models are highly uncertain \citep[e.g.][]{2022MNRAS.511.3751H}.
+
+\citet{2023arXiv231016085K} explored the impact of quenching in the Magneticum Pathfinder suite.
+They found that galaxies which quench undergo a starburst followed by an AGN-driven quenching phase.
+In the post-starburst regime, they claim galaxies are $\alpha$-enhanced.
+We do find that the bulk stellar \MgFe{} is enhanced after the merger in our bimodal simulation compared to the isolated simulation, but only at the $\sim0.01\,\dex$ level.
+
+\subsection{Infall Interpretations}\label{ssec:dilute}
+In some previous work, it was reported that the bimodality is a consequence of a sudden deposition of metal-poor, $\alpha$-poor gas by a satellite or cosmological filament -- i.e., a ``dilution'' \citep{2020MNRAS.491.5435B,2021MNRAS.503.5846R}.
+The separation of the sequences follows from the rapidity of the dilution.
+This was elaborated upon by \citet{2021MNRAS.503.5868R} who described a zoom where the low-$\alpha$ disk forms out of a relatively pristine cosmological filament.
+This disk is inclined relative to the high-$\alpha$ disk, with the two disks later tidally realigning.
+The longer-standing two-infall class of models argue that the two sequences diverge due to two episodic accretion episodes, with some possible enrichment of the second episode arising from an associated satellite \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}.
+
+We have shown that minor changes to the orbit of our idealized merger can result in outcomes that are either bimodal or unimodal.
+The content of gas that is delivered to the system is nearly identical regardless of the orbit, and so the dilution interpretation is not applicable to our simulations.
+That being said, a removal of gas from the system either through star formation or through ejection could make dilution from infalling gas more efficient, so the two scenarios are not mutually exclusive.
+
+It was recently elaborated by \citet{2024arXiv240511025S} that these models also argue for a star formation gap between the two accretion episodes \citep[see also][]{1996ASPC...92..307G,1998A&A...338..161F,2000A&A...358..671G,2015A&A...578A..87S,2020A&A...640A..81N}.
+This gap is starvation-driven and can last several \Gyr{}.
+The present work argues for a starburst-driven quiescence followed by a rapid rejuvenation, with the entire process taking less than $1\,\Gyr$ and the gap only lasting a few hundred \Myr{}.
+The physical origin and some details are different, but one can appreciate that the bimodality arises from the same physical process.\footnote{Compare Section~\ref{ssec:formqui} to the first key result in the Conclusions of \citet{2024arXiv240511025S}.}
+
+\subsection{Observational Connections: High Redshift Quenching}\label{ssec:obshiz}
+If the Milky Way underwent a starburst to quiescent to rejuvenation sequence, as we argue in this paper, then an an analogue at $z\sim2$ would be identified as a post-starburst galaxy (PSB).
+With abundance matching, we expect the Milky Way's total stellar mass to be $\sim10^{10.3}\,\Msun$ at $z\sim2$ \citep{2013ApJ...771L..35V}.
+A number of authors have explored PSBs and quiescent galaxies at slightly higher masses at $z\sim2$, with large advances in the post-JWST era.
+
+First, PSBs are not uncommon.
+\citet{2023ApJ...953..119P} found that in massive galaxies ($M_* > 10^{10.6}\,\Msun$) the fraction of PSBs (inferred ages $< 800\,\Myr$) increases from $\sim2.7\%$ ($99/3655$) at $1.0 < z < 1.44$ to $\sim8\%$ ($89/1118$) at $2.16 < z < 2.5$ \citep[see also][]{2012ApJ...745..179W,2019ApJ...874...17B}.
+Later, \citet{2024arXiv240417945P} found that $\sim10\%$ of galaxies at $\sim10^{10.3}\,\Msun$ are quenched \citep[consistent with][]{2013ApJ...777...18M}, and $\sim30\%$ of their quiescent sample is a PSB at $z\sim2$.
+If these galaxies can be quickly rejuvenated, as the system studied in this work would suggest, then the total fraction of galaxies that go through a starburst-quenching phase may be higher.
+
+Furthermore, \citet{2023arXiv231215012C} found that lower mass quiescent galaxies (towards $10^{10.3}\,\Msun$) tend to be younger and more disky, pointing to a merger driven scenario.
+\citet{2023arXiv231212207A} found that at even lower masses ($<10^{9.5}\,\Msun$) There is also evidence that the AGN quenching mechanism, which we believe to be responsible for the quenching in our system (Appendix~\ref{app:cause_qui}), is operating at these redshifts \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024arXiv240518685M,2024Natur.630...54B}.
+
+Overall, the starburst-driven quenching mechanism proposed in this work is allowed by high-redshift observations.
+
+\subsection{Direct Search for Quiescence}\label{ssec:obsqui}
+Figure~\ref{fig:before_after_sfh_by_iron} indicates a very direct observational test of the mechanism proposed in this work: for disk stars at a given \FeH{}, there should be a gap of $\sim300\,\Myr$ in ages at $\sim8\,\Gyr$, though in the Milky Way the gap could be larger.
+With a survey of properly chosen stars, this gap could be directly measured with a modestly sized (few hundred) sample of old stars with age uncertainties of $\sim1\%$.
+To our knowledge, the best method at these ages is differential analysis of solar twins, which can provide an age uncertainty of $\sim5\%$ \citep[e.g.][]{2014ApJ...795...23B,2018MNRAS.474.2580S}.
+However, this has only been applied to stars with solar metallicity, where there is not a clear separation between the high- and low-$\alpha$ sequences (though a gap in ages may still be present).
+A sort of differential approach could be applied also at lower metallicities, which would just lack the absolute age calibration that the Sun provides.
+
+The gap could also be indirectly probed by a larger sample of slightly less precise ages.
+Astroseismology appears to be the most promising avenue.
+Currently the largest sample is APOKASC2 \citep{2018ApJS..239...32P}, which has $\sim3400$ stars with ages measured to $<20\%$ precision.\footnote{Errors here taken to be the maximum of the upper and lower age estimates in the public APOKASC2 catalog.} The upcoming PLATO mission is looking to measure $\sim20\textrm{k}$ stars with ages measured to $<10\%$ precision \citep{2024arXiv240605447R}.
+Further work is needed to determine how well these surveys could constrain the gap.
+
+In addition to the presence of the gap, our work also predicts that: (1) the timing of the gap is \FeH{} dependent, and that (2) stars which form immediately after the gap are $\alpha$-poor compared to stars which form slightly later (see Figure~\ref{fig:alpha_vs_tform}).
+However, both of these tests rely on the precise age estimates.
+
+\subsection{Future Work}
+A natural next step would be to extend the idealized simulations in this work to a wider range of orbits, galaxy properties, and feedback models.
+However, the unrealism of our setup, which aids interpretation, limits its applicability to the real universe.
+And so something along the lines of the genetic modification technique to explore various mergers as done in this work may be useful \citep{2016MNRAS.455..974R,2017MNRAS.465..547P}.
+
+There is, of course, still great uncertainties in the stellar evolution models commonly adopted by different groups.
+Initial work on systematically exploring the stellar evolution parameters has been done by \citet{2017A&A...605A..59R,2021MNRAS.508.3365B}.
+Exploring these variations in the simulations presented in this work would be interesting, though exploring their interactions with brief quiescent periods in simpler chemical evolution models may be a better first step.
+
+There is also the perennial problem of diffusion within the hydrodynamics solver.
+In purely Lagrangian solvers, there is no diffusion between resolution elements, while in Eulerian codes the diffusion can be quite high.\footnote{No galaxy formation simulation is fully Lagrangian since there must be, at a minimum, mass exchange between star particles and gas.
+Here we just mean that there is no mass exchange between gas elements.} AREPO limits the numerical diffusion by allowing the mesh to move in a quasi-Lagrangian manner, and using a second-order solver \citep{2010MNRAS.401..791S}.
+In FIRE-2 \citep{2018MNRAS.480..800H}, which uses the Lagrangian code GIZMO \citep{2015MNRAS.450...53H}, a subgrid turbulent metal diffusion model was used.
+It would be interesting to see how models with different diffusivity properties would relax or strengthen the necessity of a quiescent period to produce a bimodality.
+
+\section{Conclusion}\label{sec:conclusion}
+The \alphaFe{}-\FeH{} plane of stellar abundances is a record of the gas-phase abundances of the Galaxy.
+In this plane, a bimodality has now been definitively measured.
+Proposals for its formation include radial migration, particular gas infall scenarios, and galaxy mergers.
+
+In this work, using idealized merger simulations, we have shown that (1) a starburst, followed by (2) a brief ($\sim300\,\Myr$) quiescent period, followed by (3) rejuvenation can lead to a bimodal abundance structure.
+We found that the starburst-to-quiescent period allowed for prodigious Fe-enrichment without any contemperaneous $\alpha$-enrichment.
+This sequence of events, somewhat resembling the life cycle of a phoenix, would predict that for stars at a given \FeH{}, there would be a $\sim300\,\Myr$ gap in stellar ages at $\sim8\,\Gyr$.
+Furthermore, stars which form directly after this gap would have lower \alphaFe{} than stars which form slightly later ($\sim1\,\Gyr$).
+
+The bimodality in the \alphaFe{}-\FeH{} plane of stellar abundances points to deeper, unobserved structure.
+That structure is a record of the complicated processes that gave rise to the Galaxy.
+In the absence of highly precise stellar ages, that history must be largely inferred.
+There are many ways in which a galaxy could end up with the coarse-grained structure we can observe in the present day.
+We have argued in this work that a brief, starburst-driven quiescent phase is one of them.
 
@@
 
-\bibliography{src/ref}{}
+\bibliography{ref}{}
 \bibliographystyle{aasjournal}
 
-\input{src/app.tex}
+\appendix
+\section{Abundance Plane of All Simulations}\label{app:allmerge}
+We show summary plots of the abundance planes of all simulations in our orbital grid in Figures~\ref{fig:allmerge0} to \ref{fig:allmerge8}.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{allmerge/allmerge0.pdf}
+  \caption{A summary of the abundance plane and star formation history of all simulations within the orbital grid.
+Each figure shows the outcome of a simulation at a fixed $R_0$ and $V_0$, varying $\eta$.
+The title of each column shows the $R_0$, $V_0$, and $\eta$ of that simulation, in order.
+The upper and middle rows replicate Figure~\ref{fig:fig1}, which show the distribution of stars in the abundance plane of \MgFe{}-\FeH{} as well as 1D histograms at a fixed \FeH{} of $-0.5$, $-0.25$, $0$, and $0.25$.
+The lower rows replicate Figure~\ref{fig:before_after_sfh_by_iron}, showing the star formation history at each \FeH{}.}
+  \label{fig:allmerge0}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{allmerge/allmerge1.pdf}
+  \caption{A continuation of Figure~\ref{fig:allmerge0}.}
+  \label{fig:allmerge1}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{allmerge/allmerge2.pdf}
+  \caption{A continuation of Figure~\ref{fig:allmerge0}.}
+  \label{fig:allmerge2}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{allmerge/allmerge3.pdf}
+  \caption{A continuation of Figure~\ref{fig:allmerge0}.}
+  \label{fig:allmerge3}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{allmerge/allmerge4.pdf}
+  \caption{A continuation of Figure~\ref{fig:allmerge0}.}
+  \label{fig:allmerge4}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{allmerge/allmerge5.pdf}
+  \caption{A continuation of Figure~\ref{fig:allmerge0}.}
+  \label{fig:allmerge5}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{allmerge/allmerge6.pdf}
+  \caption{A continuation of Figure~\ref{fig:allmerge0}.}
+  \label{fig:allmerge6}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{allmerge/allmerge7.pdf}
+  \caption{A continuation of Figure~\ref{fig:allmerge0}.}
+  \label{fig:allmerge7}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{allmerge/allmerge8.pdf}
+  \caption{A continuation of Figure~\ref{fig:allmerge0}.}
+  \label{fig:allmerge8}
+\end{figure*}
+
+\section{Cause of Suppressed Star Formation}\label{app:cause_qui}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{SFR_Mgas_tdep.pdf}
+  \caption{\textbf{The suppression of star formation in the bimodal simulation is associated with both a reduction in gas mass as well as an increase in the depletion time.} The drop in star formation (blue line) at $\sim2.5-3\,\Gyr$ is associated with both a reduction in the total gas mass (red line) as well as an increase in the depletion time (green line).
+This shows that the SFR suppression is a result of both less gas mass and more inefficient star formation.}
+  \label{fig:SFR_Mgas_tdep}
+\end{figure*}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=242.26653pt]{MdotBH_rsep.pdf}
+  \caption{\textbf{The bimodal merger is associated with high accretion rates onto the central SMBH.} Around the time of each pericentric passage, and slightly after, the accretion rate (blue line) becomes very high.
+Here, it is shown as a fraction of the Eddington accretion rate.
+During the merger, the accretion rate reaches as high as Eddington at some times, but is always above $10\%$.
+The orbital separation between the central and satellite is shown in the orange line.}
+  \label{fig:MdotBH_rsep}
+\end{figure}
 

### 2024-07-29 paper/ms.tex
Remove line numbers
Add Kruijssen citation

@@
-\documentclass[linenumbers, twocolumn]{aastex631}
+\documentclass[twocolumn]{aastex631}
 
@@
 Early estimates argued from $6\times10^8$ up to even $10^{10}\,\Msun$ \citep{2018MNRAS.478..611B,2018Natur.563...85H,2019MNRAS.484.4471F,2019MNRAS.487L..47V,2019MNRAS.488.1235M,2020MNRAS.493.5195D,2020MNRAS.497..109F}.
-Later estimates have been more conservatives with estimates from a mass of $3\times10^8\,\Msun$ to $10^9\,\Msun$ \citep{2019MNRAS.482.3426M,2020MNRAS.492.3631M,2021ApJ...923...92N,2022AJ....164..249H}, and even as low as $1.5\times10^8\,\Msun$ \citep{2023MNRAS.526.1209L}.
+Later estimates have been more conservative ranging from a mass of $2.7\times10^8\,\Msun$ to $10^9\,\Msun$ \citep{2019MNRAS.482.3426M,2020MNRAS.492.3631M,2020MNRAS.498.2472K,2021ApJ...923...92N,2022AJ....164..249H}, and even as low as $1.5\times10^8\,\Msun$ \citep{2023MNRAS.526.1209L}.
 

### 2025-01-14 paper/ms.tex
Add line numbers
Put everything in paper/ dir
Fix citations for earliest/best

@@
-\documentclass[twocolumn]{aastex631}
+\documentclass[twocolumn,linenumbers,trackchanges]{aastex631}
 
@@
 
-% \author{Lars Hernquist}
-% \affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
-
-% \author{et al}
-
 \begin{abstract}
@@
 
-% How present-day stellar surface abundances are linked to history of gas-phase abundances
-
 % Why alpha-elements are important
@@
 % Observed chemical bimodality in the Milky Way
-It is now well-established that, in the Milky Way, a bimodality exists in the \alphaFe{}-\FeH{} plane \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R,2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}.
-This bimodality is typically separated into the high-$\alpha$ and low-$\alpha$ sequences.
-These sequences are also associated with differences in their physical extent -- the high-$\alpha$ sequence is more centrally compact and vertically extended than the low-$\alpha$ sequence.
+\edit1{A decomposition of the Milky Way's disk into multiple components has a long history dating back to the work of \citet{1983MNRAS.202.1025G}, who noted that the vertical distribution of stellar altitudes is well-fit by a double exponential.
+This led naturally to a ``thin'' and ``thick'' disk, whose membership can be reasonably determined through kinematics \citep[e.g.][]{2003A&A...410..527B}.
+It was quickly realized that the thick disk is more $\alpha$-enhanced than the thin disk \citep{1996ASPC...92..307G,1998A&A...338..161F}.}
+
+\edit1{It was realized later that, without any kinematic selection, the disk can be decomposed into two high- and low-$\alpha$ components or sequences \citep{2011A&A...535L..11A,2012A&A...545A..32A}.\footnote{\citet{2003A&A...410..527B} briefly noted that the thin and thick disk seemed to not overlap in chemistry.} The high-$\alpha$ sequence is older, more centrally compact, and more vertically extended than the low-$\alpha$ sequence \citep{2013A&A...560A.109H,2024IAUS..377..115N}.
+Although the thick disk is more $\alpha$-enhanced than the thin disk, it is not immediately obvious that the chemical and kinematic separations arise from the same physical process \citep[or that they even exist][]{2012ApJ...751..131B}.}
 
@@
 Naturally, many different processes that could lead to structure in the abundance plane have been discussed in the literature.
-An early explanation of the bimodality is the two-phase gas infall model \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}.
+An early explanation of the bimodality is \edit1{based on} the two-phase gas infall model \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}.
 In this model, the thick disk first forms rapidly from an initial infall of gas.
@@
 In some variants, star formation halts completely before a second supply of pristine gas falls into the Galaxy \citep[][and references therein]{2024arXiv240511025S}.
-This dilutes the gas supply from which the thin disk forms more gradually.
-The thin disk is then more $\alpha$-poor because its associated SFR is lower.
+This dilutes the gas supply from which the thin disk forms more gradually, \edit1{creating a loop feature in the abundance plane}.
+The thin disk is then more $\alpha$-poor because its associated SFR is lower, \edit1{and in certain scenarios two chemically distinct disks are formed.}
 
@@
 Next, we turn to models which argue the bimodality results from some external influence.
-Early arguments were made that both the $\alpha$-enhancement of the disk and the thickening of the disk can result from gas-rich mergers \citep{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R}.\footnote{See also \citet{2009MNRAS.400.1347C} for an argument invoking semi-analytic models.} These mergers lead to an enhanced SFR which leads to the $\alpha$-enhancement of the thick disk.
+Early arguments were made that both the $\alpha$-enhancement of the disk and the thickening of the disk can result from gas-rich mergers \citep{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R}.\footnote{See also \citet{2009MNRAS.400.1347C} for an argument invoking semi-analytic models.} These mergers lead to an enhanced SFR which leads to the $\alpha$-enhancement of the thick disk, \edit1{with \citet{2015A&A...578A..87S} being the first to attempt to explain the abundance substructure with a merger.}
 
@@
 This merger is thought to have occurred $\sim8-10\,\Gyr$ ago \citep[see also][]{2020ApJ...897L..18B}.
+\edit1{A merger origin of the abundance bimodality is also attractive because it can simultaneously explain the origin of the kinematic thin and thick disk \citep{1985AJ.....90.2015G,1986ApJ...309..472Q,1993ApJ...403...74Q}.}
 
@@
 
-    \gridline{\fig{all_L30/all_L30_frame60.pdf}{0.3\textwidth}{}
-              \fig{all_L30/all_L30_frame70.pdf}{0.3\textwidth}{}
-              \fig{all_L30/all_L30_frame80.pdf}{0.3\textwidth}{}
+    \gridline{\fig{all_L30_frame60.pdf}{0.3\textwidth}{}
+              \fig{all_L30_frame70.pdf}{0.3\textwidth}{}
+              \fig{all_L30_frame80.pdf}{0.3\textwidth}{}
               }
-    \gridline{\fig{all_L30/all_L30_frame90.pdf}{0.3\textwidth}{}
-              \fig{all_L30/all_L30_frame100.pdf}{0.3\textwidth}{}
-              \fig{all_L30/all_L30_frame110.pdf}{0.3\textwidth}{}
+    \gridline{\fig{all_L30_frame90.pdf}{0.3\textwidth}{}
+              \fig{all_L30_frame100.pdf}{0.3\textwidth}{}
+              \fig{all_L30_frame110.pdf}{0.3\textwidth}{}
               }
-    \gridline{\fig{all_L30/all_L30_frame120.pdf}{0.3\textwidth}{}
-              \fig{all_L30/all_L30_frame200.pdf}{0.3\textwidth}{}
-              \fig{all_L30/all_L30_frame320.pdf}{0.3\textwidth}{}
+    \gridline{\fig{all_L30_frame120.pdf}{0.3\textwidth}{}
+              \fig{all_L30_frame200.pdf}{0.3\textwidth}{}
+              \fig{all_L30_frame320.pdf}{0.3\textwidth}{}
               }
@@
   \centering
-  \includegraphics[width=\textwidth]{allmerge/allmerge0.pdf}
+  \includegraphics[width=\textwidth]{allmerge0.pdf}
   \caption{A summary of the abundance plane and star formation history of all simulations within the orbital grid.
@@
   \centering
-  \includegraphics[width=\textwidth]{allmerge/allmerge1.pdf}
+  \includegraphics[width=\textwidth]{allmerge1.pdf}
   \caption{A continuation of Figure~\ref{fig:allmerge0}.}
@@
   \centering
-  \includegraphics[width=\textwidth]{allmerge/allmerge2.pdf}
+  \includegraphics[width=\textwidth]{allmerge2.pdf}
   \caption{A continuation of Figure~\ref{fig:allmerge0}.}
@@
   \centering
-  \includegraphics[width=\textwidth]{allmerge/allmerge3.pdf}
+  \includegraphics[width=\textwidth]{allmerge3.pdf}
   \caption{A continuation of Figure~\ref{fig:allmerge0}.}
@@
   \centering
-  \includegraphics[width=\textwidth]{allmerge/allmerge4.pdf}
+  \includegraphics[width=\textwidth]{allmerge4.pdf}
   \caption{A continuation of Figure~\ref{fig:allmerge0}.}
@@
   \centering
-  \includegraphics[width=\textwidth]{allmerge/allmerge5.pdf}
+  \includegraphics[width=\textwidth]{allmerge5.pdf}
   \caption{A continuation of Figure~\ref{fig:allmerge0}.}
@@
   \centering
-  \includegraphics[width=\textwidth]{allmerge/allmerge6.pdf}
+  \includegraphics[width=\textwidth]{allmerge6.pdf}
   \caption{A continuation of Figure~\ref{fig:allmerge0}.}
@@
   \centering
-  \includegraphics[width=\textwidth]{allmerge/allmerge7.pdf}
+  \includegraphics[width=\textwidth]{allmerge7.pdf}
   \caption{A continuation of Figure~\ref{fig:allmerge0}.}
@@
   \centering
-  \includegraphics[width=\textwidth]{allmerge/allmerge8.pdf}
+  \includegraphics[width=\textwidth]{allmerge8.pdf}
   \caption{A continuation of Figure~\ref{fig:allmerge0}.}

### 2025-02-13 plots/inj_rate/lvl4-template/job_lvl4.sh
Plots i dont use

@@ -1,0 +1,26 @@
+#!/bin/sh
+#SBATCH -p hernquist_ice,sapphire
+#SBATCH -J MW7_GSE4_Rs_Vv_e_l4
+#SBATCH -n 56
+#SBATCH -N 1
+#SBATCH --ntasks-per-node=56
+#SBATCH -o output/OUTPUT.%j.out
+#SBATCH -e output/ERROR.%j.err
+#SBATCH --mail-user=slurmsara+grid@gmail.com
+#SBATCH --mail-type=BEGIN
+#SBATCH --mail-type=END
+#SBATCH --mail-type=FAIL
+#SBATCH --mem-per-cpu=7800
+#SBATCH -t 3-00:00           # Runtime in D-HH:MM
+
+source ./load-modules.sh
+
+ulimit -c unlimited
+
+cd arepo
+make clean > ../output/MAKE.out 2> ../output/MAKE.err
+make -j >> ../output/MAKE.out 2> ../output/MAKE.err
+cd ../
+
+mpiexec --mca mpi_leave_pinned 0 --mca oob_tcp_listen_mode listen_thread -np $SLURM_NTASKS  arepo/Arepo param_lvl4.txt 
+

### 2025-02-13 paper/ms.tex
Update title, abstract, and keywords

@@
 
-\title{Rising from the Ashes: How the Milky Way Got Its Scars}
+\title{Rising from the Ashes: A Metallicity-Dependent Star Formation Gap Splits the Milky Way's $\alpha$-Sequences}
 
@@
 Without a large, unbiased sample of highly precise stellar ages, the exact timing and nature of this history must be \textit{inferred} from the abundances.
-In the two-dimensional plane of \alphaFe-\FeH, it is now clear that two separate populations exist -- the low-$\alpha$ and high-$\alpha$ sequences.
-Structure in the elemental abundance distribution can arise from many processes -- proposals include specific gas infall scenarios, radial migration, high-redshift clump formation, and various effects associated with galaxy mergers, among others.
-In this work, we demonstrate another possible avenue for structure formation with clear observational predictions.
-In this scenario, the Galaxy underwent a starburst followed by a brief (hundreds of Myr) quiescent phase -- i.e., the Galaxy underwent a post-starburst rejuvenation sequence at $z\sim2$.
-A natural consequence of the quiescent phase is that stars in the valley of the bimodality do not form because: (1) the absence of enrichment from high-mass stars leads to a rapid reduction in \alphaFe{}, and (2) any time the gas spends in the abundance valley is deemphasized in the present day distribution because the star formation rate is lower.
-With a set of idealized merger simulations, we demonstrate the feasibility of this proposal.
-This ``phoenix hypothesis'' predicts a $\sim300\,\Myr$ gap in stellar ages at a fixed \FeH{} and that stars which form directly after this gap would have lower \alphaFe{} than stars which form slightly ($\sim1\,\Gyr$) later.
+In the two-dimensional plane of \alphaFe{}-\FeH{}, it is now clear that two separate populations exist -- the low-$\alpha$ and high-$\alpha$ sequences.
+\edit1{We propose that a brief ($\sim300\,\Myr$) halt in star formation within a narrow metallicity bin can lead to a bimodal \alphaFe{} distribution at that metallicity, assuming a rapidly declining gas phase \alphaFe{}.
+Using simulations of an idealized setup of a high-$z$ galaxy merger, we show that the merger with the Gaia-Sausage-Enceladus satellite at $z\sim2$ is one possible way to trigger such a gap in the Milky Way.
+Our proposal does not rely on a merger to induce this age gap.
+We predict a $\sim300\,\Myr$ gap in stellar ages at a fixed \FeH{} where the $\alpha$-bimodality is prominent ($\FeH\lesssim-0.2$).}
 \end{abstract}
 
-\keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of astronomy(1868) --- Interdisciplinary astronomy(804)}
+\keywords{Milky Way disk (1050) --- Milky Way Galaxy physics (1056) --- Milky Way formation (1053), Hydrodynamical simulations (767) --- Post-starburst galaxies (2176) --- Galaxies (573) --- Starburst galaxies (1570)}
 

### 2025-02-13 paper/ms.tex
Move fig 1

@@
 \section{Introduction} \label{sec:intro}
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{figure1.pdf}
-  \caption{\textbf{The abundance bimodality seen in the Milky Way can be reproduced in some idealized merger simulations.} In the upper panels, we show the distribution of stars in the \MgFe{}-\FeH{} plane.
-The lower panels show the distribution of \MgFe{} at a fixed \FeH{} bin of width $0.05\,\dex$.
-The colors indicate the fixed \FeH values, which are $-0.5$, $-0.25$, $0$, and $0.25$.
-The left column shows the observed distribution in the Milky Way from ASPCAP DR17 \citep[][J.A.~Holtzman et al., in preparation]{2016AJ....151..144G}, while the right two columns show two idealized merger simulations.
-The idealized merger simulations are nearly identical, except that in the bimodal simulation the satellite has a starting radius of $129\,\kpc$, while in the unimodal simulation it has a starting radius of $142\,\kpc$.
-The labels ``unimodal'' and ``bimodal'' are of the \textit{outcome} of the simulation, and do not reflect a particular choice in the setup.
-The Milky Way (left column) exhibits a strong bimodal distribution of \MgFe{} at various \FeH{}.
-The idealized merger simulation marked as bimodal (center column) also exhibits a bimodal distribution of \MgFe{}, though the structure is not as strongly defined.
-The idealized merger simulation marked as unimodal (right column) exhibits only weak structure, if any at all.}
-  \label{fig:fig1}
-\end{figure*}
-
 % What leads to distribution of heavy elements in a galaxy
@@
 In the unimodal simulation, there is a hint of some structure at $\FeH \gtrsim 0.25$, but there is not a strong multimodal structure.
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{figure1.pdf}
+  \caption{The abundance bimodality seen in the Milky Way can be reproduced in some idealized merger simulations.
+In the upper panels, we show the distribution of stars in the \MgFe{}-\FeH{} plane.
+The lower panels show the distribution of \MgFe{} at a fixed \FeH{} bin of width $0.05\,\dex$.
+The colors indicate the fixed \FeH values, which are $-0.5$, $-0.25$, $0$, and $0.25$.
+The left column shows the observed distribution in the Milky Way from ASPCAP DR17 \citep[][J.A.~Holtzman et al., in preparation]{2016AJ....151..144G}, while the right two columns show two idealized merger simulations.
+The idealized merger simulations are nearly identical, except that in the bimodal simulation the satellite has a starting \edit1{velocity of $142\,\kms$}, while in the unimodal simulation it has a starting \edit1{velocity of $116\,\kms$}.
+The labels ``unimodal'' and ``bimodal'' are of the \textit{outcome} of the simulation, and do not reflect a particular choice in the setup.
+The Milky Way (left column) exhibits a strong bimodal distribution of \MgFe{} at various \FeH{}.
+The idealized merger simulation marked as bimodal (center column) also exhibits a bimodal distribution of \MgFe{}, though the structure is not as strongly defined.
+The idealized merger simulation marked as unimodal (right column) exhibits only weak structure, if any at all.}
+  \label{fig:fig1}
+\end{figure*}
 

### 2025-02-13 paper/ms.tex
Update introduction

@@
 Moreover, the surface abundance of most elements for most stars do not change over most of their lifetime.
-We therefore have the opportunity to examine the historical record of the gas-phase abundance of a galaxy by way of the distribution of the surface abundances of stars.
+\edit1{By analyzing the surface abundances of stars, we can reconstruct the historical gas-phase composition of a galaxy.}
 
-The enrichment of the gas-phase of a galaxy is determined by a complicated combination of physical processes - stellar evolution and supernovae, gas accretion, mergers, gas outflows from stellar and AGN feedback, metal mixing and diffusion, etc.
+The enrichment of the gas-phase of a galaxy is determined by a complicated combination of physical processes - stellar evolution and supernovae, gas accretion, mergers, gas outflows from stellar and active galactic nuclei (AGN) feedback, metal mixing and diffusion, etc.
 Because the processes which give rise to this distribution are complex, there is almost certainly some structure in the stellar abundance distribution for every galaxy.
-However, it has only been definitively measured in the Milky Way (there is a claim of no measured structure in M31 by \citet{2024IAUS..377..115N}).
+However, it has only been definitively measured in the Milky Way, \edit1{with conflicting claims of detection \citep{2023ApJ...956L..14K} and nondetection \citep{2024IAUS..377..115N} in M31.}
 
@@
 On the other hand, $\alpha$-elements are mainly produced in Type II supernovae.
-The ratio of $\alpha$-elements to Fe (\alphaFe{}) is then a measure of the relative contributions of Type Ia and II SNe to the enrichment of a parcel of gas.
+The ratio of $\alpha$-elements to Fe (\alphaFe{}) is then a measure of the relative contributions of Type Ia and II SNe to the enrichment of a parcel of gas, \edit1{which typically declines with time \citep{1979ApJ...229.1046T,1986A&A...154..279M}}.
 It has therefore become common to compress the high-dimensional abundance space to the two dimensional \alphaFe{}-\FeH{} plane.
@@
 % Observed chemical bimodality in the Milky Way
-\edit1{A decomposition of the Milky Way's disk into multiple components has a long history dating back to the work of \citet{1983MNRAS.202.1025G}, who noted that the vertical distribution of stellar altitudes is well-fit by a double exponential.
+\edit1{These abundances can be used to decompose the Milky Way's disk, which has a long history dating back to the work of \citet{1983MNRAS.202.1025G}, who noted that the vertical distribution of stellar altitudes is well-fit by a double exponential.
 This led naturally to a ``thin'' and ``thick'' disk, whose membership can be reasonably determined through kinematics \citep[e.g.][]{2003A&A...410..527B}.
@@
 
-\edit1{It was realized later that, without any kinematic selection, the disk can be decomposed into two high- and low-$\alpha$ components or sequences \citep{2011A&A...535L..11A,2012A&A...545A..32A}.\footnote{\citet{2003A&A...410..527B} briefly noted that the thin and thick disk seemed to not overlap in chemistry.} The high-$\alpha$ sequence is older, more centrally compact, and more vertically extended than the low-$\alpha$ sequence \citep{2013A&A...560A.109H,2024IAUS..377..115N}.
-Although the thick disk is more $\alpha$-enhanced than the thin disk, it is not immediately obvious that the chemical and kinematic separations arise from the same physical process \citep[or that they even exist][]{2012ApJ...751..131B}.}
+\edit1{Later studies showed that the disk could be decomposed into high- and low-$\alpha$ sequences without kinematic selection \citep{2011A&A...535L..11A,2012A&A...545A..32A}.\footnote{\citet{2003A&A...410..527B} briefly noted that the thin and thick disk seemed to not overlap in chemistry.} The high-$\alpha$ sequence is older, more centrally compact, and more vertically extended than the low-$\alpha$ sequence \citep{2013A&A...560A.109H,2024IAUS..377..115N}.
+Although the thick disk is more $\alpha$-enhanced than the thin disk, it is not immediately obvious that the chemical and kinematic separations arise from the same physical process \citep[or that they even exist, see][]{2012ApJ...751..131B}.}
 
@@
 Next, we turn to models which argue the bimodality results from some external influence.
-Early arguments were made that both the $\alpha$-enhancement of the disk and the thickening of the disk can result from gas-rich mergers \citep{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R}.\footnote{See also \citet{2009MNRAS.400.1347C} for an argument invoking semi-analytic models.} These mergers lead to an enhanced SFR which leads to the $\alpha$-enhancement of the thick disk, \edit1{with \citet{2015A&A...578A..87S} being the first to attempt to explain the abundance substructure with a merger.}
+Early arguments were made that both the $\alpha$-enhancement of the disk and the thickening of the disk can result from gas-rich mergers \citep{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R}.\footnote{See also \citet{2009MNRAS.400.1347C} for an argument invoking semi-analytic models.} These mergers lead to an enhanced SFR which leads to the $\alpha$-enhancement of the thick disk, \edit1{with \citet{2015A&A...578A..87S} being the first to attempt to explain abundance substructure with a merger.}
 
@@
 
-In this work, we explored an idealized simulation which resembles the merger between the Milky Way and GSE.
-We found that in certain configurations, which have only minor differences in their orbit, a bimodal distribution of stellar abundances in the \alphaFe{}-\FeH{} plane is produced.
-This is shown in Figure~\ref{fig:fig1}.
-The configurations which produce a bimodality are associated with a starburst followed by a quiescent phase followed by rejuvenation $\sim300\,\Myr$ later.
+\edit1{In this work, we propose that a brief $\sim300\,\Myr$ interruption in the formation of stars at a given metallicity can lead to the formation of an $\alpha$-abundance bimodality at that metallicity.
+It is not common to study the star formation rate at a specific metallicity, but dividing the stellar population into narrow abundance populations can be a powerful tool \citep[e.g.][]{2012ApJ...753..148B,2012ApJ...751..131B}.}
+
+\edit1{Our proposal assumes that the gas phase's \alphaFe{} is declining sufficiently rapidly at the time of the interruption.
+Using a set of idealized simulations which mimic the $z\sim2$ merger between the Milky Way and GSE, we show that such a merger can drive the formation of this gap and thus the bimodality.
+While we demonstrate this mechanism in the context of a merger scenario, it is important to note that our proposal does not inherently require a merger to induce this metallicity-dependent star formation gap.
+This scenario predicts a $\sim300\,\Myr$ gap in stellar ages at metallicities where the bimodality exists ($\FeH\lesssim-0.2$).}
 
 In Section~\ref{sec:methods}, we describe our setup.
-In Section~\ref{sec:results}, we present the main results of our simulations.
-In Section~\ref{sec:discussion}, we discuss and interpret our results, as well as connections to previous and future work, before concluding in Section~\ref{sec:conclusion}.
+\edit1{In Section~\ref{sec:results}, we present in detail the main results of two example simulations before expanding our results to the full suite.} In Section~\ref{sec:discussion}, we discuss and interpret our results, as well as connections to previous and future work, before concluding in Section~\ref{sec:conclusion}.
 Throughout this work we refer to the standard native time unit $\kpc/\left(\kms\right)$ as \Gyr{} for convenience.

### 2025-02-13 paper/ms.tex
Minor updates to methods

@@
 \end{equation*}
-The total mass within the virial radius is kept fixed, and the mass of the dark matter halo and central density of the gaseous halo are chosen to satisfy a given baryon fraction $f_b$.
+The total mass within the virial radius is kept fixed, and the mass of the dark matter halo and central density of the gaseous halo are chosen to satisfy a given baryon fraction $f_b$ \edit1{within the virial radius}.
 The dark matter halo is initialized to be in gravitational equilibrium with the total potential.
@@
 The orbit begins retrograde but then radializes after the first pericentric passage.
-The satellite then coalesces quickly after the second pericentric passage, after $\sim2\,\Gyr$ of evolution.}
+The satellite then coalesces quickly after the second pericentric passage, after $\sim2\,\Gyr$ of evolution.
+\edit1{A blue dashed line is shown for the bimodal simulation at $2.8\,\Gyr$, the time of a star formation gap at $\FeH=0$ (see Figure~\ref{fig:before_after}).
+An orange dashed line is shown for the unimodal simulation (which has no gap) at the same time after its second pericentric passage ($2.3\,\Gyr$).}}
     \label{fig:orbit}
@@
 We used a mass resolution of $6\times10^4\,\Msun$ for the gas and $3\times10^5\,\Msun$ for the dark matter.
-This is closest to a resolution of level 4 in the AURIGA simulations \citep{2017MNRAS.467..179G}, and is about $0.7\times$ the mass resolution of TNG50-1 \citep{2019MNRAS.490.3234N,2019MNRAS.490.3196P}.
+This is closest to a level~4 resolution in the AURIGA simulations \citep{2017MNRAS.467..179G}, and is about $0.7\times$ the mass resolution of TNG50-1 \citep{2019MNRAS.490.3234N,2019MNRAS.490.3196P}.
 All collisionless particles have a fixed softening length of $40\,\pc$.
@@
 In order to combine the galaxies, we follow \citet{2021ApJ...923...92N}, and place the satellite on a retrograde orbit.
-In the fiducial simulation of \citet{2021ApJ...923...92N}, the satellite is placed at the virial radius ($129\,\kpc$), with the virial velocity ($129\,\kms$), and with a circularity of $0.5$.
+In the fiducial simulation of \citet{2021ApJ...923...92N}, the satellite is placed at the virial radius ($R_0=129\,\kpc$), with the virial velocity ($V_0=129\,\kms$), and with a circularity of $\eta=0.5$.
 To test minor changes to the orbit, we ran a grid of simulations with $\pm10\%$ in each the starting radius and velocity, and $\pm0.1$ in the circularity, for a total of $27$ simulations.
@@
 Some of the simulations in this orbital grid resulted in bimodal abundance distributions, while some had little to no structure in the abundance distribution plane.
-We show the abundance plane for all $27$ simulations in Appendix~\ref{app:allmerge}, but for the main body of this work we consider two representative simulations in detail which were chosen based on their structure in the abundance plane as shown in Figure~\ref{fig:fig1}.
-For the bimodal simulation, we chose the simulation with $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$.
-For the unimodal simulation, the parameters are the same except that $R_0=129\,\kpc$.
+\edit1{We will first study two representative simulations in detail chosen based on their structure in the abundance plane as shown in Figure~\ref{fig:fig1}, one which we refer to as bimodal and one as unimodal.
+For the bimodal simulation, we chose the simulation with $R_0=129\,\kpc$, $V_0=142\,\kms$, and $\eta=0.4$.
+For the unimodal simulation, the parameters are the same except that $V_0=116\,\kms$.
+These simulations will later be identified as having the highest and second lowest bimodality score $\mathcal{B}$.
+We will then examine the full simulation suite, and show the detailed abundance plane for the full suite5 in Appendix~\ref{app:allmerge}.}
 
 We show the bimodal and unimodal simulations' orbits in Figure~\ref{fig:orbit}.
-For the center of the central and satellite, we use the position of the particle with minimum potential in each substructure identified by \texttt{SUBFIND}.
-The upper and middle panels show the orbits in the $x$-$y$ and $x$-$z$ planes, respectively.
+\edit1{We use a shrinking spheres center of mass method to identify the centers of the central and satellite galaxy \citep[e.g.,][]{2003MNRAS.338...14P}.\footnote{The position of the minimum potential particle in each substructured identified by \texttt{SUBFIND} is used as the starting guess, and we use an initial/final radius and step factor of $10\,\kpc$, $5\,\kpc$, and $0.9$, respectively.}} The upper and middle panels show the orbits in the $x$-$y$ and $x$-$z$ planes, respectively.
 The lower panel shows the separation distance as a function of time.
@@
 \subsection{Feedback and Enrichment Model}\label{ssec:gfm}
-Our feedback model is most closely related to that used in the Illustris TNG simulation suite \citep{2013MNRAS.436.3031V,2017MNRAS.465.3291W,2018MNRAS.473.4077P}.
+Our feedback model is \edit1{a variant of the Illustris TNG model} \citep{2013MNRAS.436.3031V,2017MNRAS.465.3291W,2018MNRAS.473.4077P}.
 In this model, gravity and magnetohydrodynamics are solved using a \citet{1986Natur.324..446B} tree coupled to a second order finite volume fluid solver in AREPO \citep{2010MNRAS.401..791S,2016MNRAS.455.1134P}.
@@
 In this model, star particles synthesize elements through three different channels for which we cite the relevant yield tables: SNe Ia \citep{1997NuPhA.621..467N}, SNe II \citep{1998A&A...334..505P,2006ApJ...653.1145K}, and AGB stars \citep{2010MNRAS.403.1413K,2014MNRAS.437..195D,2014ApJ...797...44F}.
-Recall that star particles are simple stellar populations (i.e., a collection of stars with the same age and chemical composition).
-Each star particle continuously injects metals into its surroundings in the following sequence\footnote{The kinetic/thermal feedback component is handled through the wind generation, which is completely separate in this model.}:
+Each star particle, \edit1{which is modeled as a simple stellar population}, continuously injects metals into its surroundings in the following sequence\footnote{The kinetic/thermal feedback component is handled through the wind generation, which is completely separate in this model.}:
 \begin{enumerate}
@@
 
-We first make some quality cuts, as well as restricting our sample to giants. We require:
+We \edit1{applied quality cuts and restricted our sample to giants}, requiring:
 \begin{itemize}[noitemsep]
@@
 
-We next make a selection on the angular momentum of stars in order to make a solar neighborhood selection.
-We assume the solar radius and azimuthal velocity are $R_0=8\,\kpc$ and $V_0=220\,\kms$ \citep{2016ARA&A..54..529B}, and select stars which have $L_z$ within $10\%$ of the solar angular momentum.
+\edit1{We next make a solar neighborhood selection of stars based on their angular momenta.} We assume the solar radius and azimuthal velocity are $R_0=8\,\kpc$ and $V_0=220\,\kms$ \citep{2016ARA&A..54..529B}, and select stars which have $L_z$ within $10\%$ of the solar angular momentum.
 We further require that $\left|z\right| < 3\,\kpc$.
+As is typically done, we use \FeH{} as an indicator of the total metallicity of a star.
+We use Mg alone as a representative of the $\alpha$-elements.
 
-As is typically done, we use \FeH{} as an indicator of the total metallicity of a star. We use Mg alone as a representative of the $\alpha$-elements.
+\edit1{For stellar ages, we used the APOKASC-3 catalog \citep{2025ApJS..276...69P}.
+This catalog uses a combination of APOGEE spectroscopic parameters and \textit{Kepler} time series photometry to compute astroseismic ages.
+Using only stars with $25\%$ age uncertainties (taken as the maximum of the upper and lower uncertainty), we cross-match this catalog to our larger sample from ASPCAP which results in a sample of 2525 stars.}
 

### 2025-02-13 paper/ms.tex
Add bimodality score methods

@@
 This corresponds to roughly selecting star particles with radii between $2$ and $5\,\kpc$.
+
+\subsection{Bimodality Score}\label{ssec:bim_score}
+\edit1{Given the modest size of our suite, some method for scoring the degree of bimodality for a given 1D distribution is desirable.
+Tests of whether a distribution is bimodal or unimodal exist -- e.g., the Hartigan dip test \citep{10.1214/aos/1176346577}, but they lack the ability to rank order based on ``bimodalitiness.'' In order to do this, we fit a given distribution of \alphaFe{} as a two-component gaussian mixture model.
+The bimodality score $\mathcal{B}$ is then computed as
+\begin{equation}\label{eq:bimscore}
+\mathcal{B} = \frac{\left|\mu_1-\mu_2\right|}{\sqrt{\sigma_1^2-\sigma_2^2}}\times w(A_2, t, k)\textrm{,}
+\end{equation}
+where $(\mu_1, \sigma_1)$ is the mean and standard deviation of the higher weighted mode, $(\mu_2, \sigma_2)$ likewise for the less weighted mode, $A_2$ is the amplitude of the less weighted mode, and $w$ is a penalty function with parameters $t$ and $k$ given by
+\begin{equation}\label{eq:bimscore_penalty}
+w(A, t, k) = \left[1+e^{-k\left(A-t\right)}\right]^{-1}\text{.}
+\end{equation}
+We take $t$ and $k$ to be $0.1$ and $20$, respectively.}
+
+\edit1{This metric effectively measures the distance between two modes normalized by their variances, with a penalty when one mode is not highly weighted.
+These choices were made in order for the score to match by eye which distributions appear to have one as opposed to two peaks, and was found to empirically be more reliable than other statistics like peak-to-trough ratios or mode overlap.
+As demonstrated in Section~\ref{ssec:full_sim_suite}, a score of $\mathcal{B}>2.25$ appears to select the bimodal populations.}
 

### 2025-02-13 paper/ms.tex
Update surface density section

@@
 \subsection{Surface Density Projections}\label{ssec:projections}
-Before dissecting the simulated galaxies in detail, we first take a look at the surface density projections of the gas and stars in the central region, situated on the central galaxy in the bimodal simulation.
+Before dissecting the simulated galaxies in detail, we first examine the surface density projections of the gas and stars in the central region, situated on the central galaxy in the bimodal simulation.
 This is shown in Figure~\ref{fig:projections}.
@@
 The left and right columns show the gas (blue) and stellar (orange) surface density, respectively.
-Each panel is oriented with respect to the stellar angular momentum of the final snapshot ($t=8\,\Gyr$).
-The angular momentum is computed using all star particles within the half-mass radius.
+Each panel is oriented with respect to the stellar angular momentum of the final snapshot ($t=8\,\Gyr$), computed using all star particles within the half-mass radius.
 
@@
 
-    \gridline{\fig{all_L30_frame60.pdf}{0.3\textwidth}{}
-              \fig{all_L30_frame70.pdf}{0.3\textwidth}{}
-              \fig{all_L30_frame80.pdf}{0.3\textwidth}{}
+    \gridline{\fig{bimodal_L30_frame60.pdf}{0.3\textwidth}{}
+              \fig{bimodal_L30_frame70.pdf}{0.3\textwidth}{}
+              \fig{bimodal_L30_frame80.pdf}{0.3\textwidth}{}
               }
-    \gridline{\fig{all_L30_frame90.pdf}{0.3\textwidth}{}
-              \fig{all_L30_frame100.pdf}{0.3\textwidth}{}
-              \fig{all_L30_frame110.pdf}{0.3\textwidth}{}
+    \gridline{\fig{bimodal_L30_frame90.pdf}{0.3\textwidth}{}
+              \fig{bimodal_L30_frame100.pdf}{0.3\textwidth}{}
+              \fig{bimodal_L30_frame110.pdf}{0.3\textwidth}{}
               }
-    \gridline{\fig{all_L30_frame120.pdf}{0.3\textwidth}{}
-              \fig{all_L30_frame200.pdf}{0.3\textwidth}{}
-              \fig{all_L30_frame320.pdf}{0.3\textwidth}{}
+    \gridline{\fig{bimodal_L30_frame120.pdf}{0.3\textwidth}{}
+              \fig{bimodal_L30_frame200.pdf}{0.3\textwidth}{}
+              \fig{bimodal_L30_frame320.pdf}{0.3\textwidth}{}
               }
-  % \includegraphics[width=\textwidth]{surfdens.pdf}
   \caption{Frames from a movie showing a surface density projection of the bimodal simulation over time.
@@
 The colormap for the gas ranges from $1$ to $10^2\,\Msun/\pc^2$, while for the stars ranges from $1$ to $10^4\,\Msun/\pc^2$.
-(A full movie is \href{https://drive.google.com/file/d/1RKpFpnFIpl7XYAX5lvF7CyaPVO5dS3EO/view?usp=drive_link}{here}.)}
+\edit1{Description of movie: The disk collapses quickly, forming a disk within $500\,\Myr$.
+The satellite galaxy quickly passes in the background at $\sim700\,\Myr$.
+At $\sim2\,\Gyr$, the satellite directly merges with the central galaxy, fully coalescing by $\sim3\,\Gyr$.
+Over the next $5\,\Gyr$, the disk steadily grows, expanding in size.} (A full movie is \edit1{linked in submission}.)}
   \label{fig:projections}

### 2025-02-13 paper/ms.tex
Major changes to results
The git diff on this was weird so I just committed everything at once :/

@@
 \subsection{Abundance Distribution}\label{ssec:abundplane}
-In Figure~\ref{fig:fig1}, briefly discussed in Section~\ref{sec:intro}, we show the abundance distribution of the Milky Way as well as two of our idealized merger simulations in the upper panels.
-A number of our idealized simulations exhibit either a bimodal or unimodal abundance distribution, and so we have selected two representative examples.
-The simulation labeled bimodal had orbital parameters of $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$.
-The unimodal simulation is identical, except that $R_0=129\,\kpc$.
-The bimodal and unimodal labels are of the outcome of the simulation, and do not reflect any particular choice made in their setup.
-
-There are, of course, differences between the bimodal simulation and the Milky Way.
-First, the scaling in \MgFe{} is different -- in the simulation, the low-$\alpha$ sequence lies at $\sim0.2$, while in the Milky Way it is at about $\MgFe\sim0$.
-Second, in the Milky Way the high-$\alpha$ sequence neatly joins the low-$\alpha$ sequence at $\FeH\sim0$, while in the simulation the two actually diverge more at higher \FeH{}.
-Finally, at high \FeH{} the distribution bends upwards while in the simulation it bends downwards.
-
-In the lower panels of Figure~\ref{fig:fig1}, we show the distributions of \MgFe{} at different fixed \FeH{}.
-The (blue, orange, red, green) lines show the \MgFe{} distribution at a \FeH{} of ($-0.5$, $-0.25$, $0$, $0.25$), in bins of width $0.05\,\dex$.
-The distributions of \MgFe{} are offset (but not rescaled) so that they do not overlap.
-Here, the bimodality seen in the Milky Way is quite striking at lower metallicities.
-The peaks are well-separated, by $\sim0.2\,\dex$.
-In the bimodal simulation, the distribution is still clearly bimodal, but the peaks are less well-separated, by $\sim0.1\,\dex$.
-In the unimodal simulation, there is a hint of some structure at $\FeH \gtrsim 0.25$, but there is not a strong multimodal structure.
 \begin{figure*}
@@
 
+In Figure~\ref{fig:fig1}, we show the abundance distribution of the Milky Way as well as two of our idealized merger simulations in the upper panels.
+A number of our idealized simulations exhibit either a bimodal or unimodal abundance distribution, and so we have selected two representative examples \edit1{as discussed in Section~\ref{ssec:orbit_setup}.} The bimodal and unimodal labels are of the outcome of the simulation, and do not reflect any particular choice made in their setup.
+
+There are, of course, differences between the bimodal simulation and the Milky Way.
+First, the scaling in \MgFe{} is different -- in the simulation, the low-$\alpha$ sequence lies at $\sim0.2$, while in the Milky Way it is at about $\MgFe\sim0$.
+Second, in the Milky Way the high-$\alpha$ sequence neatly joins the low-$\alpha$ sequence at $\FeH\sim0$, while in the simulation the two actually diverge more at higher \FeH{}.
+
+In the lower panels of Figure~\ref{fig:fig1}, we show the distributions of \MgFe{} at different fixed \FeH{}.
+The (blue, orange, red, green) lines show the \MgFe{} distribution at a \FeH{} of ($-0.5$, $-0.25$, $0$, $0.25$), in bins of width $0.05\,\dex$.
+The distributions of \MgFe{} are offset (but not rescaled) so that they do not overlap.
+Here, the bimodality seen in the Milky Way is quite striking at lower metallicities.
+The peaks are well-separated, by $\sim0.2\,\dex$.
+In the bimodal simulation, the distribution is still clearly bimodal, but the peaks are less well-separated, by $\sim0.1\,\dex$.
+In the unimodal simulation, there is a hint of some structure at $\FeH > 0.25$, but there is not a strong multimodal structure.
+
 \subsection{Build up of the Abundance Plane}\label{ssec:abundplane_build}
 Next, we examine the build up of the abundance plane.
-First, in Figure~\ref{fig:before_after}, we show the abundance plane at various points along the merger.
-We have divided the history of the merger into ``before'' ($t < 1.5\,\Gyr$), ``during'' ($1.5\,\Gyr < t < 2.5\,\Gyr$), and ``after'' ($t > 2.5\,\Gyr$).
-These times have been chosen somewhat by the orbital history and somewhat by visually inspecting the simulation, and so these deliniations are, to an extent, arbitrary.
-Nonetheless, it is clear that the high-$\alpha$ sequence forms before and during the merger (middle panels), and that the low-$\alpha$ sequence forms after the merger (right panel).
-We show a dashed line given by $-0.1\times\FeH + 0.31$, which is a crude way of separating the high- and low-$\alpha$ sequence.
+\edit1{In the left panel of Figure~\ref{fig:before_after}, we show the metallicity-dependent star formation rate of the bimodal simulation using star particles in the solar neighborhood at the end of the simulation within a $0.1\,\dex$ bin centered at $\FeH=0$.
+There is a clear dip in the SFR at $\sim2.8\,\Gyr$, which we indicate with a vertical line.}
 
-It is informative to examine the star formation history (SFH) split into the high- and low-$\alpha$ sequences at a fixed \FeH{}, shown in Figure~\ref{fig:before_after_sfh}.
-The high- and low-$\alpha$ sequences (blue and orange) are defined as the star particles lying above and below the dashed line in Figure~\ref{fig:before_after}, respectively.
-We show this only in a narrow bin of width $0.1\,\dex$ at $\FeH\sim0$.
-We chose this value of \FeH{} because here the valley of the bimodality is deepest (see Figure~\ref{fig:fig1}).
-One can see a very clear separation in time between the high- and low-$\alpha$ sequences, with the high-$\alpha$ sequence forming before the low-$\alpha$ sequence.\footnote{There is a small amount of low-$\alpha$ formation at the very end of the high-$\alpha$ sequence, but this can be understood as simply an inadequacy in our simple way of separating the two sequences.
-Alternatively, one could assert that the separation in time is the real delineation between the two sequences, and that the boundary in the abundance plane has only mild contamination.} Furthermore, there is a brief period of $\sim300\,\Myr$ between the two sequences where no stars have formed.
+\edit1{In the center left panel, we show the abundance plane distribution from the bimodal simulation for all stars in the solar neighborhood, replicating Figure~\ref{fig:fig1}.
+A dashed line at $-0.1\times\FeH+0.3$, chosen by eye, is plotted to demarcate the high- and low-$\alpha$ sequences.
+In the center right and right panels, we show the distribution of star particles which form before and after the dip in the metallicity-dependent SFR at $t=2.8\,\Gyr$, respectively.
+The vast majority of the high-$\alpha$ sequence forms before the dip, while most of the low-$\alpha$ sequence forms afterward.}
 
-It can also be shown that the exact timing of this quiescent period is metallicity-dependent.
-We show the same SFH in Figure~\ref{fig:before_after_sfh_by_iron}, but at varying bins in \FeH{} of $-0.5$, $-0.25$, and $0$ (blue, orange, and red, respectively).
-For clarity, we do not separate the SFHs by the high- and low-$\alpha$ sequences, but have verified that the same demarcation arises as in Figure~\ref{fig:before_after_sfh}.
-Here, we can see that at $\FeH=-0.5$ the quiescent period begins $\sim250\,\Myr$ earlier than at $\FeH=0$.
+\edit1{This sequence of build up is markedly different in the unimodal simulation, which we show in Figure~\ref{fig:before_after_uni}.
+Here, there is no clear dip in the metallicity dependent SFR in the left panel.
+We still place a vertical line similar to the one in Figure~\ref{fig:before_after}, except now it is chosen to be at $t=2.3\,\Gyr$, which is $\sim300\,\Myr$ after the second pericentric passage.
+This is where the gap appears in the bimodal simulation (see Figure~\ref{fig:orbit}).
+We see that stars which form before and after this point in the simulation overlap considerably in the abundance plane.}
 
-\subsection{\alphaFe{} Behavior Associated with Quiescence}
-We now examine more closely the natural suspicion that the quiescent phase in Figure~\ref{fig:before_after_sfh} is responsible for the bimodal structure in Figure~\ref{fig:before_after}.
-In Figure~\ref{fig:SFR_alpha}, we show the SFR (blue lines) of each of the bimodal and unimodal galaxies (left and right panels, respectively) as well as the median \MgFe{} of the gas (orange lines) in a bin centered on $\FeH{}=-0.1$ with width $0.05\,\dex$.
-The SFR is shown for the entire galaxy ($r<15\,\kpc$) while the median \MgFe{} is shown for $2\,\kpc<r<5\,\kpc$.\footnote{The solar neighborhood-like selection of stars (discussed in Section~\ref{ssec:solarneigh}) mostly selects stars at $2\,\kpc<r<5\,\kpc$.
-We choose to plot the median \MgFe{} of the gas at these radii, since it is roughly that gas which is forming stars that ends up in our sample.
-On the other hand, we choose to show the SFR for the entire galaxy, as the enrichment from that star formation affects the entire galaxy at this epoch.}
+\edit1{The timing and duration of the metallicity-dependent SFR dip is not the same for all \FeH{}.
+In the upper panel of Figure~\ref{fig:before_after_sfh_by_iron}, we show the SFR at metallicities of $-0.5$, $-0.25$, $0$, and $0.25$ in blue, orange, red, and green, respectively.
+We mark the location of the dip in the red $\FeH=0$ SFR with a vertical line at $t=2.8\,\Gyr$, as in Figure~\ref{fig:before_after}.
+In the orange SFR at $\FeH=-0.25$, which displayed a prominent bimodality in Figure~\ref{fig:fig1}, there is a similar dip.
+However, it occurs about $250\,\Myr$ earlier.
+The $\FeH=0$ and $\FeH=-0.25$ dips have widths of about $500$ and $250\,\Myr$, respectively.
+In the blue $\FeH=-0.25$ SFR, which does not display a prominent bimodality, there is no dip separating two periods of sustained SF.
+In the green $\FeH=0.25$ SFR, a small amount of SF occurs before an extended $\sim1\,\Gyr$ dip, leading to a bimodality with a weak although well-separated high-$\alpha$ mode.}
 
-The merger appears to induce a starburst, where the SFR rises from $\sim3.5\,\Msunyr$ at $\sim1\Gyr$ to a peak of $\sim12\,\Msunyr$ at $\sim2\,\Gyr$.
-This starburst is then followed by a quiescent period, with a minimum SFR of $\sim1\,\Msunyr$ and a duration of $\sim500\,\Myr$.
-The dip in SFR is not as pronounced as it was when we plotted the SFH at a particular iron (Figure~\ref{fig:before_after_sfh}).
-This quiescent period is associated with a drop in \MgFe{} from $\sim0.35$ to $\sim0.2\,\dex$ in only $\sim250\,\Myr$.
-Once the SFR recovers $\sim500\,\Myr$ later, \MgFe{} again rises, but only to $\sim0.28\,\dex$.
-
-This behavior is absent in the unimodal simulation (right panel) -- while there is a starburst, it does not display a period of suppressed star formation, and there is no associated drop in \MgFe{}.
-It does still have a period of enhanced star formation, but this is actually coincident with an enhancement in \MgFe{}.
-This sequence of events is further emphasized in Figure~\ref{fig:alpha_vs_tform}, which shows a transparent scatter plot of \MgFe{} as a function of formation time.
-In the bimodal simulation, there is a clear gap in \MgFe{} during the period of quiescence followed by the brief formation of $\alpha$-deficient stars.
-In the unimodal simulation, on the other hand, there is no gap and instead a brief formation of $\alpha$-enhanced stars.
-
-\subsection{Cause of Quiescence}\label{ssec:cause_qui}
-Why there is a quiescent period in the bimodal simulation but not the unimodal simulation probably has to do with some transient, stochastic property of the gas in and around the galaxy.
-In some states, the AGN is better able to quench the galaxy than in others.
-Verifying this further is beyond the scope of this work, but we show some evidence of the association in Appendix~\ref{app:cause_qui}.
-
-This outcome suggests that a merger alone is not sufficient in order to generate a bimodality.
-Rather, the merger must induce a quenching phase.
-Whether this occurs depends both on the properties of the merger but also on the state of the central galaxy itself and whether it can launch AGN-driven winds that result in significant gas removal.
-Our work would argue for some stochasticity in whether a particular merger leads to such quenching.
+\edit1{In the lower panel of Figure~\ref{fig:before_after_sfh_by_iron}, we show corresponding curves for the unimodal simulation.
+A vertical line is shown at $2.3\,\Gyr$, as described earlier.
+Here, we see that at no \FeH{} is there a prominent dip.}
 
@@
   \includegraphics[width=\textwidth]{before_after.pdf}
-  \caption{\textbf{The high-$\alpha$ sequence forms before the merger, the low-$\alpha$ sequence forms after the merger.} This plot shows the sequence of events leading to the build-up of the low- and high-$\alpha$ sequences for our fiducial bimodal simulation.
-We have separated the high- and low-$\alpha$ sequences by a dashed line at $-0.1\FeH + 0.31$, which was chosen by eye to lie in the trough.
-The left panel shows all star particles in our solar neighborhood cut.
-The middle left panel shows the star particles that form before the merger ($\tform < 1.5\,\Gyr$), which form a weak sequence of star particles at the lowest \FeH and highest \MgFe.
-The middle right panel shows the star particles that form during the starburst ($1.5\,\Gyr < \tform < 2.5\,\Gyr$).
-These star particles form the portion of the high-$\alpha$ sequence closest to the trough, and the density of star particless is higher than those that form before.
-The right panel shows the star particles which form after the merger ($\tform > 2.5\,\Gyr$).
-These star particles form almost entirely below the trough.}
+  \caption{\edit1{The buildup of the abundance plane in the bimodal simulation.
+The left panel shows the metallicity-dependent star formation rate (SFR) for star particles in the solar neighborhood at the end of the simulation, selected within a $0.1\,\dex$ bin centered at $\FeH=0$.
+A clear dip in this SFR occurs at $t \sim 2.8\,\Gyr$, marked by the vertical line.
+The center-left panel shows the abundance plane distribution for all stars in the solar neighborhood, with a dashed line at $-0.1\times\FeH+0.3$ (chosen by eye) demarcating the high- and low-$\alpha$ sequences.
+The center-right and right panels show the abundance plane distributions for stars formed before and after the SFR dip, respectively.
+The majority of the high-$\alpha$ sequence forms before the dip, while most of the low-$\alpha$ sequence forms afterward.}}
   \label{fig:before_after}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{before_after_uni.pdf}
+  \caption{\edit1{The buildup of the abundance plane in the unimodal simulation, similar to Figure~\ref{fig:before_after}.
+The left panel shows the metallicity-dependent star formation rate (SFR) for stars in the solar neighborhood, with no clear dip.
+A vertical line at $t=2.3\,\Gyr$, corresponding to the orbital stage of the gap in the bimodal simulation (see text), is included for comparison.
+The center left shows the abundance plane for all stars.
+The center-right and right panels show the abundance plane for stars formed before and after $t=2.3\,\Gyr$, respectively.
+Unlike the bimodal case, stars formed before and after this time overlap considerably in the abundance plane, indicating the absence of a distinct separation between high- and low-$\alpha$ sequences.}}
+  \label{fig:before_after_uni}
 \end{figure*}
@@
   \centering
-  \includegraphics[width=\columnwidth]{before_after_sfh.pdf}
-  \caption{\textbf{At fixed metallicity, the low- and high-$\alpha$ sequence are cleanly separated in time by an intervening quiescent period.} Here we show the star formation history of the high- and low-$\alpha$ sequences.
-The blue (low-$\alpha$) and orange (high-$\alpha$) histograms correspond to the dashed line cut made in the \MgFe{}-\FeH{} plane in Figure~\ref{fig:before_after}, at a fixed metallicity of $\FeH=0$ with width $0.05\,\dex$.
-One can see that there is a nearly perfect separation in time between the formation of the high-$\alpha$ and low-$\alpha$ sequences by a quiescent period lasting $\sim300\,\Myr$.
-There is a small amount of contamination at the end of the high-$\alpha$ sequence which can be attributed to the inadequacy of the linear cut model of the two sequences.}
-  \label{fig:before_after_sfh}
-\end{figure}
-
-\begin{figure}
-  \centering
   \includegraphics[width=\columnwidth]{before_after_sfh_by_iron.pdf}
-  \caption{\textbf{The timing of the quiescent period which divides the high- and low-$\alpha$ sequences is metallicity dependent.} The star formation history of stars at various fixed metallicities ($\FeH=0$, $-0.25$, and $-0.5\,\textrm{dex}$) in bins of width $0.05\,\dex$.
-As in Figure~\ref{fig:before_after_sfh}, there is a quiescent period period which separates the formation of the low- and high-$\alpha$ sequence.
-However, the timing of the quiescent period is metallicity-dependent.
-It occurs earlier at lower metallicities, by $\sim250\,\Myr$ for the metallicities shown in this plot.}
+  \caption{\edit1{Metallicity-dependent star formation histories (SFH) for the bimodal (top) and unimodal (bottom) simulations.
+The SFH at different metallicities ($\FeH=-0.5, -0.25, 0.0, 0.25$) is shown in blue, orange, red, and green, respectively.
+In the top panel, the vertical line at $t=2.8\,\Gyr$ marks the SFR dip at $\FeH=0$, corresponding to the gap seen in Figure~\ref{fig:before_after}.
+A similar dip is present in the orange $\FeH=-0.25$ SFR, but it occurs $\sim250\,\Myr$ earlier, with a width of about $250\,\Myr$.
+The $\FeH=-0.5$ (blue) SFR lacks a distinct dip, while the $\FeH=0.25$ (green) SFR features an extended $\sim1\,\Gyr$ dip after a short period of SF, leading to a weak but well-separated high-$\alpha$ mode.
+The bottom panel shows the corresponding SFHs for the unimodal simulation, with a vertical line at $t=2.3\,\Gyr$.
+There are no strong dips at any metallicity, consistent with the absence of a well-defined bimodality.}}
   \label{fig:before_after_sfh_by_iron}
@@
   \centering
-  \includegraphics[width=\textwidth]{SFR_alpha.pdf}
-  \caption{\textbf{A global suppression of star formation is associcated with a decrease in \MgFe{}, which is seen in the bimodal simulation but not in the unimodal simulation.} Here, we show both the SFR of the central galaxy ($r<15\,\kpc$) and the median \MgFe{} for gas at $2\,\kpc<r<5\,\kpc$ at a fixed \FeH{} bin centered on $0$ with width $0.05\,\dex$.
-The left panel shows the bimodal simulation while the right panel shows the unimodal simulation.
-A vertical dashed line at $2\,\Gyr$ in each plot indicates the approximate time of the merger, but before complete coalescence.
-In the left panel, a shaded region from $2.5\,\Gyr$ to $2.75\,\Gyr$ indicates the approximate period of quiescence shown in Figure~\ref{fig:before_after_sfh}.
-This suppression of star formation is associated with a sudden drop in the median \MgFe{} of the gas.
-Neither the suppression of star formation nor the drop in \MgFe{} are seen in the unimodal simulation.}
-  \label{fig:SFR_alpha}
+  \includegraphics[width=\textwidth]{alpha_vs_tform_obserr.pdf}
+  \caption{\edit1{In the bimodal simulation, a gap appears when plotting stars in a $0.05\,\dex$ bin at $\FeH=0$ on the \MgFe{}-$t_{\textrm{form}}$ plane (blue, left panel).
+In the unimodal simulation there is no such gap (orange, left panel).
+In the middle panel, we show the same data but assuming errors in \FeH{}, \MgFe{}, and $t_{\textrm{form}}$ of $0.0075\,\dex$, $0.012\,\dex$, and $1\,\Gyr$, respectively.
+The gap in the bimodal simulation appears weakly as two populations overlapping in age.
+In the right panel we show stars in the Milky Way from APOKASC3 in $0.2\,\dex$ bins at $\FeH=-0.5$ (blue) and $0$ (orange).
+The low-metallicity bin is where the Milky Way bimodality is strongest while there is no bimodality at the solar-metallicty bin (see Figure~\ref{fig:fig1}).
+Offsets have been added to \MgFe{} values for clarity: $-0.3$ in the unimodal points in the left and middle panels, and $+0.1$ and $-0.1$ in the low/solar-metallicity bins, respectively, in the right panel.}}
+  \label{fig:alpha_vs_tform}
 \end{figure*}
 
-\begin{figure}
+\subsection{Comparison to Observations}\label{ssec:compare_obs}
+\edit1{A plot of \MgFe{} vs age or formation time is a useful way to further demonstrate the formation scenario of the bimodality, as well as making comparison to observations.
+We show this for the simulation data in the left panel of Figure~\ref{fig:alpha_vs_tform} in bins of width $0.05\,\dex$ centered at $\FeH=0$.
+The bimodal simulation (blue, upper data) displays a gap in the ages at $\sim2.8\,\Gyr$, coinciding with the gap in Figure~\ref{fig:before_after}.
+On the other hand, the unimodal simulation (orange, lower data) displays no such age gap.}
+
+\edit1{The center panel shows these simulation data points convolved with realistic observational errors.
+We assume errors in \FeH{}, \MgFe{}, and $t_{\textrm{form}}$ of $0.0075\,\dex$, $0.012\,\dex$, and $1\,\Gyr$, respectively.\footnote{The \FeH{} error impacts which star particles lie in the \FeH{} selection.} The \FeH{} and \MgFe{} errors are characteristic of the errors provided in the APOGEE dataset, and the $1\,\Gyr$ comes from assuming the typical $12.5\%$ uncertainty from APOKASC-3 at an age of $8\,\Gyr$.
+In the bimodal simulation (blue, upper data), separate populations can be seen that overlap significantly in $t_{\textrm{form}}$.
+There is not a strong separation in the unimodal case (orange, lower data).}
+
+\edit1{The right panel shows observational data from APOKASC-3.
+We show in the blue, upper data a $0.2\,\dex$ bin centered at $\FeH=-0.5$ and in the orange, lower data centered at $\FeH=0$.
+In the Milky Way, there is a bimodal and unimodal \MgFe{} distribution at these metallicities, respectively.
+At $\FeH=-0.5$, one could weakly argue that there are separate populations as in the simulation.
+However, the large uncertainties at the relevant ages ($\sim1\,\Gyr$ at ages of $\sim8\,\Gyr$) and the small sample size (125 and 1175 at $\FeH=-0.5$ and $0$, respectively) prevents a definitive statement from being made.
+Larger sample sizes and more precise age estimates in the future would clarify the connection between simulation and observation, although achieving age uncertainities of $<10\%$ for such old stars is very challenging \citep[e.g.][]{2010ARA&A..48..581S}.}
+
+\edit1{There is an additional complication in the data coming from the presence of young, $\alpha$-rich stars.
+These have been argued to be old stars with misclassified astroseismic ages due to binary mass transfer \citep[and references therein]{2023A&A...671A..21J}, though with some appearing to be genuinely young \citep[and references therein]{2024arXiv241002962L}, with a range of explanations given \citep[e.g.][]{2015A&A...576L..12C,2021MNRAS.508.4484J,2023arXiv231105815S}.
+It is unclear which of the $\alpha$-rich stars faithfully reflect the mean ISM chemistry at their inferred age, and so it is not obvious if any detailed conclusions can be drawn from this comparison.}
+
+\subsection{Full Simulation Suite}\label{ssec:full_sim_suite}
+\edit1{We next expand our discussion to the full simulation suite by studying the conditional 1D \MgFe{} distribution in Figure~\ref{fig:all_hist}.
+We plot the distribution of \MgFe{} for all stars with \FeH{} lying in a bin of width $0.1\,\dex$ centered at $0\,\dex$.
+Each distribution corresponds to a choice in the three orbital variables $R_0$, $V_0$, and $\eta$.
+We rank the simulations in alphabetical order from least to most bimodal\footnote{There is one more simulation in the suite than letters in the English alphabet, so the simulation with the highest bimodality score is labeled aa.}, as determined by the bimodality score $\mathcal{B}$ introduced in Section~\ref{ssec:bim_score}.
+The list of simulations in the orbital grid along with the associated orbital parameters and bimodality scores is given in Table~\ref{tab:my-table}.}
+
+\edit1{Simulations from r onwards, which have $\mathcal{B}>2.25$, are considered bimodal.
+This demarcation was chosen by eye using Figure~\ref{fig:all_hist}.
+For these simulations, we plot the trough \MgFe{} (the location of the minimum between the two maxima) as a vertical line.
+This value was determined by taking the location of the minimum of the distribution between $0.25$ and $0.35\,\dex$, and is also given in Table~\ref{tab:my-table}.}
+
+\edit1{Simulations from r to aa have clear bimodalities.
+The trough \MgFe{} is roughly consistent between simulations, appearing between $\sim0.25$ and $0.3\,\dex$.
+For simulations marked as unimodal, some appear to have two populations but which are not distinct enough to form a clear bimodality (e.g., m, n, and o).}
+
+\begin{figure*}
   \centering
-  \includegraphics[width=\columnwidth]{alpha_vs_tform.pdf}
-  \caption{\textbf{In the bimodal simulation, a gap in stellar ages is briefly followed by the formation of $\alpha$-deficient star particles.} The formation times and \MgFe{} values of star particles in the bimodal (blue) and unimodal (orange) simulations.
-In the unimodal simulation, no gap is present and there is briefly the formation of $\alpha$-enhanced star particles at the same time.
-The \MgFe{} values of the unimodal simulation have been offset by $-0.3$ for clarity.}
-  \label{fig:alpha_vs_tform}
-\end{figure}
+  \includegraphics[width=\textwidth]{hist.pdf}
+  \caption{\edit1{The conditional 1D \MgFe{} distribution for all stars with \FeH{} in a bin of width $0.1\,\dex$ centered at $0\,\dex$.
+Each panel corresponds to a different set of orbital parameters ($R_0$, $V_0$, and $\eta$) and is labeled alphabetically from least to most bimodal, with the labels defined in Table~\ref{tab:my-table}.
+The final simulation, which has the highest bimodality score $\mathcal{B}$, is labeled ``aa.'' Simulations with $\mathcal{B}>2.25$ (starting from simulation r) exhibit clear bimodalities, with the trough \MgFe{} (minimum between the two peaks) marked.
+This trough generally falls between $0.25$ and $0.3\,\dex$.
+Simulations with lower bimodality scores appear unimodal, though some (e.g., m, n, and o) show hints of a secondary population without forming a distinct bimodal structure.}}
+  \label{fig:all_hist}
+\end{figure*}
+
+\begin{table}[]
+\centering
+\begin{tabular}{cccccc}
+$\textrm{letter}$ & $R_0$ & $V_0$ & $\eta$ & $\mathcal{B}$ & $\textrm{trough}\,\MgFe{}$ \\ \hline
+a                 & $129$ & $129$ & $0.4$  & $0.29$        &                            \\
+b                 & $129$ & $116$ & $0.4$  & $0.35$        &                            \\
+c                 & $116$ & $116$ & $0.4$  & $0.77$        &                            \\
+d                 & $142$ & $116$ & $0.5$  & $0.79$        &                            \\
+e                 & $142$ & $129$ & $0.6$  & $0.89$        &                            \\
+f                 & $116$ & $129$ & $0.4$  & $1.12$        &                            \\
+g                 & $116$ & $116$ & $0.5$  & $1.25$        &                            \\
+h                 & $116$ & $142$ & $0.4$  & $1.34$        &                            \\
+i                 & $142$ & $142$ & $0.5$  & $1.43$        &                            \\
+j                 & $129$ & $142$ & $0.5$  & $1.46$        &                            \\
+k                 & $142$ & $129$ & $0.4$  & $1.62$        &                            \\
+l                 & $142$ & $142$ & $0.6$  & $1.75$        &                            \\
+m                 & $116$ & $129$ & $0.5$  & $1.82$        &                            \\
+n                 & $129$ & $129$ & $0.5$  & $1.96$        &                            \\
+o                 & $129$ & $116$ & $0.5$  & $2.04$        &                            \\
+p                 & $116$ & $116$ & $0.6$  & $2.16$        &                            \\
+q                 & $116$ & $129$ & $0.6$  & $2.24$        &                            \\ \hline
+r                 & $142$ & $129$ & $0.5$  & $2.26$        & $0.283$                    \\
+s                 & $142$ & $116$ & $0.4$  & $2.52$        & $0.313$                    \\
+t                 & $116$ & $142$ & $0.6$  & $2.59$        & $0.258$                    \\
+u                 & $116$ & $142$ & $0.5$  & $2.62$        & $0.293$                    \\
+v                 & $142$ & $116$ & $0.6$  & $2.65$        & $0.273$                    \\
+w                 & $129$ & $142$ & $0.6$  & $2.66$        & $0.288$                    \\
+x                 & $142$ & $142$ & $0.4$  & $2.70$        & $0.283$                    \\
+y                 & $129$ & $116$ & $0.6$  & $2.94$        & $0.303$                    \\
+z                 & $129$ & $129$ & $0.6$  & $3.12$        & $0.278$                    \\
+aa                & $129$ & $142$ & $0.4$  & $3.34$        & $0.298$                   
+\end{tabular}
+\caption{\edit1{All simulations in the orbital grid (as defined by $R_0$, $V_0$, and $\eta$) ordered by their bimodality score $\mathcal{B}$.
+Each simulation is given an identifying letter.
+For simulations marked as bimodal ($\mathcal{B}>2.25$), we also list the trough \MgFe{}, or location of the minimum of the \MgFe{} distribution.}}
+\label{tab:my-table}
+\end{table}
+
+\edit1{We study the formation of the 1D distributions in Figure~\ref{fig:all_hist} through a scatter plot of \MgFe{} vs formation time of star particles in Figure~\ref{fig:all_scatter}, similar to Figure~\ref{fig:alpha_vs_tform}.
+The order and colors are identical as in Figure~\ref{fig:all_hist}, and we use the same \FeH{} selection.
+We only plot a random subsample of 350 stars, and points are plotted with a transparency of $\alpha=0.5$ so that the perceived density is slightly higher in cases of overlap.
+An offset of $-0.2$ and $-0.4$ are given to the second and third (orange and red) simulations in each panel.
+For simulations marked as bimodal (r through aa), we also plot a horizontal line at the location of the trough \MgFe{}.}
+
+\edit1{Most of the bimodal simulations (r through aa) have a gap in the distribution at around the time of the merger ($\sim2$-$3\,\Gyr$, depending on the orbital parameters).
+Before this gap, star formation occurs above the trough while after it occurs below the trough.
+However, there are two exceptions: simulation~t does not have a full gap (though the density does decrease), and simulation~w is irregular, with star formation simultaneously occuring above and below the trough.}
+
+\edit1{In the unimodal simulations (a through q), there does appear to be gaps (d, f, g, h, and o).
+However, in these cases, there is not a large amount of star formation occuring before the gap, and so the high-$\alpha$ sequence is underemphasized and does not lead to a significant bimodality.}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{scatter.pdf}
+  \caption{Scatter plot of \MgFe{} versus formation time for star particles in each simulation, corresponding to the 1D distributions shown in Figure~\ref{fig:all_hist}.
+Each panel represents a different set of orbital parameters ($R_0$, $V_0$, and $\eta$), arranged from least to most bimodal (as defined by the bimodal score $\mathcal{B}$.
+The colors and order match Figure~\ref{fig:all_hist}, with a random subsample of 350 stars plotted per simulation.
+Transparency ($\alpha=0.5$) is used to highlight regions of higher density.
+The second and third (orange and red) simulations in each panel are offset by $-0.2$ and $-0.4\,\dex$ for clarity, respectively.
+For bimodal simulations (r through aa), the trough \MgFe{} (minimum between the two peaks) is indicated with a horizontal line.
+In most bimodal cases, a gap in the distribution emerges at approximately the merger time ($\sim2$--$3,\Gyr$, depending on orbital parameters), with older stars forming at higher \MgFe{} and younger stars at lower \MgFe{}.
+Notably, simulation~t lacks a clear gap, and simulation~w exhibits irregular behavior with star formation occurring both above and below the trough.
+Among unimodal simulations (a through q), some exhibit apparent gaps (e.g., d, f, g, h, and o), but these do not result in strong bimodalities due to the low number of high-\MgFe{} stars forming before the gap.}
+  \label{fig:all_scatter}
+\end{figure*}
 

### 2025-02-13 paper/ms.tex
Update discussion intro par and first section

@@
 \section{Discussion}\label{sec:discussion}
-We have demonstrated that a bimodal structure in the elemental abundance plane is associated with a brief quiescent phase in our idealized merger simulations.
-We now construct a possible framework for understanding the formation of the bimodality, discuss its relation to prior work, and then discuss predictions and connections to observations.
+\edit1{We have investigated the formation of an $\alpha$-element bimodality in the Milky Way through a series of idealized merger simulations.
+Our key finding is that a metallicity-dependent quiescent period in star formation can lead to a bimodal distribution in \alphaFe{} at specific \FeH{} values.
+This scenario does not necessarily require a global quenching period.
+We now discuss the details of this mechanism, its connection to high-redshift observations and cosmological simulations, compare with some explanations in the literature, and explore its observational implications and directions for future work.}
 
-\subsection{Quiescence Leads to Bimodality}\label{ssec:formqui}
-We executed a series of idealized merger simulations in which we modified the starting radius and velocity by $\pm10\%$ and the circularity by $\pm0.1$, for a total of $27$ simulations.
+\subsection{\FeH{}-dependent Quiescence Leads to Bimodality}\label{ssec:formqui}
+\edit1{We executed a series of idealized merger simulations in which we modified the starting radius and velocity by $\pm10\%$ and the circularity by $\pm0.1$, for a total of $27$ simulations.
 The central and satellite galaxies, which are meant to resemble the Milky Way and GSE at $z\sim2$, are otherwise identical across the simulations.
 Some of these simulations induce a bimodality, while others do not.
-We have examined a representative of each scenario in detail.
+We have examined a representative of each scenario in detail.}
 
-We described a series of results in Section~\ref{sec:results} which give a natural explanation for the separation between the high- and low-$\alpha$ sequences in our simulations.
-First, a merger induces a starburst in the simulation.
-If this starburst does not induce a quiescent period, then the median \MgFe{} of the gas briefly increases before continuing along the typical evolutionary path (right panel of Figure~\ref{fig:SFR_alpha}).
-However, if there is a quiescent period, the median \MgFe{} drops for the duration of the quiescent period before recovering to the typical path (left panel of Figure~\ref{fig:SFR_alpha}).
+\edit1{The key driver of bimodality in our simulations is the presence of a metallicity-dependent quiescent period.
+This is shown most clearly in Figure~\ref{fig:before_after}, where the abundance plane is split into stars which form before and after a gap in the $\FeH=0$ SFR.
+Stars which form before and after the gap populate the high- and low-$\alpha$ sequences, respectively, with minimal overlap.
+No gap and no separation between the sequences is seen in the unimodal case (Figure~\ref{fig:before_after_uni}).}
 
-This drop can be understood in terms of the mechanics of the galaxy formation model as described in Section~\ref{ssec:gfm}.
-When a star particle forms, it only takes $\sim40\,\Myr$ before the last Type II SN has gone off and its material enrichment is dominated by Fe from Type Ia SNe.
-As a result, during the quiescent phase which lasts a few hundred Myr, there is relatively little $\alpha$-element production.
-On the other hand, star particles are still able to generate Fe through Type Ia SNe which have a longer period of influence.
-The fact that the quiescent period is preceded by a starburst is important.
-Even though star particles produce Fe through the Type Ia channel for Gyr, younger star particles still produce much more Fe than older star particles.
-In the TNG model, the number of Type Ia SNe decays with time as $(t/\tau_8)^{-s}$, where $\tau_8=40\,\Myr$ is the lifetime of an $8\,\Msun$ star and $s=1.12$.
-Therefore, the burst of star formation at $t\sim2.25\,\Gyr$ is able to generously produce Fe starting at $2.5\,\Gyr$, when is indeed when the drop in \MgFe{} is the most steep.
+\edit1{This perspective is bolstered by examining the distributions of \MgFe{} at $\FeH=0$ for the full simulation suite (Figure~\ref{fig:all_hist}).
+We order these simulations alphabetically using the bimodality score ($\mathcal{B}$, see Section~\ref{ssec:bim_score}).
+Simulations~r through aa are considered bimodal based on a visual inspection, and the location of their trough \MgFe{} (minimium of the distribution) is indicated with a vertical line.}
+
+\edit1{The formation of these bimodal populations can be understood from Figure~\ref{fig:all_scatter}, which shows a scatter plot of \MgFe{} and formation time in the same order, with the trough \MgFe{} indicated with a horizontal line.
+Here, we can see that bimodal simulations tend to have a gap shortly after their respective mergers ($\sim2$--$3\,\Gyr$, depending on the orbital configuration), lying at the position of the trough \MgFe{}.}
+
+\edit1{There are two exceptions in the bimodal cases.
+First, simulation~t does not have a complete gap, although the number of stars forming does still drop.
+This indicates that the complete absence of star formation is not necessary, but rather a reduction in the \FeH{}-dependent SFR may be sufficient if the \alphaFe{} ratio is declining fast enough.
+Second, simulation~w exhibits some irregular behavior, with star formation switching between high- and low-$\alpha$ multiple times.}
+
+\edit1{There are a few unimodal simulations that have gaps -- e.g., d, f, g, h, and o.
+However, in these cases there is very little star formation at $\FeH=0$ before the gap, and so in these cases there is not a distinct high-$\alpha$ mode that can form.}
+
+\edit1{Overall, these simulations indicate that a gap in star formation at a specific metallicity can lead to a bimodality in the conditional \alphaFe{} distribution at that metallicity.
+Determining precisely the mechanism behind generating these gaps is beyond the scope of this work, but we speculate briefly in Section~\ref{ssec:future_work}.}
 

### 2025-02-13 paper/ms.tex
Update high-z obs connection

@@
 
+\subsection{Connection to High Redshift Quenching}\label{ssec:obshiz}
+\edit1{One plausible avenue to producing a \FeH{}-dependent halt in star formation is through a global quiescent period.
+Galaxies which undergo a starburst to quiescence to rejuvenation sequence (post-starburst galaxies, or PSBs) are observed at high-$z$ ($z>1$), and may be plausible Milky Way-progenitors.} With abundance matching, we expect the Milky Way's total stellar mass to be $\sim10^{10.3}\,\Msun$ at $z\sim2$ \citep{2013ApJ...771L..35V}.
+A number of authors have explored PSBs and quiescent galaxies at slightly higher masses at $z\sim2$, with large advances in the post-JWST era.
+
+First, PSBs are not uncommon.
+\citet{2023ApJ...953..119P} found that in massive galaxies ($M_* > 10^{10.6}\,\Msun$) the fraction of PSBs (inferred ages $< 800\,\Myr$) increases from $\sim2.7\%$ ($99/3655$) at $1.0 < z < 1.44$ to $\sim8\%$ ($89/1118$) at $2.16 < z < 2.5$ \citep[see also][]{2012ApJ...745..179W,2019ApJ...874...17B}.
+Later, \citet{2024arXiv240417945P} found that $\sim10\%$ of galaxies at $\sim10^{10.3}\,\Msun$ are quenched \citep[consistent with][]{2013ApJ...777...18M}, and $\sim30\%$ of their quiescent sample is a PSB at $z\sim2$.
+If these galaxies can be quickly rejuvenated, as the system studied in this work would suggest, then the total fraction of galaxies that go through a starburst-quenching phase may be higher.
+
+Furthermore, \citet{2023arXiv231215012C} found that lower mass quiescent galaxies (towards $10^{10.3}\,\Msun$) tend to be younger and more disky, pointing to a merger driven scenario.
+There is also evidence that AGN, which we \edit1{suspect might} be responsible for the \edit1{star formation gaps} in our system (Appendix~\ref{app:cause_qui}), is operating at these redshifts \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024arXiv240518685M,2024Natur.630...54B}.
+
+\edit1{In the context of our proposed mechanism, only a metallicity-specific quenching period is necessary for generating an $\alpha$-bimodality.
+This may correspond to inside-out or outside-in quenching, for which examples are known in the local and high-$z$ universe \citep[e.g.,][]{2015Sci...348..314T,2019ApJ...872...50L}.}
+
 \subsection{Connection to Cosmological Simulations}\label{ssec:cosmo}

### 2025-02-13 paper/ms.tex
Further discussion updates

@@
 This shrinking of the disk, which occurs at $t_{\textrm{lookback}}\sim6\,\Gyr$, is associated with a dip in the SFR at that radius and a decrement in the median \alphaFe{} of $\sim0.05\,\dex$ (their Figure~2), which shortly after recovers.
-This sequence of events is more extended than in our work, but it strongly resembles the scenario in Figure~\ref{fig:before_after_sfh}.
+This sequence of events is more extended than in our work, but it resembles the scenario in Figure~\ref{fig:before_after}.
 
@@
 The present work argues for a starburst-driven quiescence followed by a rapid rejuvenation, with the entire process taking less than $1\,\Gyr$ and the gap only lasting a few hundred \Myr{}.
-The physical origin and some details are different, but one can appreciate that the bimodality arises from the same physical process.\footnote{Compare Section~\ref{ssec:formqui} to the first key result in the Conclusions of \citet{2024arXiv240511025S}.}
-
-\subsection{Observational Connections: High Redshift Quenching}\label{ssec:obshiz}
-If the Milky Way underwent a starburst to quiescent to rejuvenation sequence, as we argue in this paper, then an an analogue at $z\sim2$ would be identified as a post-starburst galaxy (PSB).
-With abundance matching, we expect the Milky Way's total stellar mass to be $\sim10^{10.3}\,\Msun$ at $z\sim2$ \citep{2013ApJ...771L..35V}.
-A number of authors have explored PSBs and quiescent galaxies at slightly higher masses at $z\sim2$, with large advances in the post-JWST era.
-
-First, PSBs are not uncommon.
-\citet{2023ApJ...953..119P} found that in massive galaxies ($M_* > 10^{10.6}\,\Msun$) the fraction of PSBs (inferred ages $< 800\,\Myr$) increases from $\sim2.7\%$ ($99/3655$) at $1.0 < z < 1.44$ to $\sim8\%$ ($89/1118$) at $2.16 < z < 2.5$ \citep[see also][]{2012ApJ...745..179W,2019ApJ...874...17B}.
-Later, \citet{2024arXiv240417945P} found that $\sim10\%$ of galaxies at $\sim10^{10.3}\,\Msun$ are quenched \citep[consistent with][]{2013ApJ...777...18M}, and $\sim30\%$ of their quiescent sample is a PSB at $z\sim2$.
-If these galaxies can be quickly rejuvenated, as the system studied in this work would suggest, then the total fraction of galaxies that go through a starburst-quenching phase may be higher.
-
-Furthermore, \citet{2023arXiv231215012C} found that lower mass quiescent galaxies (towards $10^{10.3}\,\Msun$) tend to be younger and more disky, pointing to a merger driven scenario.
-\citet{2023arXiv231212207A} found that at even lower masses ($<10^{9.5}\,\Msun$) There is also evidence that the AGN quenching mechanism, which we believe to be responsible for the quenching in our system (Appendix~\ref{app:cause_qui}), is operating at these redshifts \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024arXiv240518685M,2024Natur.630...54B}.
-
-Overall, the starburst-driven quenching mechanism proposed in this work is allowed by high-redshift observations.
+The physical origin and some details are different, but one can appreciate that the bimodality arises from a similar process.\footnote{Compare Section~\ref{ssec:formqui} to the first key result in the Conclusions of \citet{2024arXiv240511025S}.}
 
@@
 Figure~\ref{fig:before_after_sfh_by_iron} indicates a very direct observational test of the mechanism proposed in this work: for disk stars at a given \FeH{}, there should be a gap of $\sim300\,\Myr$ in ages at $\sim8\,\Gyr$, though in the Milky Way the gap could be larger.
-With a survey of properly chosen stars, this gap could be directly measured with a modestly sized (few hundred) sample of old stars with age uncertainties of $\sim1\%$.
+With a survey of properly chosen stars, this gap could be directly measured with a modestly sized (few hundred) sample of old stars with age uncertainties of \edit1{a few percent}.
 To our knowledge, the best method at these ages is differential analysis of solar twins, which can provide an age uncertainty of $\sim5\%$ \citep[e.g.][]{2014ApJ...795...23B,2018MNRAS.474.2580S}.
 However, this has only been applied to stars with solar metallicity, where there is not a clear separation between the high- and low-$\alpha$ sequences (though a gap in ages may still be present).
-A sort of differential approach could be applied also at lower metallicities, which would just lack the absolute age calibration that the Sun provides.
+A sort of differential approach could be applied also at lower metallicities, which would simply lack the absolute age calibration that the Sun provides.
 
@@
 Astroseismology appears to be the most promising avenue.
-Currently the largest sample is APOKASC2 \citep{2018ApJS..239...32P}, which has $\sim3400$ stars with ages measured to $<20\%$ precision.\footnote{Errors here taken to be the maximum of the upper and lower age estimates in the public APOKASC2 catalog.} The upcoming PLATO mission is looking to measure $\sim20\textrm{k}$ stars with ages measured to $<10\%$ precision \citep{2024arXiv240605447R}.
+\edit1{Currently the largest sample is APOKASC-3 \citep{2025ApJS..276...69P}, which has $\sim2\textrm{k}$ stars with ages measured to $<12.5\%$ precision.\footnote{Errors here taken to be the maximum of the upper and lower age estimates in the APOKASC-3 catalog.}} The upcoming PLATO mission is looking to measure $\sim20\textrm{k}$ stars with ages measured to $<10\%$ precision \citep{2024arXiv240605447R}.
 Further work is needed to determine how well these surveys could constrain the gap.
 
-In addition to the presence of the gap, our work also predicts that: (1) the timing of the gap is \FeH{} dependent, and that (2) stars which form immediately after the gap are $\alpha$-poor compared to stars which form slightly later (see Figure~\ref{fig:alpha_vs_tform}).
-However, both of these tests rely on the precise age estimates.
+\subsection{Future Work}\label{ssec:future_work}
+\edit1{The largest unanswered question in the current work is the origin of gaps in the metallicity-dependent SFR.
+In Appendix~\ref{app:cause_qui}, we show that the merger is associated with strong feedback from the central AGN.
+Determining the precise mechanism and relationship between the two is delayed to future work.
+Furthermore, other mechanisms of quenching might be able to produce the gaps studied here, and so their exploration is worthwhile.}
 
-\subsection{Future Work}
-A natural next step would be to extend the idealized simulations in this work to a wider range of orbits, galaxy properties, and feedback models.
-However, the unrealism of our setup, which aids interpretation, limits its applicability to the real universe.
-And so something along the lines of the genetic modification technique to explore various mergers as done in this work may be useful \citep{2016MNRAS.455..974R,2017MNRAS.465..547P}.
+\edit1{Another natural next step would be to extend the idealized simulations in this work to a wider range of orbits, galaxy properties, and feedback models.
+However, several aspects of our setup are unrealistic, for example, (1) the simulation is not in an expanding universe, (2) our feedback model is weaker than typical ones calibrated to full cosmological box simulations, (3) the initial conditions have a steeper potential well prior to star formation than in the real universe, and (4) our halos lack small-scale substructure.
+The simplicity of our setup aids interpretation, but also limits it applicability to the real unvierse.
+Something along the lines of the genetic modification technique to explore various mergers as done in this work may be useful \citep{2016MNRAS.455..974R,2017MNRAS.465..547P}.}
 

### 2025-02-13 paper/ms.tex
Update conc and ack

@@
 
-In this work, using idealized merger simulations, we have shown that (1) a starburst, followed by (2) a brief ($\sim300\,\Myr$) quiescent period, followed by (3) rejuvenation can lead to a bimodal abundance structure.
-We found that the starburst-to-quiescent period allowed for prodigious Fe-enrichment without any contemperaneous $\alpha$-enrichment.
-This sequence of events, somewhat resembling the life cycle of a phoenix, would predict that for stars at a given \FeH{}, there would be a $\sim300\,\Myr$ gap in stellar ages at $\sim8\,\Gyr$.
-Furthermore, stars which form directly after this gap would have lower \alphaFe{} than stars which form slightly later ($\sim1\,\Gyr$).
+\edit1{In this work, we have shown that a brief ($\sim300\,\Myr$) period of halted star formation in a narrow \FeH{} bin is capable of producing a bimodal distribution in \alphaFe{} at that \FeH{}.
+This proposal requires that the \alphaFe{} of gas within the galaxy is decreasing with time so that the gap in star formation translates to a gap in \alphaFe{}.
+A global quiescent period can satisfy these constraints, but is not necessary.
+We demonstrate the plausibility of this scenario using a grid of idealized merger simulations with slightly varied orbital parameters -- however, it is also not necessary that a merger triggers the \FeH{}-dependent halt in star formation.}
 
-The bimodality in the \alphaFe{}-\FeH{} plane of stellar abundances points to deeper, unobserved structure.
-That structure is a record of the complicated processes that gave rise to the Galaxy.
-In the absence of highly precise stellar ages, that history must be largely inferred.
-There are many ways in which a galaxy could end up with the coarse-grained structure we can observe in the present day.
-We have argued in this work that a brief, starburst-driven quiescent phase is one of them.
+\edit1{This scenario leads to the natural prediction that for stars occupying a narrow bin in \FeH{} where the bimodality is present ($\FeH\lesssim-0.2$), there should be a gap in ages for $\sim8\,\Gyr$ old stars with a width of $\sim300\,\Myr$.
+Currently, the best age estimates for such stars have errors of $\sim1\,\Gyr$.
+However, future observations targeting \textit{relative} ages of such stars might be able to achieve the necessary precision.
+Our proposed mechanism may operate in many external galaxies, whether or not these \FeH{}-dependent metallicity gaps are merger-induced.}
 
@@
 Semenov, and Turner Woody for helpful discussions.
+We would like to thank Marc Pinsonneault for sharing early access to the APOKASC-3 dataset.
 We would like to thank Filippo Barbani for kindly providing his version of \texttt{MakeNewDisk}.

### 2025-02-13 paper/ms.tex
Small changes to appendix

@@
 \appendix
+\section{Star Formation Histories}\label{app:all_sfh}
+One potential avenue for creating an \FeH{}-dependent star formation gap is through quiescence.
+This is demonstrated by examining the global SFH in Figure~\ref{fig:all_sfh}, with the panels and colors showing each simulation in the grid ordered by their bimodality score $\mathcal{B}$ in the same way as Figures~\ref{fig:all_hist} and \ref{fig:all_scatter}.
+One can see that there is a global quiescent period in simulations~g, s, and x.
+Simulations~s and x have a bimodal pattern, while simulation~g has a unimodal pattern.
+As mentioned in Figure~\ref{fig:all_scatter}, simulation~g has an age gap but there is not enough star formation at $\FeH\sim0$ before the gap to result in a strong bimodality.
+Otherwise, while a global quiescent period is sufficient for generating an age gap, most simulations do not have a global quiescent period.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{sfh.pdf}
+  \caption{Global star formation history (SFH) for each simulation, plotted in the same order as Figures~\ref{fig:all_hist} and \ref{fig:all_scatter}, with increasing bimodality score $\mathcal{B}$ from left to right.
+The colors correspond to the same simulations as in previous figures.
+A global quiescent period, characterized by a significant dip in the SFR, is observed in simulations~g, s, and x.
+Among these, simulations~s and x exhibit strong bimodal \MgFe{} distributions, while simulation~g remains unimodal due to insufficient early star formation at $\FeH\sim0$ before the quiescent phase.
+Most other simulations do not display a clear global quiescent period, indicating that such a phase is not strictly necessary for bimodality to emerge.}
+  \label{fig:all_sfh}
+\end{figure*}
+
+\section{Cause of Suppressed Star Formation}\label{app:cause_qui}
+\edit1{In Figure~\ref{fig:MdotBH_rsep}, we demonstrate how the orbit of the bimodal simulation is closely related to the strength of BH feedback.
+On the $y$-axis, we show in blue the black hole accretion rate as a ratio of the maximum (Eddington) accretion rate at that time.
+In orange we show the orbital separation between the satellite and central galaxies.
+We see that the accretion rate is high early on at $\sim10\%$.
+At the time around coalescence at $\sim2\,\Gyr$, the accretion rate rises up to Eddington, before dropping to a much lower value $<10\%$ later on.}
+
+\edit1{In the TNG model, the strength of AGN feedback is directly tied to the BH's accretion rate \citep{2017MNRAS.465.3291W}.
+Therefore, it is reasonable to suspect that the feedback from the AGN is responsible for removing gas from the galaxy or keeping it above the star forming density threshold.}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=242.26653pt]{MdotBH_rsep.pdf}
+  \caption{\edit1{Evolution of black hole accretion rate and orbital separation over time in the bimodal simulation.
+The blue line shows the black hole accretion rate as a fraction of the Eddington rate, while the orange line shows the orbital separation between the satellite and central galaxies.
+The accretion rate peaks during coalescence at $\sim2\,\Gyr$, suggesting a strong connection between the merger and AGN activity.}}
+  \label{fig:MdotBH_rsep}
+\end{figure}
+
 \section{Abundance Plane of All Simulations}\label{app:allmerge}
@@
 
-\section{Cause of Suppressed Star Formation}\label{app:cause_qui}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{SFR_Mgas_tdep.pdf}
-  \caption{\textbf{The suppression of star formation in the bimodal simulation is associated with both a reduction in gas mass as well as an increase in the depletion time.} The drop in star formation (blue line) at $\sim2.5-3\,\Gyr$ is associated with both a reduction in the total gas mass (red line) as well as an increase in the depletion time (green line).
-This shows that the SFR suppression is a result of both less gas mass and more inefficient star formation.}
-  \label{fig:SFR_Mgas_tdep}
-\end{figure*}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=242.26653pt]{MdotBH_rsep.pdf}
-  \caption{\textbf{The bimodal merger is associated with high accretion rates onto the central SMBH.} Around the time of each pericentric passage, and slightly after, the accretion rate (blue line) becomes very high.
-Here, it is shown as a fraction of the Eddington accretion rate.
-During the merger, the accretion rate reaches as high as Eddington at some times, but is always above $10\%$.
-The orbital separation between the central and satellite is shown in the orange line.}
-  \label{fig:MdotBH_rsep}
-\end{figure}
-
 \end{document}

### 2025-02-14 paper/ms.tex
Lars suggestions

@@
 Using simulations of an idealized setup of a high-$z$ galaxy merger, we show that the merger with the Gaia-Sausage-Enceladus satellite at $z\sim2$ is one possible way to trigger such a gap in the Milky Way.
-Our proposal does not rely on a merger to induce this age gap.
+This mechanism may also operate in non-merger scenarios.
 We predict a $\sim300\,\Myr$ gap in stellar ages at a fixed \FeH{} where the $\alpha$-bimodality is prominent ($\FeH\lesssim-0.2$).}
@@
 These simulations will later be identified as having the highest and second lowest bimodality score $\mathcal{B}$.
-We will then examine the full simulation suite, and show the detailed abundance plane for the full suite5 in Appendix~\ref{app:allmerge}.}
+We will then examine the full simulation suite, and show the detailed abundance plane for the full suite in Appendix~\ref{app:allmerge}.}
 
@@
 
-\subsection{Direct Search for Quiescence}\label{ssec:obsqui}
+\subsection{Direct Observational Test}\label{ssec:obsqui}
 Figure~\ref{fig:before_after_sfh_by_iron} indicates a very direct observational test of the mechanism proposed in this work: for disk stars at a given \FeH{}, there should be a gap of $\sim300\,\Myr$ in ages at $\sim8\,\Gyr$, though in the Milky Way the gap could be larger.
@@
 A global quiescent period can satisfy these constraints, but is not necessary.
-We demonstrate the plausibility of this scenario using a grid of idealized merger simulations with slightly varied orbital parameters -- however, it is also not necessary that a merger triggers the \FeH{}-dependent halt in star formation.}
+We demonstrate the plausibility of this scenario using a grid of idealized merger simulations with slightly varied orbital parameters.
+This scenario could potentially be triggered in non-merger scenarios, which we plan to explore in future work.}
 
@@
 \begin{acknowledgements}
-We would like to thank Megan Bedell, Christopher Carr, Vedant Chandra, Charlie Conroy, Drummond B.
+\edit1{We would like to thank the anonymous referee for their helpful comments which have served to clarify and strengthen our main arguments.} We would like to thank Megan Bedell, Christopher Carr, Vedant Chandra, Charlie Conroy, Drummond B.
 Fielding, Lars Hernquist, Federico Marinacci, Rohan P.

### 2025-02-14 paper/ms.tex
Spellcheck

@@
 Many elements heavier than hydrogen are produced through nuclear fusion in compact objects such as supernovae, dying low mass stars, and neutron star-neutron star mergers \citep[e.g.][]{2023A&ARv..31....1A}.
-By necessity, stars inherit the constituitive properties of the gas from which they formed.
+By necessity, stars inherit the constitutive properties of the gas from which they formed.
 Moreover, the surface abundance of most elements for most stars do not change over most of their lifetime.
@@
 Because the processes which give rise to this distribution are complex, there is almost certainly some structure in the stellar abundance distribution for every galaxy.
-However, it has only been definitively measured in the Milky Way, \edit1{with conflicting claims of detection \citep{2023ApJ...956L..14K} and nondetection \citep{2024IAUS..377..115N} in M31.}
+However, it has only been definitively measured in the Milky Way, \edit1{with conflicting claims of detection \citep{2023ApJ...956L..14K} and non-detection \citep{2024IAUS..377..115N} in M31.}
 
@@
 Using the trick in e.g.
-\citet{2022MNRAS.515.1524Z}, we take the bulge mass to be twice the counterrotating stellar mass.
+\citet{2022MNRAS.515.1524Z}, we take the bulge mass to be twice the counter-rotating stellar mass.
 At $3\,\Gyr$ in the isolated Milky Way-like galaxy, the bulge mass is $\sim7\times10^{8}\,\Msun$, or $\sim13\%$ of the total mass.
@@
 We show the bimodal and unimodal simulations' orbits in Figure~\ref{fig:orbit}.
-\edit1{We use a shrinking spheres center of mass method to identify the centers of the central and satellite galaxy \citep[e.g.,][]{2003MNRAS.338...14P}.\footnote{The position of the minimum potential particle in each substructured identified by \texttt{SUBFIND} is used as the starting guess, and we use an initial/final radius and step factor of $10\,\kpc$, $5\,\kpc$, and $0.9$, respectively.}} The upper and middle panels show the orbits in the $x$-$y$ and $x$-$z$ planes, respectively.
+\edit1{We use a shrinking spheres center of mass method to identify the centers of the central and satellite galaxy \citep[e.g.,][]{2003MNRAS.338...14P}.\footnote{The position of the minimum potential particle in each substructure identified by \texttt{SUBFIND} is used as the starting guess, and we use an initial/final radius and step factor of $10\,\kpc$, $5\,\kpc$, and $0.9$, respectively.}} The upper and middle panels show the orbits in the $x$-$y$ and $x$-$z$ planes, respectively.
 The lower panel shows the separation distance as a function of time.
@@
 \edit1{Given the modest size of our suite, some method for scoring the degree of bimodality for a given 1D distribution is desirable.
-Tests of whether a distribution is bimodal or unimodal exist -- e.g., the Hartigan dip test \citep{10.1214/aos/1176346577}, but they lack the ability to rank order based on ``bimodalitiness.'' In order to do this, we fit a given distribution of \alphaFe{} as a two-component gaussian mixture model.
+Tests of whether a distribution is bimodal or unimodal exist -- e.g., the Hartigan dip test \citep{10.1214/aos/1176346577}, but they lack the ability to rank order based on ``bimodalitiness.'' In order to do this, we fit a given distribution of \alphaFe{} as a two-component Gaussian mixture model.
 The bimodality score $\mathcal{B}$ is then computed as
@@
 The side-length of each panel is $30\,\kpc$, and the image is a projection through a box with the same side-length.
-The colormap for the gas ranges from $1$ to $10^2\,\Msun/\pc^2$, while for the stars ranges from $1$ to $10^4\,\Msun/\pc^2$.
+The color map for the gas ranges from $1$ to $10^2\,\Msun/\pc^2$, while for the stars ranges from $1$ to $10^4\,\Msun/\pc^2$.
 \edit1{Description of movie: The disk collapses quickly, forming a disk within $500\,\Myr$.
@@
 In the right panel we show stars in the Milky Way from APOKASC3 in $0.2\,\dex$ bins at $\FeH=-0.5$ (blue) and $0$ (orange).
-The low-metallicity bin is where the Milky Way bimodality is strongest while there is no bimodality at the solar-metallicty bin (see Figure~\ref{fig:fig1}).
+The low-metallicity bin is where the Milky Way bimodality is strongest while there is no bimodality at the solar-metallicity bin (see Figure~\ref{fig:fig1}).
 Offsets have been added to \MgFe{} values for clarity: $-0.3$ in the unimodal points in the left and middle panels, and $+0.1$ and $-0.1$ in the low/solar-metallicity bins, respectively, in the right panel.}}
@@
 However, the large uncertainties at the relevant ages ($\sim1\,\Gyr$ at ages of $\sim8\,\Gyr$) and the small sample size (125 and 1175 at $\FeH=-0.5$ and $0$, respectively) prevents a definitive statement from being made.
-Larger sample sizes and more precise age estimates in the future would clarify the connection between simulation and observation, although achieving age uncertainities of $<10\%$ for such old stars is very challenging \citep[e.g.][]{2010ARA&A..48..581S}.}
+Larger sample sizes and more precise age estimates in the future would clarify the connection between simulation and observation, although achieving age uncertainties of $<10\%$ for such old stars is very challenging \citep[e.g.][]{2010ARA&A..48..581S}.}
 
@@
 
-\edit1{Simulations from r onwards, which have $\mathcal{B}>2.25$, are considered bimodal.
+\edit1{Simulations from r onward, which have $\mathcal{B}>2.25$, are considered bimodal.
 This demarcation was chosen by eye using Figure~\ref{fig:all_hist}.
@@
 Before this gap, star formation occurs above the trough while after it occurs below the trough.
-However, there are two exceptions: simulation~t does not have a full gap (though the density does decrease), and simulation~w is irregular, with star formation simultaneously occuring above and below the trough.}
+However, there are two exceptions: simulation~t does not have a full gap (though the density does decrease), and simulation~w is irregular, with star formation simultaneously occurring above and below the trough.}
 
 \edit1{In the unimodal simulations (a through q), there does appear to be gaps (d, f, g, h, and o).
-However, in these cases, there is not a large amount of star formation occuring before the gap, and so the high-$\alpha$ sequence is underemphasized and does not lead to a significant bimodality.}
+However, in these cases, there is not a large amount of star formation occurring before the gap, and so the high-$\alpha$ sequence is underemphasized and does not lead to a significant bimodality.}
 
@@
 We order these simulations alphabetically using the bimodality score ($\mathcal{B}$, see Section~\ref{ssec:bim_score}).
-Simulations~r through aa are considered bimodal based on a visual inspection, and the location of their trough \MgFe{} (minimium of the distribution) is indicated with a vertical line.}
+Simulations~r through aa are considered bimodal based on a visual inspection, and the location of their trough \MgFe{} (minimum of the distribution) is indicated with a vertical line.}
 
@@
 \subsection{Connection to High Redshift Quenching}\label{ssec:obshiz}
-\edit1{One plausible avenue to producing a \FeH{}-dependent halt in star formation is through a global quiescent period.
+\edit1{One plausible avenue to producing a \FeH{}-dependent halt in star formation is through a global quiescent period (see Appendix~\ref{app:all_sfh}).
 Galaxies which undergo a starburst to quiescence to rejuvenation sequence (post-starburst galaxies, or PSBs) are observed at high-$z$ ($z>1$), and may be plausible Milky Way-progenitors.} With abundance matching, we expect the Milky Way's total stellar mass to be $\sim10^{10.3}\,\Msun$ at $z\sim2$ \citep{2013ApJ...771L..35V}.
@@
 
-\citet{2018MNRAS.477.5072M} found that Milky Way-like bimodalities are rare in EAGLE, occuring in $\sim5\%$ of galaxies.
+\citet{2018MNRAS.477.5072M} found that Milky Way-like bimodalities are rare in EAGLE, occurring in $\sim5\%$ of galaxies.
 \citet{2021MNRAS.501..236D,2022MNRAS.515.1430D} showed that merger-induced quenching in zooms can occur in the EAGLE model \citep[see also][]{2017MNRAS.465..547P}.
@@
 However, several aspects of our setup are unrealistic, for example, (1) the simulation is not in an expanding universe, (2) our feedback model is weaker than typical ones calibrated to full cosmological box simulations, (3) the initial conditions have a steeper potential well prior to star formation than in the real universe, and (4) our halos lack small-scale substructure.
-The simplicity of our setup aids interpretation, but also limits it applicability to the real unvierse.
+The simplicity of our setup aids interpretation, but also limits it applicability to the real universe.
 Something along the lines of the genetic modification technique to explore various mergers as done in this work may be useful \citep{2016MNRAS.455..974R,2017MNRAS.465..547P}.}

### 2025-02-14 paper/ms.tex
Add orcid
Add LLM/software citations

@@
 
-\author{Angus Beane}
+\author[0000-0002-8658-1453]{Angus Beane}
 \affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
@@
 
+We acknowledge the use of OpenAI’s ChatGPT and Anthropic's Claude for assistance in editing this manuscript for clarity and conciseness and in generating small analysis scripts and code snippets.
+
 \end{acknowledgements}
@@
 \bibliographystyle{aasjournal}
+
+\software{ {\sc astropy} \citep{astropy:2013,astropy:2018,astropy:2022}, {\sc h5py} \url{http://www.h5py.org/}, {\sc inspector\_gadget} \url{https://bitbucket.org/abauer/inspector_gadget/}, {\sc joblib} \url{https://joblib.readthedocs.io/en/latest/}, {\sc matplotlib} \citep{Hunter:2007}, {\sc numba} \citep{lam2015numba}, {\sc numpy} \citep{harris2020array}, {\sc scikit-learn} \citep{scikit-learn}, {\sc scipy} \citep{2020SciPy-NMeth}, {\sc tqdm} \url{https://tqdm.github.io/}, {\sc vortrace} \url{https://github.com/gusbeane/vortrace}}
 

### 2025-02-24 paper/ms.tex
Remove edits for arxiv posting

@@
 In the two-dimensional plane of \alphaFe{}-\FeH{}, it is now clear that two separate populations exist -- the low-$\alpha$ and high-$\alpha$ sequences.
-\edit1{We propose that a brief ($\sim300\,\Myr$) halt in star formation within a narrow metallicity bin can lead to a bimodal \alphaFe{} distribution at that metallicity, assuming a rapidly declining gas phase \alphaFe{}.
+We propose that a brief ($\sim300\,\Myr$) halt in star formation within a narrow metallicity bin can lead to a bimodal \alphaFe{} distribution at that metallicity, assuming a rapidly declining gas phase \alphaFe{}.
 Using simulations of an idealized setup of a high-$z$ galaxy merger, we show that the merger with the Gaia-Sausage-Enceladus satellite at $z\sim2$ is one possible way to trigger such a gap in the Milky Way.
 This mechanism may also operate in non-merger scenarios.
-We predict a $\sim300\,\Myr$ gap in stellar ages at a fixed \FeH{} where the $\alpha$-bimodality is prominent ($\FeH\lesssim-0.2$).}
+We predict a $\sim300\,\Myr$ gap in stellar ages at a fixed \FeH{} where the $\alpha$-bimodality is prominent ($\FeH\lesssim-0.2$).
 \end{abstract}
@@
 Moreover, the surface abundance of most elements for most stars do not change over most of their lifetime.
-\edit1{By analyzing the surface abundances of stars, we can reconstruct the historical gas-phase composition of a galaxy.}
+By analyzing the surface abundances of stars, we can reconstruct the historical gas-phase composition of a galaxy.
 
@@
 Because the processes which give rise to this distribution are complex, there is almost certainly some structure in the stellar abundance distribution for every galaxy.
-However, it has only been definitively measured in the Milky Way, \edit1{with conflicting claims of detection \citep{2023ApJ...956L..14K} and non-detection \citep{2024IAUS..377..115N} in M31.}
+However, it has only been definitively measured in the Milky Way, with conflicting claims of detection \citep{2023ApJ...956L..14K} and non-detection \citep{2024IAUS..377..115N} in M31.
 
@@
 On the other hand, $\alpha$-elements are mainly produced in Type II supernovae.
-The ratio of $\alpha$-elements to Fe (\alphaFe{}) is then a measure of the relative contributions of Type Ia and II SNe to the enrichment of a parcel of gas, \edit1{which typically declines with time \citep{1979ApJ...229.1046T,1986A&A...154..279M}}.
+The ratio of $\alpha$-elements to Fe (\alphaFe{}) is then a measure of the relative contributions of Type Ia and II SNe to the enrichment of a parcel of gas, which typically declines with time \citep{1979ApJ...229.1046T,1986A&A...154..279M}.
 It has therefore become common to compress the high-dimensional abundance space to the two dimensional \alphaFe{}-\FeH{} plane.
@@
 % Observed chemical bimodality in the Milky Way
-\edit1{These abundances can be used to decompose the Milky Way's disk, which has a long history dating back to the work of \citet{1983MNRAS.202.1025G}, who noted that the vertical distribution of stellar altitudes is well-fit by a double exponential.
+These abundances can be used to decompose the Milky Way's disk, which has a long history dating back to the work of \citet{1983MNRAS.202.1025G}, who noted that the vertical distribution of stellar altitudes is well-fit by a double exponential.
 This led naturally to a ``thin'' and ``thick'' disk, whose membership can be reasonably determined through kinematics \citep[e.g.][]{2003A&A...410..527B}.
-It was quickly realized that the thick disk is more $\alpha$-enhanced than the thin disk \citep{1996ASPC...92..307G,1998A&A...338..161F}.}
+It was quickly realized that the thick disk is more $\alpha$-enhanced than the thin disk \citep{1996ASPC...92..307G,1998A&A...338..161F}.
 
-\edit1{Later studies showed that the disk could be decomposed into high- and low-$\alpha$ sequences without kinematic selection \citep{2011A&A...535L..11A,2012A&A...545A..32A}.\footnote{\citet{2003A&A...410..527B} briefly noted that the thin and thick disk seemed to not overlap in chemistry.} The high-$\alpha$ sequence is older, more centrally compact, and more vertically extended than the low-$\alpha$ sequence \citep{2013A&A...560A.109H,2024IAUS..377..115N}.
-Although the thick disk is more $\alpha$-enhanced than the thin disk, it is not immediately obvious that the chemical and kinematic separations arise from the same physical process \citep[or that they even exist, see][]{2012ApJ...751..131B}.}
+Later studies showed that the disk could be decomposed into high- and low-$\alpha$ sequences without kinematic selection \citep{2011A&A...535L..11A,2012A&A...545A..32A}.\footnote{\citet{2003A&A...410..527B} briefly noted that the thin and thick disk seemed to not overlap in chemistry.} The high-$\alpha$ sequence is older, more centrally compact, and more vertically extended than the low-$\alpha$ sequence \citep{2013A&A...560A.109H,2024IAUS..377..115N}.
+Although the thick disk is more $\alpha$-enhanced than the thin disk, it is not immediately obvious that the chemical and kinematic separations arise from the same physical process \citep[or that they even exist, see][]{2012ApJ...751..131B}.
 
@@
 Naturally, many different processes that could lead to structure in the abundance plane have been discussed in the literature.
-An early explanation of the bimodality is \edit1{based on} the two-phase gas infall model \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}.
+An early explanation of the bimodality is based on the two-phase gas infall model \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}.
 In this model, the thick disk first forms rapidly from an initial infall of gas.
@@
 In some variants, star formation halts completely before a second supply of pristine gas falls into the Galaxy \citep[][and references therein]{2024arXiv240511025S}.
-This dilutes the gas supply from which the thin disk forms more gradually, \edit1{creating a loop feature in the abundance plane}.
-The thin disk is then more $\alpha$-poor because its associated SFR is lower, \edit1{and in certain scenarios two chemically distinct disks are formed.}
+This dilutes the gas supply from which the thin disk forms more gradually, creating a loop feature in the abundance plane.
+The thin disk is then more $\alpha$-poor because its associated SFR is lower, and in certain scenarios two chemically distinct disks are formed.
 
@@
 Next, we turn to models which argue the bimodality results from some external influence.
-Early arguments were made that both the $\alpha$-enhancement of the disk and the thickening of the disk can result from gas-rich mergers \citep{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R}.\footnote{See also \citet{2009MNRAS.400.1347C} for an argument invoking semi-analytic models.} These mergers lead to an enhanced SFR which leads to the $\alpha$-enhancement of the thick disk, \edit1{with \citet{2015A&A...578A..87S} being the first to attempt to explain abundance substructure with a merger.}
+Early arguments were made that both the $\alpha$-enhancement of the disk and the thickening of the disk can result from gas-rich mergers \citep{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R}.\footnote{See also \citet{2009MNRAS.400.1347C} for an argument invoking semi-analytic models.} These mergers lead to an enhanced SFR which leads to the $\alpha$-enhancement of the thick disk, with \citet{2015A&A...578A..87S} being the first to attempt to explain abundance substructure with a merger.
 
@@
 This merger is thought to have occurred $\sim8-10\,\Gyr$ ago \citep[see also][]{2020ApJ...897L..18B}.
-\edit1{A merger origin of the abundance bimodality is also attractive because it can simultaneously explain the origin of the kinematic thin and thick disk \citep{1985AJ.....90.2015G,1986ApJ...309..472Q,1993ApJ...403...74Q}.}
+A merger origin of the abundance bimodality is also attractive because it can simultaneously explain the origin of the kinematic thin and thick disk \citep{1985AJ.....90.2015G,1986ApJ...309..472Q,1993ApJ...403...74Q}.
 
@@
 
-\edit1{In this work, we propose that a brief $\sim300\,\Myr$ interruption in the formation of stars at a given metallicity can lead to the formation of an $\alpha$-abundance bimodality at that metallicity.
-It is not common to study the star formation rate at a specific metallicity, but dividing the stellar population into narrow abundance populations can be a powerful tool \citep[e.g.][]{2012ApJ...753..148B,2012ApJ...751..131B}.}
+In this work, we propose that a brief $\sim300\,\Myr$ interruption in the formation of stars at a given metallicity can lead to the formation of an $\alpha$-abundance bimodality at that metallicity.
+It is not common to study the star formation rate at a specific metallicity, but dividing the stellar population into narrow abundance populations can be a powerful tool \citep[e.g.][]{2012ApJ...753..148B,2012ApJ...751..131B}.
 
-\edit1{Our proposal assumes that the gas phase's \alphaFe{} is declining sufficiently rapidly at the time of the interruption.
+Our proposal assumes that the gas phase's \alphaFe{} is declining sufficiently rapidly at the time of the interruption.
 Using a set of idealized simulations which mimic the $z\sim2$ merger between the Milky Way and GSE, we show that such a merger can drive the formation of this gap and thus the bimodality.
 While we demonstrate this mechanism in the context of a merger scenario, it is important to note that our proposal does not inherently require a merger to induce this metallicity-dependent star formation gap.
-This scenario predicts a $\sim300\,\Myr$ gap in stellar ages at metallicities where the bimodality exists ($\FeH\lesssim-0.2$).}
+This scenario predicts a $\sim300\,\Myr$ gap in stellar ages at metallicities where the bimodality exists ($\FeH\lesssim-0.2$).
 
 In Section~\ref{sec:methods}, we describe our setup.
-\edit1{In Section~\ref{sec:results}, we present in detail the main results of two example simulations before expanding our results to the full suite.} In Section~\ref{sec:discussion}, we discuss and interpret our results, as well as connections to previous and future work, before concluding in Section~\ref{sec:conclusion}.
+In Section~\ref{sec:results}, we present in detail the main results of two example simulations before expanding our results to the full suite.
+In Section~\ref{sec:discussion}, we discuss and interpret our results, as well as connections to previous and future work, before concluding in Section~\ref{sec:conclusion}.
 Throughout this work we refer to the standard native time unit $\kpc/\left(\kms\right)$ as \Gyr{} for convenience.
@@
 \end{equation*}
-The total mass within the virial radius is kept fixed, and the mass of the dark matter halo and central density of the gaseous halo are chosen to satisfy a given baryon fraction $f_b$ \edit1{within the virial radius}.
+The total mass within the virial radius is kept fixed, and the mass of the dark matter halo and central density of the gaseous halo are chosen to satisfy a given baryon fraction $f_b$ within the virial radius.
 The dark matter halo is initialized to be in gravitational equilibrium with the total potential.
@@
 The satellite then coalesces quickly after the second pericentric passage, after $\sim2\,\Gyr$ of evolution.
-\edit1{A blue dashed line is shown for the bimodal simulation at $2.8\,\Gyr$, the time of a star formation gap at $\FeH=0$ (see Figure~\ref{fig:before_after}).
-An orange dashed line is shown for the unimodal simulation (which has no gap) at the same time after its second pericentric passage ($2.3\,\Gyr$).}}
+A blue dashed line is shown for the bimodal simulation at $2.8\,\Gyr$, the time of a star formation gap at $\FeH=0$ (see Figure~\ref{fig:before_after}).
+An orange dashed line is shown for the unimodal simulation (which has no gap) at the same time after its second pericentric passage ($2.3\,\Gyr$).}
     \label{fig:orbit}
@@
 Some of the simulations in this orbital grid resulted in bimodal abundance distributions, while some had little to no structure in the abundance distribution plane.
-\edit1{We will first study two representative simulations in detail chosen based on their structure in the abundance plane as shown in Figure~\ref{fig:fig1}, one which we refer to as bimodal and one as unimodal.
+We will first study two representative simulations in detail chosen based on their structure in the abundance plane as shown in Figure~\ref{fig:fig1}, one which we refer to as bimodal and one as unimodal.
 For the bimodal simulation, we chose the simulation with $R_0=129\,\kpc$, $V_0=142\,\kms$, and $\eta=0.4$.
@@
 These simulations will later be identified as having the highest and second lowest bimodality score $\mathcal{B}$.
-We will then examine the full simulation suite, and show the detailed abundance plane for the full suite in Appendix~\ref{app:allmerge}.}
+We will then examine the full simulation suite, and show the detailed abundance plane for the full suite in Appendix~\ref{app:allmerge}.
 
 We show the bimodal and unimodal simulations' orbits in Figure~\ref{fig:orbit}.
-\edit1{We use a shrinking spheres center of mass method to identify the centers of the central and satellite galaxy \citep[e.g.,][]{2003MNRAS.338...14P}.\footnote{The position of the minimum potential particle in each substructure identified by \texttt{SUBFIND} is used as the starting guess, and we use an initial/final radius and step factor of $10\,\kpc$, $5\,\kpc$, and $0.9$, respectively.}} The upper and middle panels show the orbits in the $x$-$y$ and $x$-$z$ planes, respectively.
+We use a shrinking spheres center of mass method to identify the centers of the central and satellite galaxy \citep[e.g.,][]{2003MNRAS.338...14P}.\footnote{The position of the minimum potential particle in each substructure identified by \texttt{SUBFIND} is used as the starting guess, and we use an initial/final radius and step factor of $10\,\kpc$, $5\,\kpc$, and $0.9$, respectively.} The upper and middle panels show the orbits in the $x$-$y$ and $x$-$z$ planes, respectively.
 The lower panel shows the separation distance as a function of time.
@@
 \subsection{Feedback and Enrichment Model}\label{ssec:gfm}
-Our feedback model is \edit1{a variant of the Illustris TNG model} \citep{2013MNRAS.436.3031V,2017MNRAS.465.3291W,2018MNRAS.473.4077P}.
+Our feedback model is a variant of the Illustris TNG model \citep{2013MNRAS.436.3031V,2017MNRAS.465.3291W,2018MNRAS.473.4077P}.
 In this model, gravity and magnetohydrodynamics are solved using a \citet{1986Natur.324..446B} tree coupled to a second order finite volume fluid solver in AREPO \citep{2010MNRAS.401..791S,2016MNRAS.455.1134P}.
@@
 In this model, star particles synthesize elements through three different channels for which we cite the relevant yield tables: SNe Ia \citep{1997NuPhA.621..467N}, SNe II \citep{1998A&A...334..505P,2006ApJ...653.1145K}, and AGB stars \citep{2010MNRAS.403.1413K,2014MNRAS.437..195D,2014ApJ...797...44F}.
-Each star particle, \edit1{which is modeled as a simple stellar population}, continuously injects metals into its surroundings in the following sequence\footnote{The kinetic/thermal feedback component is handled through the wind generation, which is completely separate in this model.}:
+Each star particle, which is modeled as a simple stellar population, continuously injects metals into its surroundings in the following sequence\footnote{The kinetic/thermal feedback component is handled through the wind generation, which is completely separate in this model.}:
 \begin{enumerate}
@@
 
-We \edit1{applied quality cuts and restricted our sample to giants}, requiring:
+We applied quality cuts and restricted our sample to giants, requiring:
 \begin{itemize}[noitemsep]
@@
 
-\edit1{We next make a solar neighborhood selection of stars based on their angular momenta.} We assume the solar radius and azimuthal velocity are $R_0=8\,\kpc$ and $V_0=220\,\kms$ \citep{2016ARA&A..54..529B}, and select stars which have $L_z$ within $10\%$ of the solar angular momentum.
+We next make a solar neighborhood selection of stars based on their angular momenta.
+We assume the solar radius and azimuthal velocity are $R_0=8\,\kpc$ and $V_0=220\,\kms$ \citep{2016ARA&A..54..529B}, and select stars which have $L_z$ within $10\%$ of the solar angular momentum.
 We further require that $\left|z\right| < 3\,\kpc$.
@@
 
-\edit1{For stellar ages, we used the APOKASC-3 catalog \citep{2025ApJS..276...69P}.
+For stellar ages, we used the APOKASC-3 catalog \citep{2025ApJS..276...69P}.
 This catalog uses a combination of APOGEE spectroscopic parameters and \textit{Kepler} time series photometry to compute astroseismic ages.
-Using only stars with $25\%$ age uncertainties (taken as the maximum of the upper and lower uncertainty), we cross-match this catalog to our larger sample from ASPCAP which results in a sample of 2525 stars.}
+Using only stars with $25\%$ age uncertainties (taken as the maximum of the upper and lower uncertainty), we cross-match this catalog to our larger sample from ASPCAP which results in a sample of 2525 stars.
 
@@
 \subsection{Bimodality Score}\label{ssec:bim_score}
-\edit1{Given the modest size of our suite, some method for scoring the degree of bimodality for a given 1D distribution is desirable.
+Given the modest size of our suite, some method for scoring the degree of bimodality for a given 1D distribution is desirable.
 Tests of whether a distribution is bimodal or unimodal exist -- e.g., the Hartigan dip test \citep{10.1214/aos/1176346577}, but they lack the ability to rank order based on ``bimodalitiness.'' In order to do this, we fit a given distribution of \alphaFe{} as a two-component Gaussian mixture model.
@@
 \end{equation}
-We take $t$ and $k$ to be $0.1$ and $20$, respectively.}
+We take $t$ and $k$ to be $0.1$ and $20$, respectively.
 
-\edit1{This metric effectively measures the distance between two modes normalized by their variances, with a penalty when one mode is not highly weighted.
+This metric effectively measures the distance between two modes normalized by their variances, with a penalty when one mode is not highly weighted.
 These choices were made in order for the score to match by eye which distributions appear to have one as opposed to two peaks, and was found to empirically be more reliable than other statistics like peak-to-trough ratios or mode overlap.
-As demonstrated in Section~\ref{ssec:full_sim_suite}, a score of $\mathcal{B}>2.25$ appears to select the bimodal populations.}
+As demonstrated in Section~\ref{ssec:full_sim_suite}, a score of $\mathcal{B}>2.25$ appears to select the bimodal populations.
 
@@
 The color map for the gas ranges from $1$ to $10^2\,\Msun/\pc^2$, while for the stars ranges from $1$ to $10^4\,\Msun/\pc^2$.
-\edit1{Description of movie: The disk collapses quickly, forming a disk within $500\,\Myr$.
+Description of movie: The disk collapses quickly, forming a disk within $500\,\Myr$.
 The satellite galaxy quickly passes in the background at $\sim700\,\Myr$.
 At $\sim2\,\Gyr$, the satellite directly merges with the central galaxy, fully coalescing by $\sim3\,\Gyr$.
-Over the next $5\,\Gyr$, the disk steadily grows, expanding in size.} (A full movie is \edit1{linked in submission}.)}
+Over the next $5\,\Gyr$, the disk steadily grows, expanding in size.
+(A full movie is available in published version.)}
   \label{fig:projections}
@@
 The left column shows the observed distribution in the Milky Way from ASPCAP DR17 \citep[][J.A.~Holtzman et al., in preparation]{2016AJ....151..144G}, while the right two columns show two idealized merger simulations.
-The idealized merger simulations are nearly identical, except that in the bimodal simulation the satellite has a starting \edit1{velocity of $142\,\kms$}, while in the unimodal simulation it has a starting \edit1{velocity of $116\,\kms$}.
+The idealized merger simulations are nearly identical, except that in the bimodal simulation the satellite has a starting velocity of $142\,\kms$, while in the unimodal simulation it has a starting velocity of $116\,\kms$.
 The labels ``unimodal'' and ``bimodal'' are of the \textit{outcome} of the simulation, and do not reflect a particular choice in the setup.
@@
 In Figure~\ref{fig:fig1}, we show the abundance distribution of the Milky Way as well as two of our idealized merger simulations in the upper panels.
-A number of our idealized simulations exhibit either a bimodal or unimodal abundance distribution, and so we have selected two representative examples \edit1{as discussed in Section~\ref{ssec:orbit_setup}.} The bimodal and unimodal labels are of the outcome of the simulation, and do not reflect any particular choice made in their setup.
+A number of our idealized simulations exhibit either a bimodal or unimodal abundance distribution, and so we have selected two representative examples as discussed in Section~\ref{ssec:orbit_setup}.
+The bimodal and unimodal labels are of the outcome of the simulation, and do not reflect any particular choice made in their setup.
 
@@
 Next, we examine the build up of the abundance plane.
-\edit1{In the left panel of Figure~\ref{fig:before_after}, we show the metallicity-dependent star formation rate of the bimodal simulation using star particles in the solar neighborhood at the end of the simulation within a $0.1\,\dex$ bin centered at $\FeH=0$.
-There is a clear dip in the SFR at $\sim2.8\,\Gyr$, which we indicate with a vertical line.}
+In the left panel of Figure~\ref{fig:before_after}, we show the metallicity-dependent star formation rate of the bimodal simulation using star particles in the solar neighborhood at the end of the simulation within a $0.1\,\dex$ bin centered at $\FeH=0$.
+There is a clear dip in the SFR at $\sim2.8\,\Gyr$, which we indicate with a vertical line.
 
-\edit1{In the center left panel, we show the abundance plane distribution from the bimodal simulation for all stars in the solar neighborhood, replicating Figure~\ref{fig:fig1}.
+In the center left panel, we show the abundance plane distribution from the bimodal simulation for all stars in the solar neighborhood, replicating Figure~\ref{fig:fig1}.
 A dashed line at $-0.1\times\FeH+0.3$, chosen by eye, is plotted to demarcate the high- and low-$\alpha$ sequences.
 In the center right and right panels, we show the distribution of star particles which form before and after the dip in the metallicity-dependent SFR at $t=2.8\,\Gyr$, respectively.
-The vast majority of the high-$\alpha$ sequence forms before the dip, while most of the low-$\alpha$ sequence forms afterward.}
+The vast majority of the high-$\alpha$ sequence forms before the dip, while most of the low-$\alpha$ sequence forms afterward.
 
-\edit1{This sequence of build up is markedly different in the unimodal simulation, which we show in Figure~\ref{fig:before_after_uni}.
+This sequence of build up is markedly different in the unimodal simulation, which we show in Figure~\ref{fig:before_after_uni}.
 Here, there is no clear dip in the metallicity dependent SFR in the left panel.
@@
 This is where the gap appears in the bimodal simulation (see Figure~\ref{fig:orbit}).
-We see that stars which form before and after this point in the simulation overlap considerably in the abundance plane.}
+We see that stars which form before and after this point in the simulation overlap considerably in the abundance plane.
 
-\edit1{The timing and duration of the metallicity-dependent SFR dip is not the same for all \FeH{}.
+The timing and duration of the metallicity-dependent SFR dip is not the same for all \FeH{}.
 In the upper panel of Figure~\ref{fig:before_after_sfh_by_iron}, we show the SFR at metallicities of $-0.5$, $-0.25$, $0$, and $0.25$ in blue, orange, red, and green, respectively.
@@
 In the blue $\FeH=-0.25$ SFR, which does not display a prominent bimodality, there is no dip separating two periods of sustained SF.
-In the green $\FeH=0.25$ SFR, a small amount of SF occurs before an extended $\sim1\,\Gyr$ dip, leading to a bimodality with a weak although well-separated high-$\alpha$ mode.}
+In the green $\FeH=0.25$ SFR, a small amount of SF occurs before an extended $\sim1\,\Gyr$ dip, leading to a bimodality with a weak although well-separated high-$\alpha$ mode.
 
-\edit1{In the lower panel of Figure~\ref{fig:before_after_sfh_by_iron}, we show corresponding curves for the unimodal simulation.
+In the lower panel of Figure~\ref{fig:before_after_sfh_by_iron}, we show corresponding curves for the unimodal simulation.
 A vertical line is shown at $2.3\,\Gyr$, as described earlier.
-Here, we see that at no \FeH{} is there a prominent dip.}
+Here, we see that at no \FeH{} is there a prominent dip.
 
@@
   \includegraphics[width=\textwidth]{before_after.pdf}
-  \caption{\edit1{The buildup of the abundance plane in the bimodal simulation.
+  \caption{The buildup of the abundance plane in the bimodal simulation.
 The left panel shows the metallicity-dependent star formation rate (SFR) for star particles in the solar neighborhood at the end of the simulation, selected within a $0.1\,\dex$ bin centered at $\FeH=0$.
@@
 The center-right and right panels show the abundance plane distributions for stars formed before and after the SFR dip, respectively.
-The majority of the high-$\alpha$ sequence forms before the dip, while most of the low-$\alpha$ sequence forms afterward.}}
+The majority of the high-$\alpha$ sequence forms before the dip, while most of the low-$\alpha$ sequence forms afterward.}
   \label{fig:before_after}
@@
   \includegraphics[width=\textwidth]{before_after_uni.pdf}
-  \caption{\edit1{The buildup of the abundance plane in the unimodal simulation, similar to Figure~\ref{fig:before_after}.
+  \caption{The buildup of the abundance plane in the unimodal simulation, similar to Figure~\ref{fig:before_after}.
 The left panel shows the metallicity-dependent star formation rate (SFR) for stars in the solar neighborhood, with no clear dip.
@@
 The center-right and right panels show the abundance plane for stars formed before and after $t=2.3\,\Gyr$, respectively.
-Unlike the bimodal case, stars formed before and after this time overlap considerably in the abundance plane, indicating the absence of a distinct separation between high- and low-$\alpha$ sequences.}}
+Unlike the bimodal case, stars formed before and after this time overlap considerably in the abundance plane, indicating the absence of a distinct separation between high- and low-$\alpha$ sequences.}
   \label{fig:before_after_uni}
@@
   \includegraphics[width=\columnwidth]{before_after_sfh_by_iron.pdf}
-  \caption{\edit1{Metallicity-dependent star formation histories (SFH) for the bimodal (top) and unimodal (bottom) simulations.
+  \caption{Metallicity-dependent star formation histories (SFH) for the bimodal (top) and unimodal (bottom) simulations.
 The SFH at different metallicities ($\FeH=-0.5, -0.25, 0.0, 0.25$) is shown in blue, orange, red, and green, respectively.
@@
 The bottom panel shows the corresponding SFHs for the unimodal simulation, with a vertical line at $t=2.3\,\Gyr$.
-There are no strong dips at any metallicity, consistent with the absence of a well-defined bimodality.}}
+There are no strong dips at any metallicity, consistent with the absence of a well-defined bimodality.}
   \label{fig:before_after_sfh_by_iron}
@@
   \includegraphics[width=\textwidth]{alpha_vs_tform_obserr.pdf}
-  \caption{\edit1{In the bimodal simulation, a gap appears when plotting stars in a $0.05\,\dex$ bin at $\FeH=0$ on the \MgFe{}-$t_{\textrm{form}}$ plane (blue, left panel).
+  \caption{In the bimodal simulation, a gap appears when plotting stars in a $0.05\,\dex$ bin at $\FeH=0$ on the \MgFe{}-$t_{\textrm{form}}$ plane (blue, left panel).
 In the unimodal simulation there is no such gap (orange, left panel).
@@
 The low-metallicity bin is where the Milky Way bimodality is strongest while there is no bimodality at the solar-metallicity bin (see Figure~\ref{fig:fig1}).
-Offsets have been added to \MgFe{} values for clarity: $-0.3$ in the unimodal points in the left and middle panels, and $+0.1$ and $-0.1$ in the low/solar-metallicity bins, respectively, in the right panel.}}
+Offsets have been added to \MgFe{} values for clarity: $-0.3$ in the unimodal points in the left and middle panels, and $+0.1$ and $-0.1$ in the low/solar-metallicity bins, respectively, in the right panel.}
   \label{fig:alpha_vs_tform}
@@
 \subsection{Comparison to Observations}\label{ssec:compare_obs}
-\edit1{A plot of \MgFe{} vs age or formation time is a useful way to further demonstrate the formation scenario of the bimodality, as well as making comparison to observations.
+A plot of \MgFe{} vs age or formation time is a useful way to further demonstrate the formation scenario of the bimodality, as well as making comparison to observations.
 We show this for the simulation data in the left panel of Figure~\ref{fig:alpha_vs_tform} in bins of width $0.05\,\dex$ centered at $\FeH=0$.
 The bimodal simulation (blue, upper data) displays a gap in the ages at $\sim2.8\,\Gyr$, coinciding with the gap in Figure~\ref{fig:before_after}.
-On the other hand, the unimodal simulation (orange, lower data) displays no such age gap.}
+On the other hand, the unimodal simulation (orange, lower data) displays no such age gap.
 
-\edit1{The center panel shows these simulation data points convolved with realistic observational errors.
+The center panel shows these simulation data points convolved with realistic observational errors.
 We assume errors in \FeH{}, \MgFe{}, and $t_{\textrm{form}}$ of $0.0075\,\dex$, $0.012\,\dex$, and $1\,\Gyr$, respectively.\footnote{The \FeH{} error impacts which star particles lie in the \FeH{} selection.} The \FeH{} and \MgFe{} errors are characteristic of the errors provided in the APOGEE dataset, and the $1\,\Gyr$ comes from assuming the typical $12.5\%$ uncertainty from APOKASC-3 at an age of $8\,\Gyr$.
 In the bimodal simulation (blue, upper data), separate populations can be seen that overlap significantly in $t_{\textrm{form}}$.
-There is not a strong separation in the unimodal case (orange, lower data).}
+There is not a strong separation in the unimodal case (orange, lower data).
 
-\edit1{The right panel shows observational data from APOKASC-3.
+The right panel shows observational data from APOKASC-3.
 We show in the blue, upper data a $0.2\,\dex$ bin centered at $\FeH=-0.5$ and in the orange, lower data centered at $\FeH=0$.
@@
 However, the large uncertainties at the relevant ages ($\sim1\,\Gyr$ at ages of $\sim8\,\Gyr$) and the small sample size (125 and 1175 at $\FeH=-0.5$ and $0$, respectively) prevents a definitive statement from being made.
-Larger sample sizes and more precise age estimates in the future would clarify the connection between simulation and observation, although achieving age uncertainties of $<10\%$ for such old stars is very challenging \citep[e.g.][]{2010ARA&A..48..581S}.}
+Larger sample sizes and more precise age estimates in the future would clarify the connection between simulation and observation, although achieving age uncertainties of $<10\%$ for such old stars is very challenging \citep[e.g.][]{2010ARA&A..48..581S}.
 
-\edit1{There is an additional complication in the data coming from the presence of young, $\alpha$-rich stars.
+There is an additional complication in the data coming from the presence of young, $\alpha$-rich stars.
 These have been argued to be old stars with misclassified astroseismic ages due to binary mass transfer \citep[and references therein]{2023A&A...671A..21J}, though with some appearing to be genuinely young \citep[and references therein]{2024arXiv241002962L}, with a range of explanations given \citep[e.g.][]{2015A&A...576L..12C,2021MNRAS.508.4484J,2023arXiv231105815S}.
-It is unclear which of the $\alpha$-rich stars faithfully reflect the mean ISM chemistry at their inferred age, and so it is not obvious if any detailed conclusions can be drawn from this comparison.}
+It is unclear which of the $\alpha$-rich stars faithfully reflect the mean ISM chemistry at their inferred age, and so it is not obvious if any detailed conclusions can be drawn from this comparison.
 
 \subsection{Full Simulation Suite}\label{ssec:full_sim_suite}
-\edit1{We next expand our discussion to the full simulation suite by studying the conditional 1D \MgFe{} distribution in Figure~\ref{fig:all_hist}.
+We next expand our discussion to the full simulation suite by studying the conditional 1D \MgFe{} distribution in Figure~\ref{fig:all_hist}.
 We plot the distribution of \MgFe{} for all stars with \FeH{} lying in a bin of width $0.1\,\dex$ centered at $0\,\dex$.
@@
 We rank the simulations in alphabetical order from least to most bimodal\footnote{There is one more simulation in the suite than letters in the English alphabet, so the simulation with the highest bimodality score is labeled aa.}, as determined by the bimodality score $\mathcal{B}$ introduced in Section~\ref{ssec:bim_score}.
-The list of simulations in the orbital grid along with the associated orbital parameters and bimodality scores is given in Table~\ref{tab:my-table}.}
+The list of simulations in the orbital grid along with the associated orbital parameters and bimodality scores is given in Table~\ref{tab:my-table}.
 
-\edit1{Simulations from r onward, which have $\mathcal{B}>2.25$, are considered bimodal.
+Simulations from r onward, which have $\mathcal{B}>2.25$, are considered bimodal.
 This demarcation was chosen by eye using Figure~\ref{fig:all_hist}.
 For these simulations, we plot the trough \MgFe{} (the location of the minimum between the two maxima) as a vertical line.
-This value was determined by taking the location of the minimum of the distribution between $0.25$ and $0.35\,\dex$, and is also given in Table~\ref{tab:my-table}.}
+This value was determined by taking the location of the minimum of the distribution between $0.25$ and $0.35\,\dex$, and is also given in Table~\ref{tab:my-table}.
 
-\edit1{Simulations from r to aa have clear bimodalities.
+Simulations from r to aa have clear bimodalities.
 The trough \MgFe{} is roughly consistent between simulations, appearing between $\sim0.25$ and $0.3\,\dex$.
-For simulations marked as unimodal, some appear to have two populations but which are not distinct enough to form a clear bimodality (e.g., m, n, and o).}
+For simulations marked as unimodal, some appear to have two populations but which are not distinct enough to form a clear bimodality (e.g., m, n, and o).
 
@@
   \includegraphics[width=\textwidth]{hist.pdf}
-  \caption{\edit1{The conditional 1D \MgFe{} distribution for all stars with \FeH{} in a bin of width $0.1\,\dex$ centered at $0\,\dex$.
+  \caption{The conditional 1D \MgFe{} distribution for all stars with \FeH{} in a bin of width $0.1\,\dex$ centered at $0\,\dex$.
 Each panel corresponds to a different set of orbital parameters ($R_0$, $V_0$, and $\eta$) and is labeled alphabetically from least to most bimodal, with the labels defined in Table~\ref{tab:my-table}.
@@
 This trough generally falls between $0.25$ and $0.3\,\dex$.
-Simulations with lower bimodality scores appear unimodal, though some (e.g., m, n, and o) show hints of a secondary population without forming a distinct bimodal structure.}}
+Simulations with lower bimodality scores appear unimodal, though some (e.g., m, n, and o) show hints of a secondary population without forming a distinct bimodal structure.}
   \label{fig:all_hist}
@@
 \end{tabular}
-\caption{\edit1{All simulations in the orbital grid (as defined by $R_0$, $V_0$, and $\eta$) ordered by their bimodality score $\mathcal{B}$.
+\caption{All simulations in the orbital grid (as defined by $R_0$, $V_0$, and $\eta$) ordered by their bimodality score $\mathcal{B}$.
 Each simulation is given an identifying letter.
-For simulations marked as bimodal ($\mathcal{B}>2.25$), we also list the trough \MgFe{}, or location of the minimum of the \MgFe{} distribution.}}
+For simulations marked as bimodal ($\mathcal{B}>2.25$), we also list the trough \MgFe{}, or location of the minimum of the \MgFe{} distribution.}
 \label{tab:my-table}
@@
 
-\edit1{We study the formation of the 1D distributions in Figure~\ref{fig:all_hist} through a scatter plot of \MgFe{} vs formation time of star particles in Figure~\ref{fig:all_scatter}, similar to Figure~\ref{fig:alpha_vs_tform}.
+We study the formation of the 1D distributions in Figure~\ref{fig:all_hist} through a scatter plot of \MgFe{} vs formation time of star particles in Figure~\ref{fig:all_scatter}, similar to Figure~\ref{fig:alpha_vs_tform}.
 The order and colors are identical as in Figure~\ref{fig:all_hist}, and we use the same \FeH{} selection.
@@
 An offset of $-0.2$ and $-0.4$ are given to the second and third (orange and red) simulations in each panel.
-For simulations marked as bimodal (r through aa), we also plot a horizontal line at the location of the trough \MgFe{}.}
+For simulations marked as bimodal (r through aa), we also plot a horizontal line at the location of the trough \MgFe{}.
 
-\edit1{Most of the bimodal simulations (r through aa) have a gap in the distribution at around the time of the merger ($\sim2$-$3\,\Gyr$, depending on the orbital parameters).
+Most of the bimodal simulations (r through aa) have a gap in the distribution at around the time of the merger ($\sim2$-$3\,\Gyr$, depending on the orbital parameters).
 Before this gap, star formation occurs above the trough while after it occurs below the trough.
-However, there are two exceptions: simulation~t does not have a full gap (though the density does decrease), and simulation~w is irregular, with star formation simultaneously occurring above and below the trough.}
+However, there are two exceptions: simulation~t does not have a full gap (though the density does decrease), and simulation~w is irregular, with star formation simultaneously occurring above and below the trough.
 
-\edit1{In the unimodal simulations (a through q), there does appear to be gaps (d, f, g, h, and o).
-However, in these cases, there is not a large amount of star formation occurring before the gap, and so the high-$\alpha$ sequence is underemphasized and does not lead to a significant bimodality.}
+In the unimodal simulations (a through q), there does appear to be gaps (d, f, g, h, and o).
+However, in these cases, there is not a large amount of star formation occurring before the gap, and so the high-$\alpha$ sequence is underemphasized and does not lead to a significant bimodality.
 
@@
 \section{Discussion}\label{sec:discussion}
-\edit1{We have investigated the formation of an $\alpha$-element bimodality in the Milky Way through a series of idealized merger simulations.
+We have investigated the formation of an $\alpha$-element bimodality in the Milky Way through a series of idealized merger simulations.
 Our key finding is that a metallicity-dependent quiescent period in star formation can lead to a bimodal distribution in \alphaFe{} at specific \FeH{} values.
 This scenario does not necessarily require a global quenching period.
-We now discuss the details of this mechanism, its connection to high-redshift observations and cosmological simulations, compare with some explanations in the literature, and explore its observational implications and directions for future work.}
+We now discuss the details of this mechanism, its connection to high-redshift observations and cosmological simulations, compare with some explanations in the literature, and explore its observational implications and directions for future work.
 
 \subsection{\FeH{}-dependent Quiescence Leads to Bimodality}\label{ssec:formqui}
-\edit1{We executed a series of idealized merger simulations in which we modified the starting radius and velocity by $\pm10\%$ and the circularity by $\pm0.1$, for a total of $27$ simulations.
+We executed a series of idealized merger simulations in which we modified the starting radius and velocity by $\pm10\%$ and the circularity by $\pm0.1$, for a total of $27$ simulations.
 The central and satellite galaxies, which are meant to resemble the Milky Way and GSE at $z\sim2$, are otherwise identical across the simulations.
 Some of these simulations induce a bimodality, while others do not.
-We have examined a representative of each scenario in detail.}
+We have examined a representative of each scenario in detail.
 
-\edit1{The key driver of bimodality in our simulations is the presence of a metallicity-dependent quiescent period.
+The key driver of bimodality in our simulations is the presence of a metallicity-dependent quiescent period.
 This is shown most clearly in Figure~\ref{fig:before_after}, where the abundance plane is split into stars which form before and after a gap in the $\FeH=0$ SFR.
 Stars which form before and after the gap populate the high- and low-$\alpha$ sequences, respectively, with minimal overlap.
-No gap and no separation between the sequences is seen in the unimodal case (Figure~\ref{fig:before_after_uni}).}
+No gap and no separation between the sequences is seen in the unimodal case (Figure~\ref{fig:before_after_uni}).
 
-\edit1{This perspective is bolstered by examining the distributions of \MgFe{} at $\FeH=0$ for the full simulation suite (Figure~\ref{fig:all_hist}).
+This perspective is bolstered by examining the distributions of \MgFe{} at $\FeH=0$ for the full simulation suite (Figure~\ref{fig:all_hist}).
 We order these simulations alphabetically using the bimodality score ($\mathcal{B}$, see Section~\ref{ssec:bim_score}).
-Simulations~r through aa are considered bimodal based on a visual inspection, and the location of their trough \MgFe{} (minimum of the distribution) is indicated with a vertical line.}
+Simulations~r through aa are considered bimodal based on a visual inspection, and the location of their trough \MgFe{} (minimum of the distribution) is indicated with a vertical line.
 
-\edit1{The formation of these bimodal populations can be understood from Figure~\ref{fig:all_scatter}, which shows a scatter plot of \MgFe{} and formation time in the same order, with the trough \MgFe{} indicated with a horizontal line.
-Here, we can see that bimodal simulations tend to have a gap shortly after their respective mergers ($\sim2$--$3\,\Gyr$, depending on the orbital configuration), lying at the position of the trough \MgFe{}.}
+The formation of these bimodal populations can be understood from Figure~\ref{fig:all_scatter}, which shows a scatter plot of \MgFe{} and formation time in the same order, with the trough \MgFe{} indicated with a horizontal line.
+Here, we can see that bimodal simulations tend to have a gap shortly after their respective mergers ($\sim2$--$3\,\Gyr$, depending on the orbital configuration), lying at the position of the trough \MgFe{}.
 
-\edit1{There are two exceptions in the bimodal cases.
+There are two exceptions in the bimodal cases.
 First, simulation~t does not have a complete gap, although the number of stars forming does still drop.
 This indicates that the complete absence of star formation is not necessary, but rather a reduction in the \FeH{}-dependent SFR may be sufficient if the \alphaFe{} ratio is declining fast enough.
-Second, simulation~w exhibits some irregular behavior, with star formation switching between high- and low-$\alpha$ multiple times.}
+Second, simulation~w exhibits some irregular behavior, with star formation switching between high- and low-$\alpha$ multiple times.
 
-\edit1{There are a few unimodal simulations that have gaps -- e.g., d, f, g, h, and o.
-However, in these cases there is very little star formation at $\FeH=0$ before the gap, and so in these cases there is not a distinct high-$\alpha$ mode that can form.}
+There are a few unimodal simulations that have gaps -- e.g., d, f, g, h, and o.
+However, in these cases there is very little star formation at $\FeH=0$ before the gap, and so in these cases there is not a distinct high-$\alpha$ mode that can form.
 
-\edit1{Overall, these simulations indicate that a gap in star formation at a specific metallicity can lead to a bimodality in the conditional \alphaFe{} distribution at that metallicity.
-Determining precisely the mechanism behind generating these gaps is beyond the scope of this work, but we speculate briefly in Section~\ref{ssec:future_work}.}
+Overall, these simulations indicate that a gap in star formation at a specific metallicity can lead to a bimodality in the conditional \alphaFe{} distribution at that metallicity.
+Determining precisely the mechanism behind generating these gaps is beyond the scope of this work, but we speculate briefly in Section~\ref{ssec:future_work}.
 
 \subsection{Connection to High Redshift Quenching}\label{ssec:obshiz}
-\edit1{One plausible avenue to producing a \FeH{}-dependent halt in star formation is through a global quiescent period (see Appendix~\ref{app:all_sfh}).
-Galaxies which undergo a starburst to quiescence to rejuvenation sequence (post-starburst galaxies, or PSBs) are observed at high-$z$ ($z>1$), and may be plausible Milky Way-progenitors.} With abundance matching, we expect the Milky Way's total stellar mass to be $\sim10^{10.3}\,\Msun$ at $z\sim2$ \citep{2013ApJ...771L..35V}.
+One plausible avenue to producing a \FeH{}-dependent halt in star formation is through a global quiescent period (see Appendix~\ref{app:all_sfh}).
+Galaxies which undergo a starburst to quiescence to rejuvenation sequence (post-starburst galaxies, or PSBs) are observed at high-$z$ ($z>1$), and may be plausible Milky Way-progenitors.
+With abundance matching, we expect the Milky Way's total stellar mass to be $\sim10^{10.3}\,\Msun$ at $z\sim2$ \citep{2013ApJ...771L..35V}.
 A number of authors have explored PSBs and quiescent galaxies at slightly higher masses at $z\sim2$, with large advances in the post-JWST era.
@@
 Furthermore, \citet{2023arXiv231215012C} found that lower mass quiescent galaxies (towards $10^{10.3}\,\Msun$) tend to be younger and more disky, pointing to a merger driven scenario.
-There is also evidence that AGN, which we \edit1{suspect might} be responsible for the \edit1{star formation gaps} in our system (Appendix~\ref{app:cause_qui}), is operating at these redshifts \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024arXiv240518685M,2024Natur.630...54B}.
+There is also evidence that AGN, which we suspect might be responsible for the star formation gaps in our system (Appendix~\ref{app:cause_qui}), is operating at these redshifts \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024arXiv240518685M,2024Natur.630...54B}.
 
-\edit1{In the context of our proposed mechanism, only a metallicity-specific quenching period is necessary for generating an $\alpha$-bimodality.
-This may correspond to inside-out or outside-in quenching, for which examples are known in the local and high-$z$ universe \citep[e.g.,][]{2015Sci...348..314T,2019ApJ...872...50L}.}
+In the context of our proposed mechanism, only a metallicity-specific quenching period is necessary for generating an $\alpha$-bimodality.
+This may correspond to inside-out or outside-in quenching, for which examples are known in the local and high-$z$ universe \citep[e.g.,][]{2015Sci...348..314T,2019ApJ...872...50L}.
 
@@
 Figure~\ref{fig:before_after_sfh_by_iron} indicates a very direct observational test of the mechanism proposed in this work: for disk stars at a given \FeH{}, there should be a gap of $\sim300\,\Myr$ in ages at $\sim8\,\Gyr$, though in the Milky Way the gap could be larger.
-With a survey of properly chosen stars, this gap could be directly measured with a modestly sized (few hundred) sample of old stars with age uncertainties of \edit1{a few percent}.
+With a survey of properly chosen stars, this gap could be directly measured with a modestly sized (few hundred) sample of old stars with age uncertainties of a few percent.
 To our knowledge, the best method at these ages is differential analysis of solar twins, which can provide an age uncertainty of $\sim5\%$ \citep[e.g.][]{2014ApJ...795...23B,2018MNRAS.474.2580S}.
@@
 Astroseismology appears to be the most promising avenue.
-\edit1{Currently the largest sample is APOKASC-3 \citep{2025ApJS..276...69P}, which has $\sim2\textrm{k}$ stars with ages measured to $<12.5\%$ precision.\footnote{Errors here taken to be the maximum of the upper and lower age estimates in the APOKASC-3 catalog.}} The upcoming PLATO mission is looking to measure $\sim20\textrm{k}$ stars with ages measured to $<10\%$ precision \citep{2024arXiv240605447R}.
+Currently the largest sample is APOKASC-3 \citep{2025ApJS..276...69P}, which has $\sim2\textrm{k}$ stars with ages measured to $<12.5\%$ precision.\footnote{Errors here taken to be the maximum of the upper and lower age estimates in the APOKASC-3 catalog.} The upcoming PLATO mission is looking to measure $\sim20\textrm{k}$ stars with ages measured to $<10\%$ precision \citep{2024arXiv240605447R}.
 Further work is needed to determine how well these surveys could constrain the gap.
@@
 \subsection{Future Work}\label{ssec:future_work}
-\edit1{The largest unanswered question in the current work is the origin of gaps in the metallicity-dependent SFR.
+The largest unanswered question in the current work is the origin of gaps in the metallicity-dependent SFR.
 In Appendix~\ref{app:cause_qui}, we show that the merger is associated with strong feedback from the central AGN.
 Determining the precise mechanism and relationship between the two is delayed to future work.
-Furthermore, other mechanisms of quenching might be able to produce the gaps studied here, and so their exploration is worthwhile.}
+Furthermore, other mechanisms of quenching might be able to produce the gaps studied here, and so their exploration is worthwhile.
 
-\edit1{Another natural next step would be to extend the idealized simulations in this work to a wider range of orbits, galaxy properties, and feedback models.
+Another natural next step would be to extend the idealized simulations in this work to a wider range of orbits, galaxy properties, and feedback models.
 However, several aspects of our setup are unrealistic, for example, (1) the simulation is not in an expanding universe, (2) our feedback model is weaker than typical ones calibrated to full cosmological box simulations, (3) the initial conditions have a steeper potential well prior to star formation than in the real universe, and (4) our halos lack small-scale substructure.
 The simplicity of our setup aids interpretation, but also limits it applicability to the real universe.
-Something along the lines of the genetic modification technique to explore various mergers as done in this work may be useful \citep{2016MNRAS.455..974R,2017MNRAS.465..547P}.}
+Something along the lines of the genetic modification technique to explore various mergers as done in this work may be useful \citep{2016MNRAS.455..974R,2017MNRAS.465..547P}.
 
@@
 
-\edit1{In this work, we have shown that a brief ($\sim300\,\Myr$) period of halted star formation in a narrow \FeH{} bin is capable of producing a bimodal distribution in \alphaFe{} at that \FeH{}.
+In this work, we have shown that a brief ($\sim300\,\Myr$) period of halted star formation in a narrow \FeH{} bin is capable of producing a bimodal distribution in \alphaFe{} at that \FeH{}.
 This proposal requires that the \alphaFe{} of gas within the galaxy is decreasing with time so that the gap in star formation translates to a gap in \alphaFe{}.
@@
 We demonstrate the plausibility of this scenario using a grid of idealized merger simulations with slightly varied orbital parameters.
-This scenario could potentially be triggered in non-merger scenarios, which we plan to explore in future work.}
+This scenario could potentially be triggered in non-merger scenarios, which we plan to explore in future work.
 
-\edit1{This scenario leads to the natural prediction that for stars occupying a narrow bin in \FeH{} where the bimodality is present ($\FeH\lesssim-0.2$), there should be a gap in ages for $\sim8\,\Gyr$ old stars with a width of $\sim300\,\Myr$.
+This scenario leads to the natural prediction that for stars occupying a narrow bin in \FeH{} where the bimodality is present ($\FeH\lesssim-0.2$), there should be a gap in ages for $\sim8\,\Gyr$ old stars with a width of $\sim300\,\Myr$.
 Currently, the best age estimates for such stars have errors of $\sim1\,\Gyr$.
 However, future observations targeting \textit{relative} ages of such stars might be able to achieve the necessary precision.
-Our proposed mechanism may operate in many external galaxies, whether or not these \FeH{}-dependent metallicity gaps are merger-induced.}
+Our proposed mechanism may operate in many external galaxies, whether or not these \FeH{}-dependent metallicity gaps are merger-induced.
 
 \begin{acknowledgements}
-\edit1{We would like to thank the anonymous referee for their helpful comments which have served to clarify and strengthen our main arguments.} We would like to thank Megan Bedell, Christopher Carr, Vedant Chandra, Charlie Conroy, Drummond B.
+We would like to thank the anonymous referee for their helpful comments which have served to clarify and strengthen our main arguments.
+We would like to thank Megan Bedell, Christopher Carr, Vedant Chandra, Charlie Conroy, Drummond B.
 Fielding, Lars Hernquist, Federico Marinacci, Rohan P.
@@
 \section{Cause of Suppressed Star Formation}\label{app:cause_qui}
-\edit1{In Figure~\ref{fig:MdotBH_rsep}, we demonstrate how the orbit of the bimodal simulation is closely related to the strength of BH feedback.
+In Figure~\ref{fig:MdotBH_rsep}, we demonstrate how the orbit of the bimodal simulation is closely related to the strength of BH feedback.
 On the $y$-axis, we show in blue the black hole accretion rate as a ratio of the maximum (Eddington) accretion rate at that time.
@@
 We see that the accretion rate is high early on at $\sim10\%$.
-At the time around coalescence at $\sim2\,\Gyr$, the accretion rate rises up to Eddington, before dropping to a much lower value $<10\%$ later on.}
+At the time around coalescence at $\sim2\,\Gyr$, the accretion rate rises up to Eddington, before dropping to a much lower value $<10\%$ later on.
 
-\edit1{In the TNG model, the strength of AGN feedback is directly tied to the BH's accretion rate \citep{2017MNRAS.465.3291W}.
-Therefore, it is reasonable to suspect that the feedback from the AGN is responsible for removing gas from the galaxy or keeping it above the star forming density threshold.}
+In the TNG model, the strength of AGN feedback is directly tied to the BH's accretion rate \citep{2017MNRAS.465.3291W}.
+Therefore, it is reasonable to suspect that the feedback from the AGN is responsible for removing gas from the galaxy or keeping it above the star forming density threshold.
 
@@
   \includegraphics[width=242.26653pt]{MdotBH_rsep.pdf}
-  \caption{\edit1{Evolution of black hole accretion rate and orbital separation over time in the bimodal simulation.
+  \caption{Evolution of black hole accretion rate and orbital separation over time in the bimodal simulation.
 The blue line shows the black hole accretion rate as a fraction of the Eddington rate, while the orange line shows the orbital separation between the satellite and central galaxies.
-The accretion rate peaks during coalescence at $\sim2\,\Gyr$, suggesting a strong connection between the merger and AGN activity.}}
+The accretion rate peaks during coalescence at $\sim2\,\Gyr$, suggesting a strong connection between the merger and AGN activity.}
   \label{fig:MdotBH_rsep}
